### 2017-12-15 article/ms.tex
initial commit

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Kemp et al.]{
Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
A. N. Other,$^{2}$
Third Author$^{2,3}$
and Fourth Author$^{3}$
\\
% List of institutions
$^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2015}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

This is a simple template for authors to write new MNRAS papers.
See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
for a full user guide.

All papers should start with an Introduction section, which sets the work
in context, cites relevant earlier studies in the field by \citet{Others2013},
and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.

\section{Methods, Observations, Simulations etc.}

Normally the next section describes the techniques the authors used.
It is frequently split into subsections, such as Section~\ref{sec:maths} below.

\subsection{Maths}
\label{sec:maths} % used for referring to this section from elsewhere

Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
as a numbered equation:

\begin{equation}
    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
	\label{eq:quadratic}
\end{equation}

Refer back to them as e.g. equation~(\ref{eq:quadratic}).

\subsection{Figures and tables}

Figures and tables should be placed at logical positions in the text. Don't
worry about the exact layout, which will be handled by the publishers.

Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
e.g. Table~\ref{tab:example_table}.

% Example figure
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{example}
    \caption{This is an example figure. Captions appear below each figure.
	Give enough detail for the reader to understand what they're looking at,
	but leave detailed discussion to the main body of the text.}
    \label{fig:example_figure}
\end{figure}

% Example table
\begin{table}
	\centering
	\caption{This is an example table. Captions appear above each table.
	Remember to define the quantities, symbols and units used.}
	\label{tab:example_table}
	\begin{tabular}{lccr} % four columns, alignment for each
		\hline
		A & B & C & D\\
		\hline
		1 & 2 & 3 & 4\\
		2 & 4 & 6 & 8\\
		3 & 5 & 7 & 9\\
		\hline
	\end{tabular}
\end{table}

\section{Conclusions}

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

%\bibliographystyle{mnras}
%\bibliography{example} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
Others S., 2012, Journal of Interesting Stuff, 17, 198
\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2017-12-17 article/ms.tex
extremely bare bones method + histogram, gal cood and teff/logg/metalicity

@@
 
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
 \usepackage{graphicx}	% Including figure files
@@
 \usepackage{amssymb}	% Extra maths symbols
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 % Keep the title short and informative.
-\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}
+\title[Short title, max. 45 characters]{Mg Depleted and K Enriched Stars from LAMOST Spectral Data}
 
@@
 
-% Don't change these lines
 \begin{document}
@@
 \begin{abstract}
-This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.
+
 \end{abstract}
@@
 
-Normally the next section describes the techniques the authors used.
-It is frequently split into subsections, such as Section~\ref{sec:maths} below.
+\textit{The Cannon}, a data based spectral model devloped by \cite{ho2017}, was fitted to each star in the spectra based around each star's $T_{eff}$, log(g), [Fe/H] and [$\alpha$/M].
+%Ho2017 says that using Appogee, they found almost 10000 giants which were common between the lamost and apoggeee surveys and used that to fit a predictive model to the lamost giants (450000) to determine the 'Teff, logg, [Fe/H], and [α/M]'.
+This model is treated as representative of the expected spectra for each star.
 
-\subsection{Maths}
-\label{sec:maths} % used for referring to this section from elsewhere
+The residuals were taken of the normalised LAMOST flux data and 
+\textit{The Cannon} according to $residual=data-model$.
+A positive residual implies a higher normalised flux than expected by the model, while a negative residual implies a lower normalised flux than expected.
+In turn, at a given spectral line a lower normalised flux is associated with an over-abundance, while a higher normalised flux is associated with a depleted abundance.
 
-Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
-or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
-as a numbered equation:
+A Gaussian curve was fitted to the residuals about each spectral line in the Mg triplet (5167 \AA, 5172 \AA, 5184 \AA) as well as the K doublet (7665 \AA, 7699 \AA) to characterise any deviation from the model.
+The amplitude and amplitude error for this curve was then used as the basis for a data filter designed to produce potential candidate stars with spectra indicative of Mg depletion, as well as K enrichment.
 
-\begin{equation}
-    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
-	\label{eq:quadratic}
-\end{equation}
+Two filters were applied separately, with the candidate pool formed from all unique stars identified in either filter.
+The first, broader filter required the Mg 5184 line's Gaussian to satisfy $Amp > 0.05$ and $\frac{Amp}{Amp_{err}}>3$, and the K 7665 line to satisfy $Amp < 0.05$ and $\frac{Amp}{Amp_{err}}>3$.
+The second, more demanding filter was applied to require 2 of the three Mg lines to satisfy $Amp > 0.05$ and $\frac{Amp}{Amp_{err}}>3$, as well as either of the K lines.
+These filters together produced 280 candidate stars to be vetted manually.
 
-Refer back to them as e.g. equation~(\ref{eq:quadratic}).
+The vetting process was done through visual examination of each case.
+The minimum criterion for a pass was two out of the three Mg lines to look at least plausibly depleted, and at least one of the K lines to look convincing.
+The local noisiness of the signal was taken into account when making these determinations.
+Of the 280 candidates manually vetted, 156 were ultimately determined to be sufficiently strong candidates to make the list, presented in Table [INSERT TABLE REFERENCE HERE].
 
@@
 
-% Example figure
 \begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{example}
-    \caption{This is an example figure. Captions appear below each figure.
-	Give enough detail for the reader to understand what they're looking at,
-	but leave detailed discussion to the main body of the text.}
-    \label{fig:example_figure}
+	\includegraphics[width=\columnwidth]{m_hhist.png}
+    \caption{Metalicity Histogram}
+    \label{mhist}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{teff_logg.png}
+    \caption{Effective temperature, log surface gravity, metalicity}
+    \label{mhist}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{galcoord.png}
+    \caption{Galactic coordinates for Mg-K stars and known globular clusters}
+    \label{mhist}
 \end{figure}
@@
 
-%\bibliographystyle{mnras}
-%\bibliography{example} % if your bibtex file is called example.bib
+\bibliographystyle{mnras}
+\bibliography{mgkbib} % if your bibtex file is called example.bib
 
@@
 % This method is tedious and prone to error if you have lots of references
-\begin{thebibliography}{99}
-\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
-Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
-\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
-Others S., 2012, Journal of Interesting Stuff, 17, 198
-\end{thebibliography}
 

### 2017-12-18 article/ms.tex
introduced poster children scrappy

@@
 
-\usepackage{graphicx}	% Including figure files
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
+\usepackage{graphicx}
+\usepackage{subcaption}
+\usepackage{float}
+
+\usepackage{color}
+\usepackage{booktabs,chemformula}
+\usepackage[export]{adjustbox}
+
+\usepackage{tabularx}
+
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{amsmath}
+
+\usepackage{tikz}
+\usepackage{hyperref}
 
@@
 
-\textit{The Cannon}, a data based spectral model devloped by \cite{ho2017}, was fitted to each star in the spectra based around each star's $T_{eff}$, log(g), [Fe/H] and [$\alpha$/M].
-%Ho2017 says that using Appogee, they found almost 10000 giants which were common between the lamost and apoggeee surveys and used that to fit a predictive model to the lamost giants (450000) to determine the 'Teff, logg, [Fe/H], and [α/M]'.
+\textit{The Cannon}, a data based spectral model devloped by \cite{ho2017} using APOGEE data, was fitted to each star in our 450000 star sample of LAMOST giants.
+%Ho2017 says that using Appogee, they found almost 10000 giants which were common between the lamost and apoggeee surveys and used that to fit a predictive model to to lamost giants (450000) to determine the 'Teff, logg, [Fe/H], and [α/M]'.
 This model is treated as representative of the expected spectra for each star.
@@
 e.g. Table~\ref{tab:example_table}.
+
+\begin{figure}
+\centering
+\begin{subfigure}{.5\linewidth}
+  \centering
+  \includegraphics[width=.95\linewidth]{29277_Mg}
+  \caption{Mg}
+  \label{Mgposter}
+\end{subfigure}%       %Note: the % to the left is VERY IMPORTANT.
+
+\begin{subfigure}{.5\linewidth}
+  \centering
+  \includegraphics[width=.95\linewidth]{29277_K}
+  \caption{K}
+  \label{Kposter}
+\end{subfigure}
+\caption{}
+\label{posterchildren}
+\end{figure}
 

### 2018-01-01 article/ms.tex
Added intro thats way too long and focuses almost entirely on work on NGC 2419.

@@
 
-This is a simple template for authors to write new MNRAS papers.
-See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
-for a full user guide.
+NGC 2419 is the Milky Way's third most massive cluster, and one of the oldest at an age of 12.3 +/- 1.3 Gy (CITE FORBES AND BRIDGES 2010).
+It resides in the outer halo 87.5 kpc (original source unknown) from the galactic centre, and has been identified as perhaps one of the most unusual clusters in the galaxy.
 
-All papers should start with an Introduction section, which sets the work
-in context, cites relevant earlier studies in the field by \citet{Others2013},
-and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.
+A spectroscopic study of RGB giant stars in NGC 2419 led to the discovery discovery of a strong anti-correlation between Mg and K in around 30-40 \% of the studied stars, along with weaker relations in Si, Sc, Ca, Ti and V (CITE MUCIARELLI AND COHEN AND KIRBY 2012).
+Depletions of Mg within globular clusters are not uncommon, but they are always accompanied with an increase in [Fe/H], with the mechanism for this phenomena being the introduction of $\alpha$ element poor but iron rich material released from Type Ia supernovae locally polluting the 'normal' [Mg/Fe] material released from Type II supernovae.
+However, the two sub-populations are indistinguishable in their [Fe/H] abundance (Cite Kirby and Cohen), and this mechanism fails to account for the enhanced K abundance or trends in the other elements.
+
+Recently (cite Young Wook Lee 2017) used a Ca filter to identify two population in NGC 2419 corresponding to two generations of stars: G1, first generation metal poor stars, and G2, second generation stars displaying enhanced Ca and significantly increased He abundance ($\Delta Y = 0.19$).
+The Mg depleted population identified previously was found to be contained with the G2 population.
+
+With the exception of NGC 2808, where several K enhanced (with weaker enhancements than NGC2419) have been found (cite Muciarelli 2015), this anti-correlation between Mg and K has, with the exception of this study, been found to be contained within NGC 2419, with a targeted search looking at the K abundance in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and ω Cen as well as some field stars finding in all cases K abundances falling within the range of the Mg normal population in NGC 2419 (cite carreta 2013).
+
+At present, there is no accepted nuclear process that can explain the elemental abundance in NGC 2419.
+Although the fact that Mg-K anti-correlation is confined to this specific globular cluster would seem to imply either a small population  of unusual polluter stars of some sort, or a single extremely massive polluter star, the details of these polluter candidates remain unknown.
+
+An early modelling attempt at replicating the anomalous abundances in NGC 2419 assumed hot-bottom burning in AGB and super-AGB stars, with high temperatures of approximately 150 MK, was able to reproduce the Mg-K anti-correlation, through proton capture on Argon, but only if the reaction cross section was set to 100 times the standard rate or temperatures could be made higher than currently accepted values [cite VENTURA 2012].
+
+A more recent, comprehensive attempt to replicate not only the Mg and K abundances in NGC 2419 but also the abundances of Si, Sc, Ca, Ti and V, with the aim of constraining the temperatures and pressures required was undertaken by [Cite Illiadis].
+It was found that (with the exception of extremely high densities $\>10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^-4$ and 10$^8$ g/cm$^3$.
+Using this information, core and shell burning of low mass, high mass and super massive stars were ruled out as potential poluter candidates, as well as regular AGB stars.
+Super-AGB (SAGB) stars however were regarded as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
+The other potential candidate identified was Novae, although the lack of detailed models of white dwarfs accreting material similar to NGC 2419 either from a binary companion or the intra cluster medium limit appraisals of its feasibility regarding whether enough ejecta could be produced and retained by the cluster.
+Estimates based on current novae frequency in globular clusters by [CITE HENZE 2013] carried out in the work conclude that the amount of material that would be produced by Novae is at most 1 \% of the total required mass to pollute 30 \% of NGC 2419.
+
+However, the question remains: why is this signature unique to 2419?
+It has been suggested that the cluster's position and size, being both very massive and very distant from the Milky Way for a globular cluster, aids it in retaining material from explosive events.
+This would cause in its first generation polluter stars to have an increased effect on the second generation of stars.
+It has also been proposed that NGC 2419 is the stripped core of a dwarf spheroidal galaxy similar to $\omega$ Centauri, which would imply that in the past it was even more massive, allowing it to retain its ejecta even more efficiently.
+
+Although to the knowledge of the author not formally studied in terms of feasibility, another suggested polluter candidate is a pair instability super nova (PISN) (CITE CARRETA 2013).
+Unique to extremely massive population III stars, these events involve the total destruction of the star, with no black hole remnant being left behind.
+The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material involved, could perhaps allow the entire signature in NGC 2419 to be the result of a single event, explaining why it is not seen in any other globular clusters.
+
+This study, which queries 450000ish LAMOST giants for depleted Mg and enhanced K, seeks to provide additional data points from which theories regarding the origin of this signature can be developed.
+190 strong candidates for this signature, almost all of them not at this time associated with any globular cluster, are detailed in Table [REFERENCE TABLE HERE].
+These stars occur at a wide range of metalicities, including solar metalicity.
+The implications for theories attempting to explain the origin of this signiature first found in NGC 2419 is likely to be significant, as for such a theory to be complete, it must now account not only for the stars in the metal poor NGC 2419, but also these stars existing at a range of metalicities in the galactic plane.
+Further, the task of explaining the uniqueness of NGC 2419 is not removed, as it remains the only globular cluster to significantly display this phenomena.
 

### 2018-01-03 article/ms.tex
Altered the method, adding the additional filter we ran and redoing the section on the work of Ho2017.

@@
 
-This study, which queries 450000ish LAMOST giants for depleted Mg and enhanced K, seeks to provide additional data points from which theories regarding the origin of this signature can be developed.
+This study, which queries 454180 LAMOST giants for depleted Mg and enhanced K, seeks to provide additional data points from which theories regarding the origin of this signature can be developed.
 190 strong candidates for this signature, almost all of them not at this time associated with any globular cluster, are detailed in Table [REFERENCE TABLE HERE].
@@
 
-\textit{The Cannon}, a data based spectral model devloped by \cite{ho2017} using APOGEE data, was fitted to each star in our 450000 star sample of LAMOST giants.
-%Ho2017 says that using Appogee, they found almost 10000 giants which were common between the lamost and apoggeee surveys and used that to fit a predictive model to to lamost giants (450000) to determine the 'Teff, logg, [Fe/H], and [α/M]'.
-This model is treated as representative of the expected spectra for each star.
+The data set of 454180 LAMOST giants was prepared by \citet{ho2017} for use with the supervised machine learning code \textit{The Cannon}.
+The LAMOST data was shifted to rest frame, normalised, and sampled to a common uniform wavelength grid between 3905 \AA and 9000 \AA.
+\textit{The Cannon} was used to infer $\text{T}_{\text{eff}}$, log(g), [Fe/H] and [$\alpha$/M] using 9952 common stars between LAMOST and the higher resolution APOGEE survey, through the use of a data-driven spectral model, referred to henceforth and simply 'the model'.
+For details regarding the process of the preparatory work, model generation and label transfer between the APOGEE and LAMOST surveys, the reader is directed to \citet{ho2017}.
+The data-driven model generated by \textit{The Cannon} is treated in this study as the typical spectra for each star.
 
-The residuals were taken of the normalised LAMOST flux data and 
+Residuals were taken of the normalised LAMOST flux data and 
 \textit{The Cannon} according to $residual=data-model$.
-A positive residual implies a higher normalised flux than expected by the model, while a negative residual implies a lower normalised flux than expected.
+A positive residual therefore implies a higher normalised flux than expected by the model, while a negative residual implies a lower normalised flux than expected.
 In turn, at a given spectral line a lower normalised flux is associated with an over-abundance, while a higher normalised flux is associated with a depleted abundance.
@@
 
-Two filters were applied separately, with the candidate pool formed from all unique stars identified in either filter.
-The first, broader filter required the Mg 5184 line's Gaussian to satisfy $Amp > 0.05$ and $\frac{Amp}{Amp_{err}}>3$, and the K 7665 line to satisfy $Amp < 0.05$ and $\frac{Amp}{Amp_{err}}>3$.
-The second, more demanding filter was applied to require 2 of the three Mg lines to satisfy $Amp > 0.05$ and $\frac{Amp}{Amp_{err}}>3$, as well as either of the K lines.
-These filters together produced 280 candidate stars to be vetted manually.
+Three filters were applied separately, with the candidate pool formed from all unique stars identified any of the three filters.
+The first filter required the Mg 5184 line's Gaussian to satisfy $Amp > 0.05$ and $\frac{Amp}{Amp_{err}}>3$, and the K 7665 line to satisfy $Amp < 0.05$ and $\frac{Amp}{Amp_{err}}>3$.
+The second, more demanding filter was applied to require 2 of the three Mg lines to satisfy $Amp > 0.05$ and $\frac{Amp}{Amp_{err}}>3$, as well as either of the two K lines to satisfy $Amp < 0.05$ and $\frac{Amp}{Amp_{err}}>3$.
+The third filter removed the amplitude requirement to requiring only positivity on 2/3 Mg lines and negativity on \textit{both} K lines, in addition to data quality requirements $\chi^2<3$ and $S/N>30$
+These filters together produced 384 unique candidate stars to be vetted manually.
 
@@
 The minimum criterion for a pass was two out of the three Mg lines to look at least plausibly depleted, and at least one of the K lines to look convincing.
-The local noisiness of the signal was taken into account when making these determinations.
-Of the 280 candidates manually vetted, 156 were ultimately determined to be sufficiently strong candidates to make the list, presented in Table [INSERT TABLE REFERENCE HERE].
+The apparent noisiness of the signal was qualitatively taken into account when making these determinations.
+Of the 384 candidates manually vetted, 188 were ultimately determined to be sufficiently strong candidates to be worth reporting in Table [INSERT TABLE REFERENCE HERE].
 

### 2018-01-05 article/ms.tex
Draft Intro and Methodology for Andy Review

@@
 \usepackage{ae,aecompl}
+
+\usepackage{mhchem}
 
@@
 \section{Introduction}
+The Mg-K anti correlation initially established in NGC 2419 continues to elude satisfactory explanation.
+Beyond the intrinsic scientific value of identifying the polluter object which is (presumably) responsible for puzzling Mg-K anti-correlation, a satisfactory explanation for this signature could potentially offer insight into the consistent under-abundance of K predicted by models \citep{kobayashi2011}.
+The signature also has well established links to globular-cluster evolution models.
 
-NGC 2419 is the Milky Way's third most massive cluster, and one of the oldest at an age of 12.3 +/- 1.3 Gy (CITE FORBES AND BRIDGES 2010).
+NGC 2419 is the Milky Way's third most massive cluster, and one of the oldest at an age of 12.3 $\pm$ 1.3 Gy \citep{forbesandbridges2010}.
 It resides in the outer halo 87.5 kpc (original source unknown) from the galactic centre, and has been identified as perhaps one of the most unusual clusters in the galaxy.
 
-A spectroscopic study of RGB giant stars in NGC 2419 led to the discovery discovery of a strong anti-correlation between Mg and K in around 30-40 \% of the studied stars, along with weaker relations in Si, Sc, Ca, Ti and V (CITE MUCIARELLI AND COHEN AND KIRBY 2012).
+A spectroscopic study of RGB giant stars in NGC 2419 led to the discovery discovery of a strong anti-correlation between Mg and K in around 30-40 \% of the studied stars, along with weaker relations in Si, Sc, Ca, Ti and V (\citet{mucciarelli2012}, \citet{cohenkirby2012}).
 Depletions of Mg within globular clusters are not uncommon, but they are always accompanied with an increase in [Fe/H], with the mechanism for this phenomena being the introduction of $\alpha$ element poor but iron rich material released from Type Ia supernovae locally polluting the 'normal' [Mg/Fe] material released from Type II supernovae.
-However, the two sub-populations are indistinguishable in their [Fe/H] abundance (Cite Kirby and Cohen), and this mechanism fails to account for the enhanced K abundance or trends in the other elements.
+However, the two sub-populations are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}, and this mechanism fails to account for the enhanced K abundance or trends in the other elements.
 
-Recently (cite Young Wook Lee 2017) used a Ca filter to identify two population in NGC 2419 corresponding to two generations of stars: G1, first generation metal poor stars, and G2, second generation stars displaying enhanced Ca and significantly increased He abundance ($\Delta Y = 0.19$).
+Recently \cite{youngwooklee} used a Ca filter to identify two population in NGC 2419 corresponding to two generations of stars: G1, first generation metal poor stars, and G2, second generation stars displaying enhanced Ca and significantly increased He abundance ($\Delta Y = 0.19$).
 The Mg depleted population identified previously was found to be contained with the G2 population.
 
-With the exception of NGC 2808, where several K enhanced (with weaker enhancements than NGC2419) have been found (cite Muciarelli 2015), this anti-correlation between Mg and K has, with the exception of this study, been found to be contained within NGC 2419, with a targeted search looking at the K abundance in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and ω Cen as well as some field stars finding in all cases K abundances falling within the range of the Mg normal population in NGC 2419 (cite carreta 2013).
+With the exception of NGC 2808, in which all 4 of its known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, this signature has thus far been found to be contained within NGC 2419.
+A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and ω Centauri as well as 21 field stars found in all cases K abundances falling within the range of the Mg normal population in NGC 2419 \citep{carretta2013}.
 
 At present, there is no accepted nuclear process that can explain the elemental abundance in NGC 2419.
-Although the fact that Mg-K anti-correlation is confined to this specific globular cluster would seem to imply either a small population  of unusual polluter stars of some sort, or a single extremely massive polluter star, the details of these polluter candidates remain unknown.
+The fact that the Mg-K anti-correlation is confined to these very few specific globular clusters would seem to imply either a small population  of unusual polluter stars of some sort or a single extremely massive polluter star.
 
-An early modelling attempt at replicating the anomalous abundances in NGC 2419 assumed hot-bottom burning in AGB and super-AGB stars, with high temperatures of approximately 150 MK, was able to reproduce the Mg-K anti-correlation, through proton capture on Argon, but only if the reaction cross section was set to 100 times the standard rate or temperatures could be made higher than currently accepted values [cite VENTURA 2012].
+It has been suggested that the NGC 2419's position and size, being both very massive and very distant from the Milky Way compared to many other globular clusters, aids it in retaining enriched material from explosive events \citep{mucciarelli2012}.
+It is also perhaps noteworthy that NGC 2808 is also one of the more massive globular clusters of the Milky Way, although it is far closer to the Galactic Centre.
+But if this unknown pollution event is common among globular clusters and the cause of its apparent exclusivity to NGC 2808 and NGC 2419 is enhanced ejecta retention due to high mass, then other massive clusters such as $\omega$ Centauri would also be expected contain the signature, which to date has not been observed.
 
-A more recent, comprehensive attempt to replicate not only the Mg and K abundances in NGC 2419 but also the abundances of Si, Sc, Ca, Ti and V, with the aim of constraining the temperatures and pressures required was undertaken by [Cite Illiadis].
-It was found that (with the exception of extremely high densities $\>10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^-4$ and 10$^8$ g/cm$^3$.
+While it is plausible that the increased mass and greater distance from the gaseous disk of the Milky Way would cause a clusters first generation polluter stars to have an increased effect on the second generation of stars, this effect applies to all ejecta (assuming comparable energies).
+So while it might be expected that second generation stars clusters similar to NGC 2419 are present and are comprised of more material processed by the first generation than other lighter globular clusters, it doesn't explain why the ejecta from the first generation was apparently dominated by this as yet unknown polluter object resulting in the Mg-K anti-correlation.
+In the opinion of the author, it is the identity and physical characterisation of this unknown polluter that is of the greatest scientific interest.
+
+An early modelling attempt at replicating the anomalous abundances in NGC 2419 assumed hot-bottom burning in AGB and super-AGB (SAGB) stars was able to reproduce the Mg-K anti-correlation, using the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for nuclear synthesis.
+However, they were only able to do so if the reaction cross section was set to 100 times the commonly accepted rate or temperatures could be made higher than currently accepted values \citep{ventura2012}, achieving a burning temperature of 150 MK.
+
+A more recent, comprehensive attempt to replicate not only the Mg and K abundances in NGC 2419 but also the abundances of Si, Sc, Ca, Ti and V, with the aim of constraining the temperatures and pressures required was undertaken by \cite{iliadis2016}.
+It is perhaps noteworthy that they identified a diferent main reaction pathway to that of \cite{ventura2012}, which is relegated to a minor minor seccondary pathway.
+The main pathway they identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.
+It was found that (with the exception of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$.
 Using this information, core and shell burning of low mass, high mass and super massive stars were ruled out as potential poluter candidates, as well as regular AGB stars.
@@
 The other potential candidate identified was Novae, although the lack of detailed models of white dwarfs accreting material similar to NGC 2419 either from a binary companion or the intra cluster medium limit appraisals of its feasibility regarding whether enough ejecta could be produced and retained by the cluster.
-Estimates based on current novae frequency in globular clusters by [CITE HENZE 2013] carried out in the work conclude that the amount of material that would be produced by Novae is at most 1 \% of the total required mass to pollute 30 \% of NGC 2419.
+Based on current novae frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by Novae is at most 1 \% of the total required mass to pollute 30 \% of NGC 2419.
 
-However, the question remains: why is this signature unique to 2419?
-It has been suggested that the cluster's position and size, being both very massive and very distant from the Milky Way for a globular cluster, aids it in retaining material from explosive events.
-This would cause in its first generation polluter stars to have an increased effect on the second generation of stars.
-It has also been proposed that NGC 2419 is the stripped core of a dwarf spheroidal galaxy similar to $\omega$ Centauri, which would imply that in the past it was even more massive, allowing it to retain its ejecta even more efficiently.
+Another proposed  polluter candidate is a pair instability super nova (PISN) \citep{carretta2013}.
+Unique to extremely massive population III stars, these events involve the total destruction of the star, with no black hole remnant being left behind.
+The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material involved, could potentially allow the entire signature in NGC 2419 to be the result of a single event, explaining why it is not seen in any other globular clusters.
+Further, the signature odd-even proton number abundance pattern associated with PISNs could perhaps explain the anti-correlation between Mg and K, as well as the enhancements in Sc and V observed by \cite{cohenkirby2012}.
 
-Although to the knowledge of the author not formally studied in terms of feasibility, another suggested polluter candidate is a pair instability super nova (PISN) (CITE CARRETA 2013).
-Unique to extremely massive population III stars, these events involve the total destruction of the star, with no black hole remnant being left behind.
-The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material involved, could perhaps allow the entire signature in NGC 2419 to be the result of a single event, explaining why it is not seen in any other globular clusters.
-
-This study, which queries 454180 LAMOST giants for depleted Mg and enhanced K, seeks to provide additional data points from which theories regarding the origin of this signature can be developed.
-190 strong candidates for this signature, almost all of them not at this time associated with any globular cluster, are detailed in Table [REFERENCE TABLE HERE].
-These stars occur at a wide range of metalicities, including solar metalicity.
-The implications for theories attempting to explain the origin of this signiature first found in NGC 2419 is likely to be significant, as for such a theory to be complete, it must now account not only for the stars in the metal poor NGC 2419, but also these stars existing at a range of metalicities in the galactic plane.
-Further, the task of explaining the uniqueness of NGC 2419 is not removed, as it remains the only globular cluster to significantly display this phenomena.
+This study, which queries 454180 LAMOST giants for depleted Mg and enhanced K, seeks to provide additional information which can be used to guide and test models attempting to explain the Mg-K anti-correlation and related phenomena.
+The large sample size provides greater insight into the supposed exclusivity of the signature, and any stars identified present an important opportunity for follow up observations both to confirm the abundance signature and to determine data beyond the scope of this study such as the mass and orbital characteristics of the targets.
 
@@
 
-Three filters were applied separately, with the candidate pool formed from all unique stars identified any of the three filters.
+Three filters were applied independently, with the candidate pool formed from all unique stars identified each of the three filters.
 The first filter required the Mg 5184 line's Gaussian to satisfy $Amp > 0.05$ and $\frac{Amp}{Amp_{err}}>3$, and the K 7665 line to satisfy $Amp < 0.05$ and $\frac{Amp}{Amp_{err}}>3$.

### 2018-01-10 article/ms.tex
Included python plotting script, latest images, changes to intro and meth
Note: the python plotting script won't work out of the box, needs to be in the appropriate location.

@@
 The Mg-K anti correlation initially established in NGC 2419 continues to elude satisfactory explanation.
-Beyond the intrinsic scientific value of identifying the polluter object which is (presumably) responsible for puzzling Mg-K anti-correlation, a satisfactory explanation for this signature could potentially offer insight into the consistent under-abundance of K predicted by models \citep{kobayashi2011}.
-The signature also has well established links to globular-cluster evolution models.
+Beyond the intrinsic scientific value of identifying the polluter object which is (presumably) responsible for the puzzling Mg-K anti-correlation, a satisfactory explanation for this signature could potentially offer insight into the underestimation of K abundance predicted by models \citep{kobayashi2011}.
+Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.
 
 NGC 2419 is the Milky Way's third most massive cluster, and one of the oldest at an age of 12.3 $\pm$ 1.3 Gy \citep{forbesandbridges2010}.
-It resides in the outer halo 87.5 kpc (original source unknown) from the galactic centre, and has been identified as perhaps one of the most unusual clusters in the galaxy.
+It resides in the outer halo 87.5 kpc (original source unknown) from the galactic centre, and its chemical make-up makes it one of the most unusual clusters in the galaxy.
 
 A spectroscopic study of RGB giant stars in NGC 2419 led to the discovery discovery of a strong anti-correlation between Mg and K in around 30-40 \% of the studied stars, along with weaker relations in Si, Sc, Ca, Ti and V (\citet{mucciarelli2012}, \citet{cohenkirby2012}).
-Depletions of Mg within globular clusters are not uncommon, but they are always accompanied with an increase in [Fe/H], with the mechanism for this phenomena being the introduction of $\alpha$ element poor but iron rich material released from Type Ia supernovae locally polluting the 'normal' [Mg/Fe] material released from Type II supernovae.
-However, the two sub-populations are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}, and this mechanism fails to account for the enhanced K abundance or trends in the other elements.
+Depletions of Mg within globular clusters are not uncommon, but they are always accompanied with an increase in [Fe/H].
+The mechanism for this phenomena is the introduction of $\alpha$ poor but iron rich material released from Type Ia supernovae locally polluting the 'normal' [Mg/Fe] material released from Type II supernovae.
+However, the two sub-populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}.
+Further, Type Ia supernovae enrichment does not account for the enhanced K abundance or trends in the other elements.
 
@@
 With the exception of NGC 2808, in which all 4 of its known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, this signature has thus far been found to be contained within NGC 2419.
-A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and ω Centauri as well as 21 field stars found in all cases K abundances falling within the range of the Mg normal population in NGC 2419 \citep{carretta2013}.
+A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and $\omega$ Centauri as well as 21 field stars found in all cases K abundances falling within the range of the Mg normal population in NGC 2419 \citep{carretta2013}.
 
@@
 
-While it is plausible that the increased mass and greater distance from the gaseous disk of the Milky Way would cause a clusters first generation polluter stars to have an increased effect on the second generation of stars, this effect applies to all ejecta (assuming comparable energies).
-So while it might be expected that second generation stars clusters similar to NGC 2419 are present and are comprised of more material processed by the first generation than other lighter globular clusters, it doesn't explain why the ejecta from the first generation was apparently dominated by this as yet unknown polluter object resulting in the Mg-K anti-correlation.
-In the opinion of the author, it is the identity and physical characterisation of this unknown polluter that is of the greatest scientific interest.
+While it is plausible that the increased mass and greater distance from the gaseous disk of the Milky Way would cause a clusters first generation polluter stars to have an increased effect on the second generation of stars, this effect would apply to all ejecta (assuming comparable energies).
+So while it might be expected that second generation stars in clusters similar to NGC 2419 made up of more material processed by the first generation than other lighter globular clusters, it doesn't explain why the ejecta from the first generation was apparently dominated by this as yet unknown polluter object resulting in the Mg-K anti-correlation.
+In the opinion of the author, it is the identity and physical characterisation of this unknown polluter that is of the greatest scientific interest, with such a result also hopefully answering the question as to the signatures uniqueness.
 
-An early modelling attempt at replicating the anomalous abundances in NGC 2419 assumed hot-bottom burning in AGB and super-AGB (SAGB) stars was able to reproduce the Mg-K anti-correlation, using the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for nuclear synthesis.
-However, they were only able to do so if the reaction cross section was set to 100 times the commonly accepted rate or temperatures could be made higher than currently accepted values \citep{ventura2012}, achieving a burning temperature of 150 MK.
+An early modelling attempt at replicating the anomalous abundances in NGC 2419 assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}.
+This study succeeded in reproducing the Mg-K anti-correlation, using nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for nuclear synthesis of K.
+However, the required abundance patterns consistent with NGC 2419 were only attainable if the reaction cross section was set to 100 times the commonly accepted rate or temperatures could be made higher than currently accepted values, achieving a burning temperature of 150 MK.
 
-A more recent, comprehensive attempt to replicate not only the Mg and K abundances in NGC 2419 but also the abundances of Si, Sc, Ca, Ti and V, with the aim of constraining the temperatures and pressures required was undertaken by \cite{iliadis2016}.
+A more recent, comprehensive attempt to replicate the Mg and K abundances in NGC 2419 by \cite{iliadis2016} also attempted to reproduce the abundances of Si, Sc, Ca, Ti and V (elements reported as having weak correlations with Mg by \cite{cohenkirby2012}).
+The ultimate goal was to constrain the temperatures and densities required to produce the chemical signiature, and thereby provide insight into potential polluter candidates.
 It is perhaps noteworthy that they identified a diferent main reaction pathway to that of \cite{ventura2012}, which is relegated to a minor minor seccondary pathway.
 The main pathway they identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.
-It was found that (with the exception of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$.
+
+It was found that (with the exception of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required.
 Using this information, core and shell burning of low mass, high mass and super massive stars were ruled out as potential poluter candidates, as well as regular AGB stars.
@@
 The other potential candidate identified was Novae, although the lack of detailed models of white dwarfs accreting material similar to NGC 2419 either from a binary companion or the intra cluster medium limit appraisals of its feasibility regarding whether enough ejecta could be produced and retained by the cluster.
-Based on current novae frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by Novae is at most 1 \% of the total required mass to pollute 30 \% of NGC 2419.
+However, based on current novae frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by Novae is at most 1 \% of the total required mass to pollute 30 \% of NGC 2419.
 
@@
 The data set of 454180 LAMOST giants was prepared by \citet{ho2017} for use with the supervised machine learning code \textit{The Cannon}.
-The LAMOST data was shifted to rest frame, normalised, and sampled to a common uniform wavelength grid between 3905 \AA and 9000 \AA.
-\textit{The Cannon} was used to infer $\text{T}_{\text{eff}}$, log(g), [Fe/H] and [$\alpha$/M] using 9952 common stars between LAMOST and the higher resolution APOGEE survey, through the use of a data-driven spectral model, referred to henceforth and simply 'the model'.
-For details regarding the process of the preparatory work, model generation and label transfer between the APOGEE and LAMOST surveys, the reader is directed to \citet{ho2017}.
+The LAMOST data was shifted to rest frame, normalised, and sampled to a common uniform wavelength grid between 3905 \AA \\ and 9000 \AA.
+\textit{The Cannon} was used to infer $\text{T}_{\text{eff}}$, log(g), [Fe/H] and [$\alpha$/M] using 9952 common stars between LAMOST and the higher resolution APOGEE survey through the use of a data-driven spectral model, referred to henceforth and simply 'the model'.
+For details regarding the preparatory work, model generation and label transfer between the APOGEE and LAMOST surveys, the reader is directed to \citet{ho2017}.
 The data-driven model generated by \textit{The Cannon} is treated in this study as the typical spectra for each star.
@@
 The second, more demanding filter was applied to require 2 of the three Mg lines to satisfy $Amp > 0.05$ and $\frac{Amp}{Amp_{err}}>3$, as well as either of the two K lines to satisfy $Amp < 0.05$ and $\frac{Amp}{Amp_{err}}>3$.
-The third filter removed the amplitude requirement to requiring only positivity on 2/3 Mg lines and negativity on \textit{both} K lines, in addition to data quality requirements $\chi^2<3$ and $S/N>30$
+The third filter removed the amplitude requirement to requiring only positivity on 2/3 Mg lines and negativity on \textit{both} K lines, in addition to data quality requirements $\chi^2<3$ and $S/N>30$.
 These filters together produced 384 unique candidate stars to be vetted manually.
@@
 The apparent noisiness of the signal was qualitatively taken into account when making these determinations.
-Of the 384 candidates manually vetted, 188 were ultimately determined to be sufficiently strong candidates to be worth reporting in Table [INSERT TABLE REFERENCE HERE].
+Of the 384 candidates manually vetted, 188 were ultimately determined to be sufficiently strong to be reported.
+The 6556 \AA \\ H line was then visually examined for each star to identify stars with active chromosphere emissions which could result in false positives for Mg depletion.
+62 stars were removed from the sample due to being chromospheric emmiters.
+A further 13 stars were removed due to the model fitted poorly to the H 6556 line possibly due to incorrect log(g) or $\text{T}_{\text{eff}}$ estimates from \textit{The Cannon}, leaving a total of 113 candidates displaying depleted Mg and enhanced K.
 
@@
 \begin{figure}
-\centering
-\begin{subfigure}{.5\linewidth}
-  \centering
-  \includegraphics[width=.95\linewidth]{29277_Mg}
-  \caption{Mg}
-  \label{Mgposter}
-\end{subfigure}%       %Note: the % to the left is VERY IMPORTANT.
-
-\begin{subfigure}{.5\linewidth}
-  \centering
-  \includegraphics[width=.95\linewidth]{29277_K}
-  \caption{K}
-  \label{Kposter}
-\end{subfigure}
-\caption{}
-\label{posterchildren}
+	\includegraphics[width=\columnwidth]{posterchildof13.png}
+    \caption{Poster Child}
+    \label{mhist}
 \end{figure}
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{m_hhist.png}
+	\includegraphics[width=\columnwidth]{histof113.png}
     \caption{Metalicity Histogram}
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{teff_logg.png}
+	\includegraphics[width=\columnwidth]{loggteffof113.png}
     \caption{Effective temperature, log surface gravity, metalicity}
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{galcoord.png}
+	\includegraphics[width=\columnwidth]{globclustof113.png}
     \caption{Galactic coordinates for Mg-K stars and known globular clusters}

### 2018-01-10 article/plotter.py

@@ -1,0 +1,238 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jan  9 15:25:28 2018
+
+@author: alexkemp
+"""
+
+import numpy as np
+import os
+import matplotlib.pyplot as plt
+import pandas as pd
+from glob import glob
+import astropy as asp
+"""
+from mpl_toolkits.axes_grid1.inset_locator import zoomed_inset_axes
+from mpl_toolkits.axes_grid1.inset_locator import mark_inset
+from mpl_toolkits.axes_grid.inset_locator import inset_axes
+"""
+import lamost
+import utils
+import csv
+plt.ioff()
+from astropy.io import fits
+from astropy.table import Table
+plt.close('all')
+
+mgkarray=np.array(pd.read_csv("Mg-K-candidatesFINALCUT_nonHemmision.csv"))
+globarray=np.array(pd.read_csv("globular_clusters.csv"))
+
+Teff=mgkarray[:,1]
+logg=mgkarray[:,2]
+metalicity=mgkarray[:,3]
+
+mgkl=mgkarray[:,-2]
+mgkb=mgkarray[:,-1]
+globl=globarray[:,4]
+globb=globarray[:,5]
+
+catalog = lamost.load_catalog()
+wavelengths = lamost.common_wavelengths
+N, P = (len(catalog), wavelengths.size)
+
+# Open the data arrays
+all_observed_flux = np.memmap(
+    os.path.join(lamost.LAMOST_PATH, "observed_flux.memmap"),
+    mode="r", dtype='float32', shape=(N, P))
+
+all_observed_ivar = np.memmap(
+    os.path.join(lamost.LAMOST_PATH, "observed_ivar.memmap"),
+    mode="r", dtype='float32', shape=(N, P))
+
+all_model_flux = np.memmap(
+    os.path.join(lamost.LAMOST_PATH, "model_flux.memmap"),
+    mode="r", dtype="float32", shape=(N, P))
+
+
+binwidth=.05
+plt.figure(1)
+plt.hist(metalicity, bins=np.arange(-1.5, 0.5, binwidth),edgecolor='black')
+plt.xticks(np.arange(-1.5, 0.5, binwidth)[::4])
+plt.xlabel("[Fe/H]")
+plt.title('[Fe/H] for candidate stars')
+plt.show()
+
+plt.figure(2)
+plt.scatter(Teff ,logg , c=metalicity, cmap='plasma',s=40)
+cbar=plt.colorbar()
[…]

### 2018-01-10 article/ms.tex
additional csv files for purposes of code running, plus super shitty abstract

@@
 \begin{abstract}
-
+454180 RGB stars from the low resolution LAMOST dr2 survey are searched for anomalously high K and depleted Mg signatures.
+These LAMOST stars are overwhelmingly field stars, making this the largest search for field stars containing the Mg-K anti-correlation so far identified only in the globular NGC 2419 and NGC 2808.
+23 stars displaying absorption spectra with over-abundant K and depleted Mg accross a range of metalicities relative to typical Milky Way field stars, but none are identified as having abundances consistent with the extreme abundances found in NGC 2419.
+The abundances are in these 23 stars are estimated at ranging between [INSERT RANGE FOR K AND MG HERE].
+High resolution spectra for three stars (1 of which is not included among the final count of 23 spectral candidates for the signiature for reasons relating to the LAMOST signal quality for that star, despite having the highest K abundance of the three at [K/Fe]~1.54) selected based on observability were obtained using Las Campanas Observatory, and for these stars elemental abundances for heavy elements such as Sc and V are presented as well as more precise abundances for Mg and K.
 \end{abstract}

### 2018-01-10 article/ms.tex
changes to abstract, method and intro. Not yet added sections describing methodology of Kevin's observations, or todays filter to 23 stars

--- 2018-01-10 article/ms.tex
@@
 \begin{abstract}
-
+454180 RGB stars from the low resolution LAMOST DR2 survey were searched for anomalously high K and depleted Mg signatures.
+This study represents the largest search for field stars containing the Mg-K anti-correlation so far identified only in the globular NGC 2419 and NGC 2808.
+23 stars displaying absorption spectra with over-abundant K and depleted Mg accross a range of metalicities were identified, but none were identified as having [Mg/Fe] or [K/Fe] consistent with the Mg depleted population found in NGC 2419.
+The abundances in these 23 stars are estimated at ranging between [INSERT RANGE FOR K AND MG HERE BASED OFF LAMOST DATA].
+High resolution spectra for three stars (1 of which is not included among the final count of 23 spectral candidates for the signiature for reasons relating to the LAMOST signal quality for that star, despite having the highest K abundance of the three at [K/Fe]=1.54) selected based on observability characteristics were obtained using the Las Campanas Observatory, and for these stars elemental abundances for heavy elements such as Sc and V are also presented.
 \end{abstract}
@@
 A spectroscopic study of RGB giant stars in NGC 2419 led to the discovery discovery of a strong anti-correlation between Mg and K in around 30-40 \% of the studied stars, along with weaker relations in Si, Sc, Ca, Ti and V (\citet{mucciarelli2012}, \citet{cohenkirby2012}).
-Depletions of Mg within globular clusters are not uncommon, but they are always accompanied with an increase in [Fe/H].
+Depletions of Mg within globular clusters are not uncommon, but are always accompanied with an increase in [Fe/H].
 The mechanism for this phenomena is the introduction of $\alpha$ poor but iron rich material released from Type Ia supernovae locally polluting the 'normal' [Mg/Fe] material released from Type II supernovae.
@@
 With the exception of NGC 2808, in which all 4 of its known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, this signature has thus far been found to be contained within NGC 2419.
-A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and $\omega$ Centauri as well as 21 field stars found in all cases K abundances falling within the range of the Mg normal population in NGC 2419 \citep{carretta2013}.
+A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and $\omega$ Centauri as well as 21 field stars found in all cases K abundances falling within the bounds of the Mg normal population in NGC 2419 \citep{carretta2013}.
 
@@
 
-It has been suggested that the NGC 2419's position and size, being both very massive and very distant from the Milky Way compared to many other globular clusters, aids it in retaining enriched material from explosive events \citep{mucciarelli2012}.
+It has been suggested that NGC 2419's position and size, being both very massive and very distant from the Milky Way compared to many other globular clusters, aids it in retaining enriched material from explosive events \citep{mucciarelli2012}.
 It is also perhaps noteworthy that NGC 2808 is also one of the more massive globular clusters of the Milky Way, although it is far closer to the Galactic Centre.
@@
 So while it might be expected that second generation stars in clusters similar to NGC 2419 made up of more material processed by the first generation than other lighter globular clusters, it doesn't explain why the ejecta from the first generation was apparently dominated by this as yet unknown polluter object resulting in the Mg-K anti-correlation.
-In the opinion of the author, it is the identity and physical characterisation of this unknown polluter that is of the greatest scientific interest, with such a result also hopefully answering the question as to the signatures uniqueness.
+In the opinion of the author, it is the identity and physical characterisation of this unknown polluter that is of the greatest scientific interest, with such a result also hopefully answering the question of the signatures uniqueness.
 
 An early modelling attempt at replicating the anomalous abundances in NGC 2419 assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}.
-This study succeeded in reproducing the Mg-K anti-correlation, using nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for nuclear synthesis of K.
-However, the required abundance patterns consistent with NGC 2419 were only attainable if the reaction cross section was set to 100 times the commonly accepted rate or temperatures could be made higher than currently accepted values, achieving a burning temperature of 150 MK.
+This study succeeded in reproducing the Mg-K anti-correlation, using the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for nuclear synthesis of K.
+However, abundance patterns consistent with NGC 2419 were only attainable if the reaction cross section was set to 100 times the commonly accepted rate or temperatures could be made higher than currently accepted values, achieving a burning temperature of 150 MK.
 
@@
 The ultimate goal was to constrain the temperatures and densities required to produce the chemical signiature, and thereby provide insight into potential polluter candidates.
-It is perhaps noteworthy that they identified a diferent main reaction pathway to that of \cite{ventura2012}, which is relegated to a minor minor seccondary pathway.
+It is perhaps noteworthy that they identified a diferent main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor minor seccondary pathway.
 The main pathway they identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.
@@
 This study, which queries 454180 LAMOST giants for depleted Mg and enhanced K, seeks to provide additional information which can be used to guide and test models attempting to explain the Mg-K anti-correlation and related phenomena.
-The large sample size provides greater insight into the supposed exclusivity of the signature, and any stars identified present an important opportunity for follow up observations both to confirm the abundance signature and to determine data beyond the scope of this study such as the mass and orbital characteristics of the targets.
+The large sample size provides greater insight into the supposed exclusivity of the signature, and the stars identified present an important opportunity for follow up observations.
 
@@
 The apparent noisiness of the signal was qualitatively taken into account when making these determinations.
-Of the 384 candidates manually vetted, 188 were ultimately determined to be sufficiently strong to be reported.
+Of the 384 candidates manually vetted, 188 were ultimately determined to be sufficiently strong for further examination based on the spectra around the K and Mg lines.
+
 The 6556 \AA \\ H line was then visually examined for each star to identify stars with active chromosphere emissions which could result in false positives for Mg depletion.

### 2018-01-10 article/ms.tex
update authors and affil; start with ngc 2419 intro

@@
 
+\usepackage{color}
+\newcommand{\todo}[1]{\textcolor{red}{#1}}
+
 %%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
@@
 Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
-A. N. Other,$^{2}$
-Third Author$^{2,3}$
-and Fourth Author$^{3}$
+Andrew R. Casey,$^{1,2}$
+%Matthew Miles? (Monash)
+%Brodie Norfolk? (Monash)
+%Amanda Karakas? (Monash)
+%John Lattanzio? (Monash)
+%Kevin Schlaufman? (JHU)
+%Anna Ho? (Caltech)
 \\
 % List of institutions
-$^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK\\
-$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
-$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
+$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
+$^{2}$ Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
 }
@@
 % These dates will be filled out by the publisher
-\date{Accepted XXX. Received YYY; in original form ZZZ}
+\date{Accepted 2018 XX XX. Received 2018 YY YY; in original form 2018 ZZ ZZ}
 
 % Enter the current year, for the copyright statements etc.
-\pubyear{2015}
+\pubyear{2018}
 
@@
 \section{Introduction}
+
+NGC 2419 is the Milky Way's third most massive cluster, and one of the oldest at an age of 12.3 $\pm$ 1.3 Gyr \citep{forbesandbridges2010}.
+It resides in the outer halo 87.5 kpc \todo{[citation needed]} from the galactic centre, and its chemical make-up makes it one of the most unusual clusters in the galaxy.
+
 The Mg-K anti correlation initially established in NGC 2419 continues to elude satisfactory explanation.
@@
 Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.
-
-NGC 2419 is the Milky Way's third most massive cluster, and one of the oldest at an age of 12.3 $\pm$ 1.3 Gy \citep{forbesandbridges2010}.
-It resides in the outer halo 87.5 kpc (original source unknown) from the galactic centre, and its chemical make-up makes it one of the most unusual clusters in the galaxy.
 

### 2018-01-10 article/ms.tex
age not relevant - all GCs are old

@@
 
-NGC 2419 is the Milky Way's third most massive cluster, and one of the oldest at an age of 12.3 $\pm$ 1.3 Gyr \citep{forbesandbridges2010}.
-It resides in the outer halo 87.5 kpc \todo{[citation needed]} from the galactic centre, and its chemical make-up makes it one of the most unusual clusters in the galaxy.
+NGC 2419 is the Milky Way's third most massive globular cluster, and its chemical composition makes it perhaps the most unusual star cluster in the Galaxy.
 

### 2018-01-10 article/ms.tex
reordering; temp comments

@@
 
+\newcommand{\LamostGiants}{454180}
+\newcommand{\project}[1]{\emph{#1}}
+\newcommand{\lamost}{\project{LAMOST}
+
+\newcommand{\teff}{T_{\rm eff}}
+\newcommand{\logg}{\log_{10}[g\,({\rm cm\,s}^{-2})]}
+
 %%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
@@
 
-The Mg-K anti correlation initially established in NGC 2419 continues to elude satisfactory explanation.
-Beyond the intrinsic scientific value of identifying the polluter object which is (presumably) responsible for the puzzling Mg-K anti-correlation, a satisfactory explanation for this signature could potentially offer insight into the underestimation of K abundance predicted by models \citep{kobayashi2011}.
-Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.
-
 A spectroscopic study of RGB giant stars in NGC 2419 led to the discovery discovery of a strong anti-correlation between Mg and K in around 30-40 \% of the studied stars, along with weaker relations in Si, Sc, Ca, Ti and V (\citet{mucciarelli2012}, \citet{cohenkirby2012}).
@@
 
-With the exception of NGC 2808, in which all 4 of its known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, this signature has thus far been found to be contained within NGC 2419.
-A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and $\omega$ Centauri as well as 21 field stars found in all cases K abundances falling within the bounds of the Mg normal population in NGC 2419 \citep{carretta2013}.
+The Mg-K anti correlation initially established in NGC 2419 continues to elude satisfactory explanation.
+Beyond the intrinsic scientific value of identifying the polluter object which is (presumably) responsible for the puzzling Mg-K anti-correlation, a satisfactory explanation for this signature could potentially offer insight into the underestimation of K abundance predicted by models \citep{kobayashi2011}.
+Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.
 
@@
 
-While it is plausible that the increased mass and greater distance from the gaseous disk of the Milky Way would cause a clusters first generation polluter stars to have an increased effect on the second generation of stars, this effect would apply to all ejecta (assuming comparable energies).
+With the exception of NGC 2808, in which all 4 of its known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, this signature has thus far been found to be contained within NGC 2419.
+A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and $\omega$ Centauri as well as 21 field stars found in all cases K abundances falling within the bounds of the Mg normal population in NGC 2419 \citep{carretta2013}.
+
+%While it is plausible that the increased mass and greater distance from the gaseous disk of the Milky Way would cause a clusters first generation polluter stars to have an increased effect on the second generation of stars, this effect would apply to all ejecta (assuming comparable energies).
 So while it might be expected that second generation stars in clusters similar to NGC 2419 made up of more material processed by the first generation than other lighter globular clusters, it doesn't explain why the ejecta from the first generation was apparently dominated by this as yet unknown polluter object resulting in the Mg-K anti-correlation.
@@
 
-An early modelling attempt at replicating the anomalous abundances in NGC 2419 assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}.
+%An early modelling attempt at replicating the anomalous abundances in NGC 2419 assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}.
 This study succeeded in reproducing the Mg-K anti-correlation, using the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for nuclear synthesis of K.
@@
 
-A more recent, comprehensive attempt to replicate the Mg and K abundances in NGC 2419 by \cite{iliadis2016} also attempted to reproduce the abundances of Si, Sc, Ca, Ti and V (elements reported as having weak correlations with Mg by \cite{cohenkirby2012}).
+%A more recent, comprehensive attempt to replicate the Mg and K abundances in NGC 2419 by \cite{iliadis2016} also attempted to reproduce the abundances of Si, Sc, Ca, Ti and V (elements reported as having weak correlations with Mg by \cite{cohenkirby2012}).
 The ultimate goal was to constrain the temperatures and densities required to produce the chemical signiature, and thereby provide insight into potential polluter candidates.
@@
 
-It was found that (with the exception of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required.
+%It was found that (with the exception of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required.
 Using this information, core and shell burning of low mass, high mass and super massive stars were ruled out as potential poluter candidates, as well as regular AGB stars.
@@
 
-Another proposed  polluter candidate is a pair instability super nova (PISN) \citep{carretta2013}.
+%Another proposed  polluter candidate is a pair instability super nova (PISN) \citep{carretta2013}.
 Unique to extremely massive population III stars, these events involve the total destruction of the star, with no black hole remnant being left behind.
@@
 
-This study, which queries 454180 LAMOST giants for depleted Mg and enhanced K, seeks to provide additional information which can be used to guide and test models attempting to explain the Mg-K anti-correlation and related phenomena.
+This study, which queries \LamostGiants\ \lamost\ giants for depleted Mg and enhanced K, seeks to provide additional information which can be used to guide and test models attempting to explain the Mg-K anti-correlation and related phenomena.
 The large sample size provides greater insight into the supposed exclusivity of the signature, and the stars identified present an important opportunity for follow up observations.

### 2018-01-10 article/ms.tex
RGB giants @alex162 you're fired

@@
 
-A spectroscopic study of RGB giant stars in NGC 2419 led to the discovery discovery of a strong anti-correlation between Mg and K in around 30-40 \% of the studied stars, along with weaker relations in Si, Sc, Ca, Ti and V (\citet{mucciarelli2012}, \citet{cohenkirby2012}).
+A spectroscopic study of red giant branch (RGB) in NGC 2419 led to the discovery discovery of a strong anti-correlation between Mg and K in around 30-40 \% of the studied stars, along with weaker relations in Si, Sc, Ca, Ti and V (\citet{mucciarelli2012}, \citet{cohenkirby2012}).
 Depletions of Mg within globular clusters are not uncommon, but are always accompanied with an increase in [Fe/H].

### 2018-01-10 article/ms.tex
edits

--- 2018-01-10 article/ms.tex
@@
 NGC 2419 is the Milky Way's third most massive globular cluster, and its chemical composition makes it perhaps the most unusual star cluster in the Galaxy.
+Recent spectroscopic studies of red giant branch (RGB) stars in NGC 2419 revealed a strong anti-correlation between Mg and K abundances in nearly half of the studied stars, and weaker abundance relations in Si, Sc, Ca, Ti and V \citep{mucciarelli2012,cohenkirby2012}.
+Depletions of Mg within globular clusters are not uncommon, but are always accompanied with an increase in [Fe/H] \todo{[citations needed; possibly remove]}.
+One mechanism for this phenomena is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae which locally pollutes the more `normal' [Mg/Fe] ratios that arise from Type II supernovae.
+However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}.
+Furthermore, Type Ia supernovae enrichment cannot account for the enhanced K abundance or the similar  abundance trends observed in NGC 2419.
 
-A spectroscopic study of RGB giant stars in NGC 2419 led to the discovery discovery of a strong anti-correlation between Mg and K in around 30-40 \% of the studied stars, along with weaker relations in Si, Sc, Ca, Ti and V (\citet{mucciarelli2012}, \citet{cohenkirby2012}).
-Depletions of Mg within globular clusters are not uncommon, but are always accompanied with an increase in [Fe/H].
-The mechanism for this phenomena is the introduction of $\alpha$ poor but iron rich material released from Type Ia supernovae locally polluting the 'normal' [Mg/Fe] material released from Type II supernovae.
-However, the two sub-populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}.
-Further, Type Ia supernovae enrichment does not account for the enhanced K abundance or trends in the other elements.
+Currently there is no known nuclear process that can explain the abundance variations in NGC 2419 without invoking unrealistic temperature conditions or by altering reaction rates by several orders of magnitude.
 
-Recently \cite{youngwooklee} used a Ca filter to identify two population in NGC 2419 corresponding to two generations of stars: G1, first generation metal poor stars, and G2, second generation stars displaying enhanced Ca and significantly increased He abundance ($\Delta Y = 0.19$).
+%Recently \cite{youngwooklee} used a Ca filter to identify two population in NGC 2419 corresponding to two generations of stars: G1, first generation metal poor stars, and G2, second generation stars displaying enhanced Ca and significantly increased He abundance ($\Delta Y = 0.19$).
 The Mg depleted population identified previously was found to be contained with the G2 population.
@@
 Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.
-
-At present, there is no accepted nuclear process that can explain the elemental abundance in NGC 2419.
-The fact that the Mg-K anti-correlation is confined to these very few specific globular clusters would seem to imply either a small population  of unusual polluter stars of some sort or a single extremely massive polluter star.
 
@@
 A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and $\omega$ Centauri as well as 21 field stars found in all cases K abundances falling within the bounds of the Mg normal population in NGC 2419 \citep{carretta2013}.
+
+The fact that the Mg-K anti-correlation is confined to these very few specific globular clusters would seem to imply either a small population  of unusual polluter stars of some sort or a single extremely massive polluter star.
 

### 2018-01-10 article/ms.tex
words

@@
 Currently there is no known nuclear process that can explain the abundance variations in NGC 2419 without invoking unrealistic temperature conditions or by altering reaction rates by several orders of magnitude.
+Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg-K anti-correlation, a satisfactory explanation for this signature could offer insight into the underestimation of K abundances in the Milky Way predicted by models \citep{kobayashi2011}.
+Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.
 
@@
 The Mg-K anti correlation initially established in NGC 2419 continues to elude satisfactory explanation.
-Beyond the intrinsic scientific value of identifying the polluter object which is (presumably) responsible for the puzzling Mg-K anti-correlation, a satisfactory explanation for this signature could potentially offer insight into the underestimation of K abundance predicted by models \citep{kobayashi2011}.
-Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.
 

### 2018-01-10 article/ms.tex
never use a short word when a superlative one will suffice @alex162 /s
dont store .blg files

@@
 \newcommand{\project}[1]{\emph{#1}}
-\newcommand{\lamost}{\project{LAMOST}
+\newcommand{\lamost}{\project{LAMOST}}
 
@@
 Furthermore, Type Ia supernovae enrichment cannot account for the enhanced K abundance or the similar  abundance trends observed in NGC 2419.
-
-Currently there is no known nuclear process that can explain the abundance variations in NGC 2419 without invoking unrealistic temperature conditions or by altering reaction rates by several orders of magnitude.
-Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg-K anti-correlation, a satisfactory explanation for this signature could offer insight into the underestimation of K abundances in the Milky Way predicted by models \citep{kobayashi2011}.
-Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.
+Currently there is no known nuclear process that can explain the Mg-K abundance variations  without invoking unrealistic temperature conditions or by altering reaction rates by several orders of magnitude.
 
@@
 
-The Mg-K anti correlation initially established in NGC 2419 continues to elude satisfactory explanation.
+A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and $\omega$ Centauri as well as 21 field stars \todo{21 field stars or 21 clusters??
+I thought carretta looked at lots of clusters, no?} found in all cases K abundances falling within the bounds of the Mg normal population in NGC 2419 \citep{carretta2013}.
+\todo{The exception is NGC 2808......}
+With the exception of NGC 2808, in which all 4 of its known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, this signature has thus far been found to be contained within NGC 2419.
+The fact that the Mg-K anti-correlation is confined to these very few specific globular clusters would seem to imply either a small population  of unusual polluter stars of some sort or a single extremely massive polluter star.
 
-It has been suggested that NGC 2419's position and size, being both very massive and very distant from the Milky Way compared to many other globular clusters, aids it in retaining enriched material from explosive events \citep{mucciarelli2012}.
+An early modelling attempt at replicating the anomalous Mg/K abundances assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}.
+This study succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} \citep{iliadis2016} for the production of K.
+However, abundance patterns consistent with NGC 2419 were only achievable if the reaction cross section was set to 100 times the commonly accepted rate, or if the \todo{stellar interior?} temperatures could be increased to 150 MK \todo{from what?}.
+% made higher than currently accepted values, achieving a burning temperature of 150 MK.
+
+A more recent attempt to replicate the Mg/K abundance signature in NGC 2419 by \cite{iliadis2016} also attempted to reproduce the abundances of Si, Sc, Ca, Ti and V  \citep[elements reported as having weak correlations with Mg by][]{cohenkirby2012}.
+The ultimate goal was to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluter candidates.
+It is perhaps noteworthy that they identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor minor secondary pathway.
+The main pathway they identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.
+
+It was found that (with the exception of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required.
+Using this information, core and shell burning of low mass, high mass and super massive stars were ruled out as potential polluter candidates, as well as regular AGB stars.
+Super-AGB (SAGB) stars however were regarded as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
+The other potential candidate identified was Novae, although the lack of detailed models of white dwarfs accreting material similar to NGC 2419 either from a binary companion or the intra cluster medium limit appraisals of its feasibility regarding whether enough ejecta could be produced and retained by the cluster.
+However, based on current novae frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by Novae is at most 1 \% of the total required mass to pollute 30 \% of NGC 2419.
+
+Another proposed  polluter candidate is a pair instability super nova \citep[PISN;][]{carretta2013}.
+Unique to extremely massive population III stars, these events involve the total destruction of the star, with no black hole remnant being left behind.
+The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material involved, could potentially allow the entire signature in NGC 2419 to be the result of a single event, explaining why it is not seen in any other globular clusters.
+Further, the signature odd-even proton number abundance pattern associated with PISNs could perhaps explain the anti-correlation between Mg and K, as well as the enhancements in Sc and V observed by \cite{cohenkirby2012}.
+\todo{Do all the abundance variations like Sc, Si, Ca, Ti, and V go in the expected direction for PISN?}
+
+%It has been suggested that NGC 2419's position and size, being both very massive and very distant from the Milky Way compared to many other globular clusters, aids it in retaining enriched material from explosive events \citep{mucciarelli2012}.
 It is also perhaps noteworthy that NGC 2808 is also one of the more massive globular clusters of the Milky Way, although it is far closer to the Galactic Centre.
 But if this unknown pollution event is common among globular clusters and the cause of its apparent exclusivity to NGC 2808 and NGC 2419 is enhanced ejecta retention due to high mass, then other massive clusters such as $\omega$ Centauri would also be expected contain the signature, which to date has not been observed.
-
-With the exception of NGC 2808, in which all 4 of its known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, this signature has thus far been found to be contained within NGC 2419.
-A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and $\omega$ Centauri as well as 21 field stars found in all cases K abundances falling within the bounds of the Mg normal population in NGC 2419 \citep{carretta2013}.
-
-The fact that the Mg-K anti-correlation is confined to these very few specific globular clusters would seem to imply either a small population  of unusual polluter stars of some sort or a single extremely massive polluter star.
 
@@
 
-%An early modelling attempt at replicating the anomalous abundances in NGC 2419 assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}.
-This study succeeded in reproducing the Mg-K anti-correlation, using the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for nuclear synthesis of K.
-However, abundance patterns consistent with NGC 2419 were only attainable if the reaction cross section was set to 100 times the commonly accepted rate or temperatures could be made higher than currently accepted values, achieving a burning temperature of 150 MK.
+Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg-K anti-correlation, a satisfactory explanation for this signature could offer insight into the underestimation of K abundances in the Milky Way predicted by models \citep{kobayashi2011}.
+Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.
 
-%A more recent, comprehensive attempt to replicate the Mg and K abundances in NGC 2419 by \cite{iliadis2016} also attempted to reproduce the abundances of Si, Sc, Ca, Ti and V (elements reported as having weak correlations with Mg by \cite{cohenkirby2012}).
-The ultimate goal was to constrain the temperatures and densities required to produce the chemical signiature, and thereby provide insight into potential polluter candidates.
-It is perhaps noteworthy that they identified a diferent main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor minor seccondary pathway.
-The main pathway they identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.
+Here we use \lamost\ data to conduct the largest ever search for field stars that are enhanced in potassium and depleted in magnesium.
+The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.
+\todo{In Section \ref{sec:methods} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and analysis of those candidates.
+In Section \ref{sec:discussion} we discuss things.
+Section \ref{sec:conclusions} contains conclusions.}
 
-%It was found that (with the exception of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required.
-Using this information, core and shell burning of low mass, high mass and super massive stars were ruled out as potential poluter candidates, as well as regular AGB stars.
-Super-AGB (SAGB) stars however were regarded as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
-The other potential candidate identified was Novae, although the lack of detailed models of white dwarfs accreting material similar to NGC 2419 either from a binary companion or the intra cluster medium limit appraisals of its feasibility regarding whether enough ejecta could be produced and retained by the cluster.
-However, based on current novae frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by Novae is at most 1 \% of the total required mass to pollute 30 \% of NGC 2419.
-
-%Another proposed  polluter candidate is a pair instability super nova (PISN) \citep{carretta2013}.
-Unique to extremely massive population III stars, these events involve the total destruction of the star, with no black hole remnant being left behind.
-The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material involved, could potentially allow the entire signature in NGC 2419 to be the result of a single event, explaining why it is not seen in any other globular clusters.
-Further, the signature odd-even proton number abundance pattern associated with PISNs could perhaps explain the anti-correlation between Mg and K, as well as the enhancements in Sc and V observed by \cite{cohenkirby2012}.
-
-This study, which queries \LamostGiants\ \lamost\ giants for depleted Mg and enhanced K, seeks to provide additional information which can be used to guide and test models attempting to explain the Mg-K anti-correlation and related phenomena.
+%This study, which queries \LamostGiants\ \lamost\ giants for depleted Mg and enhanced K, seeks to provide additional information which can be used to guide and test models attempting to explain the Mg-K anti-correlation and related phenomena.
 The large sample size provides greater insight into the supposed exclusivity of the signature, and the stars identified present an important opportunity for follow up observations.

### 2018-01-10 article/ms.tex
edits

@@
 \newcommand{\lamost}{\project{LAMOST}}
+\newcommand{\tc}{\project{The Cannon}}
 
@@
 
-The data set of 454180 LAMOST giants was prepared by \citet{ho2017} for use with the supervised machine learning code \textit{The Cannon}.
-The LAMOST data was shifted to rest frame, normalised, and sampled to a common uniform wavelength grid between 3905 \AA \\ and 9000 \AA.
-\textit{The Cannon} was used to infer $\text{T}_{\text{eff}}$, log(g), [Fe/H] and [$\alpha$/M] using 9952 common stars between LAMOST and the higher resolution APOGEE survey through the use of a data-driven spectral model, referred to henceforth and simply 'the model'.
+The data set of \LamostGiants\ \lamost\ giants was prepared by \citet{ho2017} for use with the supervised machine learning code \tc.
+The \lamost\ data was shifted to rest frame and continuum-normalised before it was resampled to a common uniform wavelength grid between 3905\,\AA\ and 9000\,\AA.
+\tc\ was used to infer $\teff$, $\logg$, [Fe/H], and [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ survey through the use of a data-driven spectral model.
 For details regarding the preparatory work, model generation and label transfer between the APOGEE and LAMOST surveys, the reader is directed to \citet{ho2017}.

### 2018-01-10 article/ms.tex
Oxford comma. Use it. Read 'Eats, Shoots, and Leaves' if you're not convinced @alex162

@@
 \tc\ was used to infer $\teff$, $\logg$, [Fe/H], and [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ survey through the use of a data-driven spectral model.
-For details regarding the preparatory work, model generation and label transfer between the APOGEE and LAMOST surveys, the reader is directed to \citet{ho2017}.
+For details regarding the preparatory work, model generation, and label transfer between the APOGEE and LAMOST surveys, the reader is directed to \citet{ho2017}.
 The data-driven model generated by \textit{The Cannon} is treated in this study as the typical spectra for each star.

### 2018-01-10 article/ms.tex
edits on methods

--- 2018-01-10 article/ms.tex
@@
 \newcommand{\lamost}{\project{LAMOST}}
+\newcommand{\apogee}{\project{APOGEE}}
+
 \newcommand{\tc}{\project{The Cannon}}
@@
 \tc\ was used to infer $\teff$, $\logg$, [Fe/H], and [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ survey through the use of a data-driven spectral model.
-For details regarding the preparatory work, model generation and label transfer between the APOGEE and LAMOST surveys, the reader is directed to \citet{ho2017}.
-The data-driven model generated by \textit{The Cannon} is treated in this study as the typical spectra for each star.
+For details regarding the preparatory work, model generation, and label transfer between the \apogee\ and \lamost\ surveys, the reader is directed to \citet{ho2017}.
 
-Residuals were taken of the normalised LAMOST flux data and 
-\textit{The Cannon} according to $residual=data-model$.
-A positive residual therefore implies a higher normalised flux than expected by the model, while a negative residual implies a lower normalised flux than expected.
-In turn, at a given spectral line a lower normalised flux is associated with an over-abundance, while a higher normalised flux is associated with a depleted abundance.
+We identified candidate Mg/K giant stars by searching for significant deviations in flux residuals.
+The flux residuals were taken as the normalised \lamost\ flux and the best-fitting data-driven model from \tc\ (where $f_{residual} = f_{data} - f_{model}$).
+A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model).
 
-A Gaussian curve was fitted to the residuals about each spectral line in the Mg triplet (5167 \AA, 5172 \AA, 5184 \AA) as well as the K doublet (7665 \AA, 7699 \AA) to characterise any deviation from the model.
-The amplitude and amplitude error for this curve was then used as the basis for a data filter designed to produce potential candidate stars with spectra indicative of Mg depletion, as well as K enrichment.
+We fitted a gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167 \AA, 5172 \AA, 5184 \AA) as well as the K doublet (7665 \AA, 7699 \AA) for all \LamostGiants\ in \lamost\ data release 2 (DR2).
+For every star we recorded the profile amplitudes, wavelengths, widths, as well as associated measurement uncertainties of these quantities.
+We identified candidates by requiring they match at least one of the following three quality filters.
+\begin{enumerate}
+\item We required the amplitude of the profile at Mg 5184 to exceed $a_{{\rm Mg} @ 5184} > 0.05$ and the amplitude of the profile at K 7665 to exceed $a_{{\rm K}\,@\,7665} < 0.05$.
+Both amplitudes must be measured at more than $3\sigma$ ($|a|/\sigma_{a} \geq 3$).
+\item We required two of the three Mg triplet lines to satisfy $a > 0.05$ and at least one K line to have $a < 0.05$, and for those amplitudes to have $|a|/\sigma_{a} \geq 3$.
+\item We required two of the three Mg triplet lines to have $a > 0$ and both K lines to have $a < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost, and a reported $\chi_{r}^2 < 3$ from \tc.
+\end{enumerate}
 
-Three filters were applied independently, with the candidate pool formed from all unique stars identified each of the three filters.
-The first filter required the Mg 5184 line's Gaussian to satisfy $Amp > 0.05$ and $\frac{Amp}{Amp_{err}}>3$, and the K 7665 line to satisfy $Amp < 0.05$ and $\frac{Amp}{Amp_{err}}>3$.
-The second, more demanding filter was applied to require 2 of the three Mg lines to satisfy $Amp > 0.05$ and $\frac{Amp}{Amp_{err}}>3$, as well as either of the two K lines to satisfy $Amp < 0.05$ and $\frac{Amp}{Amp_{err}}>3$.
-The third filter removed the amplitude requirement to requiring only positivity on 2/3 Mg lines and negativity on \textit{both} K lines, in addition to data quality requirements $\chi^2<3$ and $S/N>30$.
-These filters together produced 384 unique candidate stars to be vetted manually.
-
-The vetting process was done through visual examination of each case.
-The minimum criterion for a pass was two out of the three Mg lines to look at least plausibly depleted, and at least one of the K lines to look convincing.
-The apparent noisiness of the signal was qualitatively taken into account when making these determinations.
-Of the 384 candidates manually vetted, 188 were ultimately determined to be sufficiently strong for further examination based on the spectra around the K and Mg lines.
-
-The 6556 \AA \\ H line was then visually examined for each star to identify stars with active chromosphere emissions which could result in false positives for Mg depletion.
-62 stars were removed from the sample due to being chromospheric emmiters.
-A further 13 stars were removed due to the model fitted poorly to the H 6556 line possibly due to incorrect log(g) or $\text{T}_{\text{eff}}$ estimates from \textit{The Cannon}, leaving a total of 113 candidates displaying depleted Mg and enhanced K.
+These filters identified 384 unique stars to be vetted manually.
+We visually inspected every candidate (multiple times) and excluded any candidate that showed any evidence of being a false positive, including candidates that exhibited data reduction issues, apparent absorption that was narrower than the expected spectral resolution, as well as 75 stars that exhibited chromospheric emission at H$\alpha$.
+The distilled catalogue includes \todo{113} candidate stars enhanced in K and depleted in Mg.
 

### 2018-01-11 article/ms.tex
add ack list
Addressed many of the todos, begun construction of an abstract in Nature structure

@@
 \begin{abstract}
-454180 RGB stars from the low resolution LAMOST DR2 survey were searched for anomalously high K and depleted Mg signatures.
+
+Stellar absorption spectra act as a fossil record of the environment of primordial conditions.
+Stars displaying unusual elemental abundances provide are of particular interest, as they offer the opportunity to learn about astrophysical events and objects that may no longer exist in our Galaxy.
+Stars with depleted Mg and enhanced K abundances present just such an opportunity.
+Thus far found only in two massive globular clusters NGC 2419 and NGC 2808, the primordial origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
+A satisfactory explanation for this signature has potential ramifications on theories of globular cluster formation and the long-standing problem of the underestimation of even galaxy-normal K abundances.
+The apparent exclusivity of this Mg-K anti-correlation to globular clusters is the focus of this survey.
+Here we present 113 field stars showing depleted Mg and enhanced K, though none with abundances extreme enough to be comparable to the stars identified in NGC 2419.
+
+%454180 RGB stars from the low resolution LAMOST DR2 survey were searched for anomalously high K and depleted Mg signatures.
 This study represents the largest search for field stars containing the Mg-K anti-correlation so far identified only in the globular NGC 2419 and NGC 2808.
@@
 Recent spectroscopic studies of red giant branch (RGB) stars in NGC 2419 revealed a strong anti-correlation between Mg and K abundances in nearly half of the studied stars, and weaker abundance relations in Si, Sc, Ca, Ti and V \citep{mucciarelli2012,cohenkirby2012}.
-Depletions of Mg within globular clusters are not uncommon, but are always accompanied with an increase in [Fe/H] \todo{[citations needed; possibly remove]}.
-One mechanism for this phenomena is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae which locally pollutes the more `normal' [Mg/Fe] ratios that arise from Type II supernovae.
+Depletions of Mg within dwarf spheroidal (dSph) galaxies are not rare \citep{mucciarelli2012}, but are always accompanied with an increase in [Fe/H].
+%\todo{[citations needed; possibly remove. RESOLVED, addapted statement slightly. relevant sources: Mucciarreli and Tsujimoto.]}
+The mechanism for this Mg depletion is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the more `normal' [Mg/Fe] ratios that arise from Type II supernovae.
 However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}.
@@
 
-A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and $\omega$ Centauri as well as 21 field stars \todo{21 field stars or 21 clusters??
-I thought carretta looked at lots of clusters, no?} found in all cases K abundances falling within the bounds of the Mg normal population in NGC 2419 \citep{carretta2013}.
-\todo{The exception is NGC 2808......}
-With the exception of NGC 2808, in which all 4 of its known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, this signature has thus far been found to be contained within NGC 2419.
-The fact that the Mg-K anti-correlation is confined to these very few specific globular clusters would seem to imply either a small population  of unusual polluter stars of some sort or a single extremely massive polluter star.
+A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and $\omega$ Centauri as well as 21 field stars 
+%\todo{21 field stars or 21 clusters?? I thought carretta looked at lots of clusters, no?} RESOLVED: Info accurate, no action taken.
+ found in all cases K abundances falling within the bounds of the Mg normal population in NGC 2419 \citep{carretta2013}.
+ % \todo{The exception is NGC 2808......} RESOLVED: Rephrased paragraph.
+NGC 2808 is the only cluster other than NGC 2419 where the anticorrelation between Mg and K has been observed.
+All 4 of its known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these abundances was weaker than that in NGC 2419.
+The fact that the Mg-K anti-correlation is apparently confined to these very few globular clusters would seem to imply either a small population  of unusual polluter stars of some sort or a single extremely massive polluter star.
 
 An early modelling attempt at replicating the anomalous Mg/K abundances assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}.
-This study succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} \citep{iliadis2016} for the production of K.
-However, abundance patterns consistent with NGC 2419 were only achievable if the reaction cross section was set to 100 times the commonly accepted rate, or if the \todo{stellar interior?} temperatures could be increased to 150 MK \todo{from what?}.
-% made higher than currently accepted values, achieving a burning temperature of 150 MK.
+This study succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) \todo{Ask andy if its right to cite iliadis here, and why he removed the 'corrected as per' bit.} for the production of K.
+However, abundance patterns consistent with NGC 2419 were only achievable if the reaction cross section was set to 100 times the commonly accepted rate or if the temperature at the base of the envelope  temperatures could be made to exceed $\sim$ 150 K.
 
@@
 
-It was found that (with the exception of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required.
+It was found that (excepting the case of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required.
 Using this information, core and shell burning of low mass, high mass and super massive stars were ruled out as potential polluter candidates, as well as regular AGB stars.
 Super-AGB (SAGB) stars however were regarded as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
-The other potential candidate identified was Novae, although the lack of detailed models of white dwarfs accreting material similar to NGC 2419 either from a binary companion or the intra cluster medium limit appraisals of its feasibility regarding whether enough ejecta could be produced and retained by the cluster.
+The other potential candidate identified was novae, although the lack of detailed models of white dwarf accretion of material similar to that of NGC 2419 either from a binary companion or the intracluster medium limits appraisals of its feasibility regarding whether enough ejecta could be produced and retained by the cluster.
 However, based on current novae frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by Novae is at most 1 \% of the total required mass to pollute 30 \% of NGC 2419.
 
-Another proposed  polluter candidate is a pair instability super nova \citep[PISN;][]{carretta2013}.
-Unique to extremely massive population III stars, these events involve the total destruction of the star, with no black hole remnant being left behind.
+Another proposed  polluter candidate is a pair-instability super nova (PISN) \citep[PISN;][]{carretta2013}.
+Unique to extremely massive Population III stars, these events involve the total destruction of the star, with no black hole remnant being left behind.
 The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material involved, could potentially allow the entire signature in NGC 2419 to be the result of a single event, explaining why it is not seen in any other globular clusters.
-Further, the signature odd-even proton number abundance pattern associated with PISNs could perhaps explain the anti-correlation between Mg and K, as well as the enhancements in Sc and V observed by \cite{cohenkirby2012}.
-\todo{Do all the abundance variations like Sc, Si, Ca, Ti, and V go in the expected direction for PISN?}
+However, the signature odd-even proton number abundance pattern associated with PISNs is absent from NGC 2419 \citep{cohenkirby2012}, making this particular scenario unlikely.
+However, some other type of extremely massive star exploding in a single event would certainly go a long way to explaining the rarity of the signal.
+% \todo{Do all the abundance variations like Sc, Si, Ca, Ti, and V go in the expected direction for PISN?} RESOLVED: You are quite correct, I was entirely mistaken.
+In fact, the odd-even abundance pattern is absent from NGC 2419 in general.
+segment is edited to reflect this.
 
@@
 The data set of \LamostGiants\ \lamost\ giants was prepared by \citet{ho2017} for use with the supervised machine learning code \tc.
-The \lamost\ data was shifted to rest frame and continuum-normalised before it was resampled to a common uniform wavelength grid between 3905\,\AA\ and 9000\,\AA.
+The \lamost\ data was shifted to rest frame and continuum-normalised \todo{double check with andy.
+I could have sworn she specifically said that it WASNT continuum normalised...} before it was resampled to a common uniform wavelength grid between 3905\,\AA\ and 9000\,\AA.
 \tc\ was used to infer $\teff$, $\logg$, [Fe/H], and [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ survey through the use of a data-driven spectral model.
@@
 
-We fitted a gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167 \AA, 5172 \AA, 5184 \AA) as well as the K doublet (7665 \AA, 7699 \AA) for all \LamostGiants\ in \lamost\ data release 2 (DR2).
+We fitted a gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167 \AA, 5172 \AA, 5184 \AA) as well as the K doublet (7665 \AA, 7699 \AA) for all \LamostGiants\ giants in \lamost\ data release 2 (DR2).
 For every star we recorded the profile amplitudes, wavelengths, widths, as well as associated measurement uncertainties of these quantities.
@@
 \begin{enumerate}
-\item We required the amplitude of the profile at Mg 5184 to exceed $a_{{\rm Mg} @ 5184} > 0.05$ and the amplitude of the profile at K 7665 to exceed $a_{{\rm K}\,@\,7665} < 0.05$.
-Both amplitudes must be measured at more than $3\sigma$ ($|a|/\sigma_{a} \geq 3$).
-\item We required two of the three Mg triplet lines to satisfy $a > 0.05$ and at least one K line to have $a < 0.05$, and for those amplitudes to have $|a|/\sigma_{a} \geq 3$.
-\item We required two of the three Mg triplet lines to have $a > 0$ and both K lines to have $a < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost, and a reported $\chi_{r}^2 < 3$ from \tc.
+\item We required the amplitude $A$ of the profile at the Mg 5184 \AA \ line to exceed $A_{{\rm Mg} @ 5184} > 0.05$ and the amplitude of the profile at the K 7665 line to exceed $A_{{\rm K}\,@\,7665} < 0.05$.
+Both amplitudes must also be measured at more than $3\sigma$ ($|A|/\sigma_{A} \geq 3$).
+\item We required two of the three Mg triplet lines to satisfy $A > 0.05$ and at least one K line to have $A < 0.05$, and for those amplitudes to have $|A|/\sigma_{A} \geq 3$.
+\item We required two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost, and a reported $\chi_{r}^2 < 3$ from \tc.
 \end{enumerate}
@@
 
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
+- LAMOST
+- ARC DP (Casey)
+- Magellan/MIKE and Australian government
+- others???
 

### 2018-01-12 article/ms.tex
added tables minus abundances

@@
 
+\usepackage{verbatim}
 \usepackage{tabularx}
@@
 \usepackage{hyperref}
-
+\usepackage{longtable}
 \usepackage{color}
@@
 The data set of \LamostGiants\ \lamost\ giants was prepared by \citet{ho2017} for use with the supervised machine learning code \tc.
-The \lamost\ data was shifted to rest frame and continuum-normalised \todo{double check with andy.
-I could have sworn she specifically said that it WASNT continuum normalised...} before it was resampled to a common uniform wavelength grid between 3905\,\AA\ and 9000\,\AA.
+The \lamost\ data was shifted to rest frame and pseudo-continuum-normalised \ before it was resampled to a common uniform wavelength grid between 3905\,\AA\ and 9000\,\AA.
 \tc\ was used to infer $\teff$, $\logg$, [Fe/H], and [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ survey through the use of a data-driven spectral model.
@@
 \section{Some extra material}
+\begin{table}
+\centering
+\begin{tabular}{llllllllll}
+\hline
+\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{Vr (km/s)} & \textbf{Teff} & \textbf{Logg} & \textbf{[Fe/H]} & \textbf{[Alpha/Fe]} & {$\boldsymbol \chi^\textbf{2}$} \\ \hline
+J060142.80+132321.4 & 90.43 & 13.39 & 45 & 33.28 & 4858 & 2.57 & -0.30 & 0.10 & 0.24 \\ \hline
+J075043.12+204658.0 & 117.68 & 20.78 & 47 & 52.46 & 4795 & 2.53 & -0.47 & 0.06 & 0.40 \\ \hline
+J032450.35+352401.8 & 51.21 & 35.40 & 143 & 95.63 & 4908 & 3.33 & -0.27 & 0.19 & 0.70 \\ \hline
+J214721.25+023958.7 & 326.84 & 2.67 & 104 & -63.83 & 4649 & 2.22 & -0.68 & 0.26 & 0.81 \\ \hline
+J040340.38+563902.4 & 60.92 & 56.65 & 30 & 39.87 & 4459 & 2.05 & -0.46 & 0.01 & 0.61 \\ \hline
+J035455.85+594730.3 & 58.73 & 59.79 & 57 & -40.17 & 4956 & 2.81 & 0.08 & 0.04 & 0.56 \\ \hline
+J035928.29+595932.8 & 59.87 & 59.99 & 35 & -38.07 & 4808 & 2.44 & -0.53 & 0.16 & 0.32 \\ \hline
+J034458.82+592955.1 & 56.25 & 59.50 & 53 & -32.68 & 4811 & 2.66 & 0.06 & 0.10 & 0.64 \\ \hline
+J220657.78+232138.3 & 331.74 & 23.36 & 50 & -27.58 & 4842 & 3.34 & -0.40 & 0.10 & 0.23 \\ \hline
+J061323.14+325543.0 & 93.35 & 32.93 & 39 & -25.78 & 4861 & 2.51 & -0.40 & 0.16 & 0.42 \\ \hline
+J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.10 & 0.44 \\ \hline
+J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 \\ \hline
+J040817.31+463252.5 & 62.07 & 46.55 & 92 & -1.80 & 5019 & 2.68 & -0.09 & 0.05 & 0.98 \\ \hline
+J072156.18+225405.3 & 110.48 & 22.90 & 101 & -46.77 & 4840 & 2.54 & -0.33 & 0.17 & 0.69 \\ \hline
+J040634.97+411354.9 & 61.65 & 41.23 & 45 & -35.38 & 4770 & 2.67 & -0.26 & 0.07 & 0.51 \\ \hline
+J041608.62+433504.7 & 64.04 & 43.58 & 30 & -20.09 & 4967 & 2.90 & -0.17 & 0.04 & 0.33 \\ \hline
+J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 \\ \hline
+J052924.25+494319.7 & 82.35 & 49.72 & 94 & -22.48 & 5087 & 3.12 & -0.35 & 0.11 & 0.70 \\ \hline
+J061427.58+331544.3 & 93.61 & 33.26 & 51 & 3.30 & 4468 & 1.87 & -0.41 & 0.11 & 0.67 \\ \hline
+J062128.63+343545.8 & 95.37 & 34.60 & 39 & 33.28 & 4831 & 2.58 & -0.23 & 0.08 & 0.27 \\ \hline
+J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 \\ \hline
+J120032.60+024438.2 & 180.14 & 2.74 & 97 & 166.98 & 4633 & 2.33 & -0.93 & 0.26 & 0.89 \\ \hline
+J163910.01+100545.3 & 249.79 & 10.10 & 39 & 123.81 & 4663 & 2.46 & -0.58 & 0.03 & 0.61 \\ \hline
+\end{tabular}
+\caption{My caption}
+\label{my-label}
+\end{table}
 
-If you want to present additional material which would interrupt the flow of the main paper,
-it can be placed in an Appendix which appears after the list of references.
+\newpage
+\begin{comment}
+\begin{table}[H]
+\centering
+\begin{tabular}{llllllllll}
+\hline
+\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{Radial\_Velocity\_(km/s)} & \textbf{Teff} & \textbf{Logg} & \textbf{{[}Fe/H{]}} & \textbf{{[}Alpha/Fe{]}} & \textbf{$\chi^2$} \\ \hline
+J234942.32+300654.0 & 357.43 & 30.11 & 20 & -195.46 & 4004 & 1.12 & -0.58 & 0.23 & 2.73 \\ \hline
+J065334.23+131639.7 & 103.39 & 13.28 & 7 & 179.88 & 4896 & 2.61 & -0.71 & 0.02 & 0.18 \\ \hline
+J112309.75+261255.9 & 170.79 & 26.22 & 3 & 113.02 & 4273 & 1.13 & -1.35 & 0.17 & 0.09 \\ \hline
+J111651.71+253038.5 & 169.22 & 25.51 & 6 & 102.83 & 4658 & 2.90 & -0.50 & 0.02 & 0.08 \\ \hline
+J045424.86+534628.5 & 73.60 & 53.77 & 6 & -36.57 & 4451 & 1.81 & -0.19 & 0.07 & 0.37 \\ \hline
+J065857.80+081714.8 & 104.74 & 8.29 & 12 & 26.68 & 5070 & 3.30 & -0.61 & 0.10 & 0.18 \\ \hline
+J045544.93+490023.3 & 73.94 & 49.01 & 6 & -38.07 & 4717 & 2.55 & -0.34 & 0.11 & 0.11 \\ \hline
+J040739.62+423724.4 & 61.92 & 42.62 & 9 & -37.77 & 4075 & 1.54 & -0.32 & 0.08 & 0.28 \\ \hline
+J043121.48+414757.2 & 67.84 & 41.80 & 8 & -12.59 & 4537 & 2.07 & -0.09 & 0.03 & 0.13 \\ \hline
+J041900.21+422223.9 & 64.75 & 42.37 & 12 & -34.18 & 4263 & 1.77 & -0.55 & 0.09 & 0.28 \\ \hline
+J041209.44+411801.0 & 63.04 & 41.30 & 35 & -20.69 & 4767 & 2.24 & -0.26 & 0.12 & 0.91 \\ \hline
+J063648.82+130723.3 & 99.20 & 13.12 & 8 & 85.74 & 4925 & 2.93 & -0.57 & -0.03 & 0.19 \\ \hline
+J070524.04+120351.0 & 106.35 & 12.06 & 19 & 60.26 & 4754 & 2.64 & -0.56 & -0.02 & 0.24 \\ \hline
+J063501.25+134744.6 & 98.76 & 13.80 & 7 & 47.67 & 4612 & 2.33 & -0.40 & 0.01 & 0.19 \\ \hline
+J053942.83+383727.8 & 84.93 & 38.62 & 18 & -85.74 & 4979 & 2.26 & -0.66 & 0.23 & 0.27 \\ \hline
+J053123.26+421952.0 & 82.85 & 42.33 & 8 & 41.07 & 4785 & 2.59 & -0.26 & 0.01 & 0.26 \\ \hline
+J052643.65+354130.3 & 81.68 & 35.69 & 9 & -18.89 & 4914 & 2.73 & -0.09 & 0.03 & 0.28 \\ \hline
+J064618.82+050545.8 & 101.58 & 5.10 & 9 & 85.74 & 4772 & 2.66 & -0.49 & -0.01 & 0.28 \\ \hline
+J063719.82+185602.6 & 99.33 & 18.93 & 5 & 15.29 & 5075 & 2.94 & -0.12 & 0.03 & 0.10 \\ \hline
+J072912.52+073436.9 & 112.30 & 7.58 & 9 & 117.52 & 4835 & 3.18 & -0.44 & 0.33 & 0.34 \\ \hline
+J193217.91+374505.6 & 293.07 & 37.75 & 28 & -70.15 & 4982 & 2.62 & -0.48 & 0.33 & 0.55 \\ \hline
+J192937.24+390211.0 & 292.41 & 39.04 & 6 & -52.16 & 4819 & 3.00 & 0.37 & 0.12 & 0.21 \\ \hline
+J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.10 & 0.05 & 1.17 \\ \hline
+J235454.61+110356.9 & 358.73 & 11.07 & 12 & -109.72 & 4794 & 3.07 & -0.16 & 0.30 & 0.21 \\ \hline
+J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 \\ \hline
+J220115.66-001432.2 & 330.32 & -0.24 & 47 & 38.37 & 4925 & 3.30 & 0.06 & 0.23 & 0.32 \\ \hline
+J064430.22+341606.3 & 101.13 & 34.27 & 9 & -40.17 & 4809 & 3.26 & 0.36 & 0.19 & 0.31 \\ \hline
+J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 \\ \hline
+J033714.25+403015.1 & 54.31 & 40.50 & 34 & -119.32 & 4674 & 2.33 & 0.32 & 0.22 & 0.86 \\ \hline
+J074807.22+261514.2 & 117.03 & 26.25 & 16 & -32.98 & 4846 & 2.69 & -0.23 & 0.05 & 0.16 \\ \hline
+J032423.46+425429.6 & 51.10 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 \\ \hline
+J055043.44+162021.2 & 87.68 & 16.34 & 24 & 83.64 & 4587 & 2.49 & 0.21 & 0.07 & 0.28 \\ \hline
+J055227.43+181628.0 & 88.11 & 18.27 & 28 & 8.09 & 5388 & 3.80 & -0.17 & 0.05 & 0.43 \\ \hline
+J055935.08+150252.1 & 89.90 & 15.05 & 23 & 90.84 & 4487 & 2.15 & -0.68 & 0.01 & 4.35 \\ \hline
+J063113.14+015900.3 & 97.80 & 1.98 & 14 & 78.55 & 4879 & 2.34 & -0.13 & 0.01 & 0.56 \\ \hline
+J111550.58+104203.9 & 168.96 & 10.70 & 9 & 114.82 & 4519 & 1.72 & -1.41 & 0.32 & 0.17 \\ \hline
+J111022.65+171251.0 & 167.59 & 17.21 & 12 & 247.33 & 4524 & 1.92 & -1.30 & 0.13 & 0.30 \\ \hline
+J100054.32+185535.5 & 150.23 & 18.93 & 17 & 149.00 & 4373 & 2.30 & 0.01 & 0.01 & 0.39 \\ \hline
+J055908.72+210037.7 & 89.79 & 21.01 & 6 & 55.76 & 4325 & 1.99 & -0.10 & -0.03 & 0.75 \\ \hline
+J055704.30+215000.1 & 89.27 & 21.83 & 9 & 49.77 & 4691 & 2.94 & 0.37 & 0.00 & 0.30 \\ \hline
+J104800.91+424311.0 & 162.00 & 42.72 & 6 & 163.99 & 5050 & 2.75 & -1.29 & 0.12 & 0.18 \\ \hline
+J075129.58+024136.9 & 117.87 & 2.69 & 18 & 128.61 & 4741 & 2.39 & -0.61 & 0.05 & 0.28 \\ \hline
+J064132.46+580400.9 & 100.39 & 58.07 & 24 & -11.69 & 5285 & 3.74 & -0.06 & 0.07 & 0.36 \\ \hline
+J063908.57+381728.0 & 99.79 & 38.29 & 5 & 25.78 & 4853 & 2.73 & -0.52 & 0.02 & 0.17 \\ \hline
+J102104.26+105617.4 & 155.27 & 10.94 & 17 & 171.48 & 4526 & 1.88 & -1.09 & 0.07 & 0.28 \\ \hline
+J061228.04-040304.1 & 93.12 & -4.05 & 16 & -1.50 & 4928 & 3.24 & -0.56 & 0.09 & 0.19 \\ \hline
+J061144.17-040845.1 & 92.93 & -4.15 & 23 & 84.54 & 4709 & 2.77 & -0.42 & -0.00 & 0.24 \\ \hline
+J074848.57+210655.5 & 117.20 & 21.12 & 9 & 101.33 & 4447 & 2.25 & -0.52 & 0.04 & 0.11 \\ \hline
+J092124.00+204559.5 & 140.35 & 20.77 & 12 & 125.31 & 4570 & 2.28 & -0.71 & 0.06 & 0.31 \\ \hline
+J074146.65+145330.5 & 115.44 & 14.89 & 6 & 105.53 & 4701 & 2.00 & -0.71 & 0.04 & 0.18 \\ \hline
+J073641.12+164710.6 & 114.17 & 16.79 & 6 & 90.84 & 4621 & 2.17 & -0.77 & 0.01 & 0.26 \\ \hline
+J175211.80+273546.6 & 268.05 & 27.60 & 7 & -33.58 & 5489 & 3.71 & -0.03 & 0.14 & 0.15 \\ \hline
+J194028.76+504047.6 & 295.12 & 50.68 & 22 & -61.76 & 4352 & 1.94 & -0.17 & 0.23 & 0.35 \\ \hline
+J213914.06+025536.2 & 324.81 & 2.93 & 29 & 57.78 & 4488 & 2.40 & -0.37 & 0.05 & 0.46 \\ \hline
+J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 \\ \hline
+J041055.45+570542.6 & 62.73 & 57.10 & 16 & -32.38 & 4141 & 1.66 & -0.23 & 0.07 & 0.47 \\ \hline
+J035840.66+574934.5 & 59.67 & 57.83 & 17 & -56.06 & 4693 & 2.02 & -0.28 & 0.14 & 0.46 \\ \hline
+J034552.01+595739.3 & 56.47 & 59.96 & 17 & -48.57 & 4627 & 2.07 & -0.38 & 0.16 & 0.41 \\ \hline
+J193130.64+432204.2 & 292.88 & 43.37 & 16 & -92.64 & 4934 & 3.08 & -0.16 & 0.30 & 0.26 \\ \hline
+J042753.62+365550.6 & 66.97 & 36.93 & 8 & -30.08 & 5249 & 2.91 & -0.21 & 0.18 & 0.30 \\ \hline
+J061808.85+313338.2 & 94.54 & 31.56 & 12 & 42.57 & 4970 & 3.03 & -0.15 & 0.10 & 0.55 \\ \hline
+J050740.59+492955.0 & 76.92 & 49.50 & 15 & 18.29 & 3879 & 0.96 & -0.72 & 0.06 & 0.54 \\ \hline
+J050606.74+494925.0 & 76.53 & 49.82 & 25 & -28.78 & 4857 & 2.50 & -0.25 & 0.12 & 0.34 \\ \hline
+J050551.93+493726.0 & 76.47 & 49.62 & 15 & -18.59 & 4961 & 2.85 & -0.47 & 0.07 & 0.27 \\ \hline
+J051046.05+523848.3 & 77.69 & 52.65 & 47 & -46.17 & 4697 & 2.61 & -0.34 & 0.26 & 1.03 \\ \hline
+J041321.95+520135.7 & 63.34 & 52.03 & 19 & -51.35 & 4694 & 2.48 & -0.05 & 0.05 & 0.50 \\ \hline
+J065356.76+344513.1 & 103.49 & 34.75 & 21 & -23.38 & 4533 & 2.46 & -0.00 & 0.15 & 0.28 \\ \hline
+J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 \\ \hline
+J040034.51+472103.8 & 60.14 & 47.35 & 18 & -55.82 & 4708 & 2.39 & -0.01 & 0.10 & 0.65 \\ \hline
+J041304.73+470013.8 & 63.27 & 47.00 & 17 & 19.19 & 4290 & 1.79 & -0.37 & 0.03 & 0.79 \\ \hline
+J035633.86+463749.2 & 59.14 & 46.63 & 17 & -54.93 & 4753 & 2.37 & -0.05 & 0.12 & 0.34 \\ \hline
+J053627.38+581132.8 & 84.11 & 58.19 & 28 & -32.94 & 4457 & 2.52 & 0.28 & 0.05 & 0.49 \\ \hline
+J052516.26+585912.5 & 81.32 & 58.99 & 19 & -75.07 & 4023 & 1.50 & -0.22 & 0.05 & 0.51 \\ \hline
+J034826.25+350123.4 & 57.11 & 35.02 & 100 & -47.97 & 4710 & 2.89 & 0.04 & 0.38 & 4.72 \\ \hline
+J035652.48+325937.2 & 59.22 & 32.99 & 24 & -20.99 & 4038 & 1.38 & -0.31 & 0.08 & 0.55 \\ \hline
+J035345.63+340429.3 & 58.44 & 34.07 & 15 & -34.48 & 4830 & 3.23 & -0.56 & 0.06 & 0.14 \\ \hline
+J042245.32+430359.8 & 65.69 & 43.07 & 16 & -35.08 & 4967 & 2.92 & -0.13 & 0.03 & 0.20 \\ \hline
+J042241.36+414255.6 & 65.67 & 41.72 & 15 & -92.76 & 4975 & 3.32 & -0.66 & 0.02 & 0.27 \\ \hline
+J053148.24+225045.6 & 82.95 & 22.85 & 15 & 11.69 & 3982 & 0.71 & -0.84 & 0.08 & 0.63 \\ \hline
+J120844.42-012151.8 & 182.19 & -1.36 & 18 & 143.30 & 4783 & 2.28 & -0.84 & 0.28 & 0.48 \\ \hline
+J091825.49+172114.5 & 139.61 & 17.35 & 11 & 232.04 & 4898 & 2.71 & -1.19 & 0.29 & 0.14 \\ \hline
+J123413.43+160353.7 & 188.56 & 16.06 & 10 & 316.88 & 4734 & 2.63 & -0.99 & 0.03 & 0.17 \\ \hline
+J054656.93+442800.0 & 86.74 & 44.47 & 17 & -41.37 & 4758 & 2.51 & -0.27 & 0.09 & 0.15 \\ \hline
+J053423.46+460026.9 & 83.60 & 46.01 & 21 & -40.77 & 4893 & 2.73 & -0.18 & 0.10 & 0.26 \\ \hline
+J052814.58+511912.4 & 82.06 & 51.32 & 16 & -64.76 & 4344 & 1.95 & -0.06 & 0.10 & 0.51 \\ \hline
+J044403.36+543203.6 & 71.01 & 54.53 & 19 & -71.05 & 4625 & 1.91 & 0.25 & 0.07 & 1.42 \\ \hline
+J043503.82+552514.6 & 68.77 & 55.42 & 19 & 9.59 & 4704 & 2.48 & -0.11 & 0.04 & 0.60 \\ \hline
+J043418.64+535250.2 & 68.58 & 53.88 & 17 & -141.15 & 4204 & 1.44 & -0.64 & 0.19 & 0.76 \\ \hline
+J070937.38+201517.2 & 107.41 & 20.25 & 9 & 148.10 & 3770 & 0.19 & -1.24 & 0.04 & 0.46 \\ \hline
+J064032.35+335207.5 & 100.13 & 33.87 & 8 & -34.48 & 4717 & 2.28 & -0.44 & 0.24 & 0.24 \\ \hline
+\end{tabular}
+\caption{Remaining candidates}
+\label{Resttab}
+\end{table}
+\end{comment}
 

### 2018-01-15 article/ms.tex
Added csv data for Mucciarreli and C+K as well as code for the plot of these overlaid. abundances from las campanas are included also.

@@
 The data set of \LamostGiants\ \lamost\ giants was prepared by \citet{ho2017} for use with the supervised machine learning code \tc.
-The \lamost\ data was shifted to rest frame and pseudo-continuum-normalised \ before it was resampled to a common uniform wavelength grid between 3905\,\AA\ and 9000\,\AA.
+The \lamost\ data was shifted to rest frame and pseudo-continuum-normalised before it was resampled to a common uniform wavelength grid between 3905\,\AA\ and 9000\,\AA.
 \tc\ was used to infer $\teff$, $\logg$, [Fe/H], and [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ survey through the use of a data-driven spectral model.

### 2018-01-15 article/plotter.py

@@ -28,6 +28,9 @@ plt.close('all')
 mgkarray=np.array(pd.read_csv("Mg-K-candidatesFINALCUT_nonHemmision.csv"))
 globarray=np.array(pd.read_csv("globular_clusters.csv"))
 
+C_K2012=np.array(pd.read_csv("C+K 2012.csv"))
+Muc2012=np.array(pd.read_csv("Mucciarelli 2012.csv"))
+LC=np.array(pd.read_csv("LasCampmgkabundances.csv"))
 Teff=mgkarray[:,1]
 logg=mgkarray[:,2]
 metalicity=mgkarray[:,3]
@@ -36,6 +39,19 @@ mgkl=mgkarray[:,-2]
 mgkb=mgkarray[:,-1]
 globl=globarray[:,4]
 globb=globarray[:,5]
+
+C_KMg=C_K2012[:,1]
+C_KMgu=C_K2012[:,2]
+C_KK=C_K2012[:,3]
+#C_KKu=C_K2012[:,4] (no uncertainties known)
+MucMg=Muc2012[:,1]
+MucMgu=Muc2012[:,2]
+MucK=Muc2012[:,3]
+MucKu=Muc2012[:,4]
+
+LCMg=LC[:,1]
+LCK=LC[:,2]
+
 
 catalog = lamost.load_catalog()
 wavelengths = lamost.common_wavelengths
@@ -80,6 +96,32 @@ plt.xticks(np.arange(0, 361, 45)[::1])
 plt.xlabel('Galactic Longitude')
 plt.ylabel('Galactic Lattitude')
 plt.legend(loc='lower right')
+plt.show()
+
+
+plt.figure(4)
+
+plt.scatter(C_KMg, C_KK, label= "Kirby & Cohen 2012", s=15)
+#plt.errorbar(C_KMg, C_KK, xerr=C_KMgu, linestyle="None")
+(_, caps, _)=plt.errorbar(C_KMg, C_KK, xerr=C_KMgu, linestyle="None", linewidth=1, capsize=4,zorder=4)
+for cap in caps:
+    cap.set_markeredgewidth(.8)
+    
+plt.scatter(MucMg, MucK, label= "Mucciarreli 2012", s=15)
+#plt.errorbar(MucMg, MucK, xerr=MucMgu, yerr=MucKu, linestyle="None",linewidth=1)
[…]

### 2018-01-15 article/ms.tex
reworded much of the abstract

@@
 
-Stellar absorption spectra act as a fossil record of the environment of primordial conditions.
-Stars displaying unusual elemental abundances provide are of particular interest, as they offer the opportunity to learn about astrophysical events and objects that may no longer exist in our Galaxy.
-Stars with depleted Mg and enhanced K abundances present just such an opportunity.
-Thus far found only in two massive globular clusters NGC 2419 and NGC 2808, the primordial origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
-A satisfactory explanation for this signature has potential ramifications on theories of globular cluster formation and the long-standing problem of the underestimation of even galaxy-normal K abundances.
+Stellar absorption spectra act as a record of the primordial conditions within which the star formed.
+Stars displaying unusual elemental abundances provide are of particular interest; these rare stars often offer clues about astrophysical events and objects that may no longer exist in our galaxy.
+Stars with  depleted Mg and enhanced K abundances have thus far found only in two massive globular clusters: NGC 2419 and NGC 2808.
+The primordial origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
+A satisfactory explanation for this signature has potential to influence theories of globular cluster formation and shed light on the long-standing problem of the underestimation of even stars with typical galactic values of K abundances.
 The apparent exclusivity of this Mg-K anti-correlation to globular clusters is the focus of this survey.
-Here we present 113 field stars showing depleted Mg and enhanced K, though none with abundances extreme enough to be comparable to the stars identified in NGC 2419.
+Here we present 113 candidate field stars (from a sample size of \LamostGiants \ giants from \lamost \ DR2) that have spectra consistent with anomalously depleted Mg and enhanced K abundances, though none with abundances comparable to the stars identified in NGC 2419.
 

### 2018-01-16 article/ms.tex
added K vs Mg plot and relevant files, begun discussion points

@@
 Stars displaying unusual elemental abundances provide are of particular interest; these rare stars often offer clues about astrophysical events and objects that may no longer exist in our galaxy.
-Stars with  depleted Mg and enhanced K abundances have thus far found only in two massive globular clusters: NGC 2419 and NGC 2808.
-The primordial origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
-A satisfactory explanation for this signature has potential to influence theories of globular cluster formation and shed light on the long-standing problem of the underestimation of even stars with typical galactic values of K abundances.
+Stars with  depleted Mg and enhanced K abundances, measured as [Mg/Fe] and [K/Fe], have thus far only been found in the two massive globular clustersr NGC 2419 and NGC 2808.
+The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
+A satisfactory explanation for this signature has potential to influence theories of globular cluster formation and shed light on the long-standing problem of the underestimation of stars with typical galactic values of [K/Fe].
 The apparent exclusivity of this Mg-K anti-correlation to globular clusters is the focus of this survey.
-Here we present 113 candidate field stars (from a sample size of \LamostGiants \ giants from \lamost \ DR2) that have spectra consistent with anomalously depleted Mg and enhanced K abundances, though none with abundances comparable to the stars identified in NGC 2419.
+Here we present 113 candidate field stars (from a sample size of \LamostGiants \ giants from \lamost \ DR2) that have spectra consistent with anomalously depleted [Mg/Fe] and enhanced [K/Fe] abundances, though none with abundances comparable to the extreme population of stars identified in NGC 2419.
 
@@
     \caption{Poster Child}
-    \label{mhist}
+    \label{posterchild}
 \end{figure}
@@
     \caption{Effective temperature, log surface gravity, metalicity}
-    \label{mhist}
+    \label{tefflogg}
 \end{figure}
@@
     \caption{Galactic coordinates for Mg-K stars and known globular clusters}
-    \label{mhist}
+    \label{galcord}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{KvsMgab.png}
+    \caption{[Comparison of K vs Mg abundances with NGC 2419 and NGC 2808.}
+    \label{KvsMg}
 \end{figure}
@@
 \end{table}
+
+\section{Discussion}
+
+\begin{itemize}
+\item Association with globular clusters: basically all stars (will have to redo plot and search for the new tables) are not associated with globular clusters.
+in terms of those which are kinda close in GC, state which cluster(s) they could be associated with.
+We lack dynamics information, but potentially the next data release from GAIA will help with that.
+Check with apparent magnitudes to see if the stars are consistent in that regard.
+
+\item Metalicity: the candidate stars are found at a wide range of metalicities, from \todo{-1.4<[Fe/H]<0.3}. for comparison, NGC 2808 and NGC 2419 have [Fe/H] ~-2.
+
+\item Abundances: K abundances are lower and Mg abundances are higher than those in the extreme population of 2419.
+however, they \textit{are} still (perhaps) significantly K enhanced and Mg depleted, perhaps the first field stars identified as such.
+However, since only 113 out of \LamostGiants stars
+
+\end{itemize}
 

### 2018-01-16 article/plotter.py

@@ -30,6 +30,10 @@ globarray=np.array(pd.read_csv("globular_clusters.csv"))
 
 C_K2012=np.array(pd.read_csv("C+K 2012.csv"))
 Muc2012=np.array(pd.read_csv("Mucciarelli 2012.csv"))
+
+ngc2808=np.array(pd.read_csv("NGC2808 Muc 2015.csv"))
+
+
 LC=np.array(pd.read_csv("LasCampmgkabundances.csv"))
 Teff=mgkarray[:,1]
 logg=mgkarray[:,2]
@@ -48,6 +52,9 @@ MucMg=Muc2012[:,1]
 MucMgu=Muc2012[:,2]
 MucK=Muc2012[:,3]
 MucKu=Muc2012[:,4]
+
+ngc2808Mg=ngc2808[:,0]
+ngc2808K=ngc2808[:,1]
 
 LCMg=LC[:,1]
 LCK=LC[:,2]
@@ -101,26 +108,40 @@ plt.show()
 
 plt.figure(4)
 
-plt.scatter(C_KMg, C_KK, label= "Kirby & Cohen 2012", s=15)
+plt.scatter(C_KMg, C_KK, label= " NGC 2419 Kirby & Cohen 2012", s=25, c='gray')
 #plt.errorbar(C_KMg, C_KK, xerr=C_KMgu, linestyle="None")
-(_, caps, _)=plt.errorbar(C_KMg, C_KK, xerr=C_KMgu, linestyle="None", linewidth=1, capsize=4,zorder=4)
+(_, caps, _)=plt.errorbar(C_KMg, C_KK, xerr=C_KMgu, linestyle="None", linewidth=.8, capsize=4,zorder=4, c='gray')
 for cap in caps:
     cap.set_markeredgewidth(.8)
     
-plt.scatter(MucMg, MucK, label= "Mucciarreli 2012", s=15)
+plt.scatter(MucMg, MucK, label= "NGC 2419 Mucciarreli 2012", s=25, c='gray', marker='s')
 #plt.errorbar(MucMg, MucK, xerr=MucMgu, yerr=MucKu, linestyle="None",linewidth=1)
-(_, caps, _) = plt.errorbar(MucMg, MucK, xerr=MucMgu, yerr=MucKu, linestyle="None",linewidth=1, capsize=4, zorder=3)
[…]

### 2018-01-17 article/ms.tex
additional discussion points

@@
 however, they \textit{are} still (perhaps) significantly K enhanced and Mg depleted, perhaps the first field stars identified as such.
-However, since only 113 out of \LamostGiants stars
+Only 113 out of \LamostGiants \ stars were found to be good candidates for enhanced K and reduced Mg.
+Likely not products of the same process as acted in NGC 2419, but possibly?
+Main implications: searched \LamostGiants \ stars, but didn't find any that we could say 'yeah that looks like it could have came from the same process that caused NGC 2419's signiature'.
+
+\item What does this abundance imply about pollution mechanisms?
+depends whether we decide that our identified stars were produced by the same process or not.
+IF they weren't produced by the same process, then this is further evidence that the event/object was unique to old globular clusters.
+If however they WERE produced by the same process, but just weren't as polluted (the primordial material was made up of a lower fraction of anomalously enriched material), then the implications are a bit weird.
+We found stars across a large range of metalicities.
+Diferent formation times is also implied by metalicity.
+
+\item spread in Logg and Teff: the fact that we see stars across a range of Teff and Logg eliminates the idea that the candidates as all being so called 'red-clump' red giants or any other phenomena specific to certain RGB stages/ types.
+
+\item working hypothesis (John, Tout): We decouple the Mg and the K.
+A SAGB binary with a smaller companion.
+the SAGB produces K, which then accretes to the companion.
+the companion will evolve long after the SAGB explodes, then will either (depending on mass/temperature) undergo hot bottom burning or it won't.
+If it does?
+undergo hot bottom burning then Na will be produced.
+If it doesn't?
+undergo hot bottom burning then Na won't be produced.
+other predictions: O shouldn't?
+be be there, nor should C or N as they get turned into Na.
+This scenario is plausible to happen in the MW disk, throughout an extended period of time, therefore being consistent with the spread in metalicities that we see.
+Look at iliadis 2017 to see some other implications of hot bottom burning in AGB (low temperature) star and SAGB (high temp) burning.
+
+\item We're not allowed to have a single big event in NGC 2419 and then clumps of material floating round the galaxy and occasionally forming a star.
+one good reason: its really distant form the galaxy.
+thus our K enhancements must source from a star inside the galaxy, NOT a globular cluster.
+this raises some interesting issues.
+If the source of our K enhancements is the same as NGC 2419, where we had Mg depletions that then were later covered up/ reduced in magnitude in the case of our disk stars, then the big question i'd want answered is: So we have this thing that only occurs in 2419...
+and the MW disk...
+throughout the life of the MW disk...
+but not in any other globular clusters.
+seems a bit picky...
+
+\item novae: the mass budged problem is much worse for NGC 2419 than \cite{iliadis2016} made it appear, and is very unlikely to be responsible for the phenomena.
+finding even more K enhanced stars in the MW doesn't change this.
 

### 2018-01-18 article/ms.tex
Discussion progressed to a slightly more structured puddle

@@
 	\includegraphics[width=\columnwidth]{KvsMgab.png}
-    \caption{[Comparison of K vs Mg abundances with NGC 2419 and NGC 2808.}
+    \caption{[Comparison of K vs Mg abundances with NGC 2419 and NGC 2808. The dotted divisor line is present simply as a visual aide.}
     \label{KvsMg}
@@
 \section{Discussion}
+\subsection{Association with globular clusters}
+
+Of the 113 candidate sample identified, J074807.22+261514.2 appears closet to a globular cluster, and even then at significant angular distance of 2.54 $\deg$ .
+Although little is known about Ko 2 other than that it is an extremely faint halo cluster \citep{koposov2007} but it would be expected that a star from such a cluster would have very low metalicty, while J074807.22+261514.2 has $ \text{[Fe/H]} = -0.24 \pm 0.07$  and would be unlikely to appear in a survey such as \lamost , which favours detection of low magnitude stars.
+In particular, none of the stars appear to be associated with NGC 2419, NGC 2808 or $\omega$ Centauri.
+Only 4 stars cross matched with GAIA's DR1, and when backwards time integrated using GAIA's data with the GALA package they exhibited orbits consistent with field stars, with none of the eccentricity and high velocity typical of a star from a disrupted cluster.
+
+The spread of metalicity shown in Figure \ref{mhist} further supports the sample being made up of field stars, displaying a spread reflective of the original \LamostGiants \ sample of giants.
+If there was a significant influence in the sample from disrupted stars from another as yet unidentified cluster containing the Mg-K anti-correlation, a significant deviation in the metalicity histogram from the base \lamost \  sample of giants should be visible.
+
+There is no evidence at this time supporting any stars from this sample having origins in globular clusters, while Figure \ref{galcord} clearly indicates that the positions of the candidates are consistent with field stars in the disk of the galaxy.
+The spread in metalicity shown in Figure \ref{mhist}, with significant numbers of high metalicity stars, further supports the conclusion that the sample is comprised of field stars presumably formed at different times throughout the lifetime of the Milky Way.
 
 \begin{itemize}
-\item Association with globular clusters: basically all stars (will have to redo plot and search for the new tables) are not associated with globular clusters.
+\item Association with globular clusters: basical
+ly all stars (will have to redo plot and search for the new tables) are not associated with globular clusters.
 in terms of those which are kinda close in GC, state which cluster(s) they could be associated with.
@@
 Check with apparent magnitudes to see if the stars are consistent in that regard.
+\end{itemize}
 
-\item Metalicity: the candidate stars are found at a wide range of metalicities, from \todo{-1.4<[Fe/H]<0.3}. for comparison, NGC 2808 and NGC 2419 have [Fe/H] ~-2.
+\subsection{Abundances}
 
+Figure \ref{KvsMg} shows the abundances for the 113 star sample overlaid with with abundances from NGC 2419 and NGC 2808 \citep{cohenkirby2012,mucciarelli2012,mucciarelli2015}.
+The sample is plotted against [$\alpha$/Fe] as reliable abundances for [Mg/Fe] were impossible to accurately obtain from the LAMOST data.
+[$\alpha$/Fe] is likely representative of [Mg/Fe], and at the very least serves as an (approximate) upper limit for [Mg/Fe].
+The use of [$\alpha$/Fe] as a proxy for [Mg/Fe] is supported by the [Mg/Fe] measurements from the high resolution spectra obtained, with the [Mg/Fe] measurements from \textit{Magellan} being similar to the [$\alpha$/Fe] abundances from \tc.
+
+The candidates exhibit K abundances which are lower and probable Mg abundances which are higher than the Mg extreme population found in NGC 2419.
+In general they appear to fall between the two populations.
+
+Relative to typical galactic ranges of [Mg/Fe] and [K/Fe], only the [K/Fe] appears anomalous from Figure \ref{KvsMg}.
+Galactic values for [K/Fe] are observed around $0.3 \pm 0.2$ dex, while the \lamost \ sample of stars varies from around 0.8-1.3, and the \textit{Magellan} abundance for candidate star J091825.49+172114.5 having [K/Fe] $\approx$ 1.54.
+
+The implications of the calculated abundances are intriguing.
+The fact that from a sample of \LamostGiants field stars none were found that exhibited the extreme abundance pattern of NGC 2419 further and perhaps definitively cements the clusters uniqueness.
+
+However, the 113 candidate pool identified represents a collection of stars that display significantly enhanced [K/Fe] and, despite indications of the flux signals (see Figure \ref{posterchild}), apparently normal levels of [Mg/Fe].
+Certainly, no Mg depletion of similar scale to NGC 2419 or even the substantially weaker NGC 2808 signature is evident.
+
+\todo{IMPORTANT: Discuss with andy the implications of this.
+We ran filters that were meant to pick up stars depleted in Mg AND enriched in K.
+instead, it seems to have picked up stars that are enriched in K, but exhibit galaxy-normal levels of Mg.
+Surely we need an explanation for this result to our filter query?}
+
+\begin{itemize}
 \item Abundances: K abundances are lower and Mg abundances are higher than those in the extreme population of 2419.
@@
 Main implications: searched \LamostGiants \ stars, but didn't find any that we could say 'yeah that looks like it could have came from the same process that caused NGC 2419's signiature'.
+
+\end{itemize}
+
+\subsection{A new approach to the Mg-K problem}
+Significantly enhanced [K/Fe] is rare; significantly enhanced [K/Fe] without an accompanying depletion of [Mg/Fe] is unknown.
+Further, the candidate stars are spread across a wide range of metalicities.
+
+This spread in metalicity is important; it strongly implies that the process responsible for this signature, rare as it is, is not necessarily tied to a certain epoch in the history of our galaxy.
+Rather, these stars appear to be continuously forming from successive generations of stars.
+
+This immediately eliminates as a polluter candidate any theoretical hyper-massive Population III star we care to come up a with.
+While such an object might be remotely plausible in the context of NGC 2419, it cannot explain the enhanced K abundances observed in the disk.
+
+As emphasized by \cite{prantzos2017}, a large part of the problem presented by the signiatures of NGC 2419 and NGC 2808 is obtaining both a depletion Mg and an enhancement in K.
+Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{23} Na} and through Mg-Al chains at temperatures around 75 MK, obtainable through hot-bottom burning in AGB stars while it takes temperatures upwards of 150 MK to produce K, temperatures possibly obtained at the bottom of the envelope in SAGB stars \citep{iliadis2016}.
+This implies that the Mg depletion and K enrichment could occur at separate sites.
+
+One possible scenario that could produce a large K enhanced signature in a few select stars in the Milky Way would be a binary in which one of the stars is a SAGB star.
+Then, if this SAGB star were to produce K, the star may accrete onto its smaller companion which would continue to evolve long after the SAGB star is gone.
+This companion would then, depending on its mass, either undergo hot-bottom burning or, more probably, would not.
+If the companion star had sufficient mass to undergo hot bottom burning, then Na should be enhanced from production from \ce{^24 Mg} and \ce{^22 Ne}.
+
+The chief advantage of this scenario is that it allows for K abundances to appear at a range of metalicities, and accounts explaining the significant minority population of the stars which show Na enhancements.
+
+It does not, however, account for the uniqueness of the signal to NGC 2419 and NGC 2808 among globular clusters, nor does it satisfactorily explain why such a large number of stars in NGC 2419 exhibit the Mg-K anti-correlation.
+It seems probable that the K enhancements evident in the identified population of candidate stars are from a different source than the Mg-K anti-correlation seen in NGC 2419.
+\begin{itemize}
 
@@
 Diferent formation times is also implied by metalicity.
-
-\item spread in Logg and Teff: the fact that we see stars across a range of Teff and Logg eliminates the idea that the candidates as all being so called 'red-clump' red giants or any other phenomena specific to certain RGB stages/ types.
 
@@
 finding even more K enhanced stars in the MW doesn't change this.
+
+\end{itemize}
+
+\begin{itemize}
+
+\item spread in Logg and Teff: the fact that we see stars across a range of Teff and Logg eliminates the idea that the candidates as all being so called 'red-clump' red giants or any other phenomena specific to certain RGB stages/ types.
 

### 2018-01-20 article/ms.tex
Discussion refinements, and insertion of my thoughts of the implications of the gradient with [K/Fe] versus Fe

--- 2018-01-17 article/ms.tex
@@
 \usepackage{float}
-
+\usepackage{gensymb}
 \usepackage{color}
@@
 \tc\ was used to infer $\teff$, $\logg$, [Fe/H], and [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ survey through the use of a data-driven spectral model.
+Unless otherwise stated, these transfered labels are those used throughout this study.
 For details regarding the preparatory work, model generation, and label transfer between the \apogee\ and \lamost\ surveys, the reader is directed to \citet{ho2017}.
@@
 	\includegraphics[width=\columnwidth]{loggteffof113.png}
-    \caption{Effective temperature, log surface gravity, metalicity}
+    \caption{Effective temperature, log surface gravity, metalicity.
+\todo{The large, random spread in $\logg$, $\teff$ and [Fe/H] implies that the candidates are simply stars which have formed from poluted material, rather than any special type of star such as red-clump giants.}}
     \label{tefflogg}
@@
 	\includegraphics[width=\columnwidth]{KvsMgab.png}
-    \caption{[Comparison of K vs Mg abundances with NGC 2419 and NGC 2808.}
+    \caption{[Comparison of K vs Mg abundances with NGC 2419 and NGC 2808. The dotted divisor line is present simply as a visual aide.}
     \label{KvsMg}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{KvsFe.png}
+    \caption{[K/Fe] vs [Fe/H] for the LAMOST data}
+    \label{KvsFe}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{NavsFe.png}
+    \caption{[Na/Fe] vs [Fe/H] for the LAMOST data.
+\todo{NOTE: NONE OF THE Na ENHANCEMENTS ARE IN OUR MOST METAL POOR STARS.
+This is interesting because Na enhancements are associated with some globular cluster populations, but here we're seeing sodium enhancements in intermediate-high metalicity stars, with the non-Na population spanning the full range of metalicities.}}
+    \label{NavsFe}
 \end{figure}
@@
 \section{Discussion}
+\subsection{Association with globular clusters}
+
+Of the 113 candidate sample identified, J074807.22+261514.2 appears closest in the sky to a globular cluster, and even then still at a significant angular separation of 2.54\degree .
+Although little is known about Ko 2 other than that it is an extremely faint halo cluster \citep{koposov2007}, it would be expected that a star from such a cluster would have very low metalicty, while J074807.22+261514.2 has $ \text{[Fe/H]} = -0.24 \pm 0.07$.
+Stars from Ko 2 would be unlikely to appear in a survey such as \lamost, which heavily favours detection of bright field stars.
+
+None of the stars appear to be associated with NGC 2419, NGC 2808 or $\omega$ Centauri.
+Only 4 stars were also contained within \textit{GAIA}'s DR1, and when backwards time integrated using GAIA's data with the GALA package they exhibited orbits consistent with field stars, with none of the eccentricity and high velocity typical of a star disrupted from a globular cluster.
+
+The spread of metalicity shown in Figure \ref{mhist} further supports the sample being made up of field stars, displaying a spread reflective of the original \LamostGiants \ sample of giants.
+If there was a significant influence in the sample from disrupted stars from another as yet unidentified globular cluster containing the Mg-K anti-correlation, a significant deviation in the metalicity histogram from the base \lamost \ sample of giants should be visible.
+
+There is no evidence at this time supporting any stars from this sample having origins in globular clusters, while Figure \ref{galcord} clearly indicates galactic latitudes of the candidates are consistent with field stars in the disk of the galaxy.
+The spread in metalicity shown in Figure \ref{mhist}, with significant numbers of high metalicity stars, further supports the conclusion that the sample is comprised of field stars presumably formed at different times throughout the lifetime of the Milky Way.
 
@@
 Check with apparent magnitudes to see if the stars are consistent in that regard.
+\end{itemize}
 
-\item Metalicity: the candidate stars are found at a wide range of metalicities, from \todo{-1.4<[Fe/H]<0.3}. for comparison, NGC 2808 and NGC 2419 have [Fe/H] ~-2.
+\subsection{Abundances}
 
+Figure \ref{KvsMg} shows [K/Fe]  for the 113 star sample plotted against $[\alpha$/Fe] overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012,mucciarelli2012,mucciarelli2015}.
+[K/Fe] vs [Mg/Fe] for the three stars from the sample observed using \textit{Magellan} are also plotted.
+$[\alpha$/Fe] is used as an upper limit for [Mg/Fe] for the 113 star sample as [Mg/Fe] proved impossible to obtain from the \lamost \ spectra.
+The use of [$\alpha$/Fe] as a proxy for [Mg/Fe] is supported by the [Mg/Fe] measurements from the high-resolution spectra obtained, these being similar to the [$\alpha$/Fe] abundances from \tc.
+
+The candidates' [K/Fe] are generally lower than the extreme Mg-depleted population in NGC 2419, but higher than the Mg-normal population.
+It is perhaps noteworthy that both populations identified in NGC 2808 have significantly lower levels of [K/Fe] than these stars.
+Levels of [$\alpha$/Fe] fall within the lower limits of the Mg-normal population of both clusters, although as this represents only an upper limit the exact level of Mg depletion for the candidates is unclear.
+The [Mg/Fe] abundances derived from \textit{Magellan}'s high resolution spectra imply that at most a small depletion relative to the Mg-normal population is present.
+
+A similar relationship emerges when comparing with typical galactic figures for [K/Fe] and [Mg/Fe], taken from \cite{kobayashi2011}.
+Only the [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$ dex, while the \lamost \ sample of stars varies from around 0.8-1.3, and the \textit{Magellan} abundance for candidate star J091825.49+172114.5 having [K/Fe] $\approx$ 1.54.
+
+The sample's [K/Fe] also exhibits an interesting anti-correlation with total metalicity, shown in Figure \ref{KvsFe}, which is absent from measurements in the Milky Way.
+This is consistent with a (somewhat) constant level of [K/H] between each star, causing [K/Fe]to fall with increasing metalicity.
+
+In contrast, [$\alpha$/Fe] varies from around 0-0.3 dex in the \lamost \ sample, similar to galactic levels of [Mg/Fe], which vary with metalicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}.
+No variation with metalicity is observed within the \lamost sample.
+
+[Na/Fe] was also measured for the \lamost\ data, shown in Figure \ref{NavsFe}. \todo{See caption for relevant discussion point.}
+
+The implications of the calculated abundances are intriguing.
+The fact that from such a large sample of field stars none were found that replicated the extreme abundance pattern of NGC 2419 further and perhaps definitively cements the clusters uniqueness.
+
+However, the 113 star candidate pool of K enhanced and potentially Mg depleted stars identified represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels and a range of metalicities.
+It seems likely that whatever process is responsible for these anomalous field stars is similar to whatever caused the unusual stellar populations in NGC 2419 and NGC 2808.
+
+\begin{itemize}
 \item Abundances: K abundances are lower and Mg abundances are higher than those in the extreme population of 2419.
@@
 Main implications: searched \LamostGiants \ stars, but didn't find any that we could say 'yeah that looks like it could have came from the same process that caused NGC 2419's signiature'.
+
+\end{itemize}
+
+\subsection{A working hypothesis}
+Significantly enhanced [K/Fe] is rare; significantly enhanced [K/Fe] without an accompanying depletion of [Mg/Fe] is unknown.
+Further, the candidate stars are spread across a wide range of metalicities.
+
+This spread in metalicity is important; it strongly implies that the process responsible for this signature, rare as it is, is not necessarily tied to a certain epoch in the history of our galaxy.
+Rather, these stars appear to be continuously forming from successive generations of stars.
+
+\todo{But...
+If real, the [K/Fe] trend with metalicity might actually imply the exact opposite.
+Perhaps a single event enriching a sufficiently large cloud of gas occurs.
+Stars are formed from the enriched gas, then die, releasing more metal to the gas, increasing iron etc, but leaving the hard-to-produce K abundance at around the same level relative to H, which would make up the majority of the gas.
+Then the successive stars formed from this material would have a lower value of [K/Fe], but a higher value of [Fe/H].
+Problems this idea might have might include: how long a star forming gas ball can really last in the disk?
+Plus, if all these stars are forming in the same place, there sure is a lot of them and they don't seem to be associated with only one place, their all over the sky.
+This idea is actually fairly compatible with NGC 2419 though; one event (still utterly mysterious) providing material from which a generation of stars formed with enhanced K.
+Since it was just a globular cluster, and was lucky to have even 2 generations of stars, such a trend in metalicity would be non existent (seeing as there is no metalicity spread within the cluster anyway).
+In short, the metalicity gradient supports a single epoch of K formation at least, if not a single localised event, rather than the continuous production of K throughout the lifetime of the galaxy.
+The real question is whether or not it is real, something that we are unlikely to be able to answer.}
+
+This immediately eliminates as a polluter candidate any theoretical hyper-massive Population III star that might be imagined.
+While such an object might be plausible in the context of NGC 2419, it cannot explain the enhanced K abundances observed in the disk at such a spread in metalicity.
+
+As emphasized by \cite{prantzos2017}, a large part of the problem presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion Mg and an enhancement in K.
+Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{23} Na} and through Mg-Al chains at temperatures around 75 MK, obtainable through hot-bottom burning in AGB stars while it takes temperatures upwards of 150 MK to produce K, temperatures potentially obtainable at the bottom of the envelope in SAGB stars \citep{iliadis2016}.
+This implies that the Mg depletion and K enrichment occur at separate sites.
+
+One possible scenario that could produce a large K enhanced signature would be a binary in which one of the stars is a SAGB star.
+Then, if this SAGB star were to produce K, the star may accrete onto its smaller companion which would continue to evolve long after the SAGB star is gone.
+This companion would then, depending on its mass after accretion, either undergo hot-bottom burning or, more probably, would not.
+If the companion star had sufficient mass to undergo hot bottom burning, then Na should be enhanced from production from \ce{^24 Mg} and \ce{^22 Ne}.
+
+\todo{Gain a much clearer picture about where Mg fits into all of this.
+NGC 2419 shows a very clear Mg division.
+However, there are only 2 generations of stars.
+I need to find out if its possible that such a clear Mg division would survive another generation; that is, when the Mg-depleted stars die, they release metals, including the Mg they formed in the core (assuming they were big enough).
+would this Mg released obliterate the signal after a generation?
+that would be nice and consistent with the data, and explain why we're not seeing a strong Mg depletion in our stars; that would only happen in the generation imediately following the enrichment of the gas with Mg-depleted material.
+Even better, because, unlike Mg which is easy to form, K is hard to form, the K signature in the material would be preserved through successively more metal rich generations of star forming material.}
+
+This scenario allows for K abundances to appear at a range of metalicities, as this scenario could play out throughout the life of the Milky Way.
+It also  accounts for the significant minority population of the stars which show Na enhancements.
+
+It does not, however, account for the uniqueness of the signal to NGC 2419 and NGC 2808 among globular clusters, nor does it satisfactorily explain why such a large proportion of stars in NGC 2419 exhibit the Mg-K anti-correlation.
+
+\begin{itemize}
 
@@
 finding even more K enhanced stars in the MW doesn't change this.
+
+\end{itemize}
+
+\subsection{My thoughts on an explanation (insatisfactory and incomplete regarding the identity of the poluter star(s)) consistent with the data}
+
+Some unknown event or events that can only occur in very metal poor environments happens. This leaves gas which can form stars with depleted Mg and enhanced K.
+
+The generation of stars that forms directly from this gas carries this signiature, and displays a significant reduction in Mg abundance and enhancement in K abundance similar to NGC 2419.
+Call this Generation 2.
+
+When the big hot stars of Generation 2 die however, they release metals into the this gas, including Mg, which is easy to form, but NOT K, which is hard to form.
+The Mg depletion originally carried in this gas relative to the original levels of iron is now harder to detect, obscured by the influx of Mg from Generation 2, but the K enhancement is still relatively easy to detect, having only been reduced relative to iron by the total amount of iron released.
+
+As this cycle continues, [K/Fe] would become lower and lower, approaching 'regular' galactic levels, while depletions in [Mg/Fe] would quickly very very faint.
+
+This cycle allows for the Mg depletions to be preserved in globular clusters, where your lucky to get 2 generations of stars forming as the cluster lacks the gravity to hold on to sufficient gas for many generations of star.
+But it also allows the Mg signal to effectively be lost within the disc of the galaxy, where many generations of stars may form.
+
+\begin{itemize}
+
+\item spread in Logg and $\teff$: the fact that we see stars across a range of $\teff$ and Logg eliminates the idea that the candidates as all being so called 'red-clump' red giants or any other phenomena specific to certain RGB stages/ types.
 

### 2018-01-22 article/ms.tex
Draft discussion complete. Abstract not updated with conclusions, nor is conclusions section written.

--- 2018-01-17 article/ms.tex
@@
 	\includegraphics[width=\columnwidth]{KvsMgab.png}
-    \caption{[Comparison of K vs Mg abundances with NGC 2419 and NGC 2808.}
+    \caption{[Comparison of K vs Mg abundances with NGC 2419 and NGC 2808. The dotted divisor line is present simply as a visual aide.}
     \label{KvsMg}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{KvsFe.png}
+    \caption{[K/Fe] vs [Fe/H] for the LAMOST data}
+    \label{KvsFe}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{NavsFe.png}
+    \caption{[Na/Fe] vs [Fe/H] for the LAMOST data.}
+    \label{NavsFe}
 \end{figure}
@@
 \section{Discussion}
+\subsection{Association with globular clusters}
+J074807.22+261514.2 is the closest star from the sample in the sky to a globular cluster, at a 2.54\degree separation from Ko 2.
+Little is known about Ko 2 other than that it is an extremely faint halo cluster \citep{koposov2007}; it would be expected that a star from such a cluster would have very low metalicty, while J074807.22+261514.2 has $ \text{[Fe/H]} = -0.24 \pm 0.07$.
+Stars from Ko 2 would be unlikely to appear in a survey such as \lamost, which favours detection of bright field stars.
 
-\begin{itemize}
-\item Association with globular clusters: basically all stars (will have to redo plot and search for the new tables) are not associated with globular clusters.
-in terms of those which are kinda close in GC, state which cluster(s) they could be associated with.
-We lack dynamics information, but potentially the next data release from GAIA will help with that.
-Check with apparent magnitudes to see if the stars are consistent in that regard.
+None of the stars appear to be associated with NGC 2419, NGC 2808 or $\omega$ Centauri.
 
-\item Metalicity: the candidate stars are found at a wide range of metalicities, from \todo{-1.4<[Fe/H]<0.3}. for comparison, NGC 2808 and NGC 2419 have [Fe/H] ~-2.
+Only 4 stars were contained within \textit{GAIA}'s DR1, and when backwards time integrated using GAIA's data with the GALA dynamics package for Python, they exhibited orbits consistent with field stars, with none of the eccentricity and high velocity typical of a star disrupted from a globular cluster.
 
-\item Abundances: K abundances are lower and Mg abundances are higher than those in the extreme population of 2419.
-however, they \textit{are} still (perhaps) significantly K enhanced and Mg depleted, perhaps the first field stars identified as such.
-Only 113 out of \LamostGiants \ stars were found to be good candidates for enhanced K and reduced Mg.
-Likely not products of the same process as acted in NGC 2419, but possibly?
-Main implications: searched \LamostGiants \ stars, but didn't find any that we could say 'yeah that looks like it could have came from the same process that caused NGC 2419's signiature'.
+The spread of metalicity shown in Figure \ref{mhist} further supports the sample being made up of field stars.
+The distribution reflects the original \LamostGiants \ sample of giants from which the candidates were drawn.
+Thus, we conclude that the candidates are not particular to any specific metalicity.
 
-\item What does this abundance imply about pollution mechanisms?
-depends whether we decide that our identified stars were produced by the same process or not.
-IF they weren't produced by the same process, then this is further evidence that the event/object was unique to old globular clusters.
-If however they WERE produced by the same process, but just weren't as polluted (the primordial material was made up of a lower fraction of anomalously enriched material), then the implications are a bit weird.
-We found stars across a large range of metalicities.
-Diferent formation times is also implied by metalicity.
+There is no evidence at this time supporting any stars from this sample having origins in globular clusters, while Figure \ref{galcord} clearly indicates galactic latitudes of the candidates are mostly consistent with field stars in the disk of the galaxy.
+The spread in metalicity shown in Figure \ref{mhist}, with significant numbers of high metalicity stars, further supports the conclusion that the sample is comprised mainly of field stars formed at different times throughout the lifetime of the Milky Way.
 
-\item spread in Logg and Teff: the fact that we see stars across a range of Teff and Logg eliminates the idea that the candidates as all being so called 'red-clump' red giants or any other phenomena specific to certain RGB stages/ types.
+\subsection{Abundances}
 
-\item working hypothesis (John, Tout): We decouple the Mg and the K.
-A SAGB binary with a smaller companion.
-the SAGB produces K, which then accretes to the companion.
-the companion will evolve long after the SAGB explodes, then will either (depending on mass/temperature) undergo hot bottom burning or it won't.
-If it does?
-undergo hot bottom burning then Na will be produced.
-If it doesn't?
-undergo hot bottom burning then Na won't be produced.
-other predictions: O shouldn't?
-be be there, nor should C or N as they get turned into Na.
-This scenario is plausible to happen in the MW disk, throughout an extended period of time, therefore being consistent with the spread in metalicities that we see.
-Look at iliadis 2017 to see some other implications of hot bottom burning in AGB (low temperature) star and SAGB (high temp) burning.
+Figure \ref{KvsMg} shows [K/Fe]  for the 113 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012,mucciarelli2012,mucciarelli2015}.
+[K/Fe] vs [Mg/Fe] for the three stars from the sample observed using \textit{Magellan} is also shown.
+$[\alpha$/Fe] is used as an upper limit for [Mg/Fe] for the 113 star sample as [Mg/Fe] proved impossible to obtain from the \lamost \ spectra.
+The use of [$\alpha$/Fe] as a proxy for [Mg/Fe] is supported by the [Mg/Fe] measurements from the high-resolution spectra obtained, these being similar to the [$\alpha$/Fe] abundances from \tc.
 
-\item We're not allowed to have a single big event in NGC 2419 and then clumps of material floating round the galaxy and occasionally forming a star.
-one good reason: its really distant form the galaxy.
-thus our K enhancements must source from a star inside the galaxy, NOT a globular cluster.
-this raises some interesting issues.
-If the source of our K enhancements is the same as NGC 2419, where we had Mg depletions that then were later covered up/ reduced in magnitude in the case of our disk stars, then the big question i'd want answered is: So we have this thing that only occurs in 2419...
-and the MW disk...
-throughout the life of the MW disk...
-but not in any other globular clusters.
-seems a bit picky...
+[K/Fe] for the candidate stars is generally lower than that of the extreme Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population.
+It is noteworthy that both populations identified in NGC 2808 have significantly lower levels of [K/Fe] than the candidate stars.
+Levels of [$\alpha$/Fe] fall within the lower limits of the Mg-normal population of both clusters, although as this represents only an upper limit the exact level of Mg depletion for the candidates is unclear.
+The [Mg/Fe] abundances derived from \textit{Magellan}'s high resolution spectra suggest that at most a small depletion relative to the Mg-normal population may be present.
 
-\item novae: the mass budged problem is much worse for NGC 2419 than \cite{iliadis2016} made it appear, and is very unlikely to be responsible for the phenomena.
-finding even more K enhanced stars in the MW doesn't change this.
+A similar relationship emerges when comparing with typical galactic numbers for [K/Fe] and [Mg/Fe], taken from \cite{kobayashi2011}.
+Only the [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$ dex, while the \lamost \ sample of stars varies from around 0.8-1.3, and the \textit{Magellan} abundance for candidate star J091825.49+172114.5 having [K/Fe] $\approx$ 1.54.
 
-\end{itemize}
+The sample's [K/Fe] also exhibits an interesting anti-correlation with total metalicity, shown in Figure \ref{KvsFe}, which is absent from measurements in the Milky Way.
+This is consistent with a (somewhat) constant level of [K/H] between each star, causing [K/Fe] to fall with increasing metalicity.
+It is interesting that the Mg poor population of NGC 2419 appears to fit with this trend.
+
+ However, for reasons related to the use of both a data-driven model and a physical model for calculating abundances, it is possible that this effect is an artefact of processing rather than a physical relation.
+Without further observations of the sample stars, we are unable to say with certainty whether this phenomena is real or not, and so both cases will be treated.
+
+In contrast with the marked departure from galactic values for [K/Fe], [$\alpha$/Fe] varies from around 0-0.3 dex in the \lamost \ sample, similar to galactic levels of [Mg/Fe], which vary with metalicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}.
+No variation with metalicity is observed within the \lamost sample's [$\alpha$/Fe].
+
+[Na/Fe] was also measured for the \lamost\ data, shown in Figure \ref{NavsFe} versus [Fe/H].
+Two distinct populations are observed, with a significant minority of approximately 30\% of the sample having [Na/Fe] > 0.5, significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}.
+It is interesting that the enhanced population does not extend to the lowest metalicities of our sample, as Na enhancements are associated with some globular clusters; thus, we might expect the Na enhanced population to be dominated by the lowest metalicity stars.
+No correlation between [Na/Fe] and the level of [K/Fe] is observed.
+
+The implications of the calculated abundances are intriguing.
+The fact that from such a large sample of field stars none were found that replicated the extreme abundance pattern of NGC 2419 further and perhaps definitively cements the clusters uniqueness.
+
+However, the 113 star candidate pool of K enhanced and potentially Mg depleted stars identified represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels and a range of metalicities.
+It seems likely that whatever process is responsible for these anomalous field stars is similar to whatever caused the unusual stellar populations in NGC 2419 and NGC 2808.
+
+\subsection{Implications on theories regarding the origin of the Mg-K anticorrelation.}
+
+The conclusions that can be drawn from the data hinge on whether or not the relation between [K/Fe] and [Fe/H] shown in Figure \ref{KvsFe} is real.
+For this reason, we deal with both cases, first disregarding the information in Figure \ref{KvsFe}, then assuming the relation to be real.
+
+\subsubsection{Disregarding the anti-correlation of [K/Fe] vs [Fe/H].}
+
+Significantly enhanced [K/Fe] is rare; significantly enhanced [K/Fe] without an accompanying depletion of [Mg/Fe] is unknown.
+Further, the candidate stars are spread across a wide range of metalicities.
+
+This spread in metalicity is important: it strongly implies that the process responsible for this signature, rare as it is, is not necessarily tied to a certain epoch in the history of our galaxy.
+Rather, these stars appear to be continuously forming from successive generations of stars.
+
+This argues against polluter candidates any theoretical hyper-massive Population III star that might be imagined.
+While such an object might be plausible in the context of NGC 2419, it cannot explain the enhanced K abundances observed in the disk at such a large spread in metalicity (assuming here no correlation between [Fe/H] and [K/Fe]), which implies formation of significant amounts K throughout the life of the galaxy.
+
+As emphasized by \cite{prantzos2017}, a large part of the problem presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion Mg and an enhancement in K.
+Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{23} Na} and through Mg-Al chains at temperatures around 75 MK, attainable in hot-bottom burning environments in AGB stars, while it takes temperatures upwards of 150 MK to produce K, temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
+This implies that the Mg depletion and K enrichment occur at separate sites.
+
+One possible scenario that could produce a large K enhanced signature throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is some less massive.
+The SAGB star then produces K, as well as possibly s-process neutron capture elements, and deposits its K rich envelope onto its smaller companion through conventional binary accretion.
+This smaller and companion would continue to evolve long after the SAGB star is gone and, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, would not.
+If the companion star had sufficient mass to undergo hot bottom burning, then Na should be enhanced from production from \ce{^24 Mg} and \ce{^22 Ne}.
+In this scenario, it is this smaller binary companion star that makes up our sample of 113 giants.
+Note that since the envelope in a hot-bottom burning star is well mixed, the spectral signatures of these elements are observable.
+
+This scenario allows for K abundances to appear at a range of metalicities, as this scenario could play out throughout the life of the Milky Way.
+It also  accounts for the significant minority population of the stars which show Na enhancements.
+
+It does not, however, account for the uniqueness of the signal to NGC 2419 and NGC 2808 among globular clusters, nor does it satisfactorily explain why such a large proportion of stars in NGC 2419 exhibit the Mg-K anti-correlation.
+The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is unlikely to say the least.
+
+A direct test of this scenario would be the determination of whether at least most of the sample are binaries with neutron star remnants.
+
+\subsubsection{Implications of the [K/Fe] vs [Fe/H] anti-correlation.}
+
+The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in a region(s) of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases.
+This interpretation is supported by the consistency of the relation with levels of [K/Fe] in NGC 2419.
+
+Here we set out an evolution scenario that could account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419 and our new 113 field star sample.
+
+Suppose some unknown event(s) that can only occur in very metal poor environments occurs. This event results in material depleted in Mg and enhanced in K.
+
+The generation of stars that forms directly from this gas carries this signiature, and displays a significant reduction in Mg abundance and enhancement in K abundance similar to NGC 2419.
+We will label this generation of stars Generation 1.
+
+When the most massive stars of Generation 1 die however, they release metals into the this gas, including Mg, which is easy to form, but \textit{not} K, which is difficult to form.
+The Mg depletion originally carried in this gas relative to the original levels of iron is much harder to detect in the next generation of stars forming from this material, Generation 2, as the original depleted signature is obscured by the influx of Mg from Generation 1.
+The K enhancement however remains relatively easy to detect, having only been reduced relative to iron by the total amount of iron released.
+
+As this cycle continues, [K/Fe] would become lower and lower, approaching 'regular' galactic levels, while depletions in [Mg/Fe] would quickly become very hard to detect.
+
+This cycle allows for the Mg depletions to be preserved in globular clusters, where even the most massive clusters only form around 2 generations of stars, as the clusters lack the gravity to hold on to sufficient gas for many generations of stars.
+But it also allows the Mg signal to effectively be lost within the disc of the galaxy, where many generations of stars may form.
+
+If the [K/Fe] anti-correlation with [Fe/H] is physical, then the presmumed production of anomalously high amounts of K throughout the life of the Milky Way is turned on its head.
+Instead, it can be concluded that the origin of the Mg-K anti-correlation is confined to a certain epoch in the evolution of galaxies and globular clusters.
 

### 2018-01-22 article/ms.tex
Expanded abstract, slightly modified some of the place holder pics

@@
 
-Stellar absorption spectra act as a record of the primordial conditions within which the star formed.
-Stars displaying unusual elemental abundances provide are of particular interest; these rare stars often offer clues about astrophysical events and objects that may no longer exist in our galaxy.
-Stars with  depleted Mg and enhanced K abundances, measured as [Mg/Fe] and [K/Fe], have thus far only been found in the two massive globular clustersr NGC 2419 and NGC 2808.
+Stellar absorption spectra act as a record of the primordial conditions within which the stars formed.
+Stars displaying unusual elemental abundances are of particular interest; these rare stars often offer clues about astrophysical events and objects that may no longer exist in our galaxy.
+Stars with  depleted Mg and enhanced K abundances, measured as [Mg/Fe] and [K/Fe], have thus far only been found in the two massive globular clusters NGC 2419 and NGC 2808.
 The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
-A satisfactory explanation for this signature has potential to influence theories of globular cluster formation and shed light on the long-standing problem of the underestimation of stars with typical galactic values of [K/Fe].
-The apparent exclusivity of this Mg-K anti-correlation to globular clusters is the focus of this survey.
-Here we present 113 candidate field stars (from a sample size of \LamostGiants \ giants from \lamost \ DR2) that have spectra consistent with anomalously depleted [Mg/Fe] and enhanced [K/Fe] abundances, though none with abundances comparable to the extreme population of stars identified in NGC 2419.
+A satisfactory explanation for this signature has potential to influence theories of globular cluster formation and shed light on the long-standing problem of the underestimation of [K/Fe] among even 'normal' field stars in the Milky Way.
+The apparent exclusivity of this Mg-K anti-correlation to globular clusters is the focus of this paper.
+Here we present 113 candidate field stars (from a sample size of \LamostGiants \ giants from \lamost \ DR2) that have spectra consistent with slightly depleted [Mg/Fe] and significantly enhanced [K/Fe] abundances.
+None of these stars have abundances comparable to the extreme population of stars identified in NGC 2419.
+These stars are of a range of metalicities, and a new anti-correlation between [K/Fe] and [Fe/H] can be observed within the sample, although the veracity of said relation remains questionable.
+Two distinct populations can be formed by Na abundance within the sample, with 30\% of the candidates having calculated abundances well above typical galactic levels.
+Two scenarios designed at explaining the data are put forth, and the implications for select existing polluter candidate proposals are briefly discussed.
+These candidate stars should provide guidance for follow up surveys and modelling attempts attempting to determine the origin of the Mg-K anti-correlation.
 
-%454180 RGB stars from the low resolution LAMOST DR2 survey were searched for anomalously high K and depleted Mg signatures.
-This study represents the largest search for field stars containing the Mg-K anti-correlation so far identified only in the globular NGC 2419 and NGC 2808.
-23 stars displaying absorption spectra with over-abundant K and depleted Mg accross a range of metalicities were identified, but none were identified as having [Mg/Fe] or [K/Fe] consistent with the Mg depleted population found in NGC 2419.
-The abundances in these 23 stars are estimated at ranging between [INSERT RANGE FOR K AND MG HERE BASED OFF LAMOST DATA].
-High resolution spectra for three stars (1 of which is not included among the final count of 23 spectral candidates for the signiature for reasons relating to the LAMOST signal quality for that star, despite having the highest K abundance of the three at [K/Fe]=1.54) selected based on observability characteristics were obtained using the Las Campanas Observatory, and for these stars elemental abundances for heavy elements such as Sc and V are also presented.
 \end{abstract}

### 2018-01-23 article/ms.tex
in the midst of going through discussion based on conversations at SINS

@@
 
-This spread in metalicity is important: it strongly implies that the process responsible for this signature, rare as it is, is not necessarily tied to a certain epoch in the history of our galaxy.
+This spread in metalicity is important: it implies that the process responsible for this signature, rare as it is, is not necessarily tied to a certain epoch in the history of our galaxy.
 Rather, these stars appear to be continuously forming from successive generations of stars.
 
-This argues against polluter candidates any theoretical hyper-massive Population III star that might be imagined.
-While such an object might be plausible in the context of NGC 2419, it cannot explain the enhanced K abundances observed in the disk at such a large spread in metalicity (assuming here no correlation between [Fe/H] and [K/Fe]), which implies formation of significant amounts K throughout the life of the galaxy.
+This argues against any theoretical hyper-massive Population III star that might be imagined being the polluter candidate.
+While such an object might be plausible in the context of NGC 2419, and appealing given the uniqueness of the cluster, it cannot explain the enhanced K abundances observed in the disk at such a large spread in metalicity, which implies formation of significant amounts K throughout the life of the galaxy.
 
@@
 
-One possible scenario that could produce a large K enhanced signature throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is some less massive.
-The SAGB star then produces K, as well as possibly s-process neutron capture elements, and deposits its K rich envelope onto its smaller companion through conventional binary accretion.
+One possible scenario that could possibly produce a large K enhanced signature, as well as the observed Na pattern, throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is some less massive star.
+The SAGB star produces K (destroying Na) which is then mixed into its envelope.
+It then deposits its K rich envelope onto its smaller companion through conventional binary accretion.
 This smaller and companion would continue to evolve long after the SAGB star is gone and, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, would not.

### 2018-01-24 article/ms.tex
added conclusions and discussion points based off sims meetings, also Na dust picture

@@
     \caption{Effective temperature, log surface gravity, metalicity.
-\todo{The large, random spread in $\logg$, $\teff$ and [Fe/H] implies that the candidates are simply stars which have formed from poluted material, rather than any special type of star such as red-clump giants.}}
+\todo{The large, random spread in $\logg$, $\teff$ and [Fe/H] implies that the candidates are simply stars which have formed from poluted material, rather than any special type of star such as red-clump giants.
+Further, this distribution allays concerns that the sample is the result of some NLTE effect.}}
     \label{tefflogg}
@@
 If the companion star had sufficient mass to undergo hot bottom burning, then Na should be enhanced from production from \ce{^24 Mg} and \ce{^22 Ne}.
-In this scenario, it is this smaller binary companion star that makes up our sample of 113 giants.
-Note that since the envelope in a hot-bottom burning star is well mixed, the spectral signatures of these elements are observable.
+In this scenario, it is this smaller binary companion star that makes up our sample of 113 giant observations.
+Recall that since the envelope in a hot-bottom burning star is well mixed, the spectral signatures of these elements are observable.
 
 This scenario allows for K abundances to appear at a range of metalicities, as this scenario could play out throughout the life of the Milky Way.
-It also  accounts for the significant minority population of the stars which show Na enhancements.
+It also  accounts for the significant minority population of the stars which show Na enhancements, while allowing others to retain normal levels of [Na/Fe].
+\todo{Check dust lanes.}
 
 It does not, however, account for the uniqueness of the signal to NGC 2419 and NGC 2808 among globular clusters, nor does it satisfactorily explain why such a large proportion of stars in NGC 2419 exhibit the Mg-K anti-correlation.
-The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is unlikely to say the least.
+The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is highly unlikely, to say the least.
+One might imagine however that the case of NGC 2808 might be accounted for by such a mechanism.
 
-A direct test of this scenario would be the determination of whether at least most of the sample are binaries with neutron star remnants.
+A direct test of this scenario would be the determination of whether at least most of the sample are binaries with O-Ne white dwarf remnants, which would indicate that they were indeed SAGB binaries once.
 
@@
 The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in a region(s) of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases.
-This interpretation is supported by the consistency of the relation with levels of [K/Fe] in NGC 2419.
+This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419.
 
@@
 
-Suppose some unknown event(s) that can only occur in very metal poor environments occurs. This event results in material depleted in Mg and enhanced in K.
+Suppose some unknown event(s) that can only occur in very metal poor environments occurs. This event results significant amounts of material depleted in Mg and enhanced in K.
 
-The generation of stars that forms directly from this gas carries this signiature, and displays a significant reduction in Mg abundance and enhancement in K abundance similar to NGC 2419.
+The generation of stars that forms directly from this gas carries this signature, and displays a significant reduction in Mg abundance and enhancement in K abundance similar to NGC 2419.
 We will label this generation of stars Generation 1.
 
-When the most massive stars of Generation 1 die however, they release metals into the this gas, including Mg, which is easy to form, but \textit{not} K, which is difficult to form.
+When the most massive stars of Generation 1 die however, they release metals into the this gas, including significant amounts of Mg which is formed in copious amounts in core collapse supernovae, but \textit{not} K, which is difficult to form.
 The Mg depletion originally carried in this gas relative to the original levels of iron is much harder to detect in the next generation of stars forming from this material, Generation 2, as the original depleted signature is obscured by the influx of Mg from Generation 1.
@@
 
-If the [K/Fe] anti-correlation with [Fe/H] is physical, then the presmumed production of anomalously high amounts of K throughout the life of the Milky Way is turned on its head.
-Instead, it can be concluded that the origin of the Mg-K anti-correlation is confined to a certain epoch in the evolution of galaxies and globular clusters.
+If the [K/Fe] anti-correlation with [Fe/H] is physical, then the presmumed production of anomalously high amounts of K throughout the life of the Milky Way may be turned on its head.
+Instead, it could concluded that the origin of the Mg-K anti-correlation is temporally confined to a certain epoch in the evolution of galaxies and globular clusters.
+
+However, even if physical, there are still several outstanding issues in the above scenario.
+
+First and most importantly, the extreme difficulty of forming the original cloud of Mg depleted, K enriched material in the first place must be emphasized.
+Primordial conditions (ie.
+pre-mystery-event) will contain some iron for the same reason that globular clusters are not at zero metalicity.
+This iron also comes with Mg; the only way to produce iron without Mg is Type Ia supernovae, which are not believed to be common in the early universe, and don't produce K anyway.
+There is no known process from which you can go from a massive cloud with galactic levels of [Mg/Fe], such as forms the Mg normal population in NGC 2419, to one with [Mg/Fe] levels of around -1.5 dex.
+Huge amounts of Fe rich material containing virtually no Mg would be required to be released into the cloud, and that's before even considering the difficulty of also producing K...
+and at the same time apparently sometimes (but not always) also producing Na.
+
+The second issue with the scenario is that it would be expected that stars would form from the hypothetical cloud in groups, as compression events pass through the gas, triggering star formation.
+There is no evidence of such grouping in any of the data for the 113 star sample.
+
+Another interpretation of the [K/Fe]-[Fe/H] anti-correlation could be that the K forming process is happening throughout the life of the galaxy, but the amount of K produced decreases with the metalicity of the star.
 
 \section{Conclusions}
+Of the 454180 giant sample from \lamost, 113 candidate stars were identified as likely to have enhanced K and depleted Mg based on absorption spectra.
+These stars show every appearance of being field stars, nor do they have the hallmarks of being the product of NLTE effects.
+The candidate sample reflected the metalicity distribution of the base \textit{LAMOST} sample.
 
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
+ Upon conducting abundance analysis, it was found that despite the searching for both Mg depletions and K enhancements, the sample of stars showed no definitive Mg depletion, although it did display anomalously high levels of K.
+None of the candidates had calculated abundances of Mg or K consistent with NGC 2419 or NGC 2808's extreme populations.
+
+The sample was also found found to be bimodal in Na, with a significant minority population of stars showing enhanced Na well above galactic levels.
+Finally, an intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains questionable.
 

### 2018-01-25 article/ms.tex
Draft with the lot, minus andies stuff

--- 2018-01-23 article/ms.tex
@@
 % Keep the title short and informative.
-\title[Short title, max. 45 characters]{Mg Depleted and K Enriched Stars from LAMOST Spectral Data}
+\title[Mg-K anti-correlation in LAMOST]{Discovery of Mg-depleted and K-enhanced Stars in \textit{LAMOST}}
 
@@
 Andrew R. Casey,$^{1,2}$
-%Matthew Miles? (Monash)
-%Brodie Norfolk? (Monash)
-%Amanda Karakas? (Monash)
-%John Lattanzio? (Monash)
-%Kevin Schlaufman? (JHU)
-%Anna Ho? (Caltech)
+Mathew T. Miles,$^{1}$
+Brodie J. Norfolk,$^{1}$\newauthor
+Amanda I. Karakas,$^{1}$
+John C. Lattanzio,$^{1}$
+Kevin C. Schlaufman,$^{3}$\newauthor
+Anna Y.Q Ho,$^{4}$
+Melissa K. Ness,$^{5}$
+David W. Hogg, $^{6}$
 \\
@@
 $^{2}$ Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
+$^{3}$, Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA\\
+$^{4}$ Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
+$^{5}$ Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
+$^{6}$ Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA\\
 }
@@
 
-Stellar absorption spectra act as a record of the primordial conditions within which the stars formed.
-Stars displaying unusual elemental abundances are of particular interest; these rare stars often offer clues about astrophysical events and objects that may no longer exist in our galaxy.
-Stars with  depleted Mg and enhanced K abundances, measured as [Mg/Fe] and [K/Fe], have thus far only been found in the two massive globular clusters NGC 2419 and NGC 2808.
+Stellar absorption spectra act as a fossil record of the conditions when stars form.
+Stars with unusual elemental abundances are of particular interest; these rare stars often offer clues about rare astrophysical events or nucleosynthetic pathways.
+Stars with  depleted Mg and enhanced K abundances have thus far only been found in the two massive globular clusters NGC 2419 and NGC 2808.
 The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
-A satisfactory explanation for this signature has potential to influence theories of globular cluster formation and shed light on the long-standing problem of the underestimation of [K/Fe] among even 'normal' field stars in the Milky Way.
-The apparent exclusivity of this Mg-K anti-correlation to globular clusters is the focus of this paper.
-Here we present 113 candidate field stars (from a sample size of \LamostGiants \ giants from \lamost \ DR2) that have spectra consistent with slightly depleted [Mg/Fe] and significantly enhanced [K/Fe] abundances.
-None of these stars have abundances comparable to the extreme population of stars identified in NGC 2419.
-These stars are of a range of metalicities, and a new anti-correlation between [K/Fe] and [Fe/H] can be observed within the sample, although the veracity of said relation remains questionable.
-Two distinct populations can be formed by Na abundance within the sample, with 30\% of the candidates having calculated abundances well above typical galactic levels.
-Two scenarios designed at explaining the data are put forth, and the implications for select existing polluter candidate proposals are briefly discussed.
+Here we present 113 candidate field stars identified from \LamostGiants \ giants observed by \lamost \ that have slightly depleted [Mg/Fe] and significantly enhanced [K/Fe] abundance ratios.
+None have abundances that are as extreme as those in NGC 2419.
+These stars have a range of metalicities.
 These candidate stars should provide guidance for follow up surveys and modelling attempts attempting to determine the origin of the Mg-K anti-correlation.
@@
 \begin{keywords}
-keyword1 -- keyword2 -- keyword3
+methods: data analysis -- catalogues -- stars: chemically peculiar -- Galaxy: abundances -- Galaxy: evolution -- galaxies: globular clusters: individual: evolution
 \end{keywords}
@@
 \section{Introduction}
-
+\label{sec:intro}
 NGC 2419 is the Milky Way's third most massive globular cluster, and its chemical composition makes it perhaps the most unusual star cluster in the Galaxy.
 Recent spectroscopic studies of red giant branch (RGB) stars in NGC 2419 revealed a strong anti-correlation between Mg and K abundances in nearly half of the studied stars, and weaker abundance relations in Si, Sc, Ca, Ti and V \citep{mucciarelli2012,cohenkirby2012}.
-Depletions of Mg within dwarf spheroidal (dSph) galaxies are not rare \citep{mucciarelli2012}, but are always accompanied with an increase in [Fe/H].
-%\todo{[citations needed; possibly remove. RESOLVED, addapted statement slightly. relevant sources: Mucciarreli and Tsujimoto.]}
-The mechanism for this Mg depletion is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the more `normal' [Mg/Fe] ratios that arise from Type II supernovae.
+
+The only known mechanism for Mg depletion is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the more `normal' [Mg/Fe] ratios that arise from Type II supernovae.
 However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}.
-Furthermore, Type Ia supernovae enrichment cannot account for the enhanced K abundance or the similar  abundance trends observed in NGC 2419.
-Currently there is no known nuclear process that can explain the Mg-K abundance variations  without invoking unrealistic temperature conditions or by altering reaction rates by several orders of magnitude.
+Furthermore, Type Ia supernovae enrichment cannot account for the enhanced K abundance observed in NGC 2419.
+In fact, K is hard to make in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates from measured values by several orders of magnitude.
 
@@
 
-A  targeted search looking [K/Fe] in RGB stars from clusters NGC 6752, NGC 6121, NGC 1904, and $\omega$ Centauri as well as 21 field stars 
-%\todo{21 field stars or 21 clusters?? I thought carretta looked at lots of clusters, no?} RESOLVED: Info accurate, no action taken.
- found in all cases K abundances falling within the bounds of the Mg normal population in NGC 2419 \citep{carretta2013}.
- % \todo{The exception is NGC 2808......} RESOLVED: Rephrased paragraph.
+A  targeted search looking for [K/Fe] in RGB and main sequence turn-off stars from clusters NGC 6752, NGC 6121, NGC 1904, 47 Tuc, NGC 6397, NGC 7099, and $\omega$ Centauri as well as 21 field stars found in all cases K abundances falling within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}.
 NGC 2808 is the only cluster other than NGC 2419 where the anticorrelation between Mg and K has been observed.
-All 4 of its known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these abundances was weaker than that in NGC 2419.
-The fact that the Mg-K anti-correlation is apparently confined to these very few globular clusters would seem to imply either a small population  of unusual polluter stars of some sort or a single extremely massive polluter star.
+All 4 of NGC 2808's known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these abundances was weaker than that in NGC 2419.
+The fact that the Mg-K anti-correlation is apparently confined to these two globular clusters would seem to imply either a small population of unusual polluter stars or a single extremely massive polluter star.
 
 An early modelling attempt at replicating the anomalous Mg/K abundances assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}.
-This study succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) \todo{Ask andy if its right to cite iliadis here, and why he removed the 'corrected as per' bit.} for the production of K.
-However, abundance patterns consistent with NGC 2419 were only achievable if the reaction cross section was set to 100 times the commonly accepted rate or if the temperature at the base of the envelope  temperatures could be made to exceed $\sim$ 150 K.
+This study succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K.
+However, abundance patterns consistent with NGC 2419 were only possible if the reaction cross section was set to 100 times the commonly accepted value or if the temperature at the base of the envelope could be made to exceed $\sim$ 150 MK.
 
-A more recent attempt to replicate the Mg/K abundance signature in NGC 2419 by \cite{iliadis2016} also attempted to reproduce the abundances of Si, Sc, Ca, Ti and V  \citep[elements reported as having weak correlations with Mg by][]{cohenkirby2012}.
-The ultimate goal was to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluter candidates.
-It is perhaps noteworthy that they identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor minor secondary pathway.
+A more recent attempt to replicate the Mg/K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}.
+The ultimate goal was to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.
+It is perhaps noteworthy that they identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway.
 The main pathway they identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.
 
-It was found that (excepting the case of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required.
-Using this information, core and shell burning of low mass, high mass and super massive stars were ruled out as potential polluter candidates, as well as regular AGB stars.
-Super-AGB (SAGB) stars however were regarded as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
-The other potential candidate identified was novae, although the lack of detailed models of white dwarf accretion of material similar to that of NGC 2419 either from a binary companion or the intracluster medium limits appraisals of its feasibility regarding whether enough ejecta could be produced and retained by the cluster.
-However, based on current novae frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by Novae is at most 1 \% of the total required mass to pollute 30 \% of NGC 2419.
+It was found that (excepting the case of extremely high densities of > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required.
+Using this information, core - and shell -  burning of low-mass, high-mass and super-massive stars were ruled out as potential polluters, as well as regular AGB stars.
+Super-AGB (SAGB) stars, however, were regarded as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
+The other potential candidate identified was novae, although the lack of detailed models of white dwarf accretion of metal-poor material limits certainty in this case.
+However, based on current novae frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1 \% of the total required mass to pollute 30 \% of NGC 2419.
 
-Another proposed  polluter candidate is a pair-instability super nova (PISN) \citep[PISN;][]{carretta2013}.
-Unique to extremely massive Population III stars, these events involve the total destruction of the star, with no black hole remnant being left behind.
-The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material involved, could potentially allow the entire signature in NGC 2419 to be the result of a single event, explaining why it is not seen in any other globular clusters.
+Another proposed  polluter candidate is a pair-instability super nova \citep[PISN;][]{carretta2013}.
+Unique to extremely massive Population III stars, these events involve the total destruction of the star, with no black hole remnant left behind.
+The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material released, could allow for the abundance signature in NGC 2419 to be the result of a single, extremely rare event, which would explain why it is not seen in any other globular clusters.
 However, the signature odd-even proton number abundance pattern associated with PISNs is absent from NGC 2419 \citep{cohenkirby2012}, making this particular scenario unlikely.
-However, some other type of extremely massive star exploding in a single event would certainly go a long way to explaining the rarity of the signal.
-% \todo{Do all the abundance variations like Sc, Si, Ca, Ti, and V go in the expected direction for PISN?} RESOLVED: You are quite correct, I was entirely mistaken.
-In fact, the odd-even abundance pattern is absent from NGC 2419 in general.
-segment is edited to reflect this.
+Some other type of rare, massive exploding star could certainly help explain the rarity of the signal though.
 
@@
 
-Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg-K anti-correlation, a satisfactory explanation for this signature could offer insight into the underestimation of K abundances in the Milky Way predicted by models \citep{kobayashi2011}.
+Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg-K anti-correlation, a satisfactory explanation for the Mg-K signature could offer insight into the underestimation of K abundances in the Milky Way predicted by galactic chemical evolution models \citep{kobayashi2011}.
 Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.
@@
 Here we use \lamost\ data to conduct the largest ever search for field stars that are enhanced in potassium and depleted in magnesium.
-The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.
-\todo{In Section \ref{sec:methods} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and analysis of those candidates.
-In Section \ref{sec:discussion} we discuss things.
-Section \ref{sec:conclusions} contains conclusions.}
+The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates.
+In Section \ref{sec:discussion} the results and their implications on possible poluters are discussed.
+Section \ref{sec:conclusion} summarises the main results.
 
@@
 
-\section{Methods, Observations, Simulations etc.}
-
-The data set of \LamostGiants\ \lamost\ giants was prepared by \citet{ho2017} for use with the supervised machine learning code \tc.
+\section{Method \& Observations}
+\label{sec:method}
+The data set of \LamostGiants\ \lamost\ giants (from \lamost\ DR2) was prepared by \citet{ho2017} for use with the supervised machine learning code \tc.
 The \lamost\ data was shifted to rest frame and pseudo-continuum-normalised before it was resampled to a common uniform wavelength grid between 3905\,\AA\ and 9000\,\AA.
-\tc\ was used to infer $\teff$, $\logg$, [Fe/H], and [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ survey through the use of a data-driven spectral model.
-Unless otherwise stated, these transfered labels are those used throughout this study.
+\tc\ \citep{ness2016,ho2017} was used to infer effective temperature ($\teff$), surface gravity ($\logg$), metallicity ([Fe/H]), and alpha abundance relative to iron ([$\alpha$/Fe]) using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ \citep{alam2015} survey through the use of a data-driven spectral model.
+Unless otherwise stated, these transferred labels are those referred to throughout this study.
 For details regarding the preparatory work, model generation, and label transfer between the \apogee\ and \lamost\ surveys, the reader is directed to \citet{ho2017}.
@@
 We identified candidate Mg/K giant stars by searching for significant deviations in flux residuals.
-The flux residuals were taken as the normalised \lamost\ flux and the best-fitting data-driven model from \tc\ (where $f_{residual} = f_{data} - f_{model}$).
+The flux residuals were taken as the normalised \lamost\ flux and the best-fitting data-driven model from \tc\ (where $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$).
 A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model).
@@
 For every star we recorded the profile amplitudes, wavelengths, widths, as well as associated measurement uncertainties of these quantities.
-We identified candidates by requiring they match at least one of the following three quality filters.
+We identified candidates by requiring they match at least one of the following three quality filters:
 \begin{enumerate}
-\item We required the amplitude $A$ of the profile at the Mg 5184 \AA \ line to exceed $A_{{\rm Mg} @ 5184} > 0.05$ and the amplitude of the profile at the K 7665 line to exceed $A_{{\rm K}\,@\,7665} < 0.05$.
+\item We required the amplitude $A$ of the profile at the Mg 5184 \AA \ line to exceed $A_{{\rm Mg} @ 5184} > 0.05$ and the amplitude of the profile at the K 7665 line to exceed $A_{{\rm K}\,@\,7665} < -0.05$.
 Both amplitudes must also be measured at more than $3\sigma$ ($|A|/\sigma_{A} \geq 3$).
-\item We required two of the three Mg triplet lines to satisfy $A > 0.05$ and at least one K line to have $A < 0.05$, and for those amplitudes to have $|A|/\sigma_{A} \geq 3$.
-\item We required two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost, and a reported $\chi_{r}^2 < 3$ from \tc.
+\item We required any two of the three Mg triplet lines to satisfy $A > 0.05$ and at least one K line to have $A < -0.05$, and for those amplitudes to have $|A|/\sigma_{A} \geq 3$.
+\item We required any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost, and a reported $\chi_{r}^2 < 3$ from \tc.
 \end{enumerate}
@@
 These filters identified 384 unique stars to be vetted manually.
-We visually inspected every candidate (multiple times) and excluded any candidate that showed any evidence of being a false positive, including candidates that exhibited data reduction issues, apparent absorption that was narrower than the expected spectral resolution, as well as 75 stars that exhibited chromospheric emission at H$\alpha$.
-The distilled catalogue includes \todo{113} candidate stars enhanced in K and depleted in Mg.
+We visually inspected every candidate (multiple times) and excluded any candidate that showed any evidence of being a false positive, including candidates that exhibited data reduction issues, apparent absorption that was narrower than the expected spectral resolution, as well as 75 stars that exhibited chromospheric emission at H$\alpha$ wavelengths.
+The distilled catalogue contains \todo{113} candidate stars enhanced in K and depleted in Mg.
 
-\subsection{Figures and tables}
+Abundances were calculated from the \lamost spectra \todo{@andy add how we did that, why we couldn't get Mg, error estimates and limitations.}
 
-Figures and tables should be placed at logical positions in the text. Don't
-worry about the exact layout, which will be handled by the publishers.
+High resolution spectra of three of the candidate stars based on observability (J075043.12+204658.0, J120032.60+024438.2 and J091825.49+172114.5) using Magellan/MIKE.
+\todo{@andy add relevant info on abundance calculations.}
 
-Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
-e.g. Table~\ref{tab:example_table}.
+The presence of Na enhancements were visually estimated from the sample of 113 candidate stars' flux spectra.
+Flux based estimates placed at most 40 of the 113 stars (35\%) as being likely Na enhanced targets.
+Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with Na above 0.5 dex.
+\todo{@andy add anything specific to Na}.
 
@@
 	\includegraphics[width=\columnwidth]{posterchildof13.png}
-    \caption{Poster Child}
+    \caption{Sample spectra for one of the candidate stars.}
     \label{posterchild}
@@
 	\includegraphics[width=\columnwidth]{histof113.png}
-    \caption{Metalicity Histogram}
+    \caption{Histogram showing the metalicity distribution for the candidate stars.}
     \label{mhist}
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{loggteffof113.png}
-    \caption{Effective temperature, log surface gravity, metalicity.
-\todo{The large, random spread in $\logg$, $\teff$ and [Fe/H] implies that the candidates are simply stars which have formed from poluted material, rather than any special type of star such as red-clump giants.}}
-    \label{tefflogg}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{globclustof113.png}
-    \caption{Galactic coordinates for Mg-K stars and known globular clusters}
-    \label{galcord}
-\end{figure}
-
-\begin{figure}
 	\includegraphics[width=\columnwidth]{KvsMgab.png}
-    \caption{[Comparison of K vs Mg abundances with NGC 2419 and NGC 2808. The dotted divisor line is present simply as a visual aide.}
+    \caption{Comparison of [K/Fe] vs [$\alpha$/Fe] for the candidate stars with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
+The dotted line is arbitrary, and is present simply as a visual aide.}
     \label{KvsMg}
@@
 	\includegraphics[width=\columnwidth]{KvsFe.png}
-    \caption{[K/Fe] vs [Fe/H] for the LAMOST data}
+    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.}
     \label{KvsFe}
@@
 
-\begin{figure}
-	\includegraphics[width=\columnwidth]{NavsFe.png}
-    \caption{[Na/Fe] vs [Fe/H] for the LAMOST data.}
-    \label{NavsFe}
-\end{figure}
+\section{Discussion}
+\label{sec:discussion}
 
-% Example table
-\begin{table}
-	\centering
-	\caption{This is an example table. Captions appear above each table.
-	Remember to define the quantities, symbols and units used.}
-	\label{tab:example_table}
-	\begin{tabular}{lccr} % four columns, alignment for each
-		\hline
-		A & B & C & D\\
-		\hline
-		1 & 2 & 3 & 4\\
-		2 & 4 & 6 & 8\\
-		3 & 5 & 7 & 9\\
-		\hline
-	\end{tabular}
-\end{table}
+\subsection{Selection effects}
+\label{sec:selectioneffects}
+\cite{ho2017}'s sample of \lamost\ giants carries with it certain selection effects determined both by \textit{APOGEE} DR12 and \lamost.
+The most metal poor stars ([Fe/H] $\lesssim-2$ are mostly absent from the sample as they were likely too dissimilar to the training stars for label transfer from \textit{APOGEE}.
+The candidate stars are distributed across the giant branch, implying the abundances detected are not associated with any NLTE effects or stage in stellar evolution.
+Unfortunately, the target selection process for \lamost\ is non-invertible, selection effects present in \lamost\ are not considered here beyond comparing the candidate stars' metallicity distribution with that of \cite{ho2017}.
 
-\section{Discussion}
-\subsection{Association with globular clusters}
-J074807.22+261514.2 is the closest star from the sample in the sky to a globular cluster, at a 2.54\degree separation from Ko 2.
-Little is known about Ko 2 other than that it is an extremely faint halo cluster \citep{koposov2007}; it would be expected that a star from such a cluster would have very low metalicty, while J074807.22+261514.2 has $ \text{[Fe/H]} = -0.24 \pm 0.07$.
-Stars from Ko 2 would be unlikely to appear in a survey such as \lamost, which favours detection of bright field stars.
+\subsection{Association with known globular clusters}
+\label{sec:globclustasoc}
+We cross-matched our sample against \cite{harris1996}'s data base of globular clusters.
+None of the stars appear to be associated with NGC 2419 or NGC 2808.
+J074807.22+261514.2 is the closest star from the sample in the sky to a globular cluster, at a 2.54\degree separation from Ko 2 \citep{koposov2007}.
+This separation is large for association with such a small, distant cluster and the star's metallicity and apparent magnitude make it even less likely to be a member.
 
-None of the stars appear to be associated with NGC 2419, NGC 2808 or $\omega$ Centauri.
-
-Only 4 stars were contained within \textit{GAIA}'s DR1, and when backwards time integrated using GAIA's data with the GALA dynamics package for Python, they exhibited orbits consistent with field stars, with none of the eccentricity and high velocity typical of a star disrupted from a globular cluster.
-
-The spread of metalicity shown in Figure \ref{mhist} further supports the sample being made up of field stars.
+The spread of metallicity shown in Figure \ref{mhist} further supports the sample being made up of field stars.
 The distribution reflects the original \LamostGiants \ sample of giants from which the candidates were drawn.
-Thus, we conclude that the candidates are not particular to any specific metalicity.
-
-There is no evidence at this time supporting any stars from this sample having origins in globular clusters, while Figure \ref{galcord} clearly indicates galactic latitudes of the candidates are mostly consistent with field stars in the disk of the galaxy.
-The spread in metalicity shown in Figure \ref{mhist}, with significant numbers of high metalicity stars, further supports the conclusion that the sample is comprised mainly of field stars formed at different times throughout the lifetime of the Milky Way.
+No stars are present at [Fe/H]$\sim -2$ - the approximate metallicity of NGC 2419 - nor is there many stars with [Fe/H]$\sim -1$ - the metallicity of NGC 2808.
+Thus, we conclude that the candidates are not particular to any specific metallicity, including metalicites associated with NGC 2419 and NGC 2808.
 
 \subsection{Abundances}
-
+\label{sec:abundances}
 Figure \ref{KvsMg} shows [K/Fe]  for the 113 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012,mucciarelli2012,mucciarelli2015}.
-[K/Fe] vs [Mg/Fe] for the three stars from the sample observed using \textit{Magellan} is also shown.
-$[\alpha$/Fe] is used as an upper limit for [Mg/Fe] for the 113 star sample as [Mg/Fe] proved impossible to obtain from the \lamost \ spectra.
+[K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE is also shown.
 The use of [$\alpha$/Fe] as a proxy for [Mg/Fe] is supported by the [Mg/Fe] measurements from the high-resolution spectra obtained, these being similar to the [$\alpha$/Fe] abundances from \tc.
@@
 Levels of [$\alpha$/Fe] fall within the lower limits of the Mg-normal population of both clusters, although as this represents only an upper limit the exact level of Mg depletion for the candidates is unclear.
-The [Mg/Fe] abundances derived from \textit{Magellan}'s high resolution spectra suggest that at most a small depletion relative to the Mg-normal population may be present.
+The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra suggest that at most a small depletion relative to the Mg-normal population may be present.
 
 A similar relationship emerges when comparing with typical galactic numbers for [K/Fe] and [Mg/Fe], taken from \cite{kobayashi2011}.
-Only the [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$ dex, while the \lamost \ sample of stars varies from around 0.8-1.3, and the \textit{Magellan} abundance for candidate star J091825.49+172114.5 having [K/Fe] $\approx$ 1.54.
+Only the sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$ dex, while the \lamost \ sample of stars varies from around 0.8-1.3, and the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$.
 
-The sample's [K/Fe] also exhibits an interesting anti-correlation with total metalicity, shown in Figure \ref{KvsFe}, which is absent from measurements in the Milky Way.
-This is consistent with a (somewhat) constant level of [K/H] between each star, causing [K/Fe] to fall with increasing metalicity.
-It is interesting that the Mg poor population of NGC 2419 appears to fit with this trend.
+The candidate stars' [K/Fe] also exhibits an interesting anti-correlation with total metallicity, shown in Figure \ref{KvsFe}, which is absent from measurements in the Milky Way.
+This is consistent with a (somewhat) constant level of [K/H] between each star, causing [K/Fe] to fall with increasing metallicity.
+It is interesting that the Mg-poor population of NGC 2419 appears to fit with this trend.
 
- However, for reasons related to the use of both a data-driven model and a physical model for calculating abundances, it is possible that this effect is an artefact of processing rather than a physical relation.
+ However, for reasons related to the use of both a data-driven model and a physical model for calculating abundances \todo{@andy add any elaboration on what the problem was, if necessary}, it is possible that this effect is an artefact of processing rather than a physical relation.
 Without further observations of the sample stars, we are unable to say with certainty whether this phenomena is real or not, and so both cases will be treated.
 
-In contrast with the marked departure from galactic values for [K/Fe], [$\alpha$/Fe] varies from around 0-0.3 dex in the \lamost \ sample, similar to galactic levels of [Mg/Fe], which vary with metalicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}.
-No variation with metalicity is observed within the \lamost sample's [$\alpha$/Fe].
+The candidate stars' levels of [$\alpha$/Fe] were generally consistent with galactic levels of [Mg/Fe], although its possible a slight depletion is present. No variation with metallicity is observed.
 
-[Na/Fe] was also measured for the \lamost\ data, shown in Figure \ref{NavsFe} versus [Fe/H].
-Two distinct populations are observed, with a significant minority of approximately 30\% of the sample having [Na/Fe] > 0.5, significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}.
-It is interesting that the enhanced population does not extend to the lowest metalicities of our sample, as Na enhancements are associated with some globular clusters; thus, we might expect the Na enhanced population to be dominated by the lowest metalicity stars.
-No correlation between [Na/Fe] and the level of [K/Fe] is observed.
+%In contrast with the marked departure from galactic values for [K/Fe], [$\alpha$/Fe] varies from around 0-0.3 dex in the \lamost \ sample, similar to galactic levels of [Mg/Fe], which vary with metallicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}.
+No variation with metallicity is observed within the \lamost sample's [$\alpha$/Fe].
+
+[Na/Fe] was also measured for the \lamost\ data.
+Two distinct populations were observed, with a substantial minority of approximately 30\% of the sample having [Na/Fe] > 0.5, significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}.
+However, this behaviour is very likely due to the effect of interstellar dust; it was found that the values of E(B-V), taken from IRSA's all-sky dust map \citep{schlafly2011}, were higher for the stars supposedly enriched in Na than for those displaying galactic levels.
+It worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K.
 
 The implications of the calculated abundances are intriguing.
-The fact that from such a large sample of field stars none were found that replicated the extreme abundance pattern of NGC 2419 further and perhaps definitively cements the clusters uniqueness.
+The fact that from such a large sample of field stars none were found that replicated the extreme abundance pattern of NGC 2419 is strong evidence for the cluster's uniqueness.
 
@@
 
-\subsection{Implications on theories regarding the origin of the Mg-K anticorrelation.}
+\subsection{Impact on theories and scenarios regarding the Mg-K anti-correlation}
 
-The conclusions that can be drawn from the data hinge on whether or not the relation between [K/Fe] and [Fe/H] shown in Figure \ref{KvsFe} is real.
-For this reason, we deal with both cases, first disregarding the information in Figure \ref{KvsFe}, then assuming the relation to be real.
-
-\subsubsection{Disregarding the anti-correlation of [K/Fe] vs [Fe/H].}
-
-Significantly enhanced [K/Fe] is rare; significantly enhanced [K/Fe] without an accompanying depletion of [Mg/Fe] is unknown.
-Further, the candidate stars are spread across a wide range of metalicities.
-
-This spread in metalicity is important: it implies that the process responsible for this signature, rare as it is, is not necessarily tied to a certain epoch in the history of our galaxy.
-Rather, these stars appear to be continuously forming from successive generations of stars.
-
-This argues against any theoretical hyper-massive Population III star that might be imagined being the polluter candidate.
-While such an object might be plausible in the context of NGC 2419, and appealing given the uniqueness of the cluster, it cannot explain the enhanced K abundances observed in the disk at such a large spread in metalicity, which implies formation of significant amounts K throughout the life of the galaxy.
-
-As emphasized by \cite{prantzos2017}, a large part of the problem presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion Mg and an enhancement in K.
-Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{23} Na} and through Mg-Al chains at temperatures around 75 MK, attainable in hot-bottom burning environments in AGB stars, while it takes temperatures upwards of 150 MK to produce K, temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
-This implies that the Mg depletion and K enrichment occur at separate sites.
-
-One possible scenario that could possibly produce a large K enhanced signature, as well as the observed Na pattern, throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is some less massive star.
-The SAGB star produces K (destroying Na) which is then mixed into its envelope.
-It then deposits its K rich envelope onto its smaller companion through conventional binary accretion.
-This smaller and companion would continue to evolve long after the SAGB star is gone and, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, would not.
-If the companion star had sufficient mass to undergo hot bottom burning, then Na should be enhanced from production from \ce{^24 Mg} and \ce{^22 Ne}.
-In this scenario, it is this smaller binary companion star that makes up our sample of 113 giants.
-Note that since the envelope in a hot-bottom burning star is well mixed, the spectral signatures of these elements are observable.
-
-This scenario allows for K abundances to appear at a range of metalicities, as this scenario could play out throughout the life of the Milky Way.
-It also  accounts for the significant minority population of the stars which show Na enhancements.
-
-It does not, however, account for the uniqueness of the signal to NGC 2419 and NGC 2808 among globular clusters, nor does it satisfactorily explain why such a large proportion of stars in NGC 2419 exhibit the Mg-K anti-correlation.
-The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is unlikely to say the least.
-
-A direct test of this scenario would be the determination of whether at least most of the sample are binaries with neutron star remnants.
-
-\subsubsection{Implications of the [K/Fe] vs [Fe/H] anti-correlation.}
-
-The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in a region(s) of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases.
-This interpretation is supported by the consistency of the relation with levels of [K/Fe] in NGC 2419.
-
-Here we set out an evolution scenario that could account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419 and our new 113 field star sample.
-
-Suppose some unknown event(s) that can only occur in very metal poor environments occurs. This event results in material depleted in Mg and enhanced in K.
-
-The generation of stars that forms directly from this gas carries this signiature, and displays a significant reduction in Mg abundance and enhancement in K abundance similar to NGC 2419.
-We will label this generation of stars Generation 1.
-
-When the most massive stars of Generation 1 die however, they release metals into the this gas, including Mg, which is easy to form, but \textit{not} K, which is difficult to form.
-The Mg depletion originally carried in this gas relative to the original levels of iron is much harder to detect in the next generation of stars forming from this material, Generation 2, as the original depleted signature is obscured by the influx of Mg from Generation 1.
-The K enhancement however remains relatively easy to detect, having only been reduced relative to iron by the total amount of iron released.
-
-As this cycle continues, [K/Fe] would become lower and lower, approaching 'regular' galactic levels, while depletions in [Mg/Fe] would quickly become very hard to detect.
-
-This cycle allows for the Mg depletions to be preserved in globular clusters, where even the most massive clusters only form around 2 generations of stars, as the clusters lack the gravity to hold on to sufficient gas for many generations of stars.
-But it also allows the Mg signal to effectively be lost within the disc of the galaxy, where many generations of stars may form.
-
-If the [K/Fe] anti-correlation with [Fe/H] is physical, then the presmumed production of anomalously high amounts of K throughout the life of the Milky Way is turned on its head.
-Instead, it can be concluded that the origin of the Mg-K anti-correlation is confined to a certain epoch in the evolution of galaxies and globular clusters.
-
-\section{Conclusions}
-
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
-
-\section*{Acknowledgements}
-
-- LAMOST
-- ARC DP (Casey)
-- Magellan/MIKE and Australian government
-- others???
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
-
-\bibliographystyle{mnras}
-\bibliography{mgkbib} % if your bibtex file is called example.bib
-
-% Alternatively you could enter them by hand, like this:
-% This method is tedious and prone to error if you have lots of references
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Some extra material}
-\begin{table}
+\label{sec:scenarios}
+\begin{table*}
 \centering
@@
 \label{my-label}
-\end{table}
+\end{table*}
 
-\newpage
+Significantly enhanced [K/Fe] is rare; significantly enhanced [K/Fe] without an accompanying depletion of [Mg/Fe] is unknown. The candidate stars are also spread across a wide range of metalicities.
+
+This spread in metallicity is important: taken in isolation, it implies that the process responsible for this signature, rare as it is, is not necessarily tied to a certain epoch in the evolutionary history of our galaxy.
+Rather, these stars appear to be continuously forming in successive generations.
+
+This argues against any theoretical hyper-massive Population III star that might be imagined being the polluter candidate.
+While such an object might be plausible in the context of NGC 2419, and appealing given the uniqueness of the cluster, it cannot account for the production of K throughout the life of the galaxy.
+
+As emphasized by \cite{prantzos2017}, a large part of the problem presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion in Mg and an enhancement in K.
+Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{23} Na} and through Mg-Al chains at temperatures around 75 MK -  attainable in hot-bottom burning environments in AGB stars - while it takes temperatures upwards of 150 MK to produce K - temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
+This implies that the Mg depletion and K enrichment occur at separate sites, assuming a simple hydrogen burning system.
+
+Allowing different sites for Mg depletion and K enrichment, one possible scenario that could possibly produce a large K enhanced signature along with - sometimes - potentially depleted Mg and enhanced Na throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is some less massive star.
+The scenario could play out as follows:
+
+The SAGB star produces K (destroying Na) which is then mixed throughout its envelope.
+It then deposits its K rich outer layers onto its smaller companion through binary accretion.
+This smaller companion would continue to evolve long after the SAGB star has formed a white-dwarf remnant and will, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, will not.
+If the companion star had sufficient mass to undergo hot bottom burning, then Na could be enhanced and Mg depleted \citep{prantzos2017}.
+In this scenario, it is this smaller binary companion star that makes up our sample of 113 giants.
+
+Although this scenario allows for consistency with the total spread in metallicity, it doe not account for the uniqueness of the signal to NGC 2419 and NGC 2808 among globular clusters, nor does it satisfactorily explain why such a large proportion of stars in NGC 2419 exhibit the Mg-K anti-correlation.
+The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is highly unlikely, to say the least.
+This scenario is perhaps also inconsistent with the [K/Fe]-[K/H] anti-correlation, although it remains uncertain whether this phenomenon is real.
+
+A direct test of this scenario would whether at least most of the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they could have formed SAGB binaries once.
+
+The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in a region(s) of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases.
+This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419.
+If this relation is real, we can perhaps - without saying anything about the polluter star - use it to motivate an  evolutionary sequence that can account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419 and our new 113 field star sample.
+
+Suppose some unknown event(s) that can only occur in very metal poor (possibly zero-metallicity) environments occurs.
+This event results in a gas cloud depleted in Mg and enhanced in K.
+The generation of stars that form directly from this gas carries this signature, and displays a significant reduction in Mg abundance and enhancement in K abundance similar to NGC 2419.
+We will refer to this generation of stars Generation 1.
+
+When the most massive stars of Generation 1 die, they release metals into the gas cloud, including significant amounts of Mg, which is formed in copious amounts in core-collapse supernovae, but \textit{not} K, which is very difficult to form in significant quantities.
+The [Mg/Fe] depletion originally carried in the cloud is much harder to detect in the next generation of stars forming from this material, Generation 2, due to the influx of Mg released by Generation 1.
+The K enhancement however remains relatively easy to detect, having only been reduced relative to iron by the total amount of iron released.
+As this cycle continues, [K/Fe] would continue to lower proportionately with the rate of iron release, while depletions in [Mg/Fe] would quickly become impossible to detect.
+
+This cycle allows for the Mg depletions to be preserved in globular clusters, where even the most massive clusters only form around 2 generations of stars.
+But it also allows the Mg signal to effectively be lost within the disc of the galaxy, where many generations of stars may form.
+Thus it provides a way of unifying the current observations of out 113 candidate stars with the observations of NGC 2419.
+Certainly the idea that both groups of anomalous stars arise from the same polluter source must be entertained.
+
+However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg depleted, K enriched material in the first place must be emphasized.
+Indeed, if we assume the primordial abundances are similar to those of NGC 2419's Mg-normal population, then it is impossible.
+If the primordial cloud already has [Mg/Fe]$\approx 0.5$, to reduce this necessitates the addition of large amounts of iron rich material that is also very depleted in [Mg/Fe].
+But as soon significant amounts of iron are added, [Fe/H] for the subsequent the Mg-depleted population should increase.
+However, no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}.
+This implies that the polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS), or at the very least the Mg-depleted population in NGC 2419 pre-dates the Mg-normal population.
+
+More generally, the [K/Fe]-[Fe/H] anti-correlation observed is supportive of the origin of the Mg-K anti-correlation being temporally confined to an early epoch in the evolution of galaxies and globular clusters.
+However, this is not necessarily the only interpretation.
+For example, it could be that the K forming process is happening throughout the life of the galaxy, but the amount of K produced decreases with the metallicity of the polluter star, though there is no obvious reason this would be the case.
+
+\section{Conclusions}
+\label{sec:conclusion}
+Of the 454180 giant sample from \lamost, 113 candidate stars were identified as likely to have enhanced K and depleted Mg based on absorption spectra.
+These stars show every appearance of being field stars, nor do they have the hallmarks of being the product of NLTE effects.
+The candidate sample reflected the metallicity distribution of the base \textit{LAMOST} sample.
+
+ Upon conducting abundance analysis, it was found that despite the searching for both Mg depletions and K enhancements, the sample of stars showed no definitive Mg depletion, although it did display anomalously high levels of K.
+None of the candidates had calculated abundances of Mg or K consistent with NGC 2419 or NGC 2808's extreme populations.
+
+The sample was also found found to be bimodal in Na, with a significant minority population of stars showing enhanced Na well above galactic levels.
+Finally, an intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains questionable.
+
+\section*{Acknowledgements}
+\todo{to be completed}
+
+\begin{comment}
+- LAMOST
+- ARC DP (Casey)
+- Magellan/MIKE and Australian government
+- others???
+\end{comment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
+
+% The best way to enter references is to use BibTeX:
+
+\bibliographystyle{mnras}
+\bibliography{mgkbib} % if your bibtex file is called example.bib
+
 \begin{comment}

### 2018-01-30 article/ms.tex
proof read, minor edits.

@@
 
-Stellar absorption spectra act as a fossil record of the conditions when stars form.
+Stellar absorption spectra act as a fossil record of the conditions where the stars form.
 Stars with unusual elemental abundances are of particular interest; these rare stars often offer clues about rare astrophysical events or nucleosynthetic pathways.
@@
 Here we present 113 candidate field stars identified from \LamostGiants \ giants observed by \lamost \ that have slightly depleted [Mg/Fe] and significantly enhanced [K/Fe] abundance ratios.
-None have abundances that are as extreme as those in NGC 2419.
-These stars have a range of metalicities.
+These stars re present at a range of metallicities, and none have abundances that are as extreme as those in NGC 2419.
 These candidate stars should provide guidance for follow up surveys and modelling attempts attempting to determine the origin of the Mg-K anti-correlation.
@@
 
-The only known mechanism for Mg depletion is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the more `normal' [Mg/Fe] ratios that arise from Type II supernovae.
+The only known mechanism for Mg depletion is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the `normal' [Mg/Fe] ratios that arise from Type II supernovae.
 However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}.
@@
 
-A  targeted search looking for [K/Fe] in RGB and main sequence turn-off stars from clusters NGC 6752, NGC 6121, NGC 1904, 47 Tuc, NGC 6397, NGC 7099, and $\omega$ Centauri as well as 21 field stars found in all cases K abundances falling within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}.
-NGC 2808 is the only cluster other than NGC 2419 where the anticorrelation between Mg and K has been observed.
-All 4 of NGC 2808's known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these abundances was weaker than that in NGC 2419.
+A targeted search looking for [K/Fe] in RGB and main sequence turn-off stars from clusters NGC 6752, NGC 6121, NGC 1904, 47 Tuc, NGC 6397, NGC 7099, and $\omega$ Centauri as well as 21 field stars found in all cases  that theK abundance fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}.
+NGC 2808 is the only cluster other than NGC 2419 where an anticorrelation between Mg and K has been observed.
+All 4 of NGC 2808's known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these anomalous abundances was far weaker than that in NGC 2419.
 The fact that the Mg-K anti-correlation is apparently confined to these two globular clusters would seem to imply either a small population of unusual polluter stars or a single extremely massive polluter star.
@@
 
-It was found that (excepting the case of extremely high densities of > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required.
-Using this information, core - and shell -  burning of low-mass, high-mass and super-massive stars were ruled out as potential polluters, as well as regular AGB stars.
+It was found that (excepting the case of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required.
+Using this information, core -- and shell --  burning of low-mass, high-mass and super-massive stars were ruled out as potential polluters, as well as regular AGB stars.
 Super-AGB (SAGB) stars, however, were regarded as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
@@
 However, the signature odd-even proton number abundance pattern associated with PISNs is absent from NGC 2419 \citep{cohenkirby2012}, making this particular scenario unlikely.
-Some other type of rare, massive exploding star could certainly help explain the rarity of the signal though.
 
@@
 Here we use \lamost\ data to conduct the largest ever search for field stars that are enhanced in potassium and depleted in magnesium.
-The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates.
+The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.
+In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates.
 In Section \ref{sec:discussion} the results and their implications on possible poluters are discussed.
@@
 
-We identified candidate Mg/K giant stars by searching for significant deviations in flux residuals.
+We identified potential Mg-K anti-correlated stars by searching for significant deviations in flux residuals.
 The flux residuals were taken as the normalised \lamost\ flux and the best-fitting data-driven model from \tc\ (where $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$).
@@
 \begin{enumerate}
-\item We required the amplitude $A$ of the profile at the Mg 5184 \AA \ line to exceed $A_{{\rm Mg} @ 5184} > 0.05$ and the amplitude of the profile at the K 7665 line to exceed $A_{{\rm K}\,@\,7665} < -0.05$.
+\item We required the amplitude $A$ of the profile at the Mg 5184 \AA \ line to satisfy $A_{{\rm Mg} @ 5184} > 0.05$ and the amplitude of the profile at the K 7665 line to satisfy $A_{{\rm K}\,@\,7665} < -0.05$.
 Both amplitudes must also be measured at more than $3\sigma$ ($|A|/\sigma_{A} \geq 3$).
@@
 
-High resolution spectra of three of the candidate stars based on observability (J075043.12+204658.0, J120032.60+024438.2 and J091825.49+172114.5) using Magellan/MIKE.
+High resolution spectra of three of the candidate stars selected based on observability (J075043.12+204658.0, J120032.60+024438.2 and J091825.49+172114.5) were obtained using Magellan/MIKE.
 \todo{@andy add relevant info on abundance calculations.}
@@
 Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with Na above 0.5 dex.
-\todo{@andy add anything specific to Na}.
+\todo{@andy add anything specific to Na abundance methods from LAMOST}.
 
@@
 \label{sec:selectioneffects}
-\cite{ho2017}'s sample of \lamost\ giants carries with it certain selection effects determined both by \textit{APOGEE} DR12 and \lamost.
-The most metal poor stars ([Fe/H] $\lesssim-2$ are mostly absent from the sample as they were likely too dissimilar to the training stars for label transfer from \textit{APOGEE}.
+\cite{ho2017}'s sample of \lamost\ giants carries with it certain selection effects as a result of both the \textit{APOGEE} DR12 and \lamost\ samples.
+Metal poor stars with [Fe/H] $\lesssim-2$ are mostly absent from the sample as they were likely too dissimilar to the training stars for label transfer from \textit{APOGEE}.
+Unfortunately, the target selection process for \lamost\ is non-invertible, and so selection effects present in \lamost\ are not considered here beyond comparing the candidate stars' metallicity distribution with that of \cite{ho2017}.
+
 The candidate stars are distributed across the giant branch, implying the abundances detected are not associated with any NLTE effects or stage in stellar evolution.
-Unfortunately, the target selection process for \lamost\ is non-invertible, selection effects present in \lamost\ are not considered here beyond comparing the candidate stars' metallicity distribution with that of \cite{ho2017}.
 
@@
 \label{sec:globclustasoc}
-We cross-matched our sample against \cite{harris1996}'s data base of globular clusters.
+Our sample was cross-matched against \cite{harris1996}'s data base of globular clusters.
 None of the stars appear to be associated with NGC 2419 or NGC 2808.
-J074807.22+261514.2 is the closest star from the sample in the sky to a globular cluster, at a 2.54\degree separation from Ko 2 \citep{koposov2007}.
+From the sample, J074807.22+261514.2 is the closest star in the sky to a globular cluster, at 2.54\degree\ separation from Ko 2 \citep{koposov2007}.
 This separation is large for association with such a small, distant cluster and the star's metallicity and apparent magnitude make it even less likely to be a member.
@@
 The distribution reflects the original \LamostGiants \ sample of giants from which the candidates were drawn.
-No stars are present at [Fe/H]$\sim -2$ - the approximate metallicity of NGC 2419 - nor is there many stars with [Fe/H]$\sim -1$ - the metallicity of NGC 2808.
-Thus, we conclude that the candidates are not particular to any specific metallicity, including metalicites associated with NGC 2419 and NGC 2808.
+No stars are present at [Fe/H]$\sim -2$ -- the approximate metallicity of NGC 2419 -- nor are there many stars with [Fe/H]$\sim -1$ -- the metallicity of NGC 2808.
+Thus, we conclude that the candidates are not particular to any specific metallicity, including metallicites associated with NGC 2419 and NGC 2808.
 
@@
 \label{sec:abundances}
-Figure \ref{KvsMg} shows [K/Fe]  for the 113 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012,mucciarelli2012,mucciarelli2015}.
+Figure \ref{KvsMg} shows [K/Fe]  for the 113 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
 [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE is also shown.
-The use of [$\alpha$/Fe] as a proxy for [Mg/Fe] is supported by the [Mg/Fe] measurements from the high-resolution spectra obtained, these being similar to the [$\alpha$/Fe] abundances from \tc.
+The use of [$\alpha$/Fe] as a proxy for [Mg/Fe] is supported by the [Mg/Fe] measurements from the high-resolution spectra, these being similar to the [$\alpha$/Fe] abundances from \tc.
 
-[K/Fe] for the candidate stars is generally lower than that of the extreme Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population.
-It is noteworthy that both populations identified in NGC 2808 have significantly lower levels of [K/Fe] than the candidate stars.
+[K/Fe] for the candidate stars is generally lower than that of the Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population.
+It is noteworthy that both of these populations identified in NGC 2808 have significantly lower levels of [K/Fe] than the candidate stars.
 Levels of [$\alpha$/Fe] fall within the lower limits of the Mg-normal population of both clusters, although as this represents only an upper limit the exact level of Mg depletion for the candidates is unclear.
-The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra suggest that at most a small depletion relative to the Mg-normal population may be present.
+The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra suggest that at most a small depletion relative to the Mg-normal population in NGC 2419 may be present.
 
 A similar relationship emerges when comparing with typical galactic numbers for [K/Fe] and [Mg/Fe], taken from \cite{kobayashi2011}.
-Only the sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$ dex, while the \lamost \ sample of stars varies from around 0.8-1.3, and the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$.
+Only the sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$ dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8-1.3.
+Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample are likely to have extremely high levels of [K/Fe].
 
 The candidate stars' [K/Fe] also exhibits an interesting anti-correlation with total metallicity, shown in Figure \ref{KvsFe}, which is absent from measurements in the Milky Way.
-This is consistent with a (somewhat) constant level of [K/H] between each star, causing [K/Fe] to fall with increasing metallicity.
-It is interesting that the Mg-poor population of NGC 2419 appears to fit with this trend.
+This may be consistent with a (somewhat) constant level of [K/H] between each star, which would then cause [K/Fe] to fall as [Fe/H] increases.
+It is interesting that the Mg-poor population of NGC 2419 appears to fit this relation.
 
 However, for reasons related to the use of both a data-driven model and a physical model for calculating abundances \todo{@andy add any elaboration on what the problem was, if necessary}, it is possible that this effect is an artefact of processing rather than a physical relation.
-Without further observations of the sample stars, we are unable to say with certainty whether this phenomena is real or not, and so both cases will be treated.
+Without further observations of the sample stars, we are unable to say with certainty whether this phenomena is real or not.
 
-The candidate stars' levels of [$\alpha$/Fe] were generally consistent with galactic levels of [Mg/Fe], although its possible a slight depletion is present. No variation with metallicity is observed.
+The candidate stars' levels of [$\alpha$/Fe] were generally consistent with galactic levels of [Mg/Fe], although its possible a slight depletion is present.
+No variation with metallicity is observed for [$\alpha$/Fe].
 
@@
 It worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K.
+For these newly identified candidate stars, neither relation between [K/Fe] and [Na/Fe] beyond probable dust effects is observed.
 
 The implications of the calculated abundances are intriguing.
-The fact that from such a large sample of field stars none were found that replicated the extreme abundance pattern of NGC 2419 is strong evidence for the cluster's uniqueness.
+The fact that from such a large sample of field stars none were found that replicated the extreme abundance pattern of NGC 2419 is strong evidence for the cluster's uniqueness regarding the extreme bi-modal nature of its abundance pattern.
 
-However, the 113 star candidate pool of K enhanced and potentially Mg depleted stars identified represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels and a range of metalicities.
+The 113 star candidate pool of K enhanced and potentially Mg depleted stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels and a range of metalicities.
 It seems likely that whatever process is responsible for these anomalous field stars is similar to whatever caused the unusual stellar populations in NGC 2419 and NGC 2808.
@@
 \end{tabular}
-\caption{My caption}
+\caption{Placeholder table}
 \label{my-label}
@@
 
-Significantly enhanced [K/Fe] is rare; significantly enhanced [K/Fe] without an accompanying depletion of [Mg/Fe] is unknown. The candidate stars are also spread across a wide range of metalicities.
+Significantly enhanced [K/Fe] is rare; significantly enhanced [K/Fe] without an accompanying depletion of [Mg/Fe] is unknown. The candidate stars are also spread across a wide range of metallicities.
 
@@
 
-This argues against any theoretical hyper-massive Population III star that might be imagined being the polluter candidate.
-While such an object might be plausible in the context of NGC 2419, and appealing given the uniqueness of the cluster, it cannot account for the production of K throughout the life of the galaxy.
+This interpretation argues against any theoretical hyper-massive Population III star, no matter how contrived, being the polluter candidate.
+While such an object might be somewhat appealing in the context of NGC 2419 given the uniqueness of the cluster, it cannot account for the production of K throughout the life of the galaxy.
 
-As emphasized by \cite{prantzos2017}, a large part of the problem presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion in Mg and an enhancement in K.
-Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{23} Na} and through Mg-Al chains at temperatures around 75 MK -  attainable in hot-bottom burning environments in AGB stars - while it takes temperatures upwards of 150 MK to produce K - temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
-This implies that the Mg depletion and K enrichment occur at separate sites, assuming a simple hydrogen burning system.
+As emphasized by \cite{prantzos2017}, a significant challenge presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion in Mg and an enhancement in K.
+Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{23} Na} and through Mg-Al chains at temperatures around 75 MK --  attainable in hot-bottom burning environments in AGB stars -- while it takes temperatures upwards of 150 MK to produce K -- temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
+This implies that the Mg depletion and K enrichment likely occur at separate sites, assuming a relatively simple hydrogen burning system.
 
-Allowing different sites for Mg depletion and K enrichment, one possible scenario that could possibly produce a large K enhanced signature along with - sometimes - potentially depleted Mg and enhanced Na throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is some less massive star.
-The scenario could play out as follows:
+Allowing different sites for Mg depletion and K enrichment, one scenario that could possibly produce a large K enhanced signature along with (inconsistently) depleted Mg and enhanced Na throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is some less massive star.
+The scenario might proceed as follows:
 
-The SAGB star produces K (destroying Na) which is then mixed throughout its envelope.
+The SAGB star produces K (destroying Na in the process \citep{prantzos2017}) which is then mixed throughout its envelope.
 It then deposits its K rich outer layers onto its smaller companion through binary accretion.
 This smaller companion would continue to evolve long after the SAGB star has formed a white-dwarf remnant and will, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, will not.
-If the companion star had sufficient mass to undergo hot bottom burning, then Na could be enhanced and Mg depleted \citep{prantzos2017}.
-In this scenario, it is this smaller binary companion star that makes up our sample of 113 giants.
+If the companion star had sufficient mass to undergo hot bottom burning, then Na could be produced and Mg depleted \citep{prantzos2017}, with this material mixed throughout the envelope.
+In this scenario, it is observations of this smaller binary companion star that make up our sample of 113 giants.
 
@@
 The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is highly unlikely, to say the least.
-This scenario is perhaps also inconsistent with the [K/Fe]-[K/H] anti-correlation, although it remains uncertain whether this phenomenon is real.
 
-A direct test of this scenario would whether at least most of the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they could have formed SAGB binaries once.
+A direct test of this scenario would be whether at least most of the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they could have formed SAGB binaries once.
 
-The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in a region(s) of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases.
+The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in at least one region of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases.
 This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419.
-If this relation is real, we can perhaps - without saying anything about the polluter star - use it to motivate an  evolutionary sequence that can account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419 and our new 113 field star sample.
+If this relation is real, we can perhaps -- without saying anything about the polluter star -- use it to motivate an evolutionary sequence that can account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419 and our new 113 field star sample.
 
-Suppose some unknown event(s) that can only occur in very metal poor (possibly zero-metallicity) environments occurs.
+Suppose some unknown event(s) unique to very metal poor (possibly zero-metallicity) environments occurs.
 This event results in a gas cloud depleted in Mg and enhanced in K.
-The generation of stars that form directly from this gas carries this signature, and displays a significant reduction in Mg abundance and enhancement in K abundance similar to NGC 2419.
+The generation of stars that form directly from this gas carries this signature, and displays a significant reduction in Mg abundance and enhancement in K abundance similar to NGC 2419's extreme population.
 We will refer to this generation of stars Generation 1.
@@
 The [Mg/Fe] depletion originally carried in the cloud is much harder to detect in the next generation of stars forming from this material, Generation 2, due to the influx of Mg released by Generation 1.
-The K enhancement however remains relatively easy to detect, having only been reduced relative to iron by the total amount of iron released.
+The K enhancement however remains (in principle) relatively easy to detect, having only been reduced relative to [Fe/H] by the total amount of iron released.
 As this cycle continues, [K/Fe] would continue to lower proportionately with the rate of iron release, while depletions in [Mg/Fe] would quickly become impossible to detect.
 
-This cycle allows for the Mg depletions to be preserved in globular clusters, where even the most massive clusters only form around 2 generations of stars.
+This cycle allows for the Mg depletions to be preserved in globular clusters, where even the most massive clusters only form at most 2 generations of stars.
 But it also allows the Mg signal to effectively be lost within the disc of the galaxy, where many generations of stars may form.
-Thus it provides a way of unifying the current observations of out 113 candidate stars with the observations of NGC 2419.
+Thus it provides a way of linking the current observations of our 113 candidate stars with the observations of NGC 2419.
 Certainly the idea that both groups of anomalous stars arise from the same polluter source must be entertained.
@@
 However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg depleted, K enriched material in the first place must be emphasized.
-Indeed, if we assume the primordial abundances are similar to those of NGC 2419's Mg-normal population, then it is impossible.
+Indeed, if we assume the primordial abundances (pre-mystery event) are similar to those of NGC 2419's Mg-normal population, then it is impossible.
 If the primordial cloud already has [Mg/Fe]$\approx 0.5$, to reduce this necessitates the addition of large amounts of iron rich material that is also very depleted in [Mg/Fe].
-But as soon significant amounts of iron are added, [Fe/H] for the subsequent the Mg-depleted population should increase.
-However, no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}.
-This implies that the polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS), or at the very least the Mg-depleted population in NGC 2419 pre-dates the Mg-normal population.
+But as soon significant amounts of iron are added, [Fe/H] for the subsequent the Mg-depleted population should increase, while no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}.
+This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS).
 
@@
 \label{sec:conclusion}
-Of the 454180 giant sample from \lamost, 113 candidate stars were identified as likely to have enhanced K and depleted Mg based on absorption spectra.
+Of the 454180 giant sample from \lamost, 113 candidate stars were identified as likely to have enhanced K and depleted Mg based on their absorption spectra.
 These stars show every appearance of being field stars, nor do they have the hallmarks of being the product of NLTE effects.
@@
 
- Upon conducting abundance analysis, it was found that despite the searching for both Mg depletions and K enhancements, the sample of stars showed no definitive Mg depletion, although it did display anomalously high levels of K.
-None of the candidates had calculated abundances of Mg or K consistent with NGC 2419 or NGC 2808's extreme populations.
+Upon conducting an abundance analysis, it was found that despite searching for both Mg depletions and K enhancements, the sample of stars showed no definitive Mg depletion, although it did display anomalously high levels of [K/Fe] relative to galactic levels.
+None of the candidates had calculated abundances of Mg or K consistent with the extreme populations of NGC 2419 or NGC 2808.
 
-The sample was also found found to be bimodal in Na, with a significant minority population of stars showing enhanced Na well above galactic levels.
-Finally, an intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains questionable.
+An intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains uncertain without further observations of the candidates.
 

### 2018-01-30 article/plotter.py
updated plotter code and added requisite csv file
code now shows which stars were observed, comparing K abundances (and alpha vs Mg abundacnes) between LAMOST and Magellan

@@ -31,8 +31,12 @@ globarray=np.array(pd.read_csv("globular_clusters.csv"))
 C_K2012=np.array(pd.read_csv("C+K 2012.csv"))
 Muc2012=np.array(pd.read_csv("Mucciarelli 2012.csv"))
 
+
 ngc2808=np.array(pd.read_csv("NGC2808 Muc 2015.csv"))
 
+lamK=np.array(pd.read_csv("provisionalKabundances.csv"))
+
+Maglam=np.array(pd.read_csv("Magellan.csv"))
 
 LC=np.array(pd.read_csv("LasCampmgkabundances.csv"))
 Teff=mgkarray[:,1]
@@ -56,9 +60,14 @@ MucKu=Muc2012[:,4]
 ngc2808Mg=ngc2808[:,0]
 ngc2808K=ngc2808[:,1]
 
+Maglamalpha=Maglam[:,4]
+MaglamK=Maglam[:,-4]
+
 LCMg=LC[:,1]
 LCK=LC[:,2]
 
+lamkk=lamK[:,-4]
+lamkalpha=lamK[:,4]
 
 catalog = lamost.load_catalog()
 wavelengths = lamost.common_wavelengths
@@ -97,7 +106,7 @@ plt.gca().invert_yaxis()
 plt.show()
 
 plt.figure(3)
-plt.scatter(mgkl, mgkb, label='Mg-K Stars', s=10)
+plt.scatter(mgkl, mgkb, label='Sample Mg-K stars', s=10)
 plt.scatter(globl, globb, label='Globular Clusters', facecolors='none', edgecolors='k')
 plt.xticks(np.arange(0, 361, 45)[::1])
 plt.xlabel('Galactic Longitude')
@@ -124,6 +133,12 @@ for cap in caps:
 
 plt.scatter(ngc2808Mg,ngc2808K, label="NGC 2808 Muc 2015", marker='o', facecolor='none', edgecolor='dimgray')
 plt.scatter(LCMg, LCK, label= "Las Campanas 2018", c='k',marker='d',zorder=100)
+
+plt.scatter(lamkalpha,lamkk)
+plt.plot((LCMg[0],Maglamalpha[0]),(LCK[0],MaglamK[0]),c='orange')
+plt.plot((LCMg[1],Maglamalpha[1]),(LCK[1],MaglamK[1]),c='orange')
[…]

### 2018-01-31 article/ms.tex
adjusted authors to preliminary ordering
included modified K vs gmog figures, modfified table, and todo'd sections that could conceivably be deleted to meet page limit

@@
 Brodie J. Norfolk,$^{1}$\newauthor
+John C. Lattanzio,$^{1}$
 Amanda I. Karakas,$^{1}$
-John C. Lattanzio,$^{1}$
 Kevin C. Schlaufman,$^{3}$\newauthor
@@
 The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
-Here we present 113 candidate field stars identified from \LamostGiants \ giants observed by \lamost \ that have slightly depleted [Mg/Fe] and significantly enhanced [K/Fe] abundance ratios.
+Here we present 112 candidate field stars identified from \LamostGiants \ giants observed by \lamost \ that have slightly depleted [Mg/Fe] and significantly enhanced [K/Fe] abundance ratios.
 These stars re present at a range of metallicities, and none have abundances that are as extreme as those in NGC 2419.
@@
 
-An early modelling attempt at replicating the anomalous Mg/K abundances assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}.
+\todo{An early modelling attempt at replicating the anomalous Mg/K abundances assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}.
 This study succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K.
-However, abundance patterns consistent with NGC 2419 were only possible if the reaction cross section was set to 100 times the commonly accepted value or if the temperature at the base of the envelope could be made to exceed $\sim$ 150 MK.
+However, abundance patterns consistent with NGC 2419 were only possible if the reaction cross section was set to 100 times the commonly accepted value or if the temperature at the base of the envelope could be made to exceed $\sim$ 150 MK.}
 
@@
 The ultimate goal was to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.
-It is perhaps noteworthy that they identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway.
-The main pathway they identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.
+\todo{ It is perhaps noteworthy that they identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway.
+The main pathway they identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.}
 
@@
 Here we use \lamost\ data to conduct the largest ever search for field stars that are enhanced in potassium and depleted in magnesium.
-The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.
-In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates.
+The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.\todo{ In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates.
 In Section \ref{sec:discussion} the results and their implications on possible poluters are discussed.
-Section \ref{sec:conclusion} summarises the main results.
+Section \ref{sec:conclusion} summarises the main results.}
 
@@
 We visually inspected every candidate (multiple times) and excluded any candidate that showed any evidence of being a false positive, including candidates that exhibited data reduction issues, apparent absorption that was narrower than the expected spectral resolution, as well as 75 stars that exhibited chromospheric emission at H$\alpha$ wavelengths.
-The distilled catalogue contains \todo{113} candidate stars enhanced in K and depleted in Mg.
+The distilled catalogue contains \todo{112} candidate stars enhanced in K and depleted in Mg.
 
@@
 
-The presence of Na enhancements were visually estimated from the sample of 113 candidate stars' flux spectra.
-Flux based estimates placed at most 40 of the 113 stars (35\%) as being likely Na enhanced targets.
-Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with Na above 0.5 dex.
+\todo{The presence of Na enhancements were visually estimated from the sample of 112 candidate stars' flux spectra.
+Flux based estimates placed at most 40 of the 112 stars (35\%) as being likely Na enhanced targets.} Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with Na above 0.5 dex.
 \todo{@andy add anything specific to Na abundance methods from LAMOST}.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{KvsMgab.png}
+	\includegraphics[width=\columnwidth]{Kvsmgmod.png}
     \caption{Comparison of [K/Fe] vs [$\alpha$/Fe] for the candidate stars with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
@@
 None of the stars appear to be associated with NGC 2419 or NGC 2808.
-From the sample, J074807.22+261514.2 is the closest star in the sky to a globular cluster, at 2.54\degree\ separation from Ko 2 \citep{koposov2007}.
-This separation is large for association with such a small, distant cluster and the star's metallicity and apparent magnitude make it even less likely to be a member.
+\todo{ From the sample, J074807.22+261514.2 is the closest star in the sky to a globular cluster, at 2.54\degree\ separation from Ko 2 \citep{koposov2007}.
+This separation is large for association with such a small, distant cluster and the star's metallicity and apparent magnitude make it even less likely to be a member.}
 
@@
 \label{sec:abundances}
-Figure \ref{KvsMg} shows [K/Fe]  for the 113 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
+Figure \ref{KvsMg} shows [K/Fe]  for the 112 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
 [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE is also shown.
@@
 
-The candidate stars' [K/Fe] also exhibits an interesting anti-correlation with total metallicity, shown in Figure \ref{KvsFe}, which is absent from measurements in the Milky Way.
+The candidate stars' [K/Fe] also exhibits an interesting anti-correlation with total metallicity, shown in Figure \ref{KvsFe}, \todo{which is absent from measurements in the Milky Way}.
 This may be consistent with a (somewhat) constant level of [K/H] between each star, which would then cause [K/Fe] to fall as [Fe/H] increases.
@@
 
-However, for reasons related to the use of both a data-driven model and a physical model for calculating abundances \todo{@andy add any elaboration on what the problem was, if necessary}, it is possible that this effect is an artefact of processing rather than a physical relation.
+However, for reasons related to the use of both a data-driven model and a physical model for calculating abundances \todo{@andy add any elaboration on what the problem was, if necessary}, it is possible that this effect is an artefact of abundance processing rather than a physical relation.
 Without further observations of the sample stars, we are unable to say with certainty whether this phenomena is real or not.
 
-The candidate stars' levels of [$\alpha$/Fe] were generally consistent with galactic levels of [Mg/Fe], although its possible a slight depletion is present.
+The candidate stars' levels of [$\alpha$/Fe] were generally consistent with galactic levels of [Mg/Fe], although again it's possible a slight depletion is present.
 No variation with metallicity is observed for [$\alpha$/Fe].
@@
 However, this behaviour is very likely due to the effect of interstellar dust; it was found that the values of E(B-V), taken from IRSA's all-sky dust map \citep{schlafly2011}, were higher for the stars supposedly enriched in Na than for those displaying galactic levels.
-It worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K.
-For these newly identified candidate stars, neither relation between [K/Fe] and [Na/Fe] beyond probable dust effects is observed.
+\todo{It worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K.
+For these newly identified candidate stars, neither relation between [K/Fe] and [Na/Fe] beyond probable dust effects is observed.}
 
@@
 
-The 113 star candidate pool of K enhanced and potentially Mg depleted stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels and a range of metalicities.
+The 112 star candidate pool of K enhanced and potentially Mg depleted stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels and exist at a range of metalicities.
 It seems likely that whatever process is responsible for these anomalous field stars is similar to whatever caused the unusual stellar populations in NGC 2419 and NGC 2808.
@@
 \centering
-\begin{tabular}{llllllllll}
+\caption{Tabulated data for 10 of the 112 candidate stars. Data for the full sample is available online.}
+\label{my-label}
+\begin{tabular}{cccccccccccccc}
 \hline
-\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{Vr (km/s)} & \textbf{Teff} & \textbf{Logg} & \textbf{[Fe/H]} & \textbf{[Alpha/Fe]} & {$\boldsymbol \chi^\textbf{2}$} \\ \hline
-J060142.80+132321.4 & 90.43 & 13.39 & 45 & 33.28 & 4858 & 2.57 & -0.30 & 0.10 & 0.24 \\ \hline
-J075043.12+204658.0 & 117.68 & 20.78 & 47 & 52.46 & 4795 & 2.53 & -0.47 & 0.06 & 0.40 \\ \hline
-J032450.35+352401.8 & 51.21 & 35.40 & 143 & 95.63 & 4908 & 3.33 & -0.27 & 0.19 & 0.70 \\ \hline
-J214721.25+023958.7 & 326.84 & 2.67 & 104 & -63.83 & 4649 & 2.22 & -0.68 & 0.26 & 0.81 \\ \hline
-J040340.38+563902.4 & 60.92 & 56.65 & 30 & 39.87 & 4459 & 2.05 & -0.46 & 0.01 & 0.61 \\ \hline
-J035455.85+594730.3 & 58.73 & 59.79 & 57 & -40.17 & 4956 & 2.81 & 0.08 & 0.04 & 0.56 \\ \hline
-J035928.29+595932.8 & 59.87 & 59.99 & 35 & -38.07 & 4808 & 2.44 & -0.53 & 0.16 & 0.32 \\ \hline
-J034458.82+592955.1 & 56.25 & 59.50 & 53 & -32.68 & 4811 & 2.66 & 0.06 & 0.10 & 0.64 \\ \hline
-J220657.78+232138.3 & 331.74 & 23.36 & 50 & -27.58 & 4842 & 3.34 & -0.40 & 0.10 & 0.23 \\ \hline
-J061323.14+325543.0 & 93.35 & 32.93 & 39 & -25.78 & 4861 & 2.51 & -0.40 & 0.16 & 0.42 \\ \hline
-J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.10 & 0.44 \\ \hline
-J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 \\ \hline
-J040817.31+463252.5 & 62.07 & 46.55 & 92 & -1.80 & 5019 & 2.68 & -0.09 & 0.05 & 0.98 \\ \hline
-J072156.18+225405.3 & 110.48 & 22.90 & 101 & -46.77 & 4840 & 2.54 & -0.33 & 0.17 & 0.69 \\ \hline
-J040634.97+411354.9 & 61.65 & 41.23 & 45 & -35.38 & 4770 & 2.67 & -0.26 & 0.07 & 0.51 \\ \hline
-J041608.62+433504.7 & 64.04 & 43.58 & 30 & -20.09 & 4967 & 2.90 & -0.17 & 0.04 & 0.33 \\ \hline
-J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 \\ \hline
-J052924.25+494319.7 & 82.35 & 49.72 & 94 & -22.48 & 5087 & 3.12 & -0.35 & 0.11 & 0.70 \\ \hline
-J061427.58+331544.3 & 93.61 & 33.26 & 51 & 3.30 & 4468 & 1.87 & -0.41 & 0.11 & 0.67 \\ \hline
-J062128.63+343545.8 & 95.37 & 34.60 & 39 & 33.28 & 4831 & 2.58 & -0.23 & 0.08 & 0.27 \\ \hline
-J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 \\ \hline
-J120032.60+024438.2 & 180.14 & 2.74 & 97 & 166.98 & 4633 & 2.33 & -0.93 & 0.26 & 0.89 \\ \hline
-J163910.01+100545.3 & 249.79 & 10.10 & 39 & 123.81 & 4663 & 2.46 & -0.58 & 0.03 & 0.61 \\ \hline
+\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{V$_\textrm{r}$} & \textbf{T$_\textrm{eff}$} & $\boldsymbol \log{ \, \textbf{g}}$ & \textbf{{[}Fe/H{]}} & \textbf{{[}$\alpha$/Fe{]}} & \textbf{$\boldsymbol \chi_r ^\textbf{2}$} & \textbf{{[}K/Fe{]}} & \textbf{Error} & \textbf{{[}Na/Fe{]}} & \textbf{Error} \\
+- & {[}deg{]} & {[}deg{]} & [pixel$^{-1}]$ & {[${\rm km\,s}^{-1}$]} & {[}K{]} & $[{\rm cm\,s}^{-2}]$ & {[}dex{]} & {[}dex{]} & - & {[}dex{]} & {[}dex{]} & {[}dex{]} & {[}dex{]} \\ \hline
+J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.16 & 0.86 & 0.12 \\
+J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.08 & 0.39 & 0.10 \\
+J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.06 & -0.20 & 0.00 \\
+J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 & 0.96 & 0.26 & -0.16 & 0.00 \\
+J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.10 & 0.44 & 0.76 & 0.11 & -0.02 & 0.00 \\
+J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.10 & 0.05 & 1.17 & 0.95 & 0.06 & -0.07 & 0.00 \\
+J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.00 & -0.04 & 0.00 \\
+J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.05 & 0.46 & 0.05 \\
+J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1.00 & 8.70 & -0.02 & 0.00 \\
+J032423.46+425429.6 & 51.10 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.09 & 0.80 & 0.04 \\ \hline
 \end{tabular}
-\caption{Placeholder table}
-\label{my-label}
 \end{table*}
@@
 This spread in metallicity is important: taken in isolation, it implies that the process responsible for this signature, rare as it is, is not necessarily tied to a certain epoch in the evolutionary history of our galaxy.
-Rather, these stars appear to be continuously forming in successive generations.
+Rather, these stars appear to be continuously forming \todo{ in successive generations}.
 
@@
 If the companion star had sufficient mass to undergo hot bottom burning, then Na could be produced and Mg depleted \citep{prantzos2017}, with this material mixed throughout the envelope.
-In this scenario, it is observations of this smaller binary companion star that make up our sample of 113 giants.
+In this scenario, it is observations of this smaller binary companion star that make up our sample of 112 giants.
 
 Although this scenario allows for consistency with the total spread in metallicity, it doe not account for the uniqueness of the signal to NGC 2419 and NGC 2808 among globular clusters, nor does it satisfactorily explain why such a large proportion of stars in NGC 2419 exhibit the Mg-K anti-correlation.
-The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is highly unlikely, to say the least.
+\todo{The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is highly unlikely, to say the least.}
 
@@
 This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419.
-If this relation is real, we can perhaps -- without saying anything about the polluter star -- use it to motivate an evolutionary sequence that can account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419 and our new 113 field star sample.
+If this relation is real, we can perhaps -- without saying anything about the polluter star -- use it to motivate an evolutionary sequence that can account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419 and our new 112 field star sample.
 
@@
 But it also allows the Mg signal to effectively be lost within the disc of the galaxy, where many generations of stars may form.
-Thus it provides a way of linking the current observations of our 113 candidate stars with the observations of NGC 2419.
+Thus it provides a way of linking the current observations of our 112 candidate stars with the observations of NGC 2419.
 Certainly the idea that both groups of anomalous stars arise from the same polluter source must be entertained.
 
-However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg depleted, K enriched material in the first place must be emphasized.
+\todo{However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg depleted, K enriched material in the first place must be emphasized.
 Indeed, if we assume the primordial abundances (pre-mystery event) are similar to those of NGC 2419's Mg-normal population, then it is impossible.
@@
 But as soon significant amounts of iron are added, [Fe/H] for the subsequent the Mg-depleted population should increase, while no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}.
-This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS).
+This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS).}
 
@@
 \label{sec:conclusion}
-Of the 454180 giant sample from \lamost, 113 candidate stars were identified as likely to have enhanced K and depleted Mg based on their absorption spectra.
+Of the 454180 giant sample from \lamost, 112 candidate stars were identified as likely to have enhanced K and depleted Mg based on their absorption spectra.
 These stars show every appearance of being field stars, nor do they have the hallmarks of being the product of NLTE effects.
@@
 
-\begin{comment}
-\begin{table}[H]
-\centering
-\begin{tabular}{llllllllll}
-\hline
-\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{Radial\_Velocity\_(km/s)} & \textbf{Teff} & \textbf{Logg} & \textbf{{[}Fe/H{]}} & \textbf{{[}Alpha/Fe{]}} & \textbf{$\chi^2$} \\ \hline
-J234942.32+300654.0 & 357.43 & 30.11 & 20 & -195.46 & 4004 & 1.12 & -0.58 & 0.23 & 2.73 \\ \hline
-J065334.23+131639.7 & 103.39 & 13.28 & 7 & 179.88 & 4896 & 2.61 & -0.71 & 0.02 & 0.18 \\ \hline
-J112309.75+261255.9 & 170.79 & 26.22 & 3 & 113.02 & 4273 & 1.13 & -1.35 & 0.17 & 0.09 \\ \hline
-J111651.71+253038.5 & 169.22 & 25.51 & 6 & 102.83 & 4658 & 2.90 & -0.50 & 0.02 & 0.08 \\ \hline
-J045424.86+534628.5 & 73.60 & 53.77 & 6 & -36.57 & 4451 & 1.81 & -0.19 & 0.07 & 0.37 \\ \hline
-J065857.80+081714.8 & 104.74 & 8.29 & 12 & 26.68 & 5070 & 3.30 & -0.61 & 0.10 & 0.18 \\ \hline
-J045544.93+490023.3 & 73.94 & 49.01 & 6 & -38.07 & 4717 & 2.55 & -0.34 & 0.11 & 0.11 \\ \hline
-J040739.62+423724.4 & 61.92 & 42.62 & 9 & -37.77 & 4075 & 1.54 & -0.32 & 0.08 & 0.28 \\ \hline
-J043121.48+414757.2 & 67.84 & 41.80 & 8 & -12.59 & 4537 & 2.07 & -0.09 & 0.03 & 0.13 \\ \hline
-J041900.21+422223.9 & 64.75 & 42.37 & 12 & -34.18 & 4263 & 1.77 & -0.55 & 0.09 & 0.28 \\ \hline
-J041209.44+411801.0 & 63.04 & 41.30 & 35 & -20.69 & 4767 & 2.24 & -0.26 & 0.12 & 0.91 \\ \hline
-J063648.82+130723.3 & 99.20 & 13.12 & 8 & 85.74 & 4925 & 2.93 & -0.57 & -0.03 & 0.19 \\ \hline
-J070524.04+120351.0 & 106.35 & 12.06 & 19 & 60.26 & 4754 & 2.64 & -0.56 & -0.02 & 0.24 \\ \hline
-J063501.25+134744.6 & 98.76 & 13.80 & 7 & 47.67 & 4612 & 2.33 & -0.40 & 0.01 & 0.19 \\ \hline
-J053942.83+383727.8 & 84.93 & 38.62 & 18 & -85.74 & 4979 & 2.26 & -0.66 & 0.23 & 0.27 \\ \hline
-J053123.26+421952.0 & 82.85 & 42.33 & 8 & 41.07 & 4785 & 2.59 & -0.26 & 0.01 & 0.26 \\ \hline
-J052643.65+354130.3 & 81.68 & 35.69 & 9 & -18.89 & 4914 & 2.73 & -0.09 & 0.03 & 0.28 \\ \hline
-J064618.82+050545.8 & 101.58 & 5.10 & 9 & 85.74 & 4772 & 2.66 & -0.49 & -0.01 & 0.28 \\ \hline
-J063719.82+185602.6 & 99.33 & 18.93 & 5 & 15.29 & 5075 & 2.94 & -0.12 & 0.03 & 0.10 \\ \hline
-J072912.52+073436.9 & 112.30 & 7.58 & 9 & 117.52 & 4835 & 3.18 & -0.44 & 0.33 & 0.34 \\ \hline
-J193217.91+374505.6 & 293.07 & 37.75 & 28 & -70.15 & 4982 & 2.62 & -0.48 & 0.33 & 0.55 \\ \hline
-J192937.24+390211.0 & 292.41 & 39.04 & 6 & -52.16 & 4819 & 3.00 & 0.37 & 0.12 & 0.21 \\ \hline
-J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.10 & 0.05 & 1.17 \\ \hline
-J235454.61+110356.9 & 358.73 & 11.07 & 12 & -109.72 & 4794 & 3.07 & -0.16 & 0.30 & 0.21 \\ \hline
-J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 \\ \hline
-J220115.66-001432.2 & 330.32 & -0.24 & 47 & 38.37 & 4925 & 3.30 & 0.06 & 0.23 & 0.32 \\ \hline
-J064430.22+341606.3 & 101.13 & 34.27 & 9 & -40.17 & 4809 & 3.26 & 0.36 & 0.19 & 0.31 \\ \hline
-J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 \\ \hline
-J033714.25+403015.1 & 54.31 & 40.50 & 34 & -119.32 & 4674 & 2.33 & 0.32 & 0.22 & 0.86 \\ \hline
-J074807.22+261514.2 & 117.03 & 26.25 & 16 & -32.98 & 4846 & 2.69 & -0.23 & 0.05 & 0.16 \\ \hline
-J032423.46+425429.6 & 51.10 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 \\ \hline
-J055043.44+162021.2 & 87.68 & 16.34 & 24 & 83.64 & 4587 & 2.49 & 0.21 & 0.07 & 0.28 \\ \hline
-J055227.43+181628.0 & 88.11 & 18.27 & 28 & 8.09 & 5388 & 3.80 & -0.17 & 0.05 & 0.43 \\ \hline
-J055935.08+150252.1 & 89.90 & 15.05 & 23 & 90.84 & 4487 & 2.15 & -0.68 & 0.01 & 4.35 \\ \hline
-J063113.14+015900.3 & 97.80 & 1.98 & 14 & 78.55 & 4879 & 2.34 & -0.13 & 0.01 & 0.56 \\ \hline
-J111550.58+104203.9 & 168.96 & 10.70 & 9 & 114.82 & 4519 & 1.72 & -1.41 & 0.32 & 0.17 \\ \hline
-J111022.65+171251.0 & 167.59 & 17.21 & 12 & 247.33 & 4524 & 1.92 & -1.30 & 0.13 & 0.30 \\ \hline
-J100054.32+185535.5 & 150.23 & 18.93 & 17 & 149.00 & 4373 & 2.30 & 0.01 & 0.01 & 0.39 \\ \hline
-J055908.72+210037.7 & 89.79 & 21.01 & 6 & 55.76 & 4325 & 1.99 & -0.10 & -0.03 & 0.75 \\ \hline
-J055704.30+215000.1 & 89.27 & 21.83 & 9 & 49.77 & 4691 & 2.94 & 0.37 & 0.00 & 0.30 \\ \hline
-J104800.91+424311.0 & 162.00 & 42.72 & 6 & 163.99 & 5050 & 2.75 & -1.29 & 0.12 & 0.18 \\ \hline
-J075129.58+024136.9 & 117.87 & 2.69 & 18 & 128.61 & 4741 & 2.39 & -0.61 & 0.05 & 0.28 \\ \hline
-J064132.46+580400.9 & 100.39 & 58.07 & 24 & -11.69 & 5285 & 3.74 & -0.06 & 0.07 & 0.36 \\ \hline
-J063908.57+381728.0 & 99.79 & 38.29 & 5 & 25.78 & 4853 & 2.73 & -0.52 & 0.02 & 0.17 \\ \hline
-J102104.26+105617.4 & 155.27 & 10.94 & 17 & 171.48 & 4526 & 1.88 & -1.09 & 0.07 & 0.28 \\ \hline
-J061228.04-040304.1 & 93.12 & -4.05 & 16 & -1.50 & 4928 & 3.24 & -0.56 & 0.09 & 0.19 \\ \hline
-J061144.17-040845.1 & 92.93 & -4.15 & 23 & 84.54 & 4709 & 2.77 & -0.42 & -0.00 & 0.24 \\ \hline
-J074848.57+210655.5 & 117.20 & 21.12 & 9 & 101.33 & 4447 & 2.25 & -0.52 & 0.04 & 0.11 \\ \hline
-J092124.00+204559.5 & 140.35 & 20.77 & 12 & 125.31 & 4570 & 2.28 & -0.71 & 0.06 & 0.31 \\ \hline
-J074146.65+145330.5 & 115.44 & 14.89 & 6 & 105.53 & 4701 & 2.00 & -0.71 & 0.04 & 0.18 \\ \hline
-J073641.12+164710.6 & 114.17 & 16.79 & 6 & 90.84 & 4621 & 2.17 & -0.77 & 0.01 & 0.26 \\ \hline
-J175211.80+273546.6 & 268.05 & 27.60 & 7 & -33.58 & 5489 & 3.71 & -0.03 & 0.14 & 0.15 \\ \hline
-J194028.76+504047.6 & 295.12 & 50.68 & 22 & -61.76 & 4352 & 1.94 & -0.17 & 0.23 & 0.35 \\ \hline
-J213914.06+025536.2 & 324.81 & 2.93 & 29 & 57.78 & 4488 & 2.40 & -0.37 & 0.05 & 0.46 \\ \hline
-J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 \\ \hline
-J041055.45+570542.6 & 62.73 & 57.10 & 16 & -32.38 & 4141 & 1.66 & -0.23 & 0.07 & 0.47 \\ \hline
-J035840.66+574934.5 & 59.67 & 57.83 & 17 & -56.06 & 4693 & 2.02 & -0.28 & 0.14 & 0.46 \\ \hline
-J034552.01+595739.3 & 56.47 & 59.96 & 17 & -48.57 & 4627 & 2.07 & -0.38 & 0.16 & 0.41 \\ \hline
-J193130.64+432204.2 & 292.88 & 43.37 & 16 & -92.64 & 4934 & 3.08 & -0.16 & 0.30 & 0.26 \\ \hline
-J042753.62+365550.6 & 66.97 & 36.93 & 8 & -30.08 & 5249 & 2.91 & -0.21 & 0.18 & 0.30 \\ \hline
-J061808.85+313338.2 & 94.54 & 31.56 & 12 & 42.57 & 4970 & 3.03 & -0.15 & 0.10 & 0.55 \\ \hline
-J050740.59+492955.0 & 76.92 & 49.50 & 15 & 18.29 & 3879 & 0.96 & -0.72 & 0.06 & 0.54 \\ \hline
-J050606.74+494925.0 & 76.53 & 49.82 & 25 & -28.78 & 4857 & 2.50 & -0.25 & 0.12 & 0.34 \\ \hline
-J050551.93+493726.0 & 76.47 & 49.62 & 15 & -18.59 & 4961 & 2.85 & -0.47 & 0.07 & 0.27 \\ \hline
-J051046.05+523848.3 & 77.69 & 52.65 & 47 & -46.17 & 4697 & 2.61 & -0.34 & 0.26 & 1.03 \\ \hline
-J041321.95+520135.7 & 63.34 & 52.03 & 19 & -51.35 & 4694 & 2.48 & -0.05 & 0.05 & 0.50 \\ \hline
-J065356.76+344513.1 & 103.49 & 34.75 & 21 & -23.38 & 4533 & 2.46 & -0.00 & 0.15 & 0.28 \\ \hline
-J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 \\ \hline
-J040034.51+472103.8 & 60.14 & 47.35 & 18 & -55.82 & 4708 & 2.39 & -0.01 & 0.10 & 0.65 \\ \hline
-J041304.73+470013.8 & 63.27 & 47.00 & 17 & 19.19 & 4290 & 1.79 & -0.37 & 0.03 & 0.79 \\ \hline
-J035633.86+463749.2 & 59.14 & 46.63 & 17 & -54.93 & 4753 & 2.37 & -0.05 & 0.12 & 0.34 \\ \hline
-J053627.38+581132.8 & 84.11 & 58.19 & 28 & -32.94 & 4457 & 2.52 & 0.28 & 0.05 & 0.49 \\ \hline
-J052516.26+585912.5 & 81.32 & 58.99 & 19 & -75.07 & 4023 & 1.50 & -0.22 & 0.05 & 0.51 \\ \hline
-J034826.25+350123.4 & 57.11 & 35.02 & 100 & -47.97 & 4710 & 2.89 & 0.04 & 0.38 & 4.72 \\ \hline
-J035652.48+325937.2 & 59.22 & 32.99 & 24 & -20.99 & 4038 & 1.38 & -0.31 & 0.08 & 0.55 \\ \hline
-J035345.63+340429.3 & 58.44 & 34.07 & 15 & -34.48 & 4830 & 3.23 & -0.56 & 0.06 & 0.14 \\ \hline
-J042245.32+430359.8 & 65.69 & 43.07 & 16 & -35.08 & 4967 & 2.92 & -0.13 & 0.03 & 0.20 \\ \hline
-J042241.36+414255.6 & 65.67 & 41.72 & 15 & -92.76 & 4975 & 3.32 & -0.66 & 0.02 & 0.27 \\ \hline
-J053148.24+225045.6 & 82.95 & 22.85 & 15 & 11.69 & 3982 & 0.71 & -0.84 & 0.08 & 0.63 \\ \hline
-J120844.42-012151.8 & 182.19 & -1.36 & 18 & 143.30 & 4783 & 2.28 & -0.84 & 0.28 & 0.48 \\ \hline
-J091825.49+172114.5 & 139.61 & 17.35 & 11 & 232.04 & 4898 & 2.71 & -1.19 & 0.29 & 0.14 \\ \hline
-J123413.43+160353.7 & 188.56 & 16.06 & 10 & 316.88 & 4734 & 2.63 & -0.99 & 0.03 & 0.17 \\ \hline
-J054656.93+442800.0 & 86.74 & 44.47 & 17 & -41.37 & 4758 & 2.51 & -0.27 & 0.09 & 0.15 \\ \hline
-J053423.46+460026.9 & 83.60 & 46.01 & 21 & -40.77 & 4893 & 2.73 & -0.18 & 0.10 & 0.26 \\ \hline
-J052814.58+511912.4 & 82.06 & 51.32 & 16 & -64.76 & 4344 & 1.95 & -0.06 & 0.10 & 0.51 \\ \hline
-J044403.36+543203.6 & 71.01 & 54.53 & 19 & -71.05 & 4625 & 1.91 & 0.25 & 0.07 & 1.42 \\ \hline
-J043503.82+552514.6 & 68.77 & 55.42 & 19 & 9.59 & 4704 & 2.48 & -0.11 & 0.04 & 0.60 \\ \hline
-J043418.64+535250.2 & 68.58 & 53.88 & 17 & -141.15 & 4204 & 1.44 & -0.64 & 0.19 & 0.76 \\ \hline
-J070937.38+201517.2 & 107.41 & 20.25 & 9 & 148.10 & 3770 & 0.19 & -1.24 & 0.04 & 0.46 \\ \hline
-J064032.35+335207.5 & 100.13 & 33.87 & 8 & -34.48 & 4717 & 2.28 & -0.44 & 0.24 & 0.24 \\ \hline
-\end{tabular}
-\caption{Remaining candidates}
-\label{Resttab}
-\end{table}
-\end{comment}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-02-02 article/ms.tex
Made changes in line with feedback and discussions with John and Amanda

@@
 Stellar absorption spectra act as a fossil record of the conditions where the stars form.
-Stars with unusual elemental abundances are of particular interest; these rare stars often offer clues about rare astrophysical events or nucleosynthetic pathways.
-Stars with  depleted Mg and enhanced K abundances have thus far only been found in the two massive globular clusters NGC 2419 and NGC 2808.
+Stars with unusual elemental abundances are of particular interest; these rare stars offer clues about rare astrophysical events or nucleosynthetic pathways.
+Stars with  depleted Mg and enhanced K abundances have so far only been found in the two massive globular clusters NGC 2419 and NGC 2808.
 The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
-Here we present 112 candidate field stars identified from \LamostGiants \ giants observed by \lamost \ that have slightly depleted [Mg/Fe] and significantly enhanced [K/Fe] abundance ratios.
-These stars re present at a range of metallicities, and none have abundances that are as extreme as those in NGC 2419.
-These candidate stars should provide guidance for follow up surveys and modelling attempts attempting to determine the origin of the Mg-K anti-correlation.
+Here we present 112 candidate field stars identified from \LamostGiants \ giants observed by \lamost \ that uncertain [Mg/Fe] but significantly enhanced [K/Fe] abundance ratios.
+These stars are present at a range of metallicities, and none have abundances that are as extreme as those in NGC 2419.
+These candidate stars should provide guidance for follow up surveys and modelling attempting to determine the origin of the Mg-K anti-correlation.
 
@@
 NGC 2419 is the Milky Way's third most massive globular cluster, and its chemical composition makes it perhaps the most unusual star cluster in the Galaxy.
-Recent spectroscopic studies of red giant branch (RGB) stars in NGC 2419 revealed a strong anti-correlation between Mg and K abundances in nearly half of the studied stars, and weaker abundance relations in Si, Sc, Ca, Ti and V \citep{mucciarelli2012,cohenkirby2012}.
+Recent spectroscopic studies of red giant branch (RGB) stars in NGC 2419 revealed a strong anti-correlation between Mg and K abundances in nearly half of the studied stars, and weaker abundance relations in Si, Sc, Ca, Ti and V with Mg \citep{mucciarelli2012,cohenkirby2012}.
 
-The only known mechanism for Mg depletion is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the `normal' [Mg/Fe] ratios that arise from Type II supernovae.
+A targeted search looking for [K/Fe] in RGB and main sequence turn-off stars from clusters NGC 6752, NGC 6121, NGC 1904, 47 Tuc, NGC 6397, NGC 7099, and $\omega$ Centauri as well as 21 field stars found in all cases  that the K abundance fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}.
+NGC 2808 is the only cluster other than NGC 2419 where an anticorrelation between Mg and K has been observed.
+All 4 of NGC 2808's known Mg-depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these anomalous abundances was far weaker than that in NGC 2419.
+The fact that the Mg-K anti-correlation is apparently confined to these two globular clusters would seem to imply either a small population of unusual polluter stars or a single extremely massive polluter star.
+
+One  mechanism for [Mg/Fe] depletion is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the `normal' [Mg/Fe] ratios that arise from Type II supernovae.
 However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}.
@@
 
+The other avenue for potentially reducing [Mg/Fe] is high temperature H-burning through Mg-Al chains.
+However, no Al correlation is observed with the Mg depletions in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.
+
 %Recently \cite{youngwooklee} used a Ca filter to identify two population in NGC 2419 corresponding to two generations of stars: G1, first generation metal poor stars, and G2, second generation stars displaying enhanced Ca and significantly increased He abundance ($\Delta Y = 0.19$).
-The Mg depleted population identified previously was found to be contained with the G2 population.
-
-A targeted search looking for [K/Fe] in RGB and main sequence turn-off stars from clusters NGC 6752, NGC 6121, NGC 1904, 47 Tuc, NGC 6397, NGC 7099, and $\omega$ Centauri as well as 21 field stars found in all cases  that theK abundance fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}.
-NGC 2808 is the only cluster other than NGC 2419 where an anticorrelation between Mg and K has been observed.
-All 4 of NGC 2808's known Mg depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these anomalous abundances was far weaker than that in NGC 2419.
-The fact that the Mg-K anti-correlation is apparently confined to these two globular clusters would seem to imply either a small population of unusual polluter stars or a single extremely massive polluter star.
+The Mg-depleted population identified previously was found to be contained with the G2 population.
 
@@
 This study succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K.
-However, abundance patterns consistent with NGC 2419 were only possible if the reaction cross section was set to 100 times the commonly accepted value or if the temperature at the base of the envelope could be made to exceed $\sim$ 150 MK.}
+However, abundance patterns consistent with NGC 2419 were only possible if the Ar-K reaction cross section was set to 100 times the commonly accepted value or if the temperature at the base of the envelope could be made to exceed $\sim$ 150 $\times 10^6$ K (hereafter MK).}
 
@@
 It was found that (excepting the case of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required.
-Using this information, core -- and shell --  burning of low-mass, high-mass and super-massive stars were ruled out as potential polluters, as well as regular AGB stars.
+Using this information, core and shell burning of low-mass, high-mass and super-massive stars were ruled out as potential polluters, as well as regular AGB stars.
 Super-AGB (SAGB) stars, however, were regarded as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
-The other potential candidate identified was novae, although the lack of detailed models of white dwarf accretion of metal-poor material limits certainty in this case.
-However, based on current novae frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1 \% of the total required mass to pollute 30 \% of NGC 2419.
+The other potential candidate identified were novae, although the lack of detailed models of white dwarf accretion of metal-poor material adds considerable uncertainty.
+However, based on current nova frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1\% of the total required mass to pollute 30\% of NGC 2419.
 
@@
 Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg-K anti-correlation, a satisfactory explanation for the Mg-K signature could offer insight into the underestimation of K abundances in the Milky Way predicted by galactic chemical evolution models \citep{kobayashi2011}.
-Such an explanation could also be beneficial to efforts to understand globular cluster formation and evolution.
+Recent work by \cite{ritter2017} on K production in O-C shell mergers shows promise as an alternative source of K, if their results can be confirmed in a fully 3D simulation.
+Identifying the source of the Mg-K anti-correlation could also be beneficial to efforts to understand globular cluster formation and evolution.
 
 Here we use \lamost\ data to conduct the largest ever search for field stars that are enhanced in potassium and depleted in magnesium.
-The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.\todo{ In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates.
+The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.
+In particular, the search should provide strong evidence for the uniqueness of the mysterious site of nucleosynthesis responsible for the pattern to globular clusters, or lack thereof.
+\todo{ In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates.
 In Section \ref{sec:discussion} the results and their implications on possible poluters are discussed.
@@
 A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model).
+Figure 1 shows the LAMOST spectra, along with the star's model from the \tc, for candidate J034458.82+592955.1.
 
-We fitted a gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167 \AA, 5172 \AA, 5184 \AA) as well as the K doublet (7665 \AA, 7699 \AA) for all \LamostGiants\ giants in \lamost\ data release 2 (DR2).
+We fitted a gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167 \AA, 5172 \AA, 5184 \AA) as well as the K doublet (7665 \AA, 7699 \AA) for all \LamostGiants\ giants.
 For every star we recorded the profile amplitudes, wavelengths, widths, as well as associated measurement uncertainties of these quantities.
@@
 \todo{The presence of Na enhancements were visually estimated from the sample of 112 candidate stars' flux spectra.
-Flux based estimates placed at most 40 of the 112 stars (35\%) as being likely Na enhanced targets.} Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with Na above 0.5 dex.
+Flux-based estimates placed at most 40 of the 112 stars (35\%) as being likely Na enhanced targets.} Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with [Na/Fe] above 0.5 dex.
 \todo{@andy add anything specific to Na abundance methods from LAMOST}.
@@
     \caption{Comparison of [K/Fe] vs [$\alpha$/Fe] for the candidate stars with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
+See text for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].
 The dotted line is arbitrary, and is present simply as a visual aide.}
@@
 	\includegraphics[width=\columnwidth]{KvsFe.png}
-    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.}
+    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
+Metalicities for NGC 2808 are taken as the average metalicity for the cluster from \citet{harris1996}, as individual metallicities for these stars were not available.}
     \label{KvsFe}
@@
 \todo{ From the sample, J074807.22+261514.2 is the closest star in the sky to a globular cluster, at 2.54\degree\ separation from Ko 2 \citep{koposov2007}.
-This separation is large for association with such a small, distant cluster and the star's metallicity and apparent magnitude make it even less likely to be a member.}
+This separation is large for association with such a small, distant cluster and the star's metallicity of -0.24 dex and apparent magnitude make it even less likely to be a member.}
 
@@
 The distribution reflects the original \LamostGiants \ sample of giants from which the candidates were drawn.
-No stars are present at [Fe/H]$\sim -2$ -- the approximate metallicity of NGC 2419 -- nor are there many stars with [Fe/H]$\sim -1$ -- the metallicity of NGC 2808.
+No stars are present with [Fe/H]$\sim -2$ -- the approximate metallicity of NGC 2419 -- nor are there many stars with [Fe/H]$\sim -1$ -- the metallicity of NGC 2808.
 Thus, we conclude that the candidates are not particular to any specific metallicity, including metallicites associated with NGC 2419 and NGC 2808.
@@
 [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE is also shown.
-The use of [$\alpha$/Fe] as a proxy for [Mg/Fe] is supported by the [Mg/Fe] measurements from the high-resolution spectra, these being similar to the [$\alpha$/Fe] abundances from \tc.
+As described in \ref{sec:method}, acceptably reliable abundances for Mg were unable to be obtained using the \lamost\ spectra.
+The use of $[\alpha$/Fe] to position the sample in \ref{KvsMg} is supported by the [Mg/Fe] measurements from the high-resolution spectra, which vary less than 0.1 dex from the level of $[\alpha$/Fe] for each of the relevant stars in the \lamost\ data.
+However, for the bulk of the sample decoupling [Mg/Fe] from $[\alpha$/Fe] is impossible, and so in general  we are unable to draw firm conclusions as to whether the sample exhibits anomalously low [Mg/Fe].
 
@@
 It is noteworthy that both of these populations identified in NGC 2808 have significantly lower levels of [K/Fe] than the candidate stars.
-Levels of [$\alpha$/Fe] fall within the lower limits of the Mg-normal population of both clusters, although as this represents only an upper limit the exact level of Mg depletion for the candidates is unclear.
-The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra suggest that at most a small depletion relative to the Mg-normal population in NGC 2419 may be present.
+Levels of [$\alpha$/Fe] fall within the lower limits of the Mg-normal population of both clusters, although as we are unable to decouple [Mg/Fe] from $[\alpha$/Fe] the exact level of Mg depletion for the candidates is unclear.
+The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra are consistent with the Mg-normal population in NGC 2419, although the small sample of these stars for which we have high resolution spectra means we are unable to confidently generalise this to the entire sample.
 
-A similar relationship emerges when comparing with typical galactic numbers for [K/Fe] and [Mg/Fe], taken from \cite{kobayashi2011}.
-Only the sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$ dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8-1.3.
-Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample are likely to have extremely high levels of [K/Fe].
+A similar relationship emerges when these abundances with typical galactic abundances for [K/Fe] and [Mg/Fe], taken from \cite{kobayashi2011}.
+The sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$ dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8-1.3.
+Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample has extremely high levels of [K/Fe].
 
@@
 This may be consistent with a (somewhat) constant level of [K/H] between each star, which would then cause [K/Fe] to fall as [Fe/H] increases.
-It is interesting that the Mg-poor population of NGC 2419 appears to fit this relation.
+It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation.
+\todo{make figure in python, add trend line}
 
@@
 
-The candidate stars' levels of [$\alpha$/Fe] were generally consistent with galactic levels of [Mg/Fe], although again it's possible a slight depletion is present.
-No variation with metallicity is observed for [$\alpha$/Fe].
+The candidate stars' levels of [$\alpha$/Fe] were generally consistent with galactic levels of [Mg/Fe], as were the levels of [Mg/Fe] from the high resolution Magellan/MIKE spectra.
+Once again the inability to decouple [Mg/Fe] from $[\alpha$/Fe] means we are unable do draw firm conclusions about whether [Mg/Fe] is depleted relative to typical field stars, although the data we do have suggests not.
+No variation with metallicity is observed for [$\alpha$/Fe], including GCE effects relating of Type Ia supernovae enrichments.
 
@@
 Two distinct populations were observed, with a substantial minority of approximately 30\% of the sample having [Na/Fe] > 0.5, significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}.
-However, this behaviour is very likely due to the effect of interstellar dust; it was found that the values of E(B-V), taken from IRSA's all-sky dust map \citep{schlafly2011}, were higher for the stars supposedly enriched in Na than for those displaying galactic levels.
-\todo{It worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K.
-For these newly identified candidate stars, neither relation between [K/Fe] and [Na/Fe] beyond probable dust effects is observed.}
+However, this behaviour is very likely due to the effect of interstellar dust.
+This conclusion is based on values of E(B-V), taken from IRSA's all-sky dust map \citep{schlafly2011}, which were notably higher for the stars supposedly enriched in Na than for those consistent with galactic levels.
+\todo{It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K.
+For these newly identified candidate stars, no relation between Na and K abundance is observed.}
 
@@
 The fact that from such a large sample of field stars none were found that replicated the extreme abundance pattern of NGC 2419 is strong evidence for the cluster's uniqueness regarding the extreme bi-modal nature of its abundance pattern.
+It is worth repeating however that the sample of \lamost\ giants searched had already been filtered of most of the stars that would have matched NGC 2419's metallicity.
 
-The 112 star candidate pool of K enhanced and potentially Mg depleted stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels and exist at a range of metalicities.
+The 112 star candidate pool of K enhanced stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels at a range of metallicities.
 It seems likely that whatever process is responsible for these anomalous field stars is similar to whatever caused the unusual stellar populations in NGC 2419 and NGC 2808.
@@
 This interpretation argues against any theoretical hyper-massive Population III star, no matter how contrived, being the polluter candidate.
-While such an object might be somewhat appealing in the context of NGC 2419 given the uniqueness of the cluster, it cannot account for the production of K throughout the life of the galaxy.
+While such an object might be somewhat appealing in the context of NGC 2419 given the uniqueness of the anti-correlation to the cluster, its isolation from the Milky Way, and its low metallicity of $\sim -2$, this solution cannot account for the production of K throughout the life of the galaxy.
 
 As emphasized by \cite{prantzos2017}, a significant challenge presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion in Mg and an enhancement in K.
-Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{23} Na} and through Mg-Al chains at temperatures around 75 MK --  attainable in hot-bottom burning environments in AGB stars -- while it takes temperatures upwards of 150 MK to produce K -- temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
+Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{27} Al} through Mg-Al chains at temperatures around 75 MK --  attainable in hot-bottom burning environments in AGB stars -- while it takes temperatures upwards of 150 MK to produce K -- temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
 This implies that the Mg depletion and K enrichment likely occur at separate sites, assuming a relatively simple hydrogen burning system.
 
-Allowing different sites for Mg depletion and K enrichment, one scenario that could possibly produce a large K enhanced signature along with (inconsistently) depleted Mg and enhanced Na throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is some less massive star.
+Allowing different sites for Mg depletion and K enrichment, one scenario that could possibly produce a large K enhanced signature -- along with (inconsistently) depleted Mg and enhanced Na -- throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is a less massive star.
 The scenario might proceed as follows:
@@
 The SAGB star produces K (destroying Na in the process \citep{prantzos2017}) which is then mixed throughout its envelope.
-It then deposits its K rich outer layers onto its smaller companion through binary accretion.
+It then deposits its K rich outer layers onto its smaller companion through wind-based accretion.
 This smaller companion would continue to evolve long after the SAGB star has formed a white-dwarf remnant and will, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, will not.
-If the companion star had sufficient mass to undergo hot bottom burning, then Na could be produced and Mg depleted \citep{prantzos2017}, with this material mixed throughout the envelope.
+If the companion star had sufficient mass to undergo hot bottom burning, then Na could be produced \citep{prantzos2017}, with this material mixed throughout the envelope.
 In this scenario, it is observations of this smaller binary companion star that make up our sample of 112 giants.
@@
 
-\todo{However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg depleted, K enriched material in the first place must be emphasized.
+\todo{However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg-depleted, K enriched material in the first place must be emphasized.
 Indeed, if we assume the primordial abundances (pre-mystery event) are similar to those of NGC 2419's Mg-normal population, then it is impossible.
 If the primordial cloud already has [Mg/Fe]$\approx 0.5$, to reduce this necessitates the addition of large amounts of iron rich material that is also very depleted in [Mg/Fe].
-But as soon significant amounts of iron are added, [Fe/H] for the subsequent the Mg-depleted population should increase, while no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}.
+But as soon significant amounts of iron are added, [Fe/H] for the subsequent Mg-depleted population should increase, while no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}.
 This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS).}
+
+Another issue facing the above scenario is that it requires a single gas cloud to form many generations of stars to be formed almost continously to be consistent with Figure \ref{KvsFe}.
+This is only known to occur in inside galaxies, which are massive enough and have sufficient gas to form multiple star forming regions.
+For smaller gas clouds, typically only one generation is formed before the remaining gas is lost through stellar winds.
+Although it is tempting to attempt to satisfy such concerns by allowing the stars to have formed some dwarf galaxy which then merged with the Milky Way, if the initial gas cloud increases so significantly in mass, then the difficulty of polluting such a cloud in the first place with such high levels of K increases proportionately.
 
@@
 However, this is not necessarily the only interpretation.
-For example, it could be that the K forming process is happening throughout the life of the galaxy, but the amount of K produced decreases with the metallicity of the polluter star, though there is no obvious reason this would be the case.
+For example, it could be that the K forming process is happening throughout the life of the galaxy, but the amount of K produced decreases with the metallicity of the polluter star, though there is no obvious reason why this would be the case.
 
@@
 Of the 454180 giant sample from \lamost, 112 candidate stars were identified as likely to have enhanced K and depleted Mg based on their absorption spectra.
-These stars show every appearance of being field stars, nor do they have the hallmarks of being the product of NLTE effects.
+These stars show every appearance of being field stars, and they do not have the hallmarks of being the product of NLTE effects.
 The candidate sample reflected the metallicity distribution of the base \textit{LAMOST} sample.
 
-Upon conducting an abundance analysis, it was found that despite searching for both Mg depletions and K enhancements, the sample of stars showed no definitive Mg depletion, although it did display anomalously high levels of [K/Fe] relative to galactic levels.
-None of the candidates had calculated abundances of Mg or K consistent with the extreme populations of NGC 2419 or NGC 2808.
+Upon conducting an abundance analysis, anomalously high levels of K were found in the sample, with levels of [K/Fe] as high as 1.5 confirmed through high resolution spectroscopy using Magellan/MIKE.
+The [K/Fe] abundances were not consistent with the extreme populations previsously identified in either NGC 2419 or NGC 2808.
+No conclusion can be reached regarding the presence of [Mg/Fe] depletions in the sample as [Mg/Fe] abundances were unable to be determined from the \lamost.
 
-An intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains uncertain without further observations of the candidates.
+An intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains uncertain without further higher resolution observations of the candidates.
+Further high resolution observations will also allow Mg and other elemental abundances to be determined.
 

### 2018-02-04 article/plotter.py
update plotting code as example

@@ -87,13 +87,18 @@ all_model_flux = np.memmap(
     mode="r", dtype="float32", shape=(N, P))
 
 
-binwidth=.05
-plt.figure(1)
-plt.hist(metalicity, bins=np.arange(-1.5, 0.5, binwidth),edgecolor='black')
-plt.xticks(np.arange(-1.5, 0.5, binwidth)[::4])
-plt.xlabel("[Fe/H]")
-plt.title('[Fe/H] for candidate stars')
-plt.show()
+binwidth=.10
+fig, ax = plt.subplots()
+ax.hist(metalicity, bins=np.arange(-1.5, 0.5, binwidth),
+        facecolor="#666666", edgecolor="k")
+ax.xaxis.set_major_locator(MaxNLocator(6))
+ax.set_xlim(-1.5, 0.5)
+ax.set_xlabel(r"[Fe/H]")
+fig.tight_layout()
+fig.savefig("histof113.png", dpi=300)
+fig.savefig("histof113.pdf", dpi=300)
+
+raise a
 
 plt.figure(2)
 plt.scatter(Teff ,logg , c=metalicity, cmap='plasma',s=40)
@@ -122,7 +127,7 @@ plt.scatter(C_KMg, C_KK, label= " NGC 2419 Kirby & Cohen 2012", s=25, c='gray')
 (_, caps, _)=plt.errorbar(C_KMg, C_KK, xerr=C_KMgu, linestyle="None", linewidth=.8, capsize=4,zorder=4, c='gray')
 for cap in caps:
     cap.set_markeredgewidth(.8)
-    
+
 plt.scatter(MucMg, MucK, label= "NGC 2419 Mucciarreli 2012", s=25, c='gray', marker='s')
 #plt.errorbar(MucMg, MucK, xerr=MucMgu, yerr=MucKu, linestyle="None",linewidth=1)
 (_, caps, _) = plt.errorbar(MucMg, MucK, xerr=MucMgu, yerr=MucKu, linestyle="None",linewidth=.8, capsize=4, zorder=3, c='gray')
@@ -202,7 +207,7 @@ def plot_spectrummod(wavelengths, observed_flux, observed_ivar, model_flux):
 
     observed_flux_error = observed_ivar**-2
     ax_spectrum.plot(wavelengths, observed_flux, c="k", drawstyle="steps-mid", label='LAMOST Spectra')
-    fill_between_steps(ax_spectrum, wavelengths, 
+    fill_between_steps(ax_spectrum, wavelengths,
[…]

### 2018-02-04 article/ms.tex
incomplete notes

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[Kemp et al.]{
-Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
+\author[Kemp et al.]{Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
 Andrew R. Casey,$^{1,2}$
-Mathew T. Miles,$^{1}$
+Matthew T. Miles,$^{1}$
 Brodie J. Norfolk,$^{1}$\newauthor
@@
 Amanda I. Karakas,$^{1}$
-Kevin C. Schlaufman,$^{3}$\newauthor
-Anna Y.Q Ho,$^{4}$
-Melissa K. Ness,$^{5}$
-David W. Hogg, $^{6}$
+Kevin C. Schlaufman,$^{3}$
+Anna Y.~Q. Ho,$^{4}$\newauthor
+Christopher A. Tout$^{1,5}$
+%Melissa K. Ness,$^{5}$
+%David W. Hogg,$^{6}$
 \\
@@
 $^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
-$^{2}$ Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
-$^{3}$, Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA\\
-$^{4}$ Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
-$^{5}$ Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
-$^{6}$ Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA\\
+$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
+$^{3}$Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA\\
+$^{4}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
+$^{5}$Institute of Astronomy, Madingley Road, Cambridge CH30HA, United Kingdom
+%$^{5}$ Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
+%$^{6}$ Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA\\
 }
@@
 % Abstract of the paper
+%The detailed chemical composition of a star acts as a fossil record of the conditions when it formed.
+
 \begin{abstract}
-
-Stellar absorption spectra act as a fossil record of the conditions where the stars form.
-Stars with unusual elemental abundances are of particular interest; these rare stars offer clues about rare astrophysical events or nucleosynthetic pathways.
-Stars with  depleted Mg and enhanced K abundances have so far only been found in the two massive globular clusters NGC 2419 and NGC 2808.
+Stars with unusual elemental abundances offer clues about rare astrophysical events or nucleosynthetic pathways.
+Stars with significantly depleted magnesium and enhanced potassium (e.g., $[{\rm K}/{\rm Fe}] > 1$; $[{\rm Mg}/{\rm Fe}] < -0.5$) have to date only been found in the massive globular cluster NGC~2419, and to a lesser extent, NGC~2808.
 The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
-Here we present 112 candidate field stars identified from \LamostGiants \ giants observed by \lamost \ that uncertain [Mg/Fe] but significantly enhanced [K/Fe] abundance ratios.
-These stars are present at a range of metallicities, and none have abundances that are as extreme as those in NGC 2419.
-These candidate stars should provide guidance for follow up surveys and modelling attempting to determine the origin of the Mg-K anti-correlation.
-
+Here we present 112 field stars, identified from \LamostGiants\ \lamost\ giant stars, that show significantly enhanced [K/Fe] and depleted [Mg/Fe] abundance ratios.
+Our sample spans a full range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$), yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 
+\todo{We conclude what about the origin. What does this imply.}
+This sample will help guide modelling attempts to explain the origin for the Mg-K abundance signature, which we show exists throughout the Milky Way.
 \end{abstract}
@@
 
-A targeted search looking for [K/Fe] in RGB and main sequence turn-off stars from clusters NGC 6752, NGC 6121, NGC 1904, 47 Tuc, NGC 6397, NGC 7099, and $\omega$ Centauri as well as 21 field stars found in all cases  that the K abundance fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}.
+A targeted search looking for [K/Fe] in RGB and main sequence turn-off stars in other clusters (NGC 6752, NGC 6121, NGC 1904, 47 Tuc, NGC 6397, NGC 7099, and $\omega$ Centauri) and field stars concluded that all K abundance ratios fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}.
 NGC 2808 is the only cluster other than NGC 2419 where an anticorrelation between Mg and K has been observed.
-All 4 of NGC 2808's known Mg-depleted stars have been found to have an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these anomalous abundances was far weaker than that in NGC 2419.
-The fact that the Mg-K anti-correlation is apparently confined to these two globular clusters would seem to imply either a small population of unusual polluter stars or a single extremely massive polluter star.
-
-One  mechanism for [Mg/Fe] depletion is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the `normal' [Mg/Fe] ratios that arise from Type II supernovae.
-However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}.
-Furthermore, Type Ia supernovae enrichment cannot account for the enhanced K abundance observed in NGC 2419.
-In fact, K is hard to make in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates from measured values by several orders of magnitude.
-
-The other avenue for potentially reducing [Mg/Fe] is high temperature H-burning through Mg-Al chains.
-However, no Al correlation is observed with the Mg depletions in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.
+All 4 of NGC 2808's known Mg-depleted stars show an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these abundance ratios is far weaker than that in NGC 2419.
+The fact that the Mg-K anti-correlation is apparently confined to these two globular clusters would imply either a small population of unusual polluter stars, or a single extremely massive polluter star.
 
@@
 
-\todo{An early modelling attempt at replicating the anomalous Mg/K abundances assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}.
-This study succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K.
-However, abundance patterns consistent with NGC 2419 were only possible if the Ar-K reaction cross section was set to 100 times the commonly accepted value or if the temperature at the base of the envelope could be made to exceed $\sim$ 150 $\times 10^6$ K (hereafter MK).}
+An early modelling attempt at replicating the anomalous Mg/K abundance ratios assumed hot-bottom burning in AGB and super-AGB (SAGB) stars.
+\cite{ventura2012} succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K.
+However, abundance patterns consistent with NGC 2419 were only possible if the Ar-K reaction cross section was increased to 100 times the laboratory value.
+or if the temperature at the base of the envelope could be made to exceed $\sim$150\,MK.
 
 A more recent attempt to replicate the Mg/K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}.
-The ultimate goal was to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.
-\todo{ It is perhaps noteworthy that they identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway.
-The main pathway they identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.}
-
-It was found that (excepting the case of extremely high densities > $10^8$ g/cm$^3$) temperatures between 100 and 200 MK and densities between 10$^{-4}$ and 10$^8$ g/cm$^3$ were required.
-Using this information, core and shell burning of low-mass, high-mass and super-massive stars were ruled out as potential polluters, as well as regular AGB stars.
-Super-AGB (SAGB) stars, however, were regarded as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
+The ultimate goal was to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.\footnote{It is perhaps noteworthy that \cite{iliadis2016} identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway.
+The main pathway \cite{iliadis2016} identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.}
+Unless extremely high densities were invoked ($>10^8\,{\rm g\,cm}^{-3}$), it was found that temperatures between 100 and 200\,MK were necessary.
+This constraint rules out many pollution sites, including: core and shell burning of low-mass stars, high-mass and super-massive stars, as well as regular AGB stars.
+Super-AGB (SAGB) stars, however, were considered as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
 The other potential candidate identified were novae, although the lack of detailed models of white dwarf accretion of metal-poor material adds considerable uncertainty.
@@
 
+One  mechanism for [Mg/Fe] depletion is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the `normal' [Mg/Fe] ratios that arise from Type II supernovae.
+However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}.
+Furthermore, Type Ia supernovae enrichment cannot account for the enhanced K abundance observed in NGC 2419.
+In fact, K is hard to make in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates from measured values by several orders of magnitude \todo{[citations]}.
+Another mechanism for reducing [Mg/Fe] is through the Mg-Al nucleosynthetic chain in high temperature hydrogen burning.
+However, no Al correlation is observed with the Mg depletions in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.
+
 Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg-K anti-correlation, a satisfactory explanation for the Mg-K signature could offer insight into the underestimation of K abundances in the Milky Way predicted by galactic chemical evolution models \citep{kobayashi2011}.
-Recent work by \cite{ritter2017} on K production in O-C shell mergers shows promise as an alternative source of K, if their results can be confirmed in a fully 3D simulation.
+Recent work by \cite{ritter2017} on K production in O-C shell mergers shows promise as an alternative source of K.
 Identifying the source of the Mg-K anti-correlation could also be beneficial to efforts to understand globular cluster formation and evolution.
 
-Here we use \lamost\ data to conduct the largest ever search for field stars that are enhanced in potassium and depleted in magnesium.
+Here we use \lamost\ data to conduct the largest ever search for stars enhanced in potassium and depleted in magnesium.
 The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.
 In particular, the search should provide strong evidence for the uniqueness of the mysterious site of nucleosynthesis responsible for the pattern to globular clusters, or lack thereof.
-\todo{ In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates.
-In Section \ref{sec:discussion} the results and their implications on possible poluters are discussed.
-Section \ref{sec:conclusion} summarises the main results.}
+In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates.
+In Section \ref{sec:discussion} we discuss our results and their implications for possible pollution mechanisms.
+Section \ref{sec:conclusion} summarises the main results.
 
@@
 \label{sec:method}
-The data set of \LamostGiants\ \lamost\ giants (from \lamost\ DR2) was prepared by \citet{ho2017} for use with the supervised machine learning code \tc.
-The \lamost\ data was shifted to rest frame and pseudo-continuum-normalised before it was resampled to a common uniform wavelength grid between 3905\,\AA\ and 9000\,\AA.
-\tc\ \citep{ness2016,ho2017} was used to infer effective temperature ($\teff$), surface gravity ($\logg$), metallicity ([Fe/H]), and alpha abundance relative to iron ([$\alpha$/Fe]) using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ \citep{alam2015} survey through the use of a data-driven spectral model.
+\subsection{Candidate selection from \lamost\ spectra}
+We used a set of \LamostGiants\ giant stars from the second \lamost\ data release.
+The spectra were placed at rest-frame on a common wavelength sampling from 3905\,\AA\ to 9000\,\AA\ and pseudo-continuum-normalised by \citet{ho2017}.
+\tc\ \citep{ness2016,ho2017} was used to estimate effective temperature ($\teff$), surface gravity ($\logg$), metallicity ([Fe/H]), and mean $\alpha$-element abundance relative to iron ([$\alpha$/Fe]) using 9,952 stars in common between \lamost\ and the \apogee\ \citep{alam2015} survey, through the use of a data-driven spectral model.
 Unless otherwise stated, these transferred labels are those referred to throughout this study.
-For details regarding the preparatory work, model generation, and label transfer between the \apogee\ and \lamost\ surveys, the reader is directed to \citet{ho2017}.
+For details regarding the preparatory work, model generation, and label transfer between the \apogee\ and \lamost\ surveys, we direct the reader to \citet{ho2017}.
 
-We identified potential Mg-K anti-correlated stars by searching for significant deviations in flux residuals.
+We identified potential Mg-depleted and K-enhanced stars by searching for significant deviations in residual flux.
 The flux residuals were taken as the normalised \lamost\ flux and the best-fitting data-driven model from \tc\ (where $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$).
 A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model).
-Figure 1 shows the LAMOST spectra, along with the star's model from the \tc, for candidate J034458.82+592955.1.
+Figure \ref{fig:posterchild} shows the \lamost\ spectra, and best-fitting model from \tc, for candidate J034458.82+592955.1.
 
-We fitted a gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167 \AA, 5172 \AA, 5184 \AA) as well as the K doublet (7665 \AA, 7699 \AA) for all \LamostGiants\ giants.
-For every star we recorded the profile amplitudes, wavelengths, widths, as well as associated measurement uncertainties of these quantities.
+We fit a gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167\,\AA, 5172\,\AA, 5184\,\AA) as well as the K doublet (7665\,\AA, 7699\,\AA) for all \LamostGiants\ giants.
+For each star we recorded the profile amplitudes, wavelengths, widths, as well as associated measurement uncertainties of these quantities.
 We identified candidates by requiring they match at least one of the following three quality filters:
@@
 
-These filters identified 384 unique stars to be vetted manually.
-We visually inspected every candidate (multiple times) and excluded any candidate that showed any evidence of being a false positive, including candidates that exhibited data reduction issues, apparent absorption that was narrower than the expected spectral resolution, as well as 75 stars that exhibited chromospheric emission at H$\alpha$ wavelengths.
-The distilled catalogue contains \todo{112} candidate stars enhanced in K and depleted in Mg.
+These filters identified 384 unique stars.
+We visually inspected every candidate (multiple times) and excluded stars that showed any evidence of being a false positive, including candidates that exhibited data reduction issues, apparent absorption that was narrower than the expected spectral resolution, as well as 75 stars that exhibited chromospheric emission at H$\alpha$.
+The distilled catalogue contains 112 candidate stars enhanced in K and depleted in Mg.
 
-Abundances were calculated from the \lamost spectra \todo{@andy add how we did that, why we couldn't get Mg, error estimates and limitations.}
+We estimated [K/Fe] abundance ratios for all candidates by synthesising spectra to account for the flux residuals \citep{marcs,sme,vald,ispec}.
+We assume that absorption due to metals is accounted for by \tc, and deviations in flux around the potassium doublet is due to an increased [K/Fe] with respect to the model.
+We list estimated [K/Fe] abundance ratios in Table 1, where the error includes a 0.2\,dex systematic error floor that we have applied in quadrature with the fitting errors.
+We applied the same method to estimate [Na/Fe] from \lamost\ spectra.
+We note that while enhancements in [K/Fe] or [Na/Fe] can be estimated by synthesising the flux residuals, we cannot easily estimate [Mg/Fe] depletions in the same manner because it is difficult to separate the flux contribution of [Mg/Fe] (from [$\alpha$/Fe]) from the data-driven model.
+For this reason, we will adopt [$\alpha$/Fe] as a conservative upper limit for [Mg/Fe].
 
+%\todo{The presence of Na enhancements were visually estimated from the sample of 112 candidate stars' flux spectra.
+Flux-based estimates placed at most 40 of the 112 stars (35\%) as being likely Na enhanced targets.} Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with [Na/Fe] above 0.5 dex.
+\todo{@andy add anything specific to Na abundance methods from LAMOST}.
+
+\subsection{Follow-up observations with Magellan/MIKE}
 High resolution spectra of three of the candidate stars selected based on observability (J075043.12+204658.0, J120032.60+024438.2 and J091825.49+172114.5) were obtained using Magellan/MIKE.
@@
 
-\todo{The presence of Na enhancements were visually estimated from the sample of 112 candidate stars' flux spectra.
-Flux-based estimates placed at most 40 of the 112 stars (35\%) as being likely Na enhanced targets.} Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with [Na/Fe] above 0.5 dex.
-\todo{@andy add anything specific to Na abundance methods from LAMOST}.
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{posterchildof13.png}
-    \caption{Sample spectra for one of the candidate stars.}
+\begin{figure*}
+	\includegraphics[width=\textwidth]{posterchildof13.png}
+    \caption{Pseudo-continuum-normalised \lamost\ spectra for the Mg-depleted and K-enhanced candidate J034458.82+592955.1.
+The data  are shown in black and the best-fitting data-driven model from \tc\ is shown in red.
+We show zoom-in axes around the magnesium triplet and potassium doublet, which we used to identify Mg-K candidates.
+Note that $[\alpha/{\rm Fe}$ is a label in \tc\ model used, and J034458.82+592955.1 shows Mg depletions relative to the estimated [$\alpha$/Fe] value.}
     \label{posterchild}
-\end{figure}
+\end{figure*}
 
@@
 	\includegraphics[width=\columnwidth]{histof113.png}
-    \caption{Histogram showing the metalicity distribution for the candidate stars.}
+    \caption{Metallicity distribution for all 112 candidate stars identified with K-enhancement and Mg-depletion.}
     \label{mhist}
@@
 Unfortunately, the target selection process for \lamost\ is non-invertible, and so selection effects present in \lamost\ are not considered here beyond comparing the candidate stars' metallicity distribution with that of \cite{ho2017}.
-
-The candidate stars are distributed across the giant branch, implying the abundances detected are not associated with any NLTE effects or stage in stellar evolution.
+The candidate stars are distributed across the entire giant branch, implying the abundance signature is not associated with any single particular stage in evolution, and that the chemical pattern is not due to a violation of the assumption of local thermodynamic equilibrium.
 
@@
 \label{sec:globclustasoc}
-Our sample was cross-matched against \cite{harris1996}'s data base of globular clusters.
-None of the stars appear to be associated with NGC 2419 or NGC 2808.
-\todo{ From the sample, J074807.22+261514.2 is the closest star in the sky to a globular cluster, at 2.54\degree\ separation from Ko 2 \citep{koposov2007}.
-This separation is large for association with such a small, distant cluster and the star's metallicity of -0.24 dex and apparent magnitude make it even less likely to be a member.}
+We cross-matched our candidates against a catalog of all known globular clusters \citep{harris1996}.
+No candidates can be associated with NGC~2419 or NGC~2808.
+The closest candidate to any globular cluster is J074807.22+261514.2, which lies 2.54\degree\ from Ko~2 \citep{koposov2007}.
+The large association and relatively  high metallicity of J074807.22+261514.2 ($[{\rm Fe}/{\rm H}] = -0.24$) make it highly unlikely to be a member.
 
-The spread of metallicity shown in Figure \ref{mhist} further supports the sample being made up of field stars.
-The distribution reflects the original \LamostGiants \ sample of giants from which the candidates were drawn.
-No stars are present with [Fe/H]$\sim -2$ -- the approximate metallicity of NGC 2419 -- nor are there many stars with [Fe/H]$\sim -1$ -- the metallicity of NGC 2808.
-Thus, we conclude that the candidates are not particular to any specific metallicity, including metallicites associated with NGC 2419 and NGC 2808.
+The spread in metallicity (Figure \ref{mhist}) is consistent with all candidates being field stars.
+The distribution reflects the original \LamostGiants\ sample of giants from which the candidates were selected.
+No candidates have [Fe/H] $\sim -2$ -- the approximate metallicity of NGC 2419 -- nor are there many stars with [Fe/H] $\sim -1$ -- the metallicity of NGC 2808.
+Thus, we conclude that the candidates are not particular to any specific metallicity, including metallicities associated with NGC 2419 and NGC 2808.
 
-\subsection{Abundances}
+\subsection{Detailed chemical abundances}
 \label{sec:abundances}
 Figure \ref{KvsMg} shows [K/Fe]  for the 112 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
+As described in Section \ref{sec:method}, we adopt [$\alpha$/Fe] as an upper limit for [Mg/Fe].
 [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE is also shown.
-As described in \ref{sec:method}, acceptably reliable abundances for Mg were unable to be obtained using the \lamost\ spectra.
-The use of $[\alpha$/Fe] to position the sample in \ref{KvsMg} is supported by the [Mg/Fe] measurements from the high-resolution spectra, which vary less than 0.1 dex from the level of $[\alpha$/Fe] for each of the relevant stars in the \lamost\ data.
+\todo{For these stars..}
+
+%The use of $[\alpha$/Fe] to position the sample in \ref{KvsMg} is supported by the [Mg/Fe] measurements from the high-resolution spectra, which vary less than 0.1 dex from the level of $[\alpha$/Fe] for each of the relevant stars in the \lamost\ data.
 However, for the bulk of the sample decoupling [Mg/Fe] from $[\alpha$/Fe] is impossible, and so in general  we are unable to draw firm conclusions as to whether the sample exhibits anomalously low [Mg/Fe].
@@
 [K/Fe] for the candidate stars is generally lower than that of the Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population.
-It is noteworthy that both of these populations identified in NGC 2808 have significantly lower levels of [K/Fe] than the candidate stars.
+\todo{It is noteworthy that both of these populations identified in NGC 2808 have significantly lower levels of [K/Fe] than the candidate stars.
+--> What?}
 Levels of [$\alpha$/Fe] fall within the lower limits of the Mg-normal population of both clusters, although as we are unable to decouple [Mg/Fe] from $[\alpha$/Fe] the exact level of Mg depletion for the candidates is unclear.
@@
 
-However, for reasons related to the use of both a data-driven model and a physical model for calculating abundances \todo{@andy add any elaboration on what the problem was, if necessary}, it is possible that this effect is an artefact of abundance processing rather than a physical relation.
+%However, for reasons related to the use of both a data-driven model and a physical model for calculating abundances \todo{@andy add any elaboration on what the problem was, if necessary}, it is possible that this effect is an artefact of abundance processing rather than a physical relation.
 Without further observations of the sample stars, we are unable to say with certainty whether this phenomena is real or not.
@@
 
-\subsection{Impact on theories and scenarios regarding the Mg-K anti-correlation}
+\subsection{Impact scenarios regarding the Mg-K anti-correlation}
 
@@
 \caption{Tabulated data for 10 of the 112 candidate stars. Data for the full sample is available online.}
-\label{my-label}
+\label{data}
 \begin{tabular}{cccccccccccccc}
@@
 
-Significantly enhanced [K/Fe] is rare; significantly enhanced [K/Fe] without an accompanying depletion of [Mg/Fe] is unknown. The candidate stars are also spread across a wide range of metallicities.
+%Significantly enhanced [K/Fe] is rare; significantly enhanced [K/Fe] without an accompanying depletion of [Mg/Fe] is unknown. The candidate stars are also spread across a wide range of metallicities.
 
-This spread in metallicity is important: taken in isolation, it implies that the process responsible for this signature, rare as it is, is not necessarily tied to a certain epoch in the evolutionary history of our galaxy.
-Rather, these stars appear to be continuously forming \todo{ in successive generations}.
-
-This interpretation argues against any theoretical hyper-massive Population III star, no matter how contrived, being the polluter candidate.
-While such an object might be somewhat appealing in the context of NGC 2419 given the uniqueness of the anti-correlation to the cluster, its isolation from the Milky Way, and its low metallicity of $\sim -2$, this solution cannot account for the production of K throughout the life of the galaxy.
+The spread in metallicities among our candidates is important to note.
+This implies that the process responsible for the Mg-K abundance signature is not necessarily tied to a certain epoch in the Milky Way's evolution.
+Rather, stars with enhanced K and depleted magnesium tend to form at all ages, across all metallicities.
+A hyper-massive Population III star may have been a plausible explanation for NGC~2419\todo{[CITATIONS NEEDED: WHO PROPOSED THIS]}, particularly given it's isolation from the Milky Way ($d_{GC} \approx 90\,{\rm kpc}$) and low metallicity.
+However, our discovery of Mg-K stars at all metallicities suggests against a hyper-massive Population III star as the polluter responsible.
 
@@
 \section*{Acknowledgements}
-\todo{to be completed}
-
-\begin{comment}
-- LAMOST
-- ARC DP (Casey)
-- Magellan/MIKE and Australian government
-- others???
-\end{comment}
+%- Magellan/MIKE and Australian government
+A.~R.~C. is supported through an Australian Research Council Discovery Project under grant DP160100637.
+A.~Y.~Q.~H. is supported by a Fulbright grant through the German-American Fulbright Commission and a National Science Foundation Graduate Research Fellowship under Grant No. DGE-1144469. 
+C.~A.~T. thanks Churchill College for his fellowship and Monash University for hosting him as a Kevin Westfold distinguished visitor.
+This research has made use of NASA's Astrophysics Data System.
+Guoshoujing Telescope (the Large Sky Area Multi-Object Fiber Spectroscopic Telescope LAMOST) is a National Major Scientific Project built by the Chinese Academy of Sciences.
+Funding for the project has been provided by the National Development and Reform Commission.
+LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-02-05 article/msarchive5feb2018.tex
draft prior proofreading tmo. also archive of what it was before draft

--- 2018-02-04 article/ms.tex
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[Kemp et al.]{Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
+\author[Kemp et al.]{
+Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
 Andrew R. Casey,$^{1,2}$
-Matthew T. Miles,$^{1}$
+Mathew T. Miles,$^{1}$
 Brodie J. Norfolk,$^{1}$\newauthor
@@
 Amanda I. Karakas,$^{1}$
-Kevin C. Schlaufman,$^{3}$
-Anna Y.~Q. Ho,$^{4}$\newauthor
-Christopher A. Tout$^{1,5}$
-%Melissa K. Ness,$^{5}$
-%David W. Hogg,$^{6}$
+Kevin C. Schlaufman,$^{4}$\newauthor
+Christopher A. Tout, $^{3}$
+Anna Y.Q Ho,$^{5}$
+Melissa K. Ness,$^{6}$
+David W. Hogg, $^{7}$
 \\
@@
 $^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
-$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
-$^{3}$Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA\\
-$^{4}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
-$^{5}$Institute of Astronomy, Madingley Road, Cambridge CH30HA, United Kingdom
-%$^{5}$ Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
-%$^{6}$ Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA\\
+$^{2}$ Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
+$^{3}$ Institute of Astronomy, Madingley Road, Cambridge, CB3 0HA, United Kingdom
+$^{4}$, Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA\\
+$^{5}$ Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
+$^{6}$ Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
+$^{7}$ Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA\\
 }
-
 % These dates will be filled out by the publisher
@@
 The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
-Here we present 112 field stars, identified from \LamostGiants\ \lamost\ giant stars, that show significantly enhanced [K/Fe] and depleted [Mg/Fe] abundance ratios.
+Here we present 112 field stars, identified from \LamostGiants\ \lamost\ giant stars, that show significantly enhanced [K/Fe] and possibly depleted [Mg/Fe] abundance ratios.
 Our sample spans a full range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$), yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 
-\todo{We conclude what about the origin. What does this imply.}
+We conclude that nucleosynthetic process producing the anomalous abundances in [K/Fe] and [Mg/Fe] is probably (but not necessarily) present at a wide range of metallicities.
+This makes polluter candidates which are limited to a certain epoch in GCE unlikely solutions.
 This sample will help guide modelling attempts to explain the origin for the Mg-K abundance signature, which we show exists throughout the Milky Way.
@@
 
-An early modelling attempt at replicating the anomalous Mg/K abundance ratios assumed hot-bottom burning in AGB and super-AGB (SAGB) stars.
-\cite{ventura2012} succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K.
-However, abundance patterns consistent with NGC 2419 were only possible if the Ar-K reaction cross section was increased to 100 times the laboratory value.
-or if the temperature at the base of the envelope could be made to exceed $\sim$150\,MK.
-
-A more recent attempt to replicate the Mg/K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}.
-The ultimate goal was to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.\footnote{It is perhaps noteworthy that \cite{iliadis2016} identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway.
-The main pathway \cite{iliadis2016} identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.}
-Unless extremely high densities were invoked ($>10^8\,{\rm g\,cm}^{-3}$), it was found that temperatures between 100 and 200\,MK were necessary.
-This constraint rules out many pollution sites, including: core and shell burning of low-mass stars, high-mass and super-massive stars, as well as regular AGB stars.
-Super-AGB (SAGB) stars, however, were considered as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
-The other potential candidate identified were novae, although the lack of detailed models of white dwarf accretion of metal-poor material adds considerable uncertainty.
-However, based on current nova frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1\% of the total required mass to pollute 30\% of NGC 2419.
-
-Another proposed  polluter candidate is a pair-instability super nova \citep[PISN;][]{carretta2013}.
-Unique to extremely massive Population III stars, these events involve the total destruction of the star, with no black hole remnant left behind.
-The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material released, could allow for the abundance signature in NGC 2419 to be the result of a single, extremely rare event, which would explain why it is not seen in any other globular clusters.
-However, the signature odd-even proton number abundance pattern associated with PISNs is absent from NGC 2419 \citep{cohenkirby2012}, making this particular scenario unlikely.
-
 %It has been suggested that NGC 2419's position and size, being both very massive and very distant from the Milky Way compared to many other globular clusters, aids it in retaining enriched material from explosive events \citep{mucciarelli2012}.
@@
 Furthermore, Type Ia supernovae enrichment cannot account for the enhanced K abundance observed in NGC 2419.
-In fact, K is hard to make in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates from measured values by several orders of magnitude \todo{[citations]}.
+In fact, K is hard to make in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates from measured values by several orders of magnitude \citep{ventura2012,iliadis2016}.
 Another mechanism for reducing [Mg/Fe] is through the Mg-Al nucleosynthetic chain in high temperature hydrogen burning.
@@
 A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model).
-Figure \ref{fig:posterchild} shows the \lamost\ spectra, and best-fitting model from \tc, for candidate J034458.82+592955.1.
+Figure \ref{posterchild} shows the \lamost\ spectra, and best-fitting model from \tc, for candidate J034458.82+592955.1.
 
@@
 We assume that absorption due to metals is accounted for by \tc, and deviations in flux around the potassium doublet is due to an increased [K/Fe] with respect to the model.
-We list estimated [K/Fe] abundance ratios in Table 1, where the error includes a 0.2\,dex systematic error floor that we have applied in quadrature with the fitting errors.
+We list estimated [K/Fe] abundance ratios in Table \ref{data}, where the error includes a 0.2\,dex systematic error floor that we have applied in quadrature with the fitting errors.
 We applied the same method to estimate [Na/Fe] from \lamost\ spectra.
@@
 %\todo{The presence of Na enhancements were visually estimated from the sample of 112 candidate stars' flux spectra.
-Flux-based estimates placed at most 40 of the 112 stars (35\%) as being likely Na enhanced targets.} Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with [Na/Fe] above 0.5 dex.
+Flux-based estimates placed at most 40 of the 112 stars (35\%) as being likely Na enhanced targets.} Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with [Na/Fe] above 0.5\,dex.
 \todo{@andy add anything specific to Na abundance methods from LAMOST}.
@@
 \label{sec:abundances}
+
+Upon examining [Na/Fe] as estimated from the \lamost\ spectra, two distinct populations were observed: one population making up approximately 30\% of the sample with [Na/Fe] > 0.5 -- significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011} -- and a seccond with [Na/Fe] consistent with typical galactic values.
+However, this behaviour is very likely due to the effect of interstellar dust.
+This conclusion is based on values of E(B-V), taken from IRSA's all-sky dust map \citep{schlafly2011}, which were notably higher for the stars supposedly enriched in Na than for those consistent with galactic levels.
+\todo{It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K.
+For these newly identified candidate stars, no relation between Na and K abundance is observed.}
+
 Figure \ref{KvsMg} shows [K/Fe]  for the 112 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
@@
 
-%The use of $[\alpha$/Fe] to position the sample in \ref{KvsMg} is supported by the [Mg/Fe] measurements from the high-resolution spectra, which vary less than 0.1 dex from the level of $[\alpha$/Fe] for each of the relevant stars in the \lamost\ data.
+%The use of $[\alpha$/Fe] to position the sample in \ref{KvsMg} is supported by the [Mg/Fe] measurements from the high-resolution spectra, which vary less than 0.1\,dex from the level of $[\alpha$/Fe] for each of the relevant stars in the \lamost\ data.
 However, for the bulk of the sample decoupling [Mg/Fe] from $[\alpha$/Fe] is impossible, and so in general  we are unable to draw firm conclusions as to whether the sample exhibits anomalously low [Mg/Fe].
@@
 [K/Fe] for the candidate stars is generally lower than that of the Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population.
-\todo{It is noteworthy that both of these populations identified in NGC 2808 have significantly lower levels of [K/Fe] than the candidate stars.
---> What?}
-Levels of [$\alpha$/Fe] fall within the lower limits of the Mg-normal population of both clusters, although as we are unable to decouple [Mg/Fe] from $[\alpha$/Fe] the exact level of Mg depletion for the candidates is unclear.
-The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra are consistent with the Mg-normal population in NGC 2419, although the small sample of these stars for which we have high resolution spectra means we are unable to confidently generalise this to the entire sample.
+The [K/Fe] level for the candidates estimated by \lamost\ is significantly higher than the [K/Fe] abundance in NGC 2808.
 
-A similar relationship emerges when these abundances with typical galactic abundances for [K/Fe] and [Mg/Fe], taken from \cite{kobayashi2011}.
-The sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$ dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8-1.3.
+Levels of [$\alpha$/Fe] fall within the lower limits for [Mg/Fe] of the Mg-normal population of both NGC 2419 and NGC 2808, although as we are unable to decouple [Mg/Fe] from $[\alpha$/Fe] the exact level of Mg depletion for the candidates is unclear.
+The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra are also consistent with the Mg-normal population in NGC 2419.
+However, the \lamost\ spectral data relative to \tc\ model are consistent with an under-abundance of Mg.
+The small sample of stars for which we have high resolution spectra, coupled with the conflict with the \lamost spectra, means we are unable to confidently make a statement regarding the level of [Mg/Fe] compared to NGC 2419 or NGC 2808.
+
+Given that the sample is almost certainly comprised of disk stars, it is relevant to also compare with typical galactic abundances for [K/Fe], taken from \cite{kobayashi2011}.
+The sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8-1.3.
 Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample has extremely high levels of [K/Fe].
@@
 The candidate stars' [K/Fe] also exhibits an interesting anti-correlation with total metallicity, shown in Figure \ref{KvsFe}, \todo{which is absent from measurements in the Milky Way}.
-This may be consistent with a (somewhat) constant level of [K/H] between each star, which would then cause [K/Fe] to fall as [Fe/H] increases.
 It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation.
-\todo{make figure in python, add trend line}
+\todo{make figure in python, add trend line} Due to the data-driven nature of the model, it is possible that this relation is an artefact of the process for calculating [K/Fe]; further high resolution observations are required to verify this anti-correlation.
 
@@
 
-The candidate stars' levels of [$\alpha$/Fe] were generally consistent with galactic levels of [Mg/Fe], as were the levels of [Mg/Fe] from the high resolution Magellan/MIKE spectra.
-Once again the inability to decouple [Mg/Fe] from $[\alpha$/Fe] means we are unable do draw firm conclusions about whether [Mg/Fe] is depleted relative to typical field stars, although the data we do have suggests not.
-No variation with metallicity is observed for [$\alpha$/Fe], including GCE effects relating of Type Ia supernovae enrichments.
-
-%In contrast with the marked departure from galactic values for [K/Fe], [$\alpha$/Fe] varies from around 0-0.3 dex in the \lamost \ sample, similar to galactic levels of [Mg/Fe], which vary with metallicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}.
+%In contrast with the marked departure from galactic values for [K/Fe], [$\alpha$/Fe] varies from around 0-0.3\,dex in the \lamost \ sample, similar to galactic levels of [Mg/Fe], which vary with metallicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}.
 No variation with metallicity is observed within the \lamost sample's [$\alpha$/Fe].
 
-[Na/Fe] was also measured for the \lamost\ data.
-Two distinct populations were observed, with a substantial minority of approximately 30\% of the sample having [Na/Fe] > 0.5, significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}.
-However, this behaviour is very likely due to the effect of interstellar dust.
-This conclusion is based on values of E(B-V), taken from IRSA's all-sky dust map \citep{schlafly2011}, which were notably higher for the stars supposedly enriched in Na than for those consistent with galactic levels.
-\todo{It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K.
-For these newly identified candidate stars, no relation between Na and K abundance is observed.}
-
-The implications of the calculated abundances are intriguing.
+The implications of the estimated abundances are intriguing.
 The fact that from such a large sample of field stars none were found that replicated the extreme abundance pattern of NGC 2419 is strong evidence for the cluster's uniqueness regarding the extreme bi-modal nature of its abundance pattern.
@@
 
-The 112 star candidate pool of K enhanced stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels at a range of metallicities.
+The 112 star candidate pool identified of K enhanced stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels at a range of metallicities.
 It seems likely that whatever process is responsible for these anomalous field stars is similar to whatever caused the unusual stellar populations in NGC 2419 and NGC 2808.
 
-\subsection{Impact scenarios regarding the Mg-K anti-correlation}
+\subsection{Impact on potential scenarios explaining the Mg-K anti-correlation}
 
@@
 
+An early modelling attempt to replicate the anomalous Mg/K abundance ratios assumed hot-bottom burning in AGB and super-AGB (SAGB) stars.
+\cite{ventura2012} succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K.
+However, abundance patterns consistent with NGC 2419 were only possible if the Ar-K reaction cross section was increased to 100 times the laboratory value.
+or if the temperature at the base of the envelope could be made to exceed $\sim$150\,MK.
+
+A more recent attempt to replicate the Mg/K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}.
+The ultimate goal was to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.\footnote{It is perhaps noteworthy that \cite{iliadis2016} identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway.
+The main pathway used by \cite{iliadis2016} is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.}
+Unless extremely high densities were invoked ($>10^8\,{\rm g\,cm}^{-3}$), it was found that temperatures between 100 and 200\,MK were necessary.
+This constraint rules out many pollution sites, including: core and shell burning of low-mass stars, high-mass and super-massive stars, as well as regular AGB stars.
+Super-AGB (SAGB) stars, however, were considered as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
+The other potential candidate identified were novae, although the lack of detailed models of white dwarf accretion of metal-poor material adds considerable uncertainty.
+However, based on current nova frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1\% of the total required mass to pollute 30\% of NGC 2419.
+
+Another proposed  polluter candidate is a pair-instability super nova \citep[PISN;][]{carretta2013}.
+Unique to extremely massive Population III stars, these events involve the total destruction of the star, with no black hole remnant left behind.
+The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material released, could allow for the abundance signature in NGC 2419 to be the result of a single, extremely rare event, which would explain why it is not seen in any other globular clusters.
+However, the signature odd-even proton number abundance pattern associated with PISNs is absent from NGC 2419 \citep{cohenkirby2012}, making this particular scenario unlikely.
+
+Our study presents a collection of stars in the disk of the galaxy at a range of metallicities showing anomalously high levels of [K/Fe].
 The spread in metallicities among our candidates is important to note.
-This implies that the process responsible for the Mg-K abundance signature is not necessarily tied to a certain epoch in the Milky Way's evolution.
-Rather, stars with enhanced K and depleted magnesium tend to form at all ages, across all metallicities.
-A hyper-massive Population III star may have been a plausible explanation for NGC~2419\todo{[CITATIONS NEEDED: WHO PROPOSED THIS]}, particularly given it's isolation from the Milky Way ($d_{GC} \approx 90\,{\rm kpc}$) and low metallicity.
-However, our discovery of Mg-K stars at all metallicities suggests against a hyper-massive Population III star as the polluter responsible.
+It implies that the process responsible for the Mg-K abundance signature may not be tied to a certain epoch in the Milky Way's evolution.
+Since the stars with enhanced K and depleted magnesium apparently tend to form at all ages, across all metallicities, it is probable that the polluter star is also able to form independently of metallicity.
 
+If we assume that the polluter star is indeed able to form at a range of metallicities, then we can attempt to constrain what sort of astrophysical scenarios may be responsible for the Mg-K anti-correlation.
+
+One class of candidates that can be immediately eliminated as a result of such an assumption are Population III stars.
+A hyper-massive Population III star may have been a plausible explanation for NGC~2419 \citep{carretta2013}, particularly given it's isolation from the Milky Way ($d_{GC} \approx 90\,{\rm kpc}$) and low metallicity.
+However, being unable to form throughout the life of the galaxy makes it difficult -- but not impossible -- for a Population III star to be the polluter candidate responsible for the pool of stars identified in this study.
+
+One possible polluter candidate that \textit{could} form throughout the life of the Milky Way is an SAGB-binary.
 As emphasized by \cite{prantzos2017}, a significant challenge presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion in Mg and an enhancement in K.
-Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{27} Al} through Mg-Al chains at temperatures around 75 MK --  attainable in hot-bottom burning environments in AGB stars -- while it takes temperatures upwards of 150 MK to produce K -- temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
+Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{27} Al} through Mg-Al chains at temperatures around 75 MK --  attainable in hot-bottom burning (HBB) environments in AGB stars -- while it takes temperatures upwards of 150 MK to produce K -- temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
 This implies that the Mg depletion and K enrichment likely occur at separate sites, assuming a relatively simple hydrogen burning system.
-
-Allowing different sites for Mg depletion and K enrichment, one scenario that could possibly produce a large K enhanced signature -- along with (inconsistently) depleted Mg and enhanced Na -- throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is a less massive star.
-The scenario might proceed as follows:
+The SAGB-binary is hypothesised produce a [K/Fe] over-abundance in select stars within the Milky Way as follows:
 
@@
 This smaller companion would continue to evolve long after the SAGB star has formed a white-dwarf remnant and will, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, will not.
-If the companion star had sufficient mass to undergo hot bottom burning, then Na could be produced \citep{prantzos2017}, with this material mixed throughout the envelope.
-In this scenario, it is observations of this smaller binary companion star that make up our sample of 112 giants.
+If the companion star had sufficient mass to undergo hot-bottom burning, then Na could be produced \citep{prantzos2017}, with this material mixed throughout the envelope.
+Further, depending on the HBB temperature, the AGB star may also deplete Mg through Mg/Al chains.
+In this scenario, it is observations of the smaller binary companion star that make up our sample of 112 giants.
 
-Although this scenario allows for consistency with the total spread in metallicity, it doe not account for the uniqueness of the signal to NGC 2419 and NGC 2808 among globular clusters, nor does it satisfactorily explain why such a large proportion of stars in NGC 2419 exhibit the Mg-K anti-correlation.
-\todo{The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is highly unlikely, to say the least.}
+Although this scenario is consistent with the total spread in metallicity, it is not applicable to NGC 2419 or NGC2808; SAGB-binaries cannot account for 30\% of the stars in NGC 2419 showing depleted Mg and enhanced K abundances.
+Further, it would only occasionally produce a depletion in [Mg/Fe], unlike the consistent bi-modality seen in NGC 2419 and NGC 2808.
 
-A direct test of this scenario would be whether at least most of the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they could have formed SAGB binaries once.
+A direct test of this scenario would be to determine whether at least most of the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they could have formed SAGB binaries once.
 
-The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in at least one region of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases.
-This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419.
+The spread in metallicity does not necessarily require the polluter candidate to be able to form throughout the life of the galaxy however; all that is required is that the stars observed formed in different metallicity environments.
+The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as indicative of a relatively constant level of [K/H] present in at least one region of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases.
+This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419, shown in Figure \ref{KvsFe}.
 If this relation is real, we can perhaps -- without saying anything about the polluter star -- use it to motivate an evolutionary sequence that can account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419 and our new 112 field star sample.
 
-Suppose some unknown event(s) unique to very metal poor (possibly zero-metallicity) environments occurs.
-This event results in a gas cloud depleted in Mg and enhanced in K.
-The generation of stars that form directly from this gas carries this signature, and displays a significant reduction in Mg abundance and enhancement in K abundance similar to NGC 2419's extreme population.
+First, suppose some unknown event(s) unique to very metal poor (possibly zero-metallicity) environments occurs that results in a gas cloud depleted in Mg and enhanced in K.
+The generation of stars that form directly from this gas displays a significant reduction in Mg and enhancement in K abundances similar to NGC 2419's extreme population.
 We will refer to this generation of stars Generation 1.
@@
 When the most massive stars of Generation 1 die, they release metals into the gas cloud, including significant amounts of Mg, which is formed in copious amounts in core-collapse supernovae, but \textit{not} K, which is very difficult to form in significant quantities.
-The [Mg/Fe] depletion originally carried in the cloud is much harder to detect in the next generation of stars forming from this material, Generation 2, due to the influx of Mg released by Generation 1.
+The [Mg/Fe] depletion originally carried in the cloud is much harder to detect in the next generation of stars forming from this material, Generation 2, due to the influx of Mg rich material released by Generation 1.
 The K enhancement however remains (in principle) relatively easy to detect, having only been reduced relative to [Fe/H] by the total amount of iron released.
-As this cycle continues, [K/Fe] would continue to lower proportionately with the rate of iron release, while depletions in [Mg/Fe] would quickly become impossible to detect.
+As this cycle repeats, [K/Fe] would decrease in each successive generation of stars, while the level of [Mg/Fe] would quickly approach galaxy-normal levels, and the original [Mg/Fe] depletion would quickly become impossible to detect in all but the most metal-poor stars.
 
-This cycle allows for the Mg depletions to be preserved in globular clusters, where even the most massive clusters only form at most 2 generations of stars.
-But it also allows the Mg signal to effectively be lost within the disc of the galaxy, where many generations of stars may form.
+This cycle allows for the Mg depletions to be preserved in globular clusters, where even the most massive clusters only form at most 2 generations of stars, while the signal would be lost within the disk of the galaxy, where many generations of stars might form.
 Thus it provides a way of linking the current observations of our 112 candidate stars with the observations of NGC 2419.
@@
 
-\todo{However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg-depleted, K enriched material in the first place must be emphasized.
+%\todo{However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg-depleted, K enriched material in the first place must be emphasized.
 Indeed, if we assume the primordial abundances (pre-mystery event) are similar to those of NGC 2419's Mg-normal population, then it is impossible.
@@
 But as soon significant amounts of iron are added, [Fe/H] for the subsequent Mg-depleted population should increase, while no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}.
-This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS).}
+This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS)}
 
-Another issue facing the above scenario is that it requires a single gas cloud to form many generations of stars to be formed almost continously to be consistent with Figure \ref{KvsFe}.
-This is only known to occur in inside galaxies, which are massive enough and have sufficient gas to form multiple star forming regions.
-For smaller gas clouds, typically only one generation is formed before the remaining gas is lost through stellar winds.
-Although it is tempting to attempt to satisfy such concerns by allowing the stars to have formed some dwarf galaxy which then merged with the Milky Way, if the initial gas cloud increases so significantly in mass, then the difficulty of polluting such a cloud in the first place with such high levels of K increases proportionately.
+One major issue facing the above evolutionary sequence is that it requires a single gas cloud to form many generations of stars almost continuously to be consistent with Figure \ref{KvsFe}.
+This is only known to occur in inside true galaxies, which are massive enough and have sufficient gas to form multiple star forming regions.
+Allowing the candidate stars to have originated in a dwarf galaxy which later merged with the Milky Way introduces many issues however.
+The required mass to be originally polluted by the mystery object increases drastically, implying multiple pollution events.
+However, invoking multiple pollution events means that the rarity of the signal is harder to explain if it happened multiple times within a single dwarf galaxy, why not in other places?
+Further, a merger should result in stars with highly elliptical orbits, while the candidate stars identified appear to be disk stars.
 

### 2018-02-06 article/msarchive5feb2018.tex
Distribution draft

@@
 Amanda I. Karakas,$^{1}$
-Kevin C. Schlaufman,$^{4}$\newauthor
-Christopher A. Tout, $^{3}$
+Kevin C. Schlaufman,$^{3}$\newauthor
+Christopher A. Tout, $^{4}$
 Anna Y.Q Ho,$^{5}$
@@
 $^{2}$ Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
-$^{3}$ Institute of Astronomy, Madingley Road, Cambridge, CB3 0HA, United Kingdom
-$^{4}$, Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA\\
+$^{3}$, Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA\\
+$^{4}$ Institute of Astronomy, Madingley Road, Cambridge, CB3 0HA, United Kingdom\\
 $^{5}$ Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
@@
 Our sample spans a full range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$), yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 
-We conclude that nucleosynthetic process producing the anomalous abundances in [K/Fe] and [Mg/Fe] is probably (but not necessarily) present at a wide range of metallicities.
-This makes polluter candidates which are limited to a certain epoch in GCE unlikely solutions.
-This sample will help guide modelling attempts to explain the origin for the Mg-K abundance signature, which we show exists throughout the Milky Way.
+We conclude that the nucleosynthetic process producing the anomalous abundances in [K/Fe] and [Mg/Fe] is probably (but not necessarily) present at a wide range of metallicities.
+This makes polluter candidates which are limited to a certain epoch in GCE, such as Population III stars, unlikely progenitors.
+This sample will help guide modelling attempts to explain the origin for the Mg-K abundance signature, which we show \todo{(propose?)} exists throughout the Milky Way.
 \end{abstract}
@@
 NGC 2808 is the only cluster other than NGC 2419 where an anticorrelation between Mg and K has been observed.
-All 4 of NGC 2808's known Mg-depleted stars show an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these abundance ratios is far weaker than that in NGC 2419.
+All 4 of NGC 2808's known Mg-depleted stars show an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these abundance ratios is far weaker than those found in NGC 2419.
 The fact that the Mg-K anti-correlation is apparently confined to these two globular clusters would imply either a small population of unusual polluter stars, or a single extremely massive polluter star.
@@
 Another mechanism for reducing [Mg/Fe] is through the Mg-Al nucleosynthetic chain in high temperature hydrogen burning.
-However, no Al correlation is observed with the Mg depletions in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.
+However, no correlation between Mg and Al is observed in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.
 
@@
 Recent work by \cite{ritter2017} on K production in O-C shell mergers shows promise as an alternative source of K.
-Identifying the source of the Mg-K anti-correlation could also be beneficial to efforts to understand globular cluster formation and evolution.
+Identifying the source of the Mg-K anti-correlation could also be beneficial to efforts in understanding globular cluster formation and evolution.
 
@@
 The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.
-In particular, the search should provide strong evidence for the uniqueness of the mysterious site of nucleosynthesis responsible for the pattern to globular clusters, or lack thereof.
+In particular, the search should provide strong evidence either for or against the uniqueness of the progenitor stars to globular clusters.
 In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates.
@@
 We visually inspected every candidate (multiple times) and excluded stars that showed any evidence of being a false positive, including candidates that exhibited data reduction issues, apparent absorption that was narrower than the expected spectral resolution, as well as 75 stars that exhibited chromospheric emission at H$\alpha$.
-The distilled catalogue contains 112 candidate stars enhanced in K and depleted in Mg.
+The distilled catalogue contains 112 candidate stars with spectra consistent with enhancements in K and depletions in Mg.
 
@@
 We show zoom-in axes around the magnesium triplet and potassium doublet, which we used to identify Mg-K candidates.
-Note that $[\alpha/{\rm Fe}$ is a label in \tc\ model used, and J034458.82+592955.1 shows Mg depletions relative to the estimated [$\alpha$/Fe] value.}
+Note that $[\alpha/{\rm Fe}]$ is a label in \tc\ model used, and J034458.82+592955.1 shows Mg depletions relative to the estimated [$\alpha$/Fe] value.}
     \label{posterchild}
@@
 The closest candidate to any globular cluster is J074807.22+261514.2, which lies 2.54\degree\ from Ko~2 \citep{koposov2007}.
-The large association and relatively  high metallicity of J074807.22+261514.2 ($[{\rm Fe}/{\rm H}] = -0.24$) make it highly unlikely to be a member.
+The large angular separation and relatively  high metallicity of J074807.22+261514.2 ($[{\rm Fe}/{\rm H}] = -0.24$) make it highly unlikely to be a member.
 
@@
 This conclusion is based on values of E(B-V), taken from IRSA's all-sky dust map \citep{schlafly2011}, which were notably higher for the stars supposedly enriched in Na than for those consistent with galactic levels.
-\todo{It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K.
-For these newly identified candidate stars, no relation between Na and K abundance is observed.}
+It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K.
+For these newly identified candidate stars, no relation between Na and K abundance is observed.
 
@@
 Levels of [$\alpha$/Fe] fall within the lower limits for [Mg/Fe] of the Mg-normal population of both NGC 2419 and NGC 2808, although as we are unable to decouple [Mg/Fe] from $[\alpha$/Fe] the exact level of Mg depletion for the candidates is unclear.
-The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra are also consistent with the Mg-normal population in NGC 2419.
-However, the \lamost\ spectral data relative to \tc\ model are consistent with an under-abundance of Mg.
+The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra are consistent with the Mg-normal population in NGC 2419.
+However, the \lamost\ spectra relative to \tc\ model is consistent with an under-abundance of Mg.
 The small sample of stars for which we have high resolution spectra, coupled with the conflict with the \lamost spectra, means we are unable to confidently make a statement regarding the level of [Mg/Fe] compared to NGC 2419 or NGC 2808.
@@
 
-The candidate stars' [K/Fe] also exhibits an interesting anti-correlation with total metallicity, shown in Figure \ref{KvsFe}, \todo{which is absent from measurements in the Milky Way}.
+The candidate stars' [K/Fe] also exhibits an interesting anti-correlation with total metallicity, shown in Figure \ref{KvsFe}, which is absent from measurements in the Milky Way.
 It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation.
-\todo{make figure in python, add trend line} Due to the data-driven nature of the model, it is possible that this relation is an artefact of the process for calculating [K/Fe]; further high resolution observations are required to verify this anti-correlation.
+Due to the data-driven nature of the model, it is possible that this relation is an artefact of the process for calculating [K/Fe]; further high resolution observations are needed to verify this anti-correlation.
 
@@
 \cite{ventura2012} succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K.
-However, abundance patterns consistent with NGC 2419 were only possible if the Ar-K reaction cross section was increased to 100 times the laboratory value.
-or if the temperature at the base of the envelope could be made to exceed $\sim$150\,MK.
+However, abundance patterns consistent with NGC 2419 were only possible if the Ar-K reaction cross section was increased to 100 times the laboratory value, or if the temperature at the base of the envelope could be made to exceed $\sim$150\,MK.
 
 A more recent attempt to replicate the Mg/K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}.
-The ultimate goal was to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.\footnote{It is perhaps noteworthy that \cite{iliadis2016} identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway.
+The study aimed to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.\footnote{It is perhaps noteworthy that \cite{iliadis2016} identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway.
 The main pathway used by \cite{iliadis2016} is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.}
@@
 Super-AGB (SAGB) stars, however, were considered as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
-The other potential candidate identified were novae, although the lack of detailed models of white dwarf accretion of metal-poor material adds considerable uncertainty.
+The other potential candidate identified was novae, although the lack of detailed models of white dwarf accretion of metal-poor material adds considerable uncertainty.
 However, based on current nova frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1\% of the total required mass to pollute 30\% of NGC 2419.
@@
 The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material released, could allow for the abundance signature in NGC 2419 to be the result of a single, extremely rare event, which would explain why it is not seen in any other globular clusters.
-However, the signature odd-even proton number abundance pattern associated with PISNs is absent from NGC 2419 \citep{cohenkirby2012}, making this particular scenario unlikely.
+However, the signature odd-even proton number abundance pattern associated with PISNs is absent from NGC 2419 \citep{cohenkirby2012}.
 
@@
 It implies that the process responsible for the Mg-K abundance signature may not be tied to a certain epoch in the Milky Way's evolution.
-Since the stars with enhanced K and depleted magnesium apparently tend to form at all ages, across all metallicities, it is probable that the polluter star is also able to form independently of metallicity.
+Since these stars with enhanced potassium apparently tend to form at all ages, across all metallicities, it is probable that the polluter star is also able to form independently of metallicity.
 
-If we assume that the polluter star is indeed able to form at a range of metallicities, then we can attempt to constrain what sort of astrophysical scenarios may be responsible for the Mg-K anti-correlation.
+If we assume that the polluter star forms at a range of metallicities, then we can constrain the astrophysical scenarios that may be responsible for the Mg-K anti-correlation.
 
-One class of candidates that can be immediately eliminated as a result of such an assumption are Population III stars.
+One class of candidates that can be immediately eliminated under such an assumption are Population III stars.
 A hyper-massive Population III star may have been a plausible explanation for NGC~2419 \citep{carretta2013}, particularly given it's isolation from the Milky Way ($d_{GC} \approx 90\,{\rm kpc}$) and low metallicity.
@@
 As emphasized by \cite{prantzos2017}, a significant challenge presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion in Mg and an enhancement in K.
-Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{27} Al} through Mg-Al chains at temperatures around 75 MK --  attainable in hot-bottom burning (HBB) environments in AGB stars -- while it takes temperatures upwards of 150 MK to produce K -- temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
+Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{27}Al} through Mg-Al chains at temperatures around 75 MK --  attainable in hot-bottom burning (HBB) environments in AGB stars -- while it takes temperatures upwards of 150 MK to produce K -- temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
 This implies that the Mg depletion and K enrichment likely occur at separate sites, assuming a relatively simple hydrogen burning system.
-The SAGB-binary is hypothesised produce a [K/Fe] over-abundance in select stars within the Milky Way as follows:
+We hypothesise that the SAGB-binary may produce a [K/Fe] over-abundance in select stars within the Milky Way as follows:
 
-The SAGB star produces K (destroying Na in the process \citep{prantzos2017}) which is then mixed throughout its envelope.
-It then deposits its K rich outer layers onto its smaller companion through wind-based accretion.
+The SAGB star produces K (destroying Na in the process \citep{prantzos2017}), which is then mixed throughout its envelope.
+It then deposits its K-rich outer layers onto its smaller companion through wind-based accretion.
 This smaller companion would continue to evolve long after the SAGB star has formed a white-dwarf remnant and will, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, will not.
-If the companion star had sufficient mass to undergo hot-bottom burning, then Na could be produced \citep{prantzos2017}, with this material mixed throughout the envelope.
+If the companion star had sufficient mass to undergo hot-bottom burning, then Na could be produced \citep{prantzos2017}.
 Further, depending on the HBB temperature, the AGB star may also deplete Mg through Mg/Al chains.
+The material produced through HBB is mixed throughout the envelope, permitting observations of these products.
 In this scenario, it is observations of the smaller binary companion star that make up our sample of 112 giants.
+A direct test would be to determine whether at least most of the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they could have formed SAGB binaries once.
 
 Although this scenario is consistent with the total spread in metallicity, it is not applicable to NGC 2419 or NGC2808; SAGB-binaries cannot account for 30\% of the stars in NGC 2419 showing depleted Mg and enhanced K abundances.
-Further, it would only occasionally produce a depletion in [Mg/Fe], unlike the consistent bi-modality seen in NGC 2419 and NGC 2808.
+Further, it would only irregularly produce a depletion in [Mg/Fe], unlike the consistent bi-modality seen in NGC 2419 and NGC 2808.
 
-A direct test of this scenario would be to determine whether at least most of the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they could have formed SAGB binaries once.
-
-The spread in metallicity does not necessarily require the polluter candidate to be able to form throughout the life of the galaxy however; all that is required is that the stars observed formed in different metallicity environments.
+Although perhaps more probable, the spread in metallicity does not necessarily require the polluter candidate to form throughout the life of the galaxy; all that is absolutely required is that the stars \textit{observed} formed in different metallicity environments.
 The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as indicative of a relatively constant level of [K/H] present in at least one region of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases.
@@
 
-First, suppose some unknown event(s) unique to very metal poor (possibly zero-metallicity) environments occurs that results in a gas cloud depleted in Mg and enhanced in K.
-The generation of stars that form directly from this gas displays a significant reduction in Mg and enhancement in K abundances similar to NGC 2419's extreme population.
-We will refer to this generation of stars Generation 1.
+First, suppose some unknown event unique to very metal poor (possibly zero-metallicity) environments occurs that results in a gas cloud depleted in Mg and enhanced in K.
+The stars that form directly from this gas display a significant reduction in Mg and enhancement in K abundances similar to NGC 2419's extreme population.
+We will refer to this generation of stars as Generation 1.
 
-When the most massive stars of Generation 1 die, they release metals into the gas cloud, including significant amounts of Mg, which is formed in copious amounts in core-collapse supernovae, but \textit{not} K, which is very difficult to form in significant quantities.
-The [Mg/Fe] depletion originally carried in the cloud is much harder to detect in the next generation of stars forming from this material, Generation 2, due to the influx of Mg rich material released by Generation 1.
+When the most massive stars of Generation 1 die, they release metals into the gas cloud, including significant amounts of Mg, which is formed in copious amounts in core-collapse supernovae, but \textit{not} K, which models predict to be very difficult to form in significant quantities.
+The [Mg/Fe] depletion originally carried in the cloud is much harder to detect in the next generation of stars forming from this material, Generation 2, due to the influx of Mg-rich material released by Generation 1.
 The K enhancement however remains (in principle) relatively easy to detect, having only been reduced relative to [Fe/H] by the total amount of iron released.
-As this cycle repeats, [K/Fe] would decrease in each successive generation of stars, while the level of [Mg/Fe] would quickly approach galaxy-normal levels, and the original [Mg/Fe] depletion would quickly become impossible to detect in all but the most metal-poor stars.
+As this cycle repeats, [K/Fe] would be reduced in each successive generation of stars, while the original [Mg/Fe] depletion would quickly become impossible to detect in all but the most metal-poor stars.
 
@@
 One major issue facing the above evolutionary sequence is that it requires a single gas cloud to form many generations of stars almost continuously to be consistent with Figure \ref{KvsFe}.
-This is only known to occur in inside true galaxies, which are massive enough and have sufficient gas to form multiple star forming regions.
-Allowing the candidate stars to have originated in a dwarf galaxy which later merged with the Milky Way introduces many issues however.
-The required mass to be originally polluted by the mystery object increases drastically, implying multiple pollution events.
-However, invoking multiple pollution events means that the rarity of the signal is harder to explain if it happened multiple times within a single dwarf galaxy, why not in other places?
-Further, a merger should result in stars with highly elliptical orbits, while the candidate stars identified appear to be disk stars.
+This is only known to occur in inside true galaxies, which are massive enough to form multiple star forming regions.
+Allowing the candidate stars to have originated in a dwarf galaxy which later merged with the Milky Way introduces many issues.
+The required mass to be polluted by the mystery object increases drastically, implying multiple pollution events.
+But invoking multiple pollution events means that the rarity of the signal is harder to explain: if it happened multiple times within a single dwarf galaxy, why not in other places?
+Further, a merger should result in stars with highly elliptical orbits, while the candidates identified appear to be disk stars.
 
@@
 These stars show every appearance of being field stars, and they do not have the hallmarks of being the product of NLTE effects.
-The candidate sample reflected the metallicity distribution of the base \textit{LAMOST} sample.
+The candidate sample's metallicity reflected the metallicity distribution of the base \textit{LAMOST} sample.
 
@@
 The [K/Fe] abundances were not consistent with the extreme populations previsously identified in either NGC 2419 or NGC 2808.
-No conclusion can be reached regarding the presence of [Mg/Fe] depletions in the sample as [Mg/Fe] abundances were unable to be determined from the \lamost.
+No conclusion can be reached regarding the presence of [Mg/Fe] depletions in the sample as [Mg/Fe] abundances were unable to be determined from the \lamost\ spectra.
 

### 2018-02-06 article/msarchive5feb2018.tex
changed names

--- 2018-02-04 article/ms.tex
@@
 A similar relationship emerges when these abundances with typical galactic abundances for [K/Fe] and [Mg/Fe], taken from \cite{kobayashi2011}.
-The sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$ dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8-1.3.
+The sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8-1.3.
 Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample has extremely high levels of [K/Fe].
@@
 
-%In contrast with the marked departure from galactic values for [K/Fe], [$\alpha$/Fe] varies from around 0-0.3 dex in the \lamost \ sample, similar to galactic levels of [Mg/Fe], which vary with metallicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}.
+%In contrast with the marked departure from galactic values for [K/Fe], [$\alpha$/Fe] varies from around 0-0.3\,dex in the \lamost \ sample, similar to galactic levels of [Mg/Fe], which vary with metallicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}.
 No variation with metallicity is observed within the \lamost sample's [$\alpha$/Fe].

### 2018-02-06 article/ms.tex
text edits

@@
 
-\newcommand{\LamostGiants}{454180}
-\newcommand{\project}[1]{\emph{#1}}
+\newcommand{\LamostGiants}{454,180}
+\newcommand{\project}[1]{#1}
 \newcommand{\lamost}{\project{LAMOST}}
@@
 % Keep the title short and informative.
-\title[Mg-K anti-correlation in LAMOST]{Discovery of Mg-depleted and K-enhanced Stars in \textit{LAMOST}}
+\title[Mg-K stars in LAMOST]{On the discovery of K-enhanced and Mg-depleted stars throughout the Milky Way}
 
@@
 Christopher A. Tout$^{1,5}$
-%Melissa K. Ness,$^{5}$
-%David W. Hogg,$^{6}$
+%Melissa K. Ness,$^{6}$
+%David W. Hogg,$^{7}$
 \\
@@
 $^{4}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
-$^{5}$Institute of Astronomy, Madingley Road, Cambridge CH30HA, United Kingdom
-%$^{5}$ Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
-%$^{6}$ Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA\\
+$^{5}$Institute of Astronomy, Madingley Road, Cambridge, CB3 0HA, United Kingdom\\
+%$^{6}$ Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
+%$^{7}$ Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA\\
 }
-
 % These dates will be filled out by the publisher
@@
 The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
-Here we present 112 field stars, identified from \LamostGiants\ \lamost\ giant stars, that show significantly enhanced [K/Fe] and depleted [Mg/Fe] abundance ratios.
+Here we present 112 field stars, identified from \LamostGiants\ \lamost\ giant stars, that show significantly enhanced [K/Fe] and possibly depleted [Mg/Fe] abundance ratios.
 Our sample spans a full range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$), yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 
-\todo{We conclude what about the origin. What does this imply.}
-This sample will help guide modelling attempts to explain the origin for the Mg-K abundance signature, which we show exists throughout the Milky Way.
+We conclude that the nucleosynthetic process producing the anomalous abundances in [K/Fe] and [Mg/Fe] probably (but not necessarily) occurs at a wide range of metallicities.
+This would suggest that pollution scenarios that are limited to early epochs (e.g., Population III supernovae) are an unlikely explanation.
+This sample is expected to help guide modelling attempts to explain the origin of the Mg-K abundance signature, which we show exists throughout the Milky Way.
 \end{abstract}
@@
 The Mg-depleted population identified previously was found to be contained with the G2 population.
-
-An early modelling attempt at replicating the anomalous Mg/K abundance ratios assumed hot-bottom burning in AGB and super-AGB (SAGB) stars.
-\cite{ventura2012} succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K.
-However, abundance patterns consistent with NGC 2419 were only possible if the Ar-K reaction cross section was increased to 100 times the laboratory value.
-or if the temperature at the base of the envelope could be made to exceed $\sim$150\,MK.
-
-A more recent attempt to replicate the Mg/K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}.
-The ultimate goal was to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.\footnote{It is perhaps noteworthy that \cite{iliadis2016} identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway.
-The main pathway \cite{iliadis2016} identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.}
-Unless extremely high densities were invoked ($>10^8\,{\rm g\,cm}^{-3}$), it was found that temperatures between 100 and 200\,MK were necessary.
-This constraint rules out many pollution sites, including: core and shell burning of low-mass stars, high-mass and super-massive stars, as well as regular AGB stars.
-Super-AGB (SAGB) stars, however, were considered as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
-The other potential candidate identified were novae, although the lack of detailed models of white dwarf accretion of metal-poor material adds considerable uncertainty.
-However, based on current nova frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1\% of the total required mass to pollute 30\% of NGC 2419.
-
-Another proposed  polluter candidate is a pair-instability super nova \citep[PISN;][]{carretta2013}.
-Unique to extremely massive Population III stars, these events involve the total destruction of the star, with no black hole remnant left behind.
-The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material released, could allow for the abundance signature in NGC 2419 to be the result of a single, extremely rare event, which would explain why it is not seen in any other globular clusters.
-However, the signature odd-even proton number abundance pattern associated with PISNs is absent from NGC 2419 \citep{cohenkirby2012}, making this particular scenario unlikely.
 
@@
 Furthermore, Type Ia supernovae enrichment cannot account for the enhanced K abundance observed in NGC 2419.
-In fact, K is hard to make in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates from measured values by several orders of magnitude \todo{[citations]}.
+In fact, K is hard to make in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates from measured values by several orders of magnitude \citep{ventura2012,iliadis2016}.
 Another mechanism for reducing [Mg/Fe] is through the Mg-Al nucleosynthetic chain in high temperature hydrogen burning.
-However, no Al correlation is observed with the Mg depletions in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.
+However, no correlation between Mg and Al is observed in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.
+Recent work by \cite{ritter2017} on K production in O-C shell mergers shows promise as an alternative source of K, but this work is ongoing.
 
-Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg-K anti-correlation, a satisfactory explanation for the Mg-K signature could offer insight into the underestimation of K abundances in the Milky Way predicted by galactic chemical evolution models \citep{kobayashi2011}.
-Recent work by \cite{ritter2017} on K production in O-C shell mergers shows promise as an alternative source of K.
-Identifying the source of the Mg-K anti-correlation could also be beneficial to efforts to understand globular cluster formation and evolution.
-
+Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg-K anti-correlation, a satisfactory explanation for the Mg-K signature may also offer insight into the underestimation of K abundances in the Milky Way predicted by galactic chemical evolution models \citep{kobayashi2011}, or more broadly help to understand globular cluster formation and evolution.
 Here we use \lamost\ data to conduct the largest ever search for stars enhanced in potassium and depleted in magnesium.
-The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.
-In particular, the search should provide strong evidence for the uniqueness of the mysterious site of nucleosynthesis responsible for the pattern to globular clusters, or lack thereof.
-In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates.
+The discovery (or non-discovery) of such stars would guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.
+In particular, such a search would provide strong evidence either for or against the uniqueness of the progenitor stars to globular clusters.
+In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis for some of those candidates.
 In Section \ref{sec:discussion} we discuss our results and their implications for possible pollution mechanisms.
-Section \ref{sec:conclusion} summarises the main results.
+Section \ref{sec:conclusion} summarises those results.
 
@@
 \subsection{Candidate selection from \lamost\ spectra}
-We used a set of \LamostGiants\ giant stars from the second \lamost\ data release.
-The spectra were placed at rest-frame on a common wavelength sampling from 3905\,\AA\ to 9000\,\AA\ and pseudo-continuum-normalised by \citet{ho2017}.
-\tc\ \citep{ness2016,ho2017} was used to estimate effective temperature ($\teff$), surface gravity ($\logg$), metallicity ([Fe/H]), and mean $\alpha$-element abundance relative to iron ([$\alpha$/Fe]) using 9,952 stars in common between \lamost\ and the \apogee\ \citep{alam2015} survey, through the use of a data-driven spectral model.
+We used a set of \LamostGiants\ giant stars from the second \lamost\ data release \todo{\citep{lamostDR2}}.
+The spectra were placed at rest-frame on a common wavelength sampling from 3905\,\AA\ to 9000\,\AA\ and pseudo-continuum-normalised as per \citet{ho2017}.
+\tc\ \citep{ness2016,ho2017} was used to estimate effective temperature ($\teff$), surface gravity ($\logg$), metallicity ([Fe/H]), and mean $\alpha$-element abundance relative to iron ([$\alpha$/Fe]) using 9,952 stars in common between \lamost\ and the \apogee\ \citep{alam2015} survey.
 Unless otherwise stated, these transferred labels are those referred to throughout this study.
@@
 
-We identified potential Mg-depleted and K-enhanced stars by searching for significant deviations in residual flux.
+We identified potential Mg-depleted and K-enhanced stars by searching for significant deviations in flux residuals.
 The flux residuals were taken as the normalised \lamost\ flux and the best-fitting data-driven model from \tc\ (where $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$).
 A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model).
-Figure \ref{fig:posterchild} shows the \lamost\ spectra, and best-fitting model from \tc, for candidate J034458.82+592955.1.
+Figure \ref{posterchild} shows the \lamost\ spectra, and best-fitting model from \tc, for candidate J034458.82+592955.1.
 
@@
 For each star we recorded the profile amplitudes, wavelengths, widths, as well as associated measurement uncertainties of these quantities.
+We note that although telluric absorption would usually swamp the K doublet lines, the contribution of telluric features have been removed from \lamost\ spectra as part of the data  reduction process.
 We identified candidates by requiring they match at least one of the following three quality filters:
 \begin{enumerate}
-\item We required the amplitude $A$ of the profile at the Mg 5184 \AA \ line to satisfy $A_{{\rm Mg} @ 5184} > 0.05$ and the amplitude of the profile at the K 7665 line to satisfy $A_{{\rm K}\,@\,7665} < -0.05$.
+\item We required the amplitude $A$ of the profile at the Mg 5184 \AA \ line to satisfy $A_{{\rm Mg} @ 5184} > 0.05$ and the amplitude of the profile at the K 7665\,\AA\ line to satisfy $A_{{\rm K}\,@\,7665} < -0.05$.
 Both amplitudes must also be measured at more than $3\sigma$ ($|A|/\sigma_{A} \geq 3$).
@@
 \label{sec:selectioneffects}
-\cite{ho2017}'s sample of \lamost\ giants carries with it certain selection effects as a result of both the \textit{APOGEE} DR12 and \lamost\ samples.
-Metal poor stars with [Fe/H] $\lesssim-2$ are mostly absent from the sample as they were likely too dissimilar to the training stars for label transfer from \textit{APOGEE}.
-Unfortunately, the target selection process for \lamost\ is non-invertible, and so selection effects present in \lamost\ are not considered here beyond comparing the candidate stars' metallicity distribution with that of \cite{ho2017}.
-The candidate stars are distributed across the entire giant branch, implying the abundance signature is not associated with any single particular stage in evolution, and that the chemical pattern is not due to a violation of the assumption of local thermodynamic equilibrium.
+
+Our sample of \lamost\ giants carries with it certain selection effects as a result of both the \apogee\ DR12 and \lamost\ samples.
+For example, metal-poor stars with [Fe/H] $\lesssim-2$ are mostly absent from our sample as they were likely too dissimilar from the training stars for label transfer from \apogee.
+Similarly, the target selection process for \lamost\ is not easily invertible, and so selection effects present in \lamost\ are not considered here beyond comparing the candidate stars' metallicity distribution with that of \cite{ho2017}.
+From this comparison we find that the frequency of Mg/K stars is consistent (within the errors) of being flat with metallicity.
+We also note that  our candidate stars are distributed across the entire giant branch, implying that the abundance signature is not associated with any single particular stage in evolution, and that the chemical pattern we observe is not due to a violation of the assumption of local thermodynamic equilibrium.
 
@@
 \label{sec:globclustasoc}
-We cross-matched our candidates against a catalog of all known globular clusters \citep{harris1996}.
+We cross-matched our candidates against the positions of all known globular clusters \citep{harris1996}.
 No candidates can be associated with NGC~2419 or NGC~2808.
-The closest candidate to any globular cluster is J074807.22+261514.2, which lies 2.54\degree\ from Ko~2 \citep{koposov2007}.
-The large association and relatively  high metallicity of J074807.22+261514.2 ($[{\rm Fe}/{\rm H}] = -0.24$) make it highly unlikely to be a member.
+The closest candidate to any star cluster is J074807.22+261514.2, which lies 2.54\degree\ from Ko~2 \citep{koposov2007}.
+The large angular separation and relatively  high metallicity of J074807.22+261514.2 ($[{\rm Fe}/{\rm H}] = -0.24$) make it highly unlikely to be associated with Ko~2.
 
@@
 No candidates have [Fe/H] $\sim -2$ -- the approximate metallicity of NGC 2419 -- nor are there many stars with [Fe/H] $\sim -1$ -- the metallicity of NGC 2808.
-Thus, we conclude that the candidates are not particular to any specific metallicity, including metallicities associated with NGC 2419 and NGC 2808.
+Thus, we conclude that the candidates are not restricted to any specific metallicity, particularly not just to the metallicities of NGC 2419 and NGC 2808.
 
@@
 \label{sec:abundances}
+
+Upon examining [Na/Fe] as estimated from the \lamost\ spectra, two distinct populations were observed: one population making up approximately 30\% of the sample with [Na/Fe] > 0.5 -- significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011} -- and a second with [Na/Fe] consistent with typical galactic values.
+However, the high [Na/Fe] abundance ratios we observe are very likely due to the effect of interstellar dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) values \citep{schlafly2011}, suggesting that the stellar absorption lines are being blended with interstellar dust absorption.
+It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a positive correlation between Na and K.
+Despite our noisy estimates of Na and K in our sample, no relation between Na and K abundances is observed.
+
 Figure \ref{KvsMg} shows [K/Fe]  for the 112 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
@@
 [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE is also shown.
-\todo{For these stars..}
+%The use of $[\alpha$/Fe] to position the sample in \ref{KvsMg} is supported by the [Mg/Fe] measurements from the high-resolution spectra, which vary less than 0.1\,dex from the level of $[\alpha$/Fe] for each of the relevant stars in the \lamost\ data.
+However, for the bulk of the sample decoupling [Mg/Fe] from $[\alpha$/Fe] is impossible, and so in general  we are unable to draw firm conclusions as to whether the sample exhibits anomalously low [Mg/Fe].
+We note that [K/Fe] for the candidate stars is generally lower than that of the Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population.
+The [K/Fe] level for the candidates estimated by \lamost\ is significantly higher than the [K/Fe] abundance in NGC 2808.
 
-%The use of $[\alpha$/Fe] to position the sample in \ref{KvsMg} is supported by the [Mg/Fe] measurements from the high-resolution spectra, which vary less than 0.1 dex from the level of $[\alpha$/Fe] for each of the relevant stars in the \lamost\ data.
-However, for the bulk of the sample decoupling [Mg/Fe] from $[\alpha$/Fe] is impossible, and so in general  we are unable to draw firm conclusions as to whether the sample exhibits anomalously low [Mg/Fe].
+Abundance ratios of [$\alpha$/Fe] in our sample fall within the lower limits for [Mg/Fe] of the Mg-normal population of both NGC 2419 and NGC 2808, although as we are unable to decouple [Mg/Fe] from $[\alpha$/Fe], the exact level of Mg depletion for the candidates is unclear.
+The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra are consistent with the Mg-normal population in NGC 2419.
+However, the \lamost\ spectra relative to \tc\ model is consistent with an under-abundance of Mg.
+The small sample of stars for which we have high resolution spectra, coupled with the conflict with the \lamost spectra, means we are unable to confidently make a statement regarding the level of [Mg/Fe] compared to NGC 2419 or NGC 2808.
 
-[K/Fe] for the candidate stars is generally lower than that of the Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population.
-\todo{It is noteworthy that both of these populations identified in NGC 2808 have significantly lower levels of [K/Fe] than the candidate stars.
---> What?}
-Levels of [$\alpha$/Fe] fall within the lower limits of the Mg-normal population of both clusters, although as we are unable to decouple [Mg/Fe] from $[\alpha$/Fe] the exact level of Mg depletion for the candidates is unclear.
-The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra are consistent with the Mg-normal population in NGC 2419, although the small sample of these stars for which we have high resolution spectra means we are unable to confidently generalise this to the entire sample.
+Given that the sample is almost certainly comprised of disk stars, it is relevant to also compare with typical galactic abundances for [K/Fe], taken from \cite{kobayashi2011}.
+The sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8-1.3.
+Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample has extremely high levels of [K/Fe], approaching the extreme levels observed in NGC 2419.
 
-A similar relationship emerges when these abundances with typical galactic abundances for [K/Fe] and [Mg/Fe], taken from \cite{kobayashi2011}.
-The sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$ dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8-1.3.
-Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample has extremely high levels of [K/Fe].
+The [K/Fe] abundance ratios in our sample also show an anti-correlation with total metallicity, as illustrated in Figure \ref{KvsFe}, which is not present in the bulk of Milky Way stars.
+It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation.
+However we caution that this may be an artefact of our analysis, further high resolution observations are needed to verify this trend.
 
-The candidate stars' [K/Fe] also exhibits an interesting anti-correlation with total metallicity, shown in Figure \ref{KvsFe}, \todo{which is absent from measurements in the Milky Way}.
-This may be consistent with a (somewhat) constant level of [K/H] between each star, which would then cause [K/Fe] to fall as [Fe/H] increases.
-It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation.
-\todo{make figure in python, add trend line}
+% due to the data-driven nature of our model, it is possible that this relation is an artefact of the process for calculating [K/Fe];
 
@@
 
-The candidate stars' levels of [$\alpha$/Fe] were generally consistent with galactic levels of [Mg/Fe], as were the levels of [Mg/Fe] from the high resolution Magellan/MIKE spectra.
-Once again the inability to decouple [Mg/Fe] from $[\alpha$/Fe] means we are unable do draw firm conclusions about whether [Mg/Fe] is depleted relative to typical field stars, although the data we do have suggests not.
-No variation with metallicity is observed for [$\alpha$/Fe], including GCE effects relating of Type Ia supernovae enrichments.
-
-%In contrast with the marked departure from galactic values for [K/Fe], [$\alpha$/Fe] varies from around 0-0.3 dex in the \lamost \ sample, similar to galactic levels of [Mg/Fe], which vary with metallicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}.
+%In contrast with the marked departure from galactic values for [K/Fe], [$\alpha$/Fe] varies from around 0-0.3\,dex in the \lamost \ sample, similar to galactic levels of [Mg/Fe], which vary with metallicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}.
 No variation with metallicity is observed within the \lamost sample's [$\alpha$/Fe].
 
-[Na/Fe] was also measured for the \lamost\ data.
-Two distinct populations were observed, with a substantial minority of approximately 30\% of the sample having [Na/Fe] > 0.5, significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}.
-However, this behaviour is very likely due to the effect of interstellar dust.
-This conclusion is based on values of E(B-V), taken from IRSA's all-sky dust map \citep{schlafly2011}, which were notably higher for the stars supposedly enriched in Na than for those consistent with galactic levels.
-\todo{It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K.
-For these newly identified candidate stars, no relation between Na and K abundance is observed.}
-
-The implications of the calculated abundances are intriguing.
-The fact that from such a large sample of field stars none were found that replicated the extreme abundance pattern of NGC 2419 is strong evidence for the cluster's uniqueness regarding the extreme bi-modal nature of its abundance pattern.
-It is worth repeating however that the sample of \lamost\ giants searched had already been filtered of most of the stars that would have matched NGC 2419's metallicity.
-
-The 112 star candidate pool of K enhanced stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels at a range of metallicities.
+The implications of the abundance ratios we find are intriguing.
+The fact that, from such a large sample of field stars, none were found that replicated (or exceeded) the extreme abundance pattern of NGC 2419 is strong evidence for the cluster's uniqueness.
+%regarding the extreme bi-modal nature of its abundance pattern. 
+It is worth repeating, however, that our sample of \lamost\ giants searched had already been filtered of most of the stars that would have matched NGC 2419's metallicity.
+The 112 star candidate pool identified of K enhanced stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels at a range of metallicities.
 It seems likely that whatever process is responsible for these anomalous field stars is similar to whatever caused the unusual stellar populations in NGC 2419 and NGC 2808.
 
-\subsection{Impact scenarios regarding the Mg-K anti-correlation}
+\subsection{Impact on potential scenarios explaining the Mg-K anti-correlation}
 
@@
 
+An early modelling attempt to replicate the anomalous Mg/K abundance ratios assumed hot-bottom burning in AGB and super-AGB (SAGB) stars.
+\cite{ventura2012} succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K.
+However, abundance patterns consistent with NGC 2419 were only possible if the Ar-K reaction cross section was increased to 100 times the laboratory value, or if the temperature at the base of the envelope could be made to exceed $\sim$150\,MK.
+
+A more recent attempt to replicate the Mg/K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}.
+The study aimed to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.\footnote{It is perhaps noteworthy that \cite{iliadis2016} identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway.
+The main pathway used by \cite{iliadis2016} is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.}
+Unless extremely high densities were invoked ($>10^8\,{\rm g\,cm}^{-3}$), it was found that temperatures between 100 and 200\,MK were necessary.
+This constraint rules out many pollution sites, including: core and shell burning of low-mass stars, high-mass and super-massive stars, as well as regular AGB stars.
+Super-AGB (SAGB) stars, however, were considered as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
+The other potential candidate identified was novae, although the lack of detailed models of white dwarf accretion of metal-poor material adds considerable uncertainty.
+However, based on current nova frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1\% of the total required mass to pollute 30\% of NGC 2419.
+
+Another proposed  polluter candidate is a pair-instability super nova \citep[PISN;][]{carretta2013}.
+Unique to extremely massive Population III stars, these events involve the total destruction of the star, with no black hole remnant left behind.
+The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material released, could allow for the abundance signature in NGC 2419 to be the result of a single, extremely rare event, which would explain why it is not seen in any other globular clusters.
+However, the signature odd-even proton number abundance pattern associated with PISNs is absent from NGC 2419 \citep{cohenkirby2012}.
+
+Our study presents a collection of stars in the disk of the galaxy at a range of metallicities showing anomalously high levels of [K/Fe].
 The spread in metallicities among our candidates is important to note.
-This implies that the process responsible for the Mg-K abundance signature is not necessarily tied to a certain epoch in the Milky Way's evolution.
-Rather, stars with enhanced K and depleted magnesium tend to form at all ages, across all metallicities.
-A hyper-massive Population III star may have been a plausible explanation for NGC~2419\todo{[CITATIONS NEEDED: WHO PROPOSED THIS]}, particularly given it's isolation from the Milky Way ($d_{GC} \approx 90\,{\rm kpc}$) and low metallicity.
-However, our discovery of Mg-K stars at all metallicities suggests against a hyper-massive Population III star as the polluter responsible.
+It implies that the process responsible for the Mg-K abundance signature may not be tied to a certain epoch in the Milky Way's evolution.
+Since these stars with enhanced potassium apparently tend to form at all ages, across all metallicities, it is probable that the polluter star is also able to form independently of metallicity.
+If we assume that the polluter star forms at a range of metallicities, then we can make qualitative constraints on scenarios that may be responsible for the Mg-K anti-correlation.
 
+One class of candidates that can be immediately eliminated under such an assumption are Population III stars.
+A hyper-massive Population III star may have been a plausible explanation for NGC~2419 \citep{carretta2013}, particularly given it's isolation from the Milky Way ($d_{GC} \approx 90\,{\rm kpc}$) and low metallicity.
+However, being unable to form throughout the life of the galaxy makes it unlikely for a Population III star to be the polluter candidate responsible for the stars we identify.
+
+One possible polluter candidate that \textit{could} form throughout the life of the Milky Way is an SAGB-binary.
 As emphasized by \cite{prantzos2017}, a significant challenge presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion in Mg and an enhancement in K.
-Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{27} Al} through Mg-Al chains at temperatures around 75 MK --  attainable in hot-bottom burning environments in AGB stars -- while it takes temperatures upwards of 150 MK to produce K -- temperatures potentially developed at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
+Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{27}Al} through Mg-Al chains at temperatures around 75 MK, which is attainable in hot-bottom burning (HBB) environments in AGB stars.
+However, temperatures upwards of 150 MK are required to produce K, and these temperatures can only potentially be reached at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
 This implies that the Mg depletion and K enrichment likely occur at separate sites, assuming a relatively simple hydrogen burning system.
 
-Allowing different sites for Mg depletion and K enrichment, one scenario that could possibly produce a large K enhanced signature -- along with (inconsistently) depleted Mg and enhanced Na -- throughout the lifetime of the Milky Way would be a binary in which one of the stars is a SAGB star and the other is a less massive star.
-The scenario might proceed as follows:
+We hypothesise that the SAGB-binary may produce a [K/Fe] over-abundance in select stars within the Milky Way as follows.
+The SAGB star produces K \citep[destroying Na in the process;][]{prantzos2017}, which is then mixed throughout its envelope.
+It then deposits its K-rich outer layers onto its lower-mass companion through accreting winds.
+The lower-mass companion would continue to evolve long after the SAGB star has formed a white-dwarf remnant and will, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, will not.
+If the companion star had sufficient mass to undergo hot-bottom burning, then Na could be produced \citep{prantzos2017}.
+Further, depending on the HBB temperature, the AGB star may also deplete Mg through Mg/Al chains.
+The material produced through HBB is mixed throughout the envelope and to the surface of the star.
+In this scenario, it is observations of the lower-mass binary companion stars that make up our sample of 112 giants.
+A direct test would be to determine whether at least most of the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they could have formed as SAGB stars.
 
-The SAGB star produces K (destroying Na in the process \citep{prantzos2017}) which is then mixed throughout its envelope.
-It then deposits its K rich outer layers onto its smaller companion through wind-based accretion.
-This smaller companion would continue to evolve long after the SAGB star has formed a white-dwarf remnant and will, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, will not.
-If the companion star had sufficient mass to undergo hot bottom burning, then Na could be produced \citep{prantzos2017}, with this material mixed throughout the envelope.
-In this scenario, it is observations of this smaller binary companion star that make up our sample of 112 giants.
+While this scenario is consistent with the total spread in metallicity, it is not applicable to NGC 2419 or NGC2808.
+SAGB-binaries cannot account for 30\% of the stars in NGC 2419 showing depleted Mg and enhanced K abundances.
+\todo{Why not, exactly?} Furthermore, it would only irregularly produce a depletion in [Mg/Fe], unlike the apparent bi-modality seen in abundance ratios in NGC 2419 and NGC 2808.
 
-Although this scenario allows for consistency with the total spread in metallicity, it doe not account for the uniqueness of the signal to NGC 2419 and NGC 2808 among globular clusters, nor does it satisfactorily explain why such a large proportion of stars in NGC 2419 exhibit the Mg-K anti-correlation.
-\todo{The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is highly unlikely, to say the least.}
+Although the metallicity spread suggests a polluter candidate that can form at all ages and metallicities, all that is absolutely required is that the stars \textit{we observe} form in different metallicity environments.
+The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in at least one region of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases.
+This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419, shown in Figure \ref{KvsFe}.
+If this relation is real, we can perhaps -- without saying anything about the polluter star -- use it to motivate an evolutionary sequence that could account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419, and our new 112 field star sample.
 
-A direct test of this scenario would be whether at least most of the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they could have formed SAGB binaries once.
+Suppose some unknown event unique to very metal-poor (possibly zero-metallicity) environments occurs that results in a gas cloud depleted in Mg and enhanced in K.
+The stars that form directly from this gas display a significant reduction in Mg and enhancement in K abundances similar to NGC 2419's extreme population.
+We will refer to this generation of stars as Generation 1\footnote{Reluctantly.}.
+When the most massive stars of Generation 1 die, they release metals into the gas cloud, including significant amounts of Mg, which is formed in copious amounts in core-collapse supernovae, but \textit{not} K, which models predict to be very difficult to form in significant quantities.
+The [Mg/Fe] depletion originally carried in the cloud is much harder to detect in the next generation of stars forming from this material, Generation 2, due to the influx of Mg-rich material released by Generation 1.
+The K enhancement, however, remains relatively easy to detect, having only been reduced relative to [Fe/H] by the total amount of iron released.
+As this cycle repeats, [K/Fe] would be reduced in each successive generation of stars, while the original [Mg/Fe] depletion would quickly become impossible to detect in all but the most metal-poor stars.
+This cycle allows for the Mg depletions to be preserved in globular clusters, where even the most massive clusters only form at most two generations of stars, while the signature would be lost within the disk of the galaxy where many generations of stars might form.
+Thus it provides a way of linking the current observations of our 112 candidate stars with the observations of NGC 2419.
+%Certainly the idea that both groups of anomalous stars arise from the same polluter source ought to be entertained.
 
-The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in at least one region of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases.
-This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419.
-If this relation is real, we can perhaps -- without saying anything about the polluter star -- use it to motivate an evolutionary sequence that can account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419 and our new 112 field star sample.
-
-Suppose some unknown event(s) unique to very metal poor (possibly zero-metallicity) environments occurs.
-This event results in a gas cloud depleted in Mg and enhanced in K.
-The generation of stars that form directly from this gas carries this signature, and displays a significant reduction in Mg abundance and enhancement in K abundance similar to NGC 2419's extreme population.
-We will refer to this generation of stars Generation 1.
-
-When the most massive stars of Generation 1 die, they release metals into the gas cloud, including significant amounts of Mg, which is formed in copious amounts in core-collapse supernovae, but \textit{not} K, which is very difficult to form in significant quantities.
-The [Mg/Fe] depletion originally carried in the cloud is much harder to detect in the next generation of stars forming from this material, Generation 2, due to the influx of Mg released by Generation 1.
-The K enhancement however remains (in principle) relatively easy to detect, having only been reduced relative to [Fe/H] by the total amount of iron released.
-As this cycle continues, [K/Fe] would continue to lower proportionately with the rate of iron release, while depletions in [Mg/Fe] would quickly become impossible to detect.
-
-This cycle allows for the Mg depletions to be preserved in globular clusters, where even the most massive clusters only form at most 2 generations of stars.
-But it also allows the Mg signal to effectively be lost within the disc of the galaxy, where many generations of stars may form.
-Thus it provides a way of linking the current observations of our 112 candidate stars with the observations of NGC 2419.
-Certainly the idea that both groups of anomalous stars arise from the same polluter source must be entertained.
-
-\todo{However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg-depleted, K enriched material in the first place must be emphasized.
+%\todo{However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg-depleted, K enriched material in the first place must be emphasized.
 Indeed, if we assume the primordial abundances (pre-mystery event) are similar to those of NGC 2419's Mg-normal population, then it is impossible.
@@
 But as soon significant amounts of iron are added, [Fe/H] for the subsequent Mg-depleted population should increase, while no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}.
-This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS).}
+This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS)}
 
-Another issue facing the above scenario is that it requires a single gas cloud to form many generations of stars to be formed almost continously to be consistent with Figure \ref{KvsFe}.
-This is only known to occur in inside galaxies, which are massive enough and have sufficient gas to form multiple star forming regions.
-For smaller gas clouds, typically only one generation is formed before the remaining gas is lost through stellar winds.
-Although it is tempting to attempt to satisfy such concerns by allowing the stars to have formed some dwarf galaxy which then merged with the Milky Way, if the initial gas cloud increases so significantly in mass, then the difficulty of polluting such a cloud in the first place with such high levels of K increases proportionately.
+\todo{One major issue facing this explanation is that it requires a single gas cloud to form many generations of stars almost continuously in order to be consistent with Figure \ref{KvsFe}.
+This is only known to occur in inside true galaxies, which are massive enough to form multiple star forming regions.
+Allowing the candidate stars to have originated in a dwarf galaxy which later merged with the Milky Way introduces many issues.
+The required mass to be polluted by the mystery object increases drastically, implying multiple pollution events.
+But invoking multiple pollution events means that the rarity of the signal is harder to explain: if it happened multiple times within a single dwarf galaxy, why not in other places?
+Further, a merger should result in stars with highly elliptical orbits, while the candidates identified appear to be disk stars.}
 
-More generally, the [K/Fe]-[Fe/H] anti-correlation observed is supportive of the origin of the Mg-K anti-correlation being temporally confined to an early epoch in the evolution of galaxies and globular clusters.
+\todo{More generally, the [K/Fe]-[Fe/H] relation we observed is supportive of the origin of the Mg-K anti-correlation being temporally confined to an early epoch in the evolution of galaxies and globular clusters.
 However, this is not necessarily the only interpretation.
-For example, it could be that the K forming process is happening throughout the life of the galaxy, but the amount of K produced decreases with the metallicity of the polluter star, though there is no obvious reason why this would be the case.
+For example, it could be that the K forming process is happening throughout the life of the galaxy, but the amount of K produced decreases with the metallicity of the polluter star, though there is no obvious reason why this would be the case.}
 
@@
 \label{sec:conclusion}
-Of the 454180 giant sample from \lamost, 112 candidate stars were identified as likely to have enhanced K and depleted Mg based on their absorption spectra.
-These stars show every appearance of being field stars, and they do not have the hallmarks of being the product of NLTE effects.
-The candidate sample reflected the metallicity distribution of the base \textit{LAMOST} sample.
+From a sample of 454,180 giant stars in \lamost, we identify 112 candidate stars that are significantly enhanced in K and depleted Mg.
+Although stars with this chemical pattern have been observed in globular clusters NGC 2419 and NGC 2808, this represents the first observations of field stars with this peculiar abundance signature.
+Our candidates are not restricted to a particular phase of stellar evolution, and their metallicity distribution is reflective of the parent \lamost\ sample.
 
-Upon conducting an abundance analysis, anomalously high levels of K were found in the sample, with levels of [K/Fe] as high as 1.5 confirmed through high resolution spectroscopy using Magellan/MIKE.
+We find extreme abundance ratios of [K/Fe] $\approx 1.5$ in our sample, but none that exceed the levels observed in NGC 2419 (up to [K/Fe] $\approx$ 2).
+While our analysis suggests the presence of substantial [Mg/Fe] depletion, follow-up observations are necessary to quantify the level of Mg-depletion.
+The spread in metallicities among our sample suggests that the mechanism responsible for the Mg-K abundance signature is not limited to early epochs (e.g., Population III supernova) or low-metallicity environments.
+We highlight SAGB-binaries as a plausible polluter candidate for the Mg-K abundance signature.
+We encourage future high-resolution observations and modelling efforts to understand this peculiar nucleosynthetic pathway.
+
+%An intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains uncertain without further higher resolution observations of the candidates.
+Further high resolution observations will also allow Mg and other elemental abundances to be determined.
+
+%Upon conducting an abundance analysis, anomalously high levels of K were found in the sample, with levels of [K/Fe] as high as 1.5 confirmed through high resolution spectroscopy using Magellan/MIKE.
 The [K/Fe] abundances were not consistent with the extreme populations previsously identified in either NGC 2419 or NGC 2808.
-No conclusion can be reached regarding the presence of [Mg/Fe] depletions in the sample as [Mg/Fe] abundances were unable to be determined from the \lamost.
-
-An intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains uncertain without further higher resolution observations of the candidates.
-Further high resolution observations will also allow Mg and other elemental abundances to be determined.
+No conclusion can be reached regarding the presence of [Mg/Fe] depletions in the sample as [Mg/Fe] abundances were unable to be determined from the \lamost\ spectra.
 

### 2018-02-07 article/ms.tex
minor changes to ms, larger changes to plotting code

@@
 The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
-Here we present 112 field stars, identified from \LamostGiants\ \lamost\ giant stars, that show significantly enhanced [K/Fe] and possibly depleted [Mg/Fe] abundance ratios.
+Here we present 112 field stars, identified from \LamostGiants\ \lamost\ giant stars \todo{using a data-driven model produced by \tc}, that show significantly enhanced [K/Fe] and possibly depleted [Mg/Fe] abundance ratios.
 Our sample spans a full range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$), yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 
@@
 This would suggest that pollution scenarios that are limited to early epochs (e.g., Population III supernovae) are an unlikely explanation.
-This sample is expected to help guide modelling attempts to explain the origin of the Mg-K abundance signature, which we show exists throughout the Milky Way.
+This sample is expected to help guide modelling \todo{and observational} attempts to explain the origin of the Mg-K abundance signature, which we show exists throughout the Milky Way.
 \end{abstract}
@@
 \subsection{Candidate selection from \lamost\ spectra}
-We used a set of \LamostGiants\ giant stars from the second \lamost\ data release \todo{\citep{lamostDR2}}.
+We used a set of \LamostGiants\ giant stars from the second \lamost\ data release \citep{luo2016vizier}.
 The spectra were placed at rest-frame on a common wavelength sampling from 3905\,\AA\ to 9000\,\AA\ and pseudo-continuum-normalised as per \citet{ho2017}.
@@
 However, the \lamost\ spectra relative to \tc\ model is consistent with an under-abundance of Mg.
-The small sample of stars for which we have high resolution spectra, coupled with the conflict with the \lamost spectra, means we are unable to confidently make a statement regarding the level of [Mg/Fe] compared to NGC 2419 or NGC 2808.
+The small sample of stars for which we have high resolution spectra, coupled with the conflict with the \lamost\ spectra, means we are unable to confidently make a statement regarding the level of [Mg/Fe] compared to NGC 2419 or NGC 2808.
 
@@
 It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation.
-However we caution that this may be an artefact of our analysis, further high resolution observations are needed to verify this trend.
+However we caution that this may be an artefact of our analysis.
+Further high resolution observations are needed to verify this trend.
 
@@
 While this scenario is consistent with the total spread in metallicity, it is not applicable to NGC 2419 or NGC2808.
-SAGB-binaries cannot account for 30\% of the stars in NGC 2419 showing depleted Mg and enhanced K abundances.
-\todo{Why not, exactly?} Furthermore, it would only irregularly produce a depletion in [Mg/Fe], unlike the apparent bi-modality seen in abundance ratios in NGC 2419 and NGC 2808.
+It would take a highly irregular IMF for SAGB-binaries to account for 30\% of the stars in NGC 2419 showing depleted Mg and enhanced K abundances.
+Furthermore, SAGB-binaries would only irregularly produce a depletion in [Mg/Fe], unlike the consistent bi-modality seen in abundance ratios in NGC 2419 and NGC 2808.
 
@@
 
-\todo{One major issue facing this explanation is that it requires a single gas cloud to form many generations of stars almost continuously in order to be consistent with Figure \ref{KvsFe}.
+%\todo{One major issue facing this explanation is that it requires a single gas cloud to form many generations of stars almost continuously in order to be consistent with Figure \ref{KvsFe}.
 This is only known to occur in inside true galaxies, which are massive enough to form multiple star forming regions.
@@
 
-\todo{More generally, the [K/Fe]-[Fe/H] relation we observed is supportive of the origin of the Mg-K anti-correlation being temporally confined to an early epoch in the evolution of galaxies and globular clusters.
+%\todo{More generally, the [K/Fe]-[Fe/H] relation we observed is supportive of the origin of the Mg-K anti-correlation being temporally confined to an early epoch in the evolution of galaxies and globular clusters.
 However, this is not necessarily the only interpretation.
@@
 
-We find extreme abundance ratios of [K/Fe] $\approx 1.5$ in our sample, but none that exceed the levels observed in NGC 2419 (up to [K/Fe] $\approx$ 2).
+We find extreme abundance ratios of [K/Fe] $\approx 1.5$ \todo{can we say they were aprox 1.5?
+only 1 star was that high...
+surely an 'up to' or an 'as high as' is more accurate} in our sample, but none that exceed the levels observed in NGC 2419 (up to [K/Fe] $\approx$ 2).
 While our analysis suggests the presence of substantial [Mg/Fe] depletion, follow-up observations are necessary to quantify the level of Mg-depletion.
 The spread in metallicities among our sample suggests that the mechanism responsible for the Mg-K abundance signature is not limited to early epochs (e.g., Population III supernova) or low-metallicity environments.
-We highlight SAGB-binaries as a plausible polluter candidate for the Mg-K abundance signature.
+We highlight SAGB-binaries as a plausible polluter candidate for the Mg-K abundance signature \todo{within the disk}.
 We encourage future high-resolution observations and modelling efforts to understand this peculiar nucleosynthetic pathway.

### 2018-02-07 article/plottera.py

@@ -9,6 +9,8 @@ Created on Tue Jan  9 15:25:28 2018
 import numpy as np
 import os
 import matplotlib.pyplot as plt
+import matplotlib.ticker as ticker
+from matplotlib.font_manager import FontProperties
 import pandas as pd
 from glob import glob
 import astropy as asp
@@ -25,8 +27,7 @@ from astropy.io import fits
 from astropy.table import Table
 plt.close('all')
 
-mgkarray=np.array(pd.read_csv("Mg-K-candidatesFINALCUT_nonHemmision.csv"))
-globarray=np.array(pd.read_csv("globular_clusters.csv"))
+mgkarray=np.array(pd.read_csv("Total112listdr2kna.csv"))
 
 C_K2012=np.array(pd.read_csv("C+K 2012.csv"))
 Muc2012=np.array(pd.read_csv("Mucciarelli 2012.csv"))
@@ -34,31 +35,39 @@ Muc2012=np.array(pd.read_csv("Mucciarelli 2012.csv"))
 
 ngc2808=np.array(pd.read_csv("NGC2808 Muc 2015.csv"))
 
-lamK=np.array(pd.read_csv("provisionalKabundances.csv"))
+lamK=mgkarray[:,[-4,-3,-2,-1]]
 
 Maglam=np.array(pd.read_csv("Magellan.csv"))
 
 LC=np.array(pd.read_csv("LasCampmgkabundances.csv"))
+
+apogee=np.array(pd.read_csv("apogeefiltered.csv"))
+
+apFe=apogee[:,113]
+apK=apogee[:,106]
+
 Teff=mgkarray[:,1]
 logg=mgkarray[:,2]
 metalicity=mgkarray[:,3]
+alpha=mgkarray[:,4]
 
-mgkl=mgkarray[:,-2]
-mgkb=mgkarray[:,-1]
-globl=globarray[:,4]
-globb=globarray[:,5]
+
 
 C_KMg=C_K2012[:,1]
 C_KMgu=C_K2012[:,2]
 C_KK=C_K2012[:,3]
 #C_KKu=C_K2012[:,4] (no uncertainties known)
+C_KFe=C_K2012[:,5]
+
 MucMg=Muc2012[:,1]
 MucMgu=Muc2012[:,2]
 MucK=Muc2012[:,3]
 MucKu=Muc2012[:,4]
+MucFe=Muc2012[:,5]
 
 ngc2808Mg=ngc2808[:,0]
 ngc2808K=ngc2808[:,1]
[…]

### 2018-02-08 article/ms.tex
worked in graphical changes, included the 0.2 quadrature flooring in both table and plots for LAMOST abundance errrors

@@
 The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
-Here we present 112 field stars, identified from \LamostGiants\ \lamost\ giant stars \todo{using a data-driven model produced by \tc}, that show significantly enhanced [K/Fe] and possibly depleted [Mg/Fe] abundance ratios.
+Here we present 112 field stars, identified from \LamostGiants\ \lamost\ giant stars using a data-driven model produced by \tc, that show significantly enhanced [K/Fe] and possibly depleted [Mg/Fe] abundance ratios.
 Our sample spans a full range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$), yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 
@@
 This would suggest that pollution scenarios that are limited to early epochs (e.g., Population III supernovae) are an unlikely explanation.
-This sample is expected to help guide modelling \todo{and observational} attempts to explain the origin of the Mg-K abundance signature, which we show exists throughout the Milky Way.
+This sample is expected to help guide modelling  attempts to explain the origin of the Mg-K abundance signature, which we show exists throughout the Milky Way.
 \end{abstract}
@@
 \begin{figure*}
-	\includegraphics[width=\textwidth]{posterchildof13.png}
+	\includegraphics[width=\textwidth]{posterchild.png}
     \caption{Pseudo-continuum-normalised \lamost\ spectra for the Mg-depleted and K-enhanced candidate J034458.82+592955.1.
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{histof113.png}
+	\includegraphics[width=\columnwidth]{mhist.png}
     \caption{Metallicity distribution for all 112 candidate stars identified with K-enhancement and Mg-depletion.}
@@
 \begin{figure}
-	\includegraphics[width=\columnwidth]{Kvsmgmod.png}
+	\includegraphics[width=\columnwidth]{KvsMg.png}
     \caption{Comparison of [K/Fe] vs [$\alpha$/Fe] for the candidate stars with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
@@
 - & {[}deg{]} & {[}deg{]} & [pixel$^{-1}]$ & {[${\rm km\,s}^{-1}$]} & {[}K{]} & $[{\rm cm\,s}^{-2}]$ & {[}dex{]} & {[}dex{]} & - & {[}dex{]} & {[}dex{]} & {[}dex{]} & {[}dex{]} \\ \hline
-J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.16 & 0.86 & 0.12 \\
-J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.08 & 0.39 & 0.10 \\
-J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.06 & -0.20 & 0.00 \\
-J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 & 0.96 & 0.26 & -0.16 & 0.00 \\
-J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.10 & 0.44 & 0.76 & 0.11 & -0.02 & 0.00 \\
-J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.10 & 0.05 & 1.17 & 0.95 & 0.06 & -0.07 & 0.00 \\
-J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.00 & -0.04 & 0.00 \\
-J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.05 & 0.46 & 0.05 \\
-J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1.00 & 8.70 & -0.02 & 0.00 \\
-J032423.46+425429.6 & 51.10 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.09 & 0.80 & 0.04 \\ \hline
+J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.26 & 0.86 & 0.23 \\
+J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.22 & 0.39 & 0.22 \\
+J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.21 & -0.20 & 0.20 \\
+J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.1 & -0.56 & 0.24 & 0.31 & 0.96 & 0.33 & -0.16 & 0.20 \\
+J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.1 & 0.44 & 0.76 & 0.23 & -0.02 & 0.20 \\
+J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.1 & 0.05 & 1.17 & 0.95 & 0.21 & -0.07 & 0.20 \\
+J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.20 & -0.04 & 0.20 \\
+J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.21 & 0.46 & 0.21 \\
+J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1 & 8.70 & -0.02 & 0.20 \\
+J032423.46+425429.6 & 51.1 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.22 & 0.80 & 0.20 \\ \hline
 \end{tabular}
@@
 
-We find extreme abundance ratios of [K/Fe] $\approx 1.5$ \todo{can we say they were aprox 1.5?
-only 1 star was that high...
-surely an 'up to' or an 'as high as' is more accurate} in our sample, but none that exceed the levels observed in NGC 2419 (up to [K/Fe] $\approx$ 2).
+We find extreme abundance ratios of up to [K/Fe] $\approx 1.5$ in our sample, but none that exceed the levels observed in NGC 2419 (up to [K/Fe] $\approx$ 2).
 While our analysis suggests the presence of substantial [Mg/Fe] depletion, follow-up observations are necessary to quantify the level of Mg-depletion.
 The spread in metallicities among our sample suggests that the mechanism responsible for the Mg-K abundance signature is not limited to early epochs (e.g., Population III supernova) or low-metallicity environments.
-We highlight SAGB-binaries as a plausible polluter candidate for the Mg-K abundance signature \todo{within the disk}.
+We highlight SAGB-binaries as a plausible polluter candidate for the Mg-K abundance signature within the disk.
 We encourage future high-resolution observations and modelling efforts to understand this peculiar nucleosynthetic pathway.

### 2018-02-08 article/ms.tex
minor
acks

@@
     \caption{Comparison of [K/Fe] vs [$\alpha$/Fe] for the candidate stars with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
-See text for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].
-The dotted line is arbitrary, and is present simply as a visual aide.}
+See text for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].}
     \label{KvsMg}
@@
 \section*{Acknowledgements}
+We thank Alex P. Ji (Carnegie Observatories), Melissa Ness (Columbia), David W. Hogg (NYU), and Hans-Walter Rix (MPIA).
 %- Magellan/MIKE and Australian government

### 2018-02-08 article/ms.tex
abstract change

@@
 The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
-Here we present 112 field stars, identified from \LamostGiants\ \lamost\ giant stars using a data-driven model produced by \tc, that show significantly enhanced [K/Fe] and possibly depleted [Mg/Fe] abundance ratios.
+Here we present
+112 field stars, identified from \LamostGiants\ \lamost\ giant stars using a data-driven model (\tc), that show significantly enhanced [K/Fe] and likely depleted [Mg/Fe] abundance ratios.
 Our sample spans a full range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$), yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 

### 2018-02-12 article/ms.tex
Worked in most comments

@@
 \newcommand{\teff}{T_{\rm eff}}
-\newcommand{\logg}{\log_{10}[g\,({\rm cm\,s}^{-2})]}
-
+\newcommand{\logg}{\log_{10}(g/{\rm cm\,s}^{-2})}
+\let\ACMmaketitle=\maketitle
+\renewcommand{\maketitle}{\begingroup\let\footnote=\thanks \ACMmaketitle\endgroup}
 %%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
@@
 % Keep the title short and informative.
-\title[Mg-K stars in LAMOST]{On the discovery of K-enhanced and Mg-depleted stars throughout the Milky Way}
+\title[Mg--K stars in LAMOST]{On the discovery of K-enhanced and Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}}
 
@@
 Stars with unusual elemental abundances offer clues about rare astrophysical events or nucleosynthetic pathways.
-Stars with significantly depleted magnesium and enhanced potassium (e.g., $[{\rm K}/{\rm Fe}] > 1$; $[{\rm Mg}/{\rm Fe}] < -0.5$) have to date only been found in the massive globular cluster NGC~2419, and to a lesser extent, NGC~2808.
+Stars with significantly depleted magnesium and enhanced potassium ($[{\rm Mg}/{\rm Fe}] < -0.5$; $[{\rm K}/{\rm Fe}] > 1$) have to date only been found in the massive globular cluster NGC~2419 and, to a lesser extent, NGC~2808.
 The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
@@
 112 field stars, identified from \LamostGiants\ \lamost\ giant stars using a data-driven model (\tc), that show significantly enhanced [K/Fe] and likely depleted [Mg/Fe] abundance ratios.
-Our sample spans a full range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$), yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 
+Our sample spans a range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$) yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 
 We conclude that the nucleosynthetic process producing the anomalous abundances in [K/Fe] and [Mg/Fe] probably (but not necessarily) occurs at a wide range of metallicities.
-This would suggest that pollution scenarios that are limited to early epochs (e.g., Population III supernovae) are an unlikely explanation.
-This sample is expected to help guide modelling  attempts to explain the origin of the Mg-K abundance signature, which we show exists throughout the Milky Way.
+This would suggest that pollution scenarios that are limited to early epochs (such as Population III supernovae) are an unlikely explanation.
+This sample is expected to help guide modelling  attempts to explain the origin of the Mg--K abundance signature, which we show exists throughout the Milky Way.
 \end{abstract}
@@
 A targeted search looking for [K/Fe] in RGB and main sequence turn-off stars in other clusters (NGC 6752, NGC 6121, NGC 1904, 47 Tuc, NGC 6397, NGC 7099, and $\omega$ Centauri) and field stars concluded that all K abundance ratios fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}.
-NGC 2808 is the only cluster other than NGC 2419 where an anticorrelation between Mg and K has been observed.
-All 4 of NGC 2808's known Mg-depleted stars show an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these abundance ratios is far weaker than those found in NGC 2419.
-The fact that the Mg-K anti-correlation is apparently confined to these two globular clusters would imply either a small population of unusual polluter stars, or a single extremely massive polluter star.
+NGC 2808 is the only cluster, other than NGC 2419, where an anticorrelation between Mg and K has been observed.
+All four of NGC 2808's known Mg-depleted stars show an anti-correlation with K \citep{mucciarelli2015}, although the amplitude of these abundance ratios is far weaker than those found in NGC 2419.
+The fact that the Mg-K anti-correlation is apparently confined to these two globular clusters implies either a small population of unusual polluter stars, or a single extremely massive polluter star.
+If it were the cumulative effect of many pollution events that was responsible for the signal, it would be expected that the anomalous abundances would be common among globular clusters, notwithstanding a reason why the stars could not form outside NGC 2419 and NGC 2808.
 
@@
 %While it is plausible that the increased mass and greater distance from the gaseous disk of the Milky Way would cause a clusters first generation polluter stars to have an increased effect on the second generation of stars, this effect would apply to all ejecta (assuming comparable energies).
-So while it might be expected that second generation stars in clusters similar to NGC 2419 made up of more material processed by the first generation than other lighter globular clusters, it doesn't explain why the ejecta from the first generation was apparently dominated by this as yet unknown polluter object resulting in the Mg-K anti-correlation.
+So while it might be expected that second generation stars in clusters similar to NGC 2419 made up of more material processed by the first generation than other lighter globular clusters, it doesn't explain why the ejecta from the first generation was apparently dominated by this as yet unknown polluter object resulting in the Mg--K anti-correlation.
 In the opinion of the author, it is the identity and physical characterisation of this unknown polluter that is of the greatest scientific interest, with such a result also hopefully answering the question of the signatures uniqueness.
 
-One  mechanism for [Mg/Fe] depletion is the introduction of $\alpha$-poor and Fe-rich material released from Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the `normal' [Mg/Fe] ratios that arise from Type II supernovae.
+One  mechanism for [Mg/Fe] depletion is the introduction of $\alpha$-poor and Fe-rich material released by Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the normal [Mg/Fe] ratios that arise from Type II supernovae.
 However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}.
-Furthermore, Type Ia supernovae enrichment cannot account for the enhanced K abundance observed in NGC 2419.
-In fact, K is hard to make in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates from measured values by several orders of magnitude \citep{ventura2012,iliadis2016}.
-Another mechanism for reducing [Mg/Fe] is through the Mg-Al nucleosynthetic chain in high temperature hydrogen burning.
+Furthermore, Type Ia supernova enrichment cannot account for the enhanced K abundance observed in NGC 2419.
+In fact it is hard to make K in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates above those measured by several orders of magnitude \citep{ventura2012,iliadis2016}.
+Another mechanism for reducing [Mg/Fe] is through the Mg--Al nucleosynthetic chain in high-temperature hydrogen burning.
 However, no correlation between Mg and Al is observed in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.
-Recent work by \cite{ritter2017} on K production in O-C shell mergers shows promise as an alternative source of K, but this work is ongoing.
+Recent work by \cite{ritter2017} on K production in O-C shell mergers in very low-metallicity stars shows promise as an alternative source of K but this work not sufficiently quantitative yet.
 
-Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg-K anti-correlation, a satisfactory explanation for the Mg-K signature may also offer insight into the underestimation of K abundances in the Milky Way predicted by galactic chemical evolution models \citep{kobayashi2011}, or more broadly help to understand globular cluster formation and evolution.
-Here we use \lamost\ data to conduct the largest ever search for stars enhanced in potassium and depleted in magnesium.
-The discovery (or non-discovery) of such stars would guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.
-In particular, such a search would provide strong evidence either for or against the uniqueness of the progenitor stars to globular clusters.
+Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg--K anti-correlation, a satisfactory explanation for the Mg--K signature may also offer insight into the underestimation of K abundances in the Milky Way predicted by Galactic chemical evolution models \citep{kobayashi2011} or more broadly help to understand globular cluster formation and evolution.
+Here we use \lamost\ data to conduct the largest search to date for stars enhanced in potassium and depleted in magnesium.
+The discovery (or non-discovery) of such stars guides models that attempt to explain the Mg--K anti-correlation and related abundance phenomena.
+In particular, such a search provides strong evidence either for or against the uniqueness of the progenitor stars to globular clusters.
 In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis for some of those candidates.
@@
 
-%This study, which queries \LamostGiants\ \lamost\ giants for depleted Mg and enhanced K, seeks to provide additional information which can be used to guide and test models attempting to explain the Mg-K anti-correlation and related phenomena.
+%This study, which queries \LamostGiants\ \lamost\ giants for depleted Mg and enhanced K, seeks to provide additional information which can be used to guide and test models attempting to explain the Mg--K anti-correlation and related phenomena.
 The large sample size provides greater insight into the supposed exclusivity of the signature, and the stars identified present an important opportunity for follow up observations.
@@
 We used a set of \LamostGiants\ giant stars from the second \lamost\ data release \citep{luo2016vizier}.
-The spectra were placed at rest-frame on a common wavelength sampling from 3905\,\AA\ to 9000\,\AA\ and pseudo-continuum-normalised as per \citet{ho2017}.
-\tc\ \citep{ness2016,ho2017} was used to estimate effective temperature ($\teff$), surface gravity ($\logg$), metallicity ([Fe/H]), and mean $\alpha$-element abundance relative to iron ([$\alpha$/Fe]) using 9,952 stars in common between \lamost\ and the \apogee\ \citep{alam2015} survey.
+The spectra were placed at rest-frame on a common wavelength sampling from 3905\,\AA\ to 9000\,\AA\ and normalised by \citet{ho2017}.
+\tc\ \citep{ness2016,ho2017} was used to estimate effective temperature $\teff$, surface gravity $\logg$, metallicity [Fe/H], and mean $\alpha$-element abundance relative to iron [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the \apogee\ \citep{alam2015} survey.
 Unless otherwise stated, these transferred labels are those referred to throughout this study.
-For details regarding the preparatory work, model generation, and label transfer between the \apogee\ and \lamost\ surveys, we direct the reader to \citet{ho2017}.
+For details regarding the preparatory work, model generation, and label transfer between the \apogee\ and \lamost\ surveys we direct the reader to \citet{ho2017}.
 
@@
 A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model).
-Figure \ref{posterchild} shows the \lamost\ spectra, and best-fitting model from \tc, for candidate J034458.82+592955.1.
+Figure \ref{posterchild} shows the \lamost\ spectrum and best-fitting model from \tc for candidate J034458.82+592955.1.
 
-We fit a gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167\,\AA, 5172\,\AA, 5184\,\AA) as well as the K doublet (7665\,\AA, 7699\,\AA) for all \LamostGiants\ giants.
+We fit a Gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167\,\AA, 5172\,\AA, 5184\,\AA) as well as the K doublet (7665\,\AA, 7699\,\AA) for all \LamostGiants\ giants.
 For each star we recorded the profile amplitudes, wavelengths, widths, as well as associated measurement uncertainties of these quantities.
-We note that although telluric absorption would usually swamp the K doublet lines, the contribution of telluric features have been removed from \lamost\ spectra as part of the data  reduction process.
-We identified candidates by requiring they match at least one of the following three quality filters:
+We note that although telluric absorption would usually swamp the K doublet lines, the contributions of telluric features have been removed from \lamost\ spectra as part of the data reduction process conducted by \lamost \citep{luo2016vizier}.
+We identified candidates by requiring that they match at least one of the following three quality filters:
 \begin{enumerate}
@@
 \item We required any two of the three Mg triplet lines to satisfy $A > 0.05$ and at least one K line to have $A < -0.05$, and for those amplitudes to have $|A|/\sigma_{A} \geq 3$.
-\item We required any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost, and a reported $\chi_{r}^2 < 3$ from \tc.
+\item We required any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost and a reported $\chi_{r}^2 < 3$ from \tc.
 \end{enumerate}
@@
 These filters identified 384 unique stars.
-We visually inspected every candidate (multiple times) and excluded stars that showed any evidence of being a false positive, including candidates that exhibited data reduction issues, apparent absorption that was narrower than the expected spectral resolution, as well as 75 stars that exhibited chromospheric emission at H$\alpha$.
+We visually inspected every candidate (multiple times) and excluded stars that showed any evidence of being a false positive, including candidates that exhibited data reduction issues, apparent absorption that was narrower than the expected spectral resolution, as well as 75 stars that exhibited chromospheric emission at H$\alpha$, indicative of chromospheric activity which can cause deceptively strong spectral lines.
 The distilled catalogue contains 112 candidate stars with spectra consistent with enhancements in K and depletions in Mg.
@@
 We estimated [K/Fe] abundance ratios for all candidates by synthesising spectra to account for the flux residuals \citep{marcs,sme,vald,ispec}.
-We assume that absorption due to metals is accounted for by \tc, and deviations in flux around the potassium doublet is due to an increased [K/Fe] with respect to the model.
+We assume that absorption due to metals is accounted for by \tc, and deviations in flux around the potassium doublet are due to an increased [K/Fe] with respect to the model.
 We list estimated [K/Fe] abundance ratios in Table \ref{data}, where the error includes a 0.2\,dex systematic error floor that we have applied in quadrature with the fitting errors.
 We applied the same method to estimate [Na/Fe] from \lamost\ spectra.
-We note that while enhancements in [K/Fe] or [Na/Fe] can be estimated by synthesising the flux residuals, we cannot easily estimate [Mg/Fe] depletions in the same manner because it is difficult to separate the flux contribution of [Mg/Fe] (from [$\alpha$/Fe]) from the data-driven model.
+We note that while enhancements in [K/Fe] or [Na/Fe] can be estimated by synthesising the flux residuals, we cannot easily estimate [Mg/Fe] depletions in the same manner because it is difficult to separate the flux contribution of [Mg/Fe] from [$\alpha$/Fe] in the data-driven model.
 For this reason, we will adopt [$\alpha$/Fe] as a conservative upper limit for [Mg/Fe].
@@
 \subsection{Follow-up observations with Magellan/MIKE}
-High resolution spectra of three of the candidate stars selected based on observability (J075043.12+204658.0, J120032.60+024438.2 and J091825.49+172114.5) were obtained using Magellan/MIKE.
+High resolution spectra of three of the candidate stars selected based on observability (J075043.12+204658.0, J120032.60+024438.2 and J091825.49+172114.5) were obtained using Magellan/MIKE (Magellan Inamori Kyocera Echelle) \citep{shectman2003magellan,bernstein2003mike}
  \todo{@andy add relevant info on abundance calculations.}
@@
 	\includegraphics[width=\textwidth]{posterchild.png}
-    \caption{Pseudo-continuum-normalised \lamost\ spectra for the Mg-depleted and K-enhanced candidate J034458.82+592955.1.
-The data  are shown in black and the best-fitting data-driven model from \tc\ is shown in red.
-We show zoom-in axes around the magnesium triplet and potassium doublet, which we used to identify Mg-K candidates.
-Note that $[\alpha/{\rm Fe}]$ is a label in \tc\ model used, and J034458.82+592955.1 shows Mg depletions relative to the estimated [$\alpha$/Fe] value.}
+    \caption{Pseudo-continuum-normalised \lamost\ spectrum for the Mg-depleted and K-enhanced candidate J034458.82+592955.1.
+The data are shown in black and the best-fitting data-driven model from \tc\ is in red.
+We zoom in around the magnesium triplet and potassium doublet, which we used to identify Mg--K candidates.
+Note that $[\alpha/{\rm Fe}]$ is a label in \tc\ model used and J034458.82+592955.1 shows Mg depletions relative to the estimated [$\alpha$/Fe] value.}
     \label{posterchild}
@@
 
-Our sample of \lamost\ giants carries with it certain selection effects as a result of both the \apogee\ DR12 and \lamost\ samples.
-For example, metal-poor stars with [Fe/H] $\lesssim-2$ are mostly absent from our sample as they were likely too dissimilar from the training stars for label transfer from \apogee.
-Similarly, the target selection process for \lamost\ is not easily invertible, and so selection effects present in \lamost\ are not considered here beyond comparing the candidate stars' metallicity distribution with that of \cite{ho2017}.
-From this comparison we find that the frequency of Mg/K stars is consistent (within the errors) of being flat with metallicity.
-We also note that  our candidate stars are distributed across the entire giant branch, implying that the abundance signature is not associated with any single particular stage in evolution, and that the chemical pattern we observe is not due to a violation of the assumption of local thermodynamic equilibrium.
+Our sample of \lamost\ giants carries with it certain selection effects from both the \apogee\ DR12 and \lamost\ samples.
+For example, metal-poor stars with [Fe/H] $\lesssim-2$ are mostly absent from our sample because they were too dissimilar from the training stars for label transfer from \apogee.
+Similarly, the target selection process for \lamost\ is not easily invertible so we do not consider selection effects present in \lamost\ beyond comparing the candidate stars' metallicity distribution with that of \cite{ho2017}.
+We find that the frequency of Mg--K stars is consistent (within the errors) of being flat with metallicity.
+We also note that our candidate stars are distributed across the entire giant branch, implying that the abundance signature is not associated with any single particular stage in evolution and that the chemical pattern we observe is not due to a violation of the assumption of local thermodynamic equilibrium.
 
@@
 \label{sec:globclustasoc}
-We cross-matched our candidates against the positions of all known globular clusters \citep{harris1996}.
+We cross-matched our candidates with the positions of all known globular clusters \citep{harris1996}.
 No candidates can be associated with NGC~2419 or NGC~2808.
@@
 The distribution reflects the original \LamostGiants\ sample of giants from which the candidates were selected.
-No candidates have [Fe/H] $\sim -2$ -- the approximate metallicity of NGC 2419 -- nor are there many stars with [Fe/H] $\sim -1$ -- the metallicity of NGC 2808.
+No candidates have [Fe/H] $\approx -2$, the approximate metallicity of NGC 2419, nor are there many stars with [Fe/H] $\approx -1$, the metallicity of NGC 2808.
 Thus, we conclude that the candidates are not restricted to any specific metallicity, particularly not just to the metallicities of NGC 2419 and NGC 2808.
@@
 
-Upon examining [Na/Fe] as estimated from the \lamost\ spectra, two distinct populations were observed: one population making up approximately 30\% of the sample with [Na/Fe] > 0.5 -- significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011} -- and a second with [Na/Fe] consistent with typical galactic values.
-However, the high [Na/Fe] abundance ratios we observe are very likely due to the effect of interstellar dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) values \citep{schlafly2011}, suggesting that the stellar absorption lines are being blended with interstellar dust absorption.
+Upon examining [Na/Fe] as estimated from the \lamost\ spectra, two distinct populations were observed: one population making up approximately 30 percent of the sample with [Na/Fe] > 0.5, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second with [Na/Fe] consistent with typical Galactic abundances.
+However, the high [Na/Fe] abundance ratios we observe are very likely due to the effect of interstellar dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption.
 It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a positive correlation between Na and K.
-Despite our noisy estimates of Na and K in our sample, no relation between Na and K abundances is observed.
+No relation between Na and K abundances is observed.
 
@@
 
-Abundance ratios of [$\alpha$/Fe] in our sample fall within the lower limits for [Mg/Fe] of the Mg-normal population of both NGC 2419 and NGC 2808, although as we are unable to decouple [Mg/Fe] from $[\alpha$/Fe], the exact level of Mg depletion for the candidates is unclear.
+Abundance ratios of [$\alpha$/Fe] in our sample fall within the lower limits for [Mg/Fe] of the Mg-normal population of both NGC 2419 and NGC 2808, although as we are unable to decouple [Mg/Fe] from $[\alpha$/Fe], the exact level of Mg depletion of the candidates is unclear.
 The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra are consistent with the Mg-normal population in NGC 2419.
-However, the \lamost\ spectra relative to \tc\ model is consistent with an under-abundance of Mg.
+However, the \lamost\ spectral flux residuals with \tc\ model are consistent with an under-abundance of Mg.
 The small sample of stars for which we have high resolution spectra, coupled with the conflict with the \lamost\ spectra, means we are unable to confidently make a statement regarding the level of [Mg/Fe] compared to NGC 2419 or NGC 2808.
 
-Given that the sample is almost certainly comprised of disk stars, it is relevant to also compare with typical galactic abundances for [K/Fe], taken from \cite{kobayashi2011}.
-The sample's [K/Fe] appears definitively anomalous, with galactic values for [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8-1.3.
-Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample has extremely high levels of [K/Fe], approaching the extreme levels observed in NGC 2419.
+Given that the sample is almost certainly comprised of disk stars, it is relevant to also compare with typical Galactic abundances for [K/Fe], taken from \cite{kobayashi2011}.
+The sample's [K/Fe] appears definitively anomalous, with Galactic [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] of 0.8 to 1.3.
+Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample stars have extremely high levels of [K/Fe], approaching the extreme levels observed in NGC 2419.
 
-The [K/Fe] abundance ratios in our sample also show an anti-correlation with total metallicity, as illustrated in Figure \ref{KvsFe}, which is not present in the bulk of Milky Way stars.
+The [K/Fe] abundance ratios in our sample also show an anti-correlation with total metallicity, illustrated in Figure \ref{KvsFe}, which is not present in the bulk of Milky Way stars.
 It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation.
@@
 
-%In contrast with the marked departure from galactic values for [K/Fe], [$\alpha$/Fe] varies from around 0-0.3\,dex in the \lamost \ sample, similar to galactic levels of [Mg/Fe], which vary with metallicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}.
+%In contrast with the marked departure from Galactic values for [K/Fe], [$\alpha$/Fe] varies from around 0-0.3\,dex in the \lamost \ sample, similar to Galactic levels of [Mg/Fe], which vary with metallicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}.
 No variation with metallicity is observed within the \lamost sample's [$\alpha$/Fe].
@@
 The implications of the abundance ratios we find are intriguing.
-The fact that, from such a large sample of field stars, none were found that replicated (or exceeded) the extreme abundance pattern of NGC 2419 is strong evidence for the cluster's uniqueness.
+The fact that in such a large sample of field stars, none were found that replicated (or exceeded) the extreme abundance pattern of NGC 2419 reinforces for the cluster's uniqueness.
 %regarding the extreme bi-modal nature of its abundance pattern. 
-It is worth repeating, however, that our sample of \lamost\ giants searched had already been filtered of most of the stars that would have matched NGC 2419's metallicity.
-The 112 star candidate pool identified of K enhanced stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels at a range of metallicities.
+However, we repeat that our sample of \lamost\ giants searched had already been filtered of most of the stars that would have matched NGC 2419's metallicity.
+The 112 star candidate pool identified of K enhanced stars represents a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical Galactic levels at a range of metallicities.
 It seems likely that whatever process is responsible for these anomalous field stars is similar to whatever caused the unusual stellar populations in NGC 2419 and NGC 2808.
+Although a unifying explanation remains elusive, it is improbable that a processes acting to produce such high levels of [K/Fe] in the Milky Way is unrelated to whatever process is responsible for the extreme abundance ratios in NGC 2419.
+The apparent consistency of NGC 2419's extreme population with the relation between [K/Fe] and [Fe/H] in Figure \ref{KvsFe} further supports the idea that the process responsible for the stars in this study and the previously known anomalous stars in NGC 2319 are related.
 
-\subsection{Impact on potential scenarios explaining the Mg-K anti-correlation}
+\subsection{Impact on potential scenarios explaining the Mg--K anti-correlation}
 
@@
 
-An early modelling attempt to replicate the anomalous Mg/K abundance ratios assumed hot-bottom burning in AGB and super-AGB (SAGB) stars.
-\cite{ventura2012} succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K.
-However, abundance patterns consistent with NGC 2419 were only possible if the Ar-K reaction cross section was increased to 100 times the laboratory value, or if the temperature at the base of the envelope could be made to exceed $\sim$150\,MK.
+An early modelling attempt to replicate the anomalous Mg--K abundance ratios assumed hot-bottom burning in asymptotic giant branch (AGB) and super-AGB (SAGB) stars.
+\cite{ventura2012} succeeded in reproducing the Mg--K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected by \cite{iliadis2016}) for the production of K.
+However, abundance patterns consistent with NGC 2419 were only possible if the Ar--K reaction cross section was increased to 100 that measured in the laboratory, or if the temperature at the base of the envelope could be made to exceed 150\,MK.
 
-A more recent attempt to replicate the Mg/K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}.
-The study aimed to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.\footnote{It is perhaps noteworthy that \cite{iliadis2016} identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway.
+A more recent attempt to replicate the Mg--K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}.
+The study aimed to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.
+\footnote{Note that \cite{iliadis2016} identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway.
 The main pathway used by \cite{iliadis2016} is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.}
-Unless extremely high densities were invoked ($>10^8\,{\rm g\,cm}^{-3}$), it was found that temperatures between 100 and 200\,MK were necessary.
-This constraint rules out many pollution sites, including: core and shell burning of low-mass stars, high-mass and super-massive stars, as well as regular AGB stars.
-Super-AGB (SAGB) stars, however, were considered as potential candidates, with only a relatively small (roughly 10-20 MK) increase in temperature required to fall in the acceptable band of parameter space identified.
-The other potential candidate identified was novae, although the lack of detailed models of white dwarf accretion of metal-poor material adds considerable uncertainty.
-However, based on current nova frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1\% of the total required mass to pollute 30\% of NGC 2419.
+Unless extremely high densities were invoked ($>10^8\,{\rm g\,cm}^{-3}$), it was found that temperatures between 100 and 200\,MK were necessary depending on the density.
+This constraint rules out many pollution sites, including core and shell burning of low-mass stars, high-mass and super-massive stars, and normal AGB stars.
+However, SAGB stars were considered as potential candidates, with only a relatively small (roughly 10 to 20 MK) increase in temperature at the bottom of the envelope required to fall in the acceptable band of parameter space identified, implying that it is possible that the conditions for K production through the Ar-K reaction pathway could be met in some SAGB stars.
+The other potential candidates identified were novae, although the lack of detailed models of white dwarf accretion of metal-poor material adds considerable uncertainty.
+However, based on current nova frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1 percent of the total required mass to pollute 30 percent of NGC 2419.
 
 Another proposed  polluter candidate is a pair-instability super nova \citep[PISN;][]{carretta2013}.
-Unique to extremely massive Population III stars, these events involve the total destruction of the star, with no black hole remnant left behind.
-The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material released, could allow for the abundance signature in NGC 2419 to be the result of a single, extremely rare event, which would explain why it is not seen in any other globular clusters.
-However, the signature odd-even proton number abundance pattern associated with PISNs is absent from NGC 2419 \citep{cohenkirby2012}.
+Unique to extremely massive Population III stars, these events involve the total destruction of the star, with no remnant left behind.
+The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material released, could allow for the abundance signature in NGC 2419 to be the result of a single event, which would explain why a similar abundance trend is not seen in any other globular clusters.
+However, the signature odd-even proton number abundance pattern associated with PISNs, where odd Z elements are enhanced and even Z elements are depleted, is absent from NGC 2419 \citep{carretta2013, cohenkirby2012}.
 
-Our study presents a collection of stars in the disk of the galaxy at a range of metallicities showing anomalously high levels of [K/Fe].
-The spread in metallicities among our candidates is important to note.
-It implies that the process responsible for the Mg-K abundance signature may not be tied to a certain epoch in the Milky Way's evolution.
-Since these stars with enhanced potassium apparently tend to form at all ages, across all metallicities, it is probable that the polluter star is also able to form independently of metallicity.
-If we assume that the polluter star forms at a range of metallicities, then we can make qualitative constraints on scenarios that may be responsible for the Mg-K anti-correlation.
+Our study presents a collection of stars in the disk of the Galaxy over a range of metallicities showing anomalously high levels of [K/Fe].
+The spread in metallicities among our candidates is important.
+It implies that the process responsible for the Mg--K abundance signature may not be tied to a certain epoch in the Milky Way's evolution.
+These stars with enhanced potassium apparently tend to form at all ages, across all metallicities, so it is probable that the polluting source is also independent of metallicity.
+If we assume that the polluter star forms at a range of metallicities, then we can make qualitative constraints on scenarios that may be responsible for the Mg--K anti-correlation by disregarding polluters that are reliant on specific metallicity environments to form.
 
 One class of candidates that can be immediately eliminated under such an assumption are Population III stars.
-A hyper-massive Population III star may have been a plausible explanation for NGC~2419 \citep{carretta2013}, particularly given it's isolation from the Milky Way ($d_{GC} \approx 90\,{\rm kpc}$) and low metallicity.
-However, being unable to form throughout the life of the galaxy makes it unlikely for a Population III star to be the polluter candidate responsible for the stars we identify.
+A hyper-massive Population III star may be been a plausible explanation for NGC~2419 \citep{carretta2013} exclusively, particularly given its isolation from the Milky Way ($d_{\rm GC} \approx 90\,{\rm kpc}$) and low metallicity.
+However, being unable to form throughout the life of the Galaxy makes it unlikely for Population III stars to be the polluters responsible for the stars we identify.
 
-One possible polluter candidate that \textit{could} form throughout the life of the Milky Way is an SAGB-binary.
+One possible polluter that \textit{could} form throughout the life of the Milky Way is a SAGB star with a binary companion.
 As emphasized by \cite{prantzos2017}, a significant challenge presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion in Mg and an enhancement in K.
-Reducing Mg is possible through conversion of \ce{^{24}Mg} to \ce{^{27}Al} through Mg-Al chains at temperatures around 75 MK, which is attainable in hot-bottom burning (HBB) environments in AGB stars.
+Reducing Mg is possible by converting \ce{^{24}Mg} to \ce{^{27}Al} through Mg--Al chains at temperatures around $75\,$ MK, which is attainable in hot-bottom burning (HBB) environments in AGB stars.
 However, temperatures upwards of 150 MK are required to produce K, and these temperatures can only potentially be reached at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
@@
 
-We hypothesise that the SAGB-binary may produce a [K/Fe] over-abundance in select stars within the Milky Way as follows.
-The SAGB star produces K \citep[destroying Na in the process;][]{prantzos2017}, which is then mixed throughout its envelope.
-It then deposits its K-rich outer layers onto its lower-mass companion through accreting winds.
-The lower-mass companion would continue to evolve long after the SAGB star has formed a white-dwarf remnant and will, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, will not.
-If the companion star had sufficient mass to undergo hot-bottom burning, then Na could be produced \citep{prantzos2017}.
-Further, depending on the HBB temperature, the AGB star may also deplete Mg through Mg/Al chains.
-The material produced through HBB is mixed throughout the envelope and to the surface of the star.
-In this scenario, it is observations of the lower-mass binary companion stars that make up our sample of 112 giants.
-A direct test would be to determine whether at least most of the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they could have formed as SAGB stars.
+We hypothesise that the SAGB-binary may produce a [K/Fe] over-abundance in some stars within the Milky Way as follows.
+The SAGB star produces K \citep[destroying Na in the process;][]{prantzos2017}, that is then mixed throughout the star's envelope.
+The SAGB star then deposits its K-rich outer layers onto its lower-mass companion through accreting winds.
+The lower-mass companion continues to evolve long after the SAGB star has formed a white-dwarf remnant and, depending on its mass after accretion, either undergoes hot-bottom burning or, more likely, does not.
+If the companion star had sufficient mass to undergo hot-bottom burning, then Na could be produced \citep{prantzos2017} at the expense of Ne.
+Further, depending on the HBB temperature, the AGB star may also deplete Mg through Mg--Al chains.
+The material produced through HBB is mixed throughout the envelope including the surface of the star.
+In this scenario, it is the lower-mass binary companion stars that make up our sample of 112 giants.
+A direct test would be to determine whether the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they formed from SAGB stars.
 
 While this scenario is consistent with the total spread in metallicity, it is not applicable to NGC 2419 or NGC2808.
-It would take a highly irregular IMF for SAGB-binaries to account for 30\% of the stars in NGC 2419 showing depleted Mg and enhanced K abundances.
+It would take a highly irregular IMF for SAGB-binaries to account for 30 percent of the stars in NGC 2419 showing depleted Mg and enhanced K abundances.
 Furthermore, SAGB-binaries would only irregularly produce a depletion in [Mg/Fe], unlike the consistent bi-modality seen in abundance ratios in NGC 2419 and NGC 2808.
 
-Although the metallicity spread suggests a polluter candidate that can form at all ages and metallicities, all that is absolutely required is that the stars \textit{we observe} form in different metallicity environments.
-The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in at least one region of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases.
-This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419, shown in Figure \ref{KvsFe}.
+Although the metallicity spread suggests a polluter that can form at all ages and metallicities, all that is absolutely required is that the stars \textit{we observe} form in different metallicity environments.
+The anti-correlation between [K/Fe] and [Fe/H], shown in Figure \ref{KvsFe} could be interpreted as a relatively constant level of [K/H] present in at least one region of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases.
+This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419, also shown in Figure \ref{KvsFe}.
 If this relation is real, we can perhaps -- without saying anything about the polluter star -- use it to motivate an evolutionary sequence that could account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419, and our new 112 field star sample.
@@
 When the most massive stars of Generation 1 die, they release metals into the gas cloud, including significant amounts of Mg, which is formed in copious amounts in core-collapse supernovae, but \textit{not} K, which models predict to be very difficult to form in significant quantities.
-The [Mg/Fe] depletion originally carried in the cloud is much harder to detect in the next generation of stars forming from this material, Generation 2, due to the influx of Mg-rich material released by Generation 1.
-The K enhancement, however, remains relatively easy to detect, having only been reduced relative to [Fe/H] by the total amount of iron released.
-As this cycle repeats, [K/Fe] would be reduced in each successive generation of stars, while the original [Mg/Fe] depletion would quickly become impossible to detect in all but the most metal-poor stars.
-This cycle allows for the Mg depletions to be preserved in globular clusters, where even the most massive clusters only form at most two generations of stars, while the signature would be lost within the disk of the galaxy where many generations of stars might form.
+The [Mg/Fe] depletion originally carried in the cloud is much harder to detect in the next generation (Generation 2) of stars forming from this material, owing to the influx of Mg-rich material released by Generation 1.
+However, the K enhancement remains relatively easy to detect, having only been reduced relative to [Fe/H] by the total amount of iron released.
+As this cycle repeats, [K/Fe] falls in each successive generation of stars, while the original [Mg/Fe] depletion quickly becomes impossible to detect in all but the most metal-poor stars.
+This cycle allows for the Mg depletions to be preserved in globular clusters, in which even the most massive clusters only form at most two generations of stars, while the signature would be lost in the disk of the Galaxy where many generations of stars form.
 Thus it provides a way of linking the current observations of our 112 candidate stars with the observations of NGC 2419.
@@
 This is only known to occur in inside true galaxies, which are massive enough to form multiple star forming regions.
-Allowing the candidate stars to have originated in a dwarf galaxy which later merged with the Milky Way introduces many issues.
+Allowing the candidate stars to have originated in a dwarf Galaxy which later merged with the Milky Way introduces many issues.
 The required mass to be polluted by the mystery object increases drastically, implying multiple pollution events.
-But invoking multiple pollution events means that the rarity of the signal is harder to explain: if it happened multiple times within a single dwarf galaxy, why not in other places?
+But invoking multiple pollution events means that the rarity of the signal is harder to explain: if it happened multiple times within a single dwarf Galaxy, why not in other places?
 Further, a merger should result in stars with highly elliptical orbits, while the candidates identified appear to be disk stars.}
 
-%\todo{More generally, the [K/Fe]-[Fe/H] relation we observed is supportive of the origin of the Mg-K anti-correlation being temporally confined to an early epoch in the evolution of galaxies and globular clusters.
+%\todo{More generally, the [K/Fe]-[Fe/H] relation we observed is supportive of the origin of the Mg--K anti-correlation being temporally confined to an early epoch in the evolution of galaxies and globular clusters.
 However, this is not necessarily the only interpretation.
-For example, it could be that the K forming process is happening throughout the life of the galaxy, but the amount of K produced decreases with the metallicity of the polluter star, though there is no obvious reason why this would be the case.}
+For example, it could be that the K forming process is happening throughout the life of the Galaxy, but the amount of K produced decreases with the metallicity of the polluter star, though there is no obvious reason why this would be the case.}
 
@@
 \label{sec:conclusion}
-From a sample of 454,180 giant stars in \lamost, we identify 112 candidate stars that are significantly enhanced in K and depleted Mg.
-Although stars with this chemical pattern have been observed in globular clusters NGC 2419 and NGC 2808, this represents the first observations of field stars with this peculiar abundance signature.
+From a sample of 454,180 giant stars in \lamost, we identify 112 candidate stars that are significantly enhanced in K and depleted in Mg.
+Stars with this chemical pattern have been observed in globular clusters NGC 2419 and NGC 2808; this work represents the first observations of field stars with this peculiar abundance signature.
 Our candidates are not restricted to a particular phase of stellar evolution, and their metallicity distribution is reflective of the parent \lamost\ sample.
@@
 We find extreme abundance ratios of up to [K/Fe] $\approx 1.5$ in our sample, but none that exceed the levels observed in NGC 2419 (up to [K/Fe] $\approx$ 2).
-While our analysis suggests the presence of substantial [Mg/Fe] depletion, follow-up observations are necessary to quantify the level of Mg-depletion.
-The spread in metallicities among our sample suggests that the mechanism responsible for the Mg-K abundance signature is not limited to early epochs (e.g., Population III supernova) or low-metallicity environments.
-We highlight SAGB-binaries as a plausible polluter candidate for the Mg-K abundance signature within the disk.
+While our analysis suggests the presence of substantial [Mg/Fe] depletion, follow-up observations are necessary to quantify the level of Mg depletion.
+The spread in metallicities among our sample suggests that the mechanism responsible for the Mg--K abundance signature is not limited to early epochs (e.g.
+Population III supernova) or low-metallicity environments, although such cases cannot be ruled out entirely.
+We highlight SAGB-binaries as a plausible polluter candidate for the Mg--K abundance signature within the disk, but acknowledge that such a candidate is not applicable to NGC 2419 and is therefore not only speculative, but insatisfactory as an explanation for the Mg--K anti-correlation in general.
 We encourage future high-resolution observations and modelling efforts to understand this peculiar nucleosynthetic pathway.
@@
 %An intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains uncertain without further higher resolution observations of the candidates.
-Further high resolution observations will also allow Mg and other elemental abundances to be determined.
+Further high resolution observations r
+will also allow Mg and other elemental abundances to be determined.
 
@@
 %- Magellan/MIKE and Australian government
-A.~R.~C. is supported through an Australian Research Council Discovery Project under grant DP160100637.
-A.~Y.~Q.~H. is supported by a Fulbright grant through the German-American Fulbright Commission and a National Science Foundation Graduate Research Fellowship under Grant No. DGE-1144469. 
-C.~A.~T. thanks Churchill College for his fellowship and Monash University for hosting him as a Kevin Westfold distinguished visitor.
+ARC is supported through an Australian Research Council Discovery Project under grant DP160100637.
+AYQH is supported by a Fulbright grant through the German-American Fulbright Commission and a National Science Foundation Graduate Research Fellowship under Grant No. DGE-1144469. 
+CAT thanks Churchill College for his fellowship and Monash University for hosting him as a Kevin Westfold distinguished visitor.
 This research has made use of NASA's Astrophysics Data System.

### 2018-02-14 article/ms.tex
Added Johns comments plus more issues

@@
 Furthermore, Type Ia supernova enrichment cannot account for the enhanced K abundance observed in NGC 2419.
-In fact it is hard to make K in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing reaction rates above those measured by several orders of magnitude \citep{ventura2012,iliadis2016}.
+In fact it is hard to make K in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing some reaction rates above those measured by several orders of magnitude \citep{ventura2012,iliadis2016}.
+Recent work by \cite{ritter2017} on K production in O-C shell mergers in very low-metallicity stars shows promise as an alternative source of K but this work not sufficiently quantitative yet.
 Another mechanism for reducing [Mg/Fe] is through the Mg--Al nucleosynthetic chain in high-temperature hydrogen burning.
 However, no correlation between Mg and Al is observed in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.
-Recent work by \cite{ritter2017} on K production in O-C shell mergers in very low-metallicity stars shows promise as an alternative source of K but this work not sufficiently quantitative yet.
 
@@
 We find that the frequency of Mg--K stars is consistent (within the errors) of being flat with metallicity.
-We also note that our candidate stars are distributed across the entire giant branch, implying that the abundance signature is not associated with any single particular stage in evolution and that the chemical pattern we observe is not due to a violation of the assumption of local thermodynamic equilibrium.
+We also note that our candidate stars are distributed across the entire giant branch, implying that the abundance signature is not associated with any single stage in evolution and that the chemical pattern we observe is not due to a violation of the assumption of local thermodynamic equilibrium.
 
@@
 However, the high [Na/Fe] abundance ratios we observe are very likely due to the effect of interstellar dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption.
-It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a positive correlation between Na and K.
+It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment, while observational data for NGC 2808 implies a positive correlation between Na and K.
 No relation between Na and K abundances is observed.
@@
 An early modelling attempt to replicate the anomalous Mg--K abundance ratios assumed hot-bottom burning in asymptotic giant branch (AGB) and super-AGB (SAGB) stars.
-\cite{ventura2012} succeeded in reproducing the Mg--K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected by \cite{iliadis2016}) for the production of K.
+\cite{ventura2012} succeeded in reproducing the Mg--K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (\cite{ventura2012} corrected by \cite{iliadis2016}) for the production of K.
 However, abundance patterns consistent with NGC 2419 were only possible if the Ar--K reaction cross section was increased to 100 that measured in the laboratory, or if the temperature at the base of the envelope could be made to exceed 150\,MK.
@@
 \label{sec:conclusion}
-From a sample of 454,180 giant stars in \lamost, we identify 112 candidate stars that are significantly enhanced in K and depleted in Mg.
+From a sample of 454,180 giant stars in \lamost, we identify 112 candidate stars that are significantly enhanced in K and potentially depleted in Mg.
 Stars with this chemical pattern have been observed in globular clusters NGC 2419 and NGC 2808; this work represents the first observations of field stars with this peculiar abundance signature.

### 2018-02-20 article/ms.tex
more comments, deleted kobayashi galaxy references in favour of APOGEE, changed graph

@@
 
-Beyond the intrinsic scientific value of identifying the responsible mechanism for the puzzling Mg--K anti-correlation, a satisfactory explanation for the Mg--K signature may also offer insight into the underestimation of K abundances in the Milky Way predicted by Galactic chemical evolution models \citep{kobayashi2011} or more broadly help to understand globular cluster formation and evolution.
-Here we use \lamost\ data to conduct the largest search to date for stars enhanced in potassium and depleted in magnesium.
+Beyond the intrinsic scientific value of identifying the mechanism responsible for the puzzling Mg--K anti-correlation, a satisfactory explanation for the Mg--K signature may also offer insight into the underestimation of K abundances in the Milky Way predicted by Galactic chemical evolution models \citep{kobayashi2011} or more broadly help to understand globular cluster formation and evolution.
+
+Here we use low resolution \lamost\ data to conduct the largest search to date for stars enhanced in potassium and depleted in magnesium.
 The discovery (or non-discovery) of such stars guides models that attempt to explain the Mg--K anti-correlation and related abundance phenomena.
@@
 For each star we recorded the profile amplitudes, wavelengths, widths, as well as associated measurement uncertainties of these quantities.
-We note that although telluric absorption would usually swamp the K doublet lines, the contributions of telluric features have been removed from \lamost\ spectra as part of the data reduction process conducted by \lamost \citep{luo2016vizier}.
 We identified candidates by requiring that they match at least one of the following three quality filters:
@@
 The distilled catalogue contains 112 candidate stars with spectra consistent with enhancements in K and depletions in Mg.
+
+We note that although telluric absorption would usually swamp the K doublet lines, the contributions of telluric features have been removed from \lamost\ spectra as part of the data reduction process conducted by \lamost\ \citep{luo2016vizier}.
+Subsequent examination the radial velocities for the (manually vetted) sample showed no behaviour indicating that the [K/Fe] over-abundances identified were due telluric absorption.
 
@@
 	\includegraphics[width=\columnwidth]{KvsMg.png}
-    \caption{Comparison of [K/Fe] vs [$\alpha$/Fe] for the candidate stars with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
-See text for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].}
+    \caption{[K/Fe] vs [$\alpha$/Fe] for the candidate stars, overlaid with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
+See section \ref{sec:method} for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].}
     \label{KvsMg}
@@
 The closest candidate to any star cluster is J074807.22+261514.2, which lies 2.54\degree\ from Ko~2 \citep{koposov2007}.
-The large angular separation and relatively  high metallicity of J074807.22+261514.2 ($[{\rm Fe}/{\rm H}] = -0.24$) make it highly unlikely to be associated with Ko~2.
+This separation implies a minimum 1.77\, kpc distance from Ko 2, while Ko 2 has an estimated size of around 3\, pc \citep{koposov2007}.
 
@@
 However, the \lamost\ spectral flux residuals with \tc\ model are consistent with an under-abundance of Mg.
-The small sample of stars for which we have high resolution spectra, coupled with the conflict with the \lamost\ spectra, means we are unable to confidently make a statement regarding the level of [Mg/Fe] compared to NGC 2419 or NGC 2808.
+The small sample of stars for which we have high resolution spectra, coupled with the conflict with the \lamost\ spectra, means we are unable to confidently make a statement regarding the level of [Mg/Fe] in our sample.
 
-Given that the sample is almost certainly comprised of disk stars, it is relevant to also compare with typical Galactic abundances for [K/Fe], taken from \cite{kobayashi2011}.
+Given that the sample is almost certainly comprised of disk stars, it is relevant to also compare with typical Galactic abundances for [K/Fe], taken from the APOGEE survey \citep{alam2015} and shown in Figures \ref{KvsMg} and \ref{KvsMg}.
 The sample's [K/Fe] appears definitively anomalous, with Galactic [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] of 0.8 to 1.3.
@@
 The stars that form directly from this gas display a significant reduction in Mg and enhancement in K abundances similar to NGC 2419's extreme population.
-We will refer to this generation of stars as Generation 1\footnote{Reluctantly.}.
+We will refer to this generation of stars as Generation 1.
 When the most massive stars of Generation 1 die, they release metals into the gas cloud, including significant amounts of Mg, which is formed in copious amounts in core-collapse supernovae, but \textit{not} K, which models predict to be very difficult to form in significant quantities.
@@
 %An intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains uncertain without further higher resolution observations of the candidates.
-Further high resolution observations r
-will also allow Mg and other elemental abundances to be determined.
+Further high resolution observations will also allow Mg and other elemental abundances to be determined.
 

### 2018-02-23 article/ms.tex
add text. closes #7

@@
 \subsection{Follow-up observations with Magellan/MIKE}
-High resolution spectra of three of the candidate stars selected based on observability (J075043.12+204658.0, J120032.60+024438.2 and J091825.49+172114.5) were obtained using Magellan/MIKE (Magellan Inamori Kyocera Echelle) \citep{shectman2003magellan,bernstein2003mike}
- \todo{@andy add relevant info on abundance calculations.}
+High resolution spectra of three of the candidate stars selected based on observability (J075043.12+204658.0, J120032.60+024438.2 and J091825.49+172114.5) were obtained using Magellan/MIKE (Magellan Inamori Kyocera Echelle) \citep{shectman2003magellan,bernstein2003mike}.
+Exposure times were calculated to achieve S/N per pixel of 30 per pixel at 450\,nm, sufficient to confirm the K-enriched and Mg-poor nature.
+We reduced the data using the \texttt{CarPy} package \citep{kelson2003}.
+We used spline functions to continuum-normalize individual echelle orders, before combining them to produce a continuum-normalized spectrum that is contiguous from 350\,nm to 950\,nm.
+With the stellar parameters from \lamost, we calculated [K/Fe] and [Mg/Fe] abundances from individual atomic lines by measuring Gaussian profiles \citep{castelli2004,sneden,casey2014}.
+K lines were unaffected by telluric contamination in these candidates.
+The estimated abundances from Magellan/MIKE spectra are consistent (within the uncertainties) of our initial abundance determinations from \lamost\ (Figure \ref{KvsMg}), confirming that all three are K-enriched and Mg-poor.
 

### 2018-02-26 article/msculled.tex
Commited major crimes

--- 2018-02-23 article/ms.tex
@@
 Anna Y.~Q. Ho,$^{4}$\newauthor
-Christopher A. Tout$^{1,5}$
-%Melissa K. Ness,$^{6}$
+Christopher A. Tout,$^{1,5}$
+Melissa K. Ness$^{6}$
 %David W. Hogg,$^{7}$
@@
 $^{5}$Institute of Astronomy, Madingley Road, Cambridge, CB3 0HA, United Kingdom\\
-%$^{6}$ Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
+$^{6}$Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
 %$^{7}$ Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA\\
@@
 Our sample spans a range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$) yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 
-We conclude that the nucleosynthetic process producing the anomalous abundances in [K/Fe] and [Mg/Fe] probably (but not necessarily) occurs at a wide range of metallicities.
-This would suggest that pollution scenarios that are limited to early epochs (such as Population III supernovae) are an unlikely explanation.
+We conclude that the nucleosynthetic process producing the anomalous abundances in [K/Fe] and [Mg/Fe] probably occurs at a wide range of metallicities.
+This would suggest that pollution scenarios that are limited to early epochs (such as Population III supernovae) are an unlikely explanation, although they cannot be ruled out entirely.
 This sample is expected to help guide modelling  attempts to explain the origin of the Mg--K abundance signature, which we show exists throughout the Milky Way.
@@
 The fact that the Mg-K anti-correlation is apparently confined to these two globular clusters implies either a small population of unusual polluter stars, or a single extremely massive polluter star.
-If it were the cumulative effect of many pollution events that was responsible for the signal, it would be expected that the anomalous abundances would be common among globular clusters, notwithstanding a reason why the stars could not form outside NGC 2419 and NGC 2808.
+If it were the cumulative effect of many pollution events that was responsible for the signal, it would be expected that the anomalous abundances would be common among globular clusters.
 
@@
 In the opinion of the author, it is the identity and physical characterisation of this unknown polluter that is of the greatest scientific interest, with such a result also hopefully answering the question of the signatures uniqueness.
-
-One  mechanism for [Mg/Fe] depletion is the introduction of $\alpha$-poor and Fe-rich material released by Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the normal [Mg/Fe] ratios that arise from Type II supernovae.
-However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}.
-Furthermore, Type Ia supernova enrichment cannot account for the enhanced K abundance observed in NGC 2419.
-In fact it is hard to make K in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing some reaction rates above those measured by several orders of magnitude \citep{ventura2012,iliadis2016}.
-Recent work by \cite{ritter2017} on K production in O-C shell mergers in very low-metallicity stars shows promise as an alternative source of K but this work not sufficiently quantitative yet.
-Another mechanism for reducing [Mg/Fe] is through the Mg--Al nucleosynthetic chain in high-temperature hydrogen burning.
-However, no correlation between Mg and Al is observed in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.
 
@@
 We identified potential Mg-depleted and K-enhanced stars by searching for significant deviations in flux residuals.
-The flux residuals were taken as the normalised \lamost\ flux and the best-fitting data-driven model from \tc\ (where $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$).
+The flux residuals were calculated as the diference between the normalised \lamost\ flux and the best-fitting data-driven model flux from \tc\ ( $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$).
 A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model).
-Figure \ref{posterchild} shows the \lamost\ spectrum and best-fitting model from \tc for candidate J034458.82+592955.1.
+Figure \ref{posterchild} shows the \lamost\ spectrum and best-fitting model from \tc\ for candidate J034458.82+592955.1.
 
@@
 \item We required any two of the three Mg triplet lines to satisfy $A > 0.05$ and at least one K line to have $A < -0.05$, and for those amplitudes to have $|A|/\sigma_{A} \geq 3$.
-\item We required any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost and a reported $\chi_{r}^2 < 3$ from \tc.
+\item We required any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost\ and a reported $\chi_{r}^2 < 3$ from \tc.
 \end{enumerate}
@@
 We note that although telluric absorption would usually swamp the K doublet lines, the contributions of telluric features have been removed from \lamost\ spectra as part of the data reduction process conducted by \lamost\ \citep{luo2016vizier}.
-Subsequent examination the radial velocities for the (manually vetted) sample showed no behaviour indicating that the [K/Fe] over-abundances identified were due telluric absorption.
+Subsequent examination of the radial velocities for the (manually vetted) sample showed no behaviour indicating that the [K/Fe] over-abundances identified were due telluric absorption.
 
@@
 We assume that absorption due to metals is accounted for by \tc, and deviations in flux around the potassium doublet are due to an increased [K/Fe] with respect to the model.
-We list estimated [K/Fe] abundance ratios in Table \ref{data}, where the error includes a 0.2\,dex systematic error floor that we have applied in quadrature with the fitting errors.
+We include a conservative 0.2\,dex systematic error floor  applied in quadrature with the fitting errors to account for some component of the flux differences not being from the abundance of K, but instead due to noise in the \lamost\ spectra.
 We applied the same method to estimate [Na/Fe] from \lamost\ spectra.
@@
 High resolution spectra of three of the candidate stars selected based on observability (J075043.12+204658.0, J120032.60+024438.2 and J091825.49+172114.5) were obtained using Magellan/MIKE (Magellan Inamori Kyocera Echelle) \citep{shectman2003magellan,bernstein2003mike}.
-Exposure times were calculated to achieve S/N per pixel of 30 per pixel at 450\,nm, sufficient to confirm the K-enriched and Mg-poor nature.
+Exposure times were calculated to achieve S/N per pixel of 30 per pixel at 450\,nm, sufficient to verify the K-enriched and Mg-poor nature of these stars.
 We reduced the data using the \texttt{CarPy} package \citep{kelson2003}.
-We used spline functions to continuum-normalize individual echelle orders, before combining them to produce a continuum-normalized spectrum that is contiguous from 350\,nm to 950\,nm.
+Spline functions were used to continuum-normalize individual echelle orders, before combining them to produce a continuum-normalized spectrum that is contiguous from 350\,nm to 950\,nm.
 With the stellar parameters from \lamost, we calculated [K/Fe] and [Mg/Fe] abundances from individual atomic lines by measuring Gaussian profiles \citep{castelli2004,sneden,casey2014}.
 K lines were unaffected by telluric contamination in these candidates.
-The estimated abundances from Magellan/MIKE spectra are consistent (within the uncertainties) of our initial abundance determinations from \lamost\ (Figure \ref{KvsMg}), confirming that all three are K-enriched and Mg-poor.
+The estimated abundances from Magellan/MIKE spectra are consistent (within the uncertainties) of our initial abundance determinations from \lamost\ (Figure \ref{KvsMg}).
 
@@
 	\includegraphics[width=\textwidth]{posterchild.png}
-    \caption{Pseudo-continuum-normalised \lamost\ spectrum for the Mg-depleted and K-enhanced candidate J034458.82+592955.1.
+    \caption{Normalised \lamost\ spectrum for the Mg-depleted and K-enhanced candidate J034458.82+592955.1.
 The data are shown in black and the best-fitting data-driven model from \tc\ is in red.
@@
     \caption{[K/Fe] vs [$\alpha$/Fe] for the candidate stars, overlaid with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
-See section \ref{sec:method} for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].}
+See Section \ref{sec:method} for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].}
     \label{KvsMg}
@@
 We cross-matched our candidates with the positions of all known globular clusters \citep{harris1996}.
-No candidates can be associated with NGC~2419 or NGC~2808.
-The closest candidate to any star cluster is J074807.22+261514.2, which lies 2.54\degree\ from Ko~2 \citep{koposov2007}.
-This separation implies a minimum 1.77\, kpc distance from Ko 2, while Ko 2 has an estimated size of around 3\, pc \citep{koposov2007}.
 
@@
 
-Upon examining [Na/Fe] as estimated from the \lamost\ spectra, two distinct populations were observed: one population making up approximately 30 percent of the sample with [Na/Fe] > 0.5, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second with [Na/Fe] consistent with typical Galactic abundances.
-However, the high [Na/Fe] abundance ratios we observe are very likely due to the effect of interstellar dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption.
+Upon examining [Na/Fe] as estimated from the \lamost\ spectra, using the doublet around 5850 \AA, two distinct populations were observed: one population making up approximately 30 percent of the sample with [Na/Fe] > 0.5, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second with [Na/Fe] consistent with typical Galactic abundances.
+However, the high [Na/Fe] abundance ratios we observe are possibly due to the effect of interstellar dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption.
+However, further investigation revealed no evidence of a difuse interstellar band (DIB) impacting spectra around the Na doublet, nor Mg or K.
 It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment, while observational data for NGC 2808 implies a positive correlation between Na and K.
-No relation between Na and K abundances is observed.
 
@@
 As described in Section \ref{sec:method}, we adopt [$\alpha$/Fe] as an upper limit for [Mg/Fe].
-[K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE is also shown.
+[K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE and for over 60000 stars from APOGEE \citep{alam2015} is also shown.
 %The use of $[\alpha$/Fe] to position the sample in \ref{KvsMg} is supported by the [Mg/Fe] measurements from the high-resolution spectra, which vary less than 0.1\,dex from the level of $[\alpha$/Fe] for each of the relevant stars in the \lamost\ data.
@@
 
-Given that the sample is almost certainly comprised of disk stars, it is relevant to also compare with typical Galactic abundances for [K/Fe], taken from the APOGEE survey \citep{alam2015} and shown in Figures \ref{KvsMg} and \ref{KvsMg}.
+Given that the sample is almost certainly comprised of disk stars, it is relevant to also compare with typical Galactic abundances for [K/Fe], taken from the APOGEE survey \citep{alam2015} and shown in Figures \ref{KvsMg} and \ref{KvsFe}.
 The sample's [K/Fe] appears definitively anomalous, with Galactic [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] of 0.8 to 1.3.
@@
 Although a unifying explanation remains elusive, it is improbable that a processes acting to produce such high levels of [K/Fe] in the Milky Way is unrelated to whatever process is responsible for the extreme abundance ratios in NGC 2419.
-The apparent consistency of NGC 2419's extreme population with the relation between [K/Fe] and [Fe/H] in Figure \ref{KvsFe} further supports the idea that the process responsible for the stars in this study and the previously known anomalous stars in NGC 2319 are related.
+The apparent consistency of NGC 2419's extreme population with the anti-correlation between [K/Fe] and [Fe/H] observed in Figure \ref{KvsFe} further supports the idea that the process responsible for the stars in this study and the previously known anomalous stars in NGC 2419 are related.
 
@@
 
-\label{sec:scenarios}
-\begin{table*}
-\centering
-\caption{Tabulated data for 10 of the 112 candidate stars. Data for the full sample is available online.}
-\label{data}
-\begin{tabular}{cccccccccccccc}
-\hline
-\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{V$_\textrm{r}$} & \textbf{T$_\textrm{eff}$} & $\boldsymbol \log{ \, \textbf{g}}$ & \textbf{{[}Fe/H{]}} & \textbf{{[}$\alpha$/Fe{]}} & \textbf{$\boldsymbol \chi_r ^\textbf{2}$} & \textbf{{[}K/Fe{]}} & \textbf{Error} & \textbf{{[}Na/Fe{]}} & \textbf{Error} \\
-- & {[}deg{]} & {[}deg{]} & [pixel$^{-1}]$ & {[${\rm km\,s}^{-1}$]} & {[}K{]} & $[{\rm cm\,s}^{-2}]$ & {[}dex{]} & {[}dex{]} & - & {[}dex{]} & {[}dex{]} & {[}dex{]} & {[}dex{]} \\ \hline
-J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.26 & 0.86 & 0.23 \\
-J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.22 & 0.39 & 0.22 \\
-J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.21 & -0.20 & 0.20 \\
-J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.1 & -0.56 & 0.24 & 0.31 & 0.96 & 0.33 & -0.16 & 0.20 \\
-J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.1 & 0.44 & 0.76 & 0.23 & -0.02 & 0.20 \\
-J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.1 & 0.05 & 1.17 & 0.95 & 0.21 & -0.07 & 0.20 \\
-J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.20 & -0.04 & 0.20 \\
-J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.21 & 0.46 & 0.21 \\
-J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1 & 8.70 & -0.02 & 0.20 \\
-J032423.46+425429.6 & 51.1 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.22 & 0.80 & 0.20 \\ \hline
-\end{tabular}
-\end{table*}
-
 %Significantly enhanced [K/Fe] is rare; significantly enhanced [K/Fe] without an accompanying depletion of [Mg/Fe] is unknown. The candidate stars are also spread across a wide range of metallicities.
 
-An early modelling attempt to replicate the anomalous Mg--K abundance ratios assumed hot-bottom burning in asymptotic giant branch (AGB) and super-AGB (SAGB) stars.
-\cite{ventura2012} succeeded in reproducing the Mg--K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (\cite{ventura2012} corrected by \cite{iliadis2016}) for the production of K.
-However, abundance patterns consistent with NGC 2419 were only possible if the Ar--K reaction cross section was increased to 100 that measured in the laboratory, or if the temperature at the base of the envelope could be made to exceed 150\,MK.
-
-A more recent attempt to replicate the Mg--K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}.
+A recent attempt to replicate the Mg--K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}.
 The study aimed to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.
-\footnote{Note that \cite{iliadis2016} identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway.
-The main pathway used by \cite{iliadis2016} is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.}
 Unless extremely high densities were invoked ($>10^8\,{\rm g\,cm}^{-3}$), it was found that temperatures between 100 and 200\,MK were necessary depending on the density.
@@
 These stars with enhanced potassium apparently tend to form at all ages, across all metallicities, so it is probable that the polluting source is also independent of metallicity.
-If we assume that the polluter star forms at a range of metallicities, then we can make qualitative constraints on scenarios that may be responsible for the Mg--K anti-correlation by disregarding polluters that are reliant on specific metallicity environments to form.
+If we assume that the polluter star forms at a range of metallicities, then we can attempt to constrain scenarios that may be responsible for the Mg--K anti-correlation by disregarding polluters that are reliant on specific metallicity environments to form.
 
@@
 As emphasized by \cite{prantzos2017}, a significant challenge presented by the signatures of NGC 2419 and NGC 2808 is obtaining both a depletion in Mg and an enhancement in K.
-Reducing Mg is possible by converting \ce{^{24}Mg} to \ce{^{27}Al} through Mg--Al chains at temperatures around $75\,$ MK, which is attainable in hot-bottom burning (HBB) environments in AGB stars.
+Reducing Mg is possible by converting \ce{^{24}Mg} to \ce{^{27}Al} through Mg--Al chains at temperatures around $75\,$MK, which is attainable in hot-bottom burning (HBB) environments in AGB stars.
 However, temperatures upwards of 150 MK are required to produce K, and these temperatures can only potentially be reached at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
@@
 
-While this scenario is consistent with the total spread in metallicity, it is not applicable to NGC 2419 or NGC2808.
-It would take a highly irregular IMF for SAGB-binaries to account for 30 percent of the stars in NGC 2419 showing depleted Mg and enhanced K abundances.
-Furthermore, SAGB-binaries would only irregularly produce a depletion in [Mg/Fe], unlike the consistent bi-modality seen in abundance ratios in NGC 2419 and NGC 2808.
-
-Although the metallicity spread suggests a polluter that can form at all ages and metallicities, all that is absolutely required is that the stars \textit{we observe} form in different metallicity environments.
-The anti-correlation between [K/Fe] and [Fe/H], shown in Figure \ref{KvsFe} could be interpreted as a relatively constant level of [K/H] present in at least one region of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases.
-This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419, also shown in Figure \ref{KvsFe}.
-If this relation is real, we can perhaps -- without saying anything about the polluter star -- use it to motivate an evolutionary sequence that could account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419, and our new 112 field star sample.
-
-Suppose some unknown event unique to very metal-poor (possibly zero-metallicity) environments occurs that results in a gas cloud depleted in Mg and enhanced in K.
-The stars that form directly from this gas display a significant reduction in Mg and enhancement in K abundances similar to NGC 2419's extreme population.
-We will refer to this generation of stars as Generation 1.
-When the most massive stars of Generation 1 die, they release metals into the gas cloud, including significant amounts of Mg, which is formed in copious amounts in core-collapse supernovae, but \textit{not} K, which models predict to be very difficult to form in significant quantities.
-The [Mg/Fe] depletion originally carried in the cloud is much harder to detect in the next generation (Generation 2) of stars forming from this material, owing to the influx of Mg-rich material released by Generation 1.
-However, the K enhancement remains relatively easy to detect, having only been reduced relative to [Fe/H] by the total amount of iron released.
-As this cycle repeats, [K/Fe] falls in each successive generation of stars, while the original [Mg/Fe] depletion quickly becomes impossible to detect in all but the most metal-poor stars.
-This cycle allows for the Mg depletions to be preserved in globular clusters, in which even the most massive clusters only form at most two generations of stars, while the signature would be lost in the disk of the Galaxy where many generations of stars form.
-Thus it provides a way of linking the current observations of our 112 candidate stars with the observations of NGC 2419.
 %Certainly the idea that both groups of anomalous stars arise from the same polluter source ought to be entertained.
@@
 
-\section{Conclusions}
-\label{sec:conclusion}
-From a sample of 454,180 giant stars in \lamost, we identify 112 candidate stars that are significantly enhanced in K and potentially depleted in Mg.
-Stars with this chemical pattern have been observed in globular clusters NGC 2419 and NGC 2808; this work represents the first observations of field stars with this peculiar abundance signature.
-Our candidates are not restricted to a particular phase of stellar evolution, and their metallicity distribution is reflective of the parent \lamost\ sample.
-
-We find extreme abundance ratios of up to [K/Fe] $\approx 1.5$ in our sample, but none that exceed the levels observed in NGC 2419 (up to [K/Fe] $\approx$ 2).
-While our analysis suggests the presence of substantial [Mg/Fe] depletion, follow-up observations are necessary to quantify the level of Mg depletion.
-The spread in metallicities among our sample suggests that the mechanism responsible for the Mg--K abundance signature is not limited to early epochs (e.g.
-Population III supernova) or low-metallicity environments, although such cases cannot be ruled out entirely.
-We highlight SAGB-binaries as a plausible polluter candidate for the Mg--K abundance signature within the disk, but acknowledge that such a candidate is not applicable to NGC 2419 and is therefore not only speculative, but insatisfactory as an explanation for the Mg--K anti-correlation in general.
-We encourage future high-resolution observations and modelling efforts to understand this peculiar nucleosynthetic pathway.
-
 %An intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains uncertain without further higher resolution observations of the candidates.
@@
 \section*{Acknowledgements}
-We thank Alex P. Ji (Carnegie Observatories), Melissa Ness (Columbia), David W. Hogg (NYU), and Hans-Walter Rix (MPIA).
+We thank Alex P. Ji (Carnegie Observatories), David W. Hogg (NYU), and Hans-Walter Rix (MPIA).
 %- Magellan/MIKE and Australian government

### 2018-03-02 article/msculled.tex
omg is this my last chance to fire Kemp on this project??
spacing
diffuse not difuse

@@
 In Section \ref{sec:discussion} we discuss our results and their implications for possible pollution mechanisms.
-Section \ref{sec:conclusion} summarises those results.
 
@@
 We cross-matched our candidates with the positions of all known globular clusters \citep{harris1996}.
-
 The spread in metallicity (Figure \ref{mhist}) is consistent with all candidates being field stars.
@@
 Upon examining [Na/Fe] as estimated from the \lamost\ spectra, using the doublet around 5850 \AA, two distinct populations were observed: one population making up approximately 30 percent of the sample with [Na/Fe] > 0.5, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second with [Na/Fe] consistent with typical Galactic abundances.
-However, the high [Na/Fe] abundance ratios we observe are possibly due to the effect of interstellar dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption.
-However, further investigation revealed no evidence of a difuse interstellar band (DIB) impacting spectra around the Na doublet, nor Mg or K.
+However, the high [Na/Fe] abundance ratios we observe are possibly due to the effect of interstellar
+dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption.
+However, further investigation revealed no evidence of a diffuse interstellar band (DIB) impacting spectra around the Na doublet, nor Mg or K.
 It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment, while observational data for NGC 2808 implies a positive correlation between Na and K.

### 2018-03-02 article/msculled.tex
authsp

@@
 Christopher A. Tout,$^{1,5}$
-Melissa K. Ness$^{6}$
-%David W. Hogg,$^{7}$
+Melissa Ness,$^{6}$
+Alexander P. Ji$^{7}$
 \\
@@
 $^{5}$Institute of Astronomy, Madingley Road, Cambridge, CB3 0HA, United Kingdom\\
-$^{6}$Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
-%$^{7}$ Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA\\
+$^{6}$Columbia University\\
+$^{7}$Carnegie Observatories
 }
@@
 \section*{Acknowledgements}
-We thank Alex P. Ji (Carnegie Observatories), David W. Hogg (NYU), and Hans-Walter Rix (MPIA).
+We thank David W. Hogg (NYU), and Hans-Walter Rix (MPIA).
 %- Magellan/MIKE and Australian government

### 2018-05-06 article/msculled.tex
pre-change push

@@
 
-A targeted search looking for [K/Fe] in RGB and main sequence turn-off stars in other clusters (NGC 6752, NGC 6121, NGC 1904, 47 Tuc, NGC 6397, NGC 7099, and $\omega$ Centauri) and field stars concluded that all K abundance ratios fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}.
+A targeted search looking for [K/Fe] in RGB and main sequence turn-off stars in other clusters (NGC 6752, NGC 6121, NGC 1904, NGC 104, NGC 6397, NGC 7099, and $\omega$ Centauri) and field stars concluded that all K abundance ratios fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}, and no correlations between Mg and K were observed.
+Recent work by \cite{cerniauskas201747tuc} searched for unusual abundance patterns in Mg and K in NGC 104 through deriving abundances using 2df/HERMES spectra, and a more comprehensive study involving over 400 stars in NGC 104, NGC 6752, and NGC 6809 by \cite{mucciarelli2017K} using FLAMES spectra \citep{cerniauskas201747tuc} both found no correlations between Mg and K, and no significant intrinsic spreads in either Mg or K.
+
 NGC 2808 is the only cluster, other than NGC 2419, where an anticorrelation between Mg and K has been observed.
@@
 \begin{figure*}
-	\includegraphics[width=\textwidth]{posterchild.png}
-    \caption{Normalised \lamost\ spectrum for the Mg-depleted and K-enhanced candidate J034458.82+592955.1.
+\centering
+\begin{subfigure}{1\textwidth}
+\centering
+\includegraphics[width=\textwidth=1]{posterchild.png}
+\caption{Mg-depleted, K-enhanced candidate J034458.82+592955.1.}
+\end{subfigure}
+
+\begin{subfigure}{1\textwidth}
+\centering
+\includegraphics[width=\textwidth=1]{postermimic.png}
+\caption{Mg-normal, K-normal star J163532.2+238131.54. }
+\end{subfigure}
+
+\caption{Normalised \lamost\ spectrum for the Mg-depleted and K-enhanced candidate J034458.82+592955.1 and for the comparable star J163532.2+238131.54.
+J163532.2+238131.54 was selected by minimising the similarity norm defined as $n=(\frac{\Delta \text{T}_{\text{eff}}}{1000})^2 +\Delta \text{logg} ^2 + \Delta \text{[Fe/H]}^2$.
 The data are shown in black and the best-fitting data-driven model from \tc\ is in red.
@@
 Note that $[\alpha/{\rm Fe}]$ is a label in \tc\ model used and J034458.82+592955.1 shows Mg depletions relative to the estimated [$\alpha$/Fe] value.}
-    \label{posterchild}
+\label{meshindepvisc}
 \end{figure*}

### 2018-05-06 article/msculled.tex
Integration of many of the figures. Na section expanded to discuss the associated figures. likewise with selection effects. [K/Fe] stuff remains to be integrated properly.

@@
 We include a conservative 0.2\,dex systematic error floor applied in quadrature with the fitting errors to account for some component of the flux differences not being from the abundance of K, but instead due to noise in the \lamost\ spectra.
-We applied the same method to estimate [Na/Fe] from \lamost\ spectra.
+We applied the same method (and error floor) to estimate [Na/Fe] from \lamost\ spectra.
 We note that while enhancements in [K/Fe] or [Na/Fe] can be estimated by synthesising the flux residuals, we cannot easily estimate [Mg/Fe] depletions in the same manner because it is difficult to separate the flux contribution of [Mg/Fe] from [$\alpha$/Fe] in the data-driven model.
@@
 
+\section{Discussion}
+\label{sec:discussion}
+
+\subsection{Selection effects}
+\label{sec:selectioneffects}
+
+Our sample of \lamost\ giants carries with it certain selection effects from both the \apogee\ DR12 and \lamost\ samples.
+For example, metal-poor stars with [Fe/H] $\lesssim-2$ are mostly absent from our sample because they were too dissimilar from the training stars for label transfer from \apogee.
+Similarly, the target selection process for \lamost\ is not easily invertible so we do not consider selection effects present in \lamost\ beyond comparing the candidate stars' metallicity distribution with that of \cite{ho2017}.
+We find that the frequency of Mg--K stars is consistent (within the errors) of being flat with metallicity.
+
+Figure \ref{loggTeffFeh} shows that the candidate stars are distributed across the entire giant branch, implying that the abundance signature is not associated with any single stage in evolution and that \todo{the chemical pattern we observe is not due to a violation of the assumption of local thermodynamic equilibrium}.
+%@ANDY is this a comment we want to make?
+If we make no assumptions about LTE...
+then I feel like we shouldn't be saying this last part, as it reads like: We made an assumption, and hey look its not violated.
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{loggTeffFeH.png}
+    \caption{Effective temperature, surface gravity and [Fe/H] as per label transfer by the \tc for LAMOST, overlaid with the 112 candidates.}
+    \label{loggTeffFeh}
+\end{figure}
+
+\subsection{Association with known globular clusters}
+\label{sec:globclustasoc}
+We cross-matched our candidates with the positions of all known globular clusters \citep{harris1996}.
+The spread in metallicity (Figure \ref{mhist}) is consistent with all candidates being field stars.
+The distribution reflects the original \LamostGiants\ sample of giants from which the candidates were selected.
+No candidates have [Fe/H] $\approx -2$, the approximate metallicity of NGC 2419, nor are there many stars with [Fe/H] $\approx -1$, the metallicity of NGC 2808.
+Thus, we conclude that the candidates are not restricted to any specific metallicity, particularly not just to the metallicities of NGC 2419 and NGC 2808.
+
+\subsection{Detailed chemical abundances}
+\label{sec:abundances}
+
+\subsubsection{[Na/Fe]}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{NavsFeh.png}
+    \caption{[Na/Fe] vs [Fe/H] for the candidate stars.}
+    \label{NavsFeh}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{Navsb.png}
+    \caption{[Na/Fe] vs galactic latitude for the candidate stars.}
+    \label{Navsb}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{Navsradvel.png}
+    \caption{[Na/Fe] vs radial velocity for the candidate stars.}
+    \label{Navsradvel}
+\end{figure}
+Upon examining [Na/Fe] as estimated from the \lamost\ spectra, using the doublet around 5850 \AA, two distinct populations were observed: one population making up approximately 30 percent of the sample with [Na/Fe] > 0.5, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second with [Na/Fe] consistent with typical Galactic abundances.
+The two groups can be clearly distinguished in Figure \ref{NavsFeh}, which also shows abundances of [Na/Fe] versus [Fe/H] from the APOGEE survey for comparison.
+
+The high [Na/Fe] abundance ratios we observe are possibly due to the effect of interstellar dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption.
+This is supported by Figures \ref{Navsb} and \ref{Navsradvel}, which show the [Na/Fe] distribution with respect to galactic latitude and the radial velocity.
+It is apparent that almost all of the stars in the anomalous group lie close to the disk of the galaxy, with radial velocities at least somewhat close to zero.
+However, further investigation revealed no evidence of a diffuse interstellar band (DIB) impacting LAMOST spectra around the Na doublet (nor around the Mg or K lines).
+It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment, while observational data for NGC 2808 implies a positive correlation between Na and K.
+
+\subsubsection{[Mg/Fe] and [K/Fe]}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{Kvslogg.png}
+    \caption{[K/Fe] versus $\logg$} 
+    \label{KvsMg}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{KvsTeff.png}
+    \caption{[K/Fe] versus $\teff$} 
+    \label{KvsMg}
+\end{figure}
+
 \begin{figure}
@@
 \end{figure}
-
-\section{Discussion}
-\label{sec:discussion}
-
-\subsection{Selection effects}
-\label{sec:selectioneffects}
-
-Our sample of \lamost\ giants carries with it certain selection effects from both the \apogee\ DR12 and \lamost\ samples.
-For example, metal-poor stars with [Fe/H] $\lesssim-2$ are mostly absent from our sample because they were too dissimilar from the training stars for label transfer from \apogee.
-Similarly, the target selection process for \lamost\ is not easily invertible so we do not consider selection effects present in \lamost\ beyond comparing the candidate stars' metallicity distribution with that of \cite{ho2017}.
-We find that the frequency of Mg--K stars is consistent (within the errors) of being flat with metallicity.
-We also note that our candidate stars are distributed across the entire giant branch, implying that the abundance signature is not associated with any single stage in evolution and that the chemical pattern we observe is not due to a violation of the assumption of local thermodynamic equilibrium.
-
-\subsection{Association with known globular clusters}
-\label{sec:globclustasoc}
-We cross-matched our candidates with the positions of all known globular clusters \citep{harris1996}.
-The spread in metallicity (Figure \ref{mhist}) is consistent with all candidates being field stars.
-The distribution reflects the original \LamostGiants\ sample of giants from which the candidates were selected.
-No candidates have [Fe/H] $\approx -2$, the approximate metallicity of NGC 2419, nor are there many stars with [Fe/H] $\approx -1$, the metallicity of NGC 2808.
-Thus, we conclude that the candidates are not restricted to any specific metallicity, particularly not just to the metallicities of NGC 2419 and NGC 2808.
-
-\subsection{Detailed chemical abundances}
-\label{sec:abundances}
-
-Upon examining [Na/Fe] as estimated from the \lamost\ spectra, using the doublet around 5850 \AA, two distinct populations were observed: one population making up approximately 30 percent of the sample with [Na/Fe] > 0.5, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second with [Na/Fe] consistent with typical Galactic abundances.
-However, the high [Na/Fe] abundance ratios we observe are possibly due to the effect of interstellar
-dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption.
-However, further investigation revealed no evidence of a diffuse interstellar band (DIB) impacting spectra around the Na doublet, nor Mg or K.
-It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment, while observational data for NGC 2808 implies a positive correlation between Na and K.
 

### 2018-05-07 article/msculled.tex
further integrations

@@
 We identified potential Mg-depleted and K-enhanced stars by searching for significant deviations in flux residuals.
-The flux residuals were calculated as the diference between the normalised \lamost\ flux and the best-fitting data-driven model flux from \tc\ ( $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$).
+The flux residuals were calculated as the difference between the normalised \lamost\ flux and the best-fitting data-driven model flux from \tc\ ( $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$).
 A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model).
-Figure \ref{posterchild} shows the \lamost\ spectrum and best-fitting model from \tc\ for candidate J034458.82+592955.1.
+Figure \ref{posterchild} shows the \lamost\ spectrum and best-fitting model from \tc\ for candidate J034458.82+592955.1, as well as the spectra for J163532.2+234847.3, the star with closest stellar parameters to J034458.82+592955.1.
 
 We fit a Gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167\,\AA, 5172\,\AA, 5184\,\AA) as well as the K doublet (7665\,\AA, 7699\,\AA) for all \LamostGiants\ giants.
-For each star we recorded the profile amplitudes, wavelengths, widths, as well as associated measurement uncertainties of these quantities.
+For each star we recorded the amplitudes, approximate widths and wavelength about which the Gaussian profiles were fit.
+The amplitude was used as the measure of the discrepancy from the model spectra, and is analogous to the depth of the absorption line.
+The relationship between equivalent width ($EW$), the amplitude ($A$) and the Gaussian width ($\sigma$) is given by $EW=\frac{2\pi A}{\sigma}$.
+
 We identified candidates by requiring that they match at least one of the following three quality filters:
@@
 \includegraphics[width=\textwidth=1]{posterchild.png}
-\caption{Mg-depleted, K-enhanced candidate J034458.82+592955.1.}
+\caption{Mg-depleted, K-enhanced candidate J034458.82+592955.1. $\teff$=4812, $\logg$=2.66, [Fe/H]=0.058}
 \end{subfigure}
@@
 \includegraphics[width=\textwidth=1]{postermimic.png}
-\caption{Mg-normal, K-normal star J163532.2+238131.54. }
+\caption{Mg-normal, K-normal star J163532.2+234847.3. $\teff$=4809, $\logg$=2.66, [Fe/H]=0.062}
 \end{subfigure}
 
-\caption{Normalised \lamost\ spectrum for the Mg-depleted and K-enhanced candidate J034458.82+592955.1 and for the comparable star J163532.2+238131.54.
-J163532.2+238131.54 was selected by minimising the similarity norm defined as $n=(\frac{\Delta \text{T}_{\text{eff}}}{1000})^2 +\Delta \text{logg} ^2 + \Delta \text{[Fe/H]}^2$.
+\caption{Normalised \lamost\ spectrum for the Mg-depleted and K-enhanced candidate J034458.82+592955.1 and for the comparable star J163532.2+234847.35.
+J163532.2+234847.35 was selected by minimising the similarity norm defined as $n=(\frac{\Delta \text{T}_{\text{eff}}}{1000})^2 +\Delta \text{logg} ^2 + \Delta \text{[Fe/H]}^2$.
 The data are shown in black and the best-fitting data-driven model from \tc\ is in red.
@@
 Note that $[\alpha/{\rm Fe}]$ is a label in \tc\ model used and J034458.82+592955.1 shows Mg depletions relative to the estimated [$\alpha$/Fe] value.}
-\label{meshindepvisc}
+\label{posterchild}
 \end{figure*}
@@
 
-Figure \ref{loggTeffFeh} shows that the candidate stars are distributed across the entire giant branch, implying that the abundance signature is not associated with any single stage in evolution and that \todo{the chemical pattern we observe is not due to a violation of the assumption of local thermodynamic equilibrium}.
+Figure \ref{loggTeffFeh} shows that the candidate stars are distributed across the entire giant branch, implying that the abundance signature is not associated with any single stage in evolution or any NLTE effects.
+One benefit of the data-driven approach is that NLTE effects need not be explicitly corrected for, as in a physically driven model.
+\tc\ predicts the flux of each star based its $\teff$, $\logg$, metalicity, and [$\alpha$/Fe] and then anomalously abundant stars are identified as those with flux significantly different from this prediction.
+Thus although it is possible the numeric value of the [K/Fe] abundances may be overpredicted due to NLTE effects, NLTE effects will not produce false positives.
+The independence of the calculated [K/Fe] abundances from these effects is demonstrated in Figures \ref{Kvslogg} and \ref{KvsTeff}, which show that no relationship exists between [K/Fe] for the identified candidate stars and $\logg$ or $\teff$.
 %@ANDY is this a comment we want to make?
@@
     \label{loggTeffFeh}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{Kvslogg.png}
+    \caption{[K/Fe] versus $\logg$} 
+    \label{Kvslogg}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\columnwidth]{KvsTeff.png}
+    \caption{[K/Fe] versus $\teff$} 
+    \label{KvsTeff}
 \end{figure}
@@
 \subsubsection{[Mg/Fe] and [K/Fe]}
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{Kvslogg.png}
-    \caption{[K/Fe] versus $\logg$} 
-    \label{KvsMg}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{KvsTeff.png}
-    \caption{[K/Fe] versus $\teff$} 
-    \label{KvsMg}
-\end{figure}
 
@@
 A direct test would be to determine whether the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they formed from SAGB stars.
+\newpage
+\begin{table*}
+\centering
+\caption{Tabulated data for 10 of the 112 candidate stars. Data for the full sample is available online.}
+\label{data}
+\begin{tabular}{cccccccccccccc}
+\hline
+\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{V$_\textrm{r}$} & \textbf{T$_\textrm{eff}$} & $\boldsymbol \log{ \, \textbf{g}}$ & \textbf{{[}Fe/H{]}} & \textbf{{[}$\alpha$/Fe{]}} & \textbf{$\boldsymbol \chi_r ^\textbf{2}$} & \textbf{{[}K/Fe{]}} & \textbf{Error} & \textbf{{[}Na/Fe{]}} & \textbf{Error} \\
+- & {[}deg{]} & {[}deg{]} & [pixel$^{-1}]$ & {[${\rm km\,s}^{-1}$]} & {[}K{]} & $[{\rm cm\,s}^{-2}]$ & {[}dex{]} & {[}dex{]} & - & {[}dex{]} & {[}dex{]} & {[}dex{]} & {[}dex{]} \\ \hline
+J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.26 & 0.86 & 0.23 \\
+J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.22 & 0.39 & 0.22 \\
+J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.21 & -0.20 & 0.20 \\
+J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 & 0.96 & 0.33 & -0.16 & 0.20 \\
+J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.1 & 0.44 & 0.76 & 0.23 & -0.02 & 0.20 \\
+J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.1 & 0.05 & 1.17 & 0.95 & 0.21 & -0.07 & 0.20 \\
+J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.20 & -0.04 & 0.20 \\
+J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.21 & 0.46 & 0.21 \\
+J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1 & 8.70 & -0.02 & 0.20 \\
+J032423.46+425429.6 & 51.1 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.22 & 0.80 & 0.20 \\ \hline
+\end{tabular}
+\end{table*}
 

### 2018-05-08 article/msculled.tex
Inclusion of Norm + Anom, additional text, small edits, dummy mag table

@@
 This would suggest that pollution scenarios that are limited to early epochs (such as Population III supernovae) are an unlikely explanation, although they cannot be ruled out entirely.
-This sample is expected to help guide modelling  attempts to explain the origin of the Mg--K abundance signature, which we show exists throughout the Milky Way.
+This sample is expected to help guide modelling  attempts to explain the origin of the Mg--K abundance signature, which we now show exists throughout the Milky Way.
 \end{abstract}
@@
 
-A targeted search looking for [K/Fe] in RGB and main sequence turn-off stars in other clusters (NGC 6752, NGC 6121, NGC 1904, NGC 104, NGC 6397, NGC 7099, and $\omega$ Centauri) and field stars concluded that all K abundance ratios fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}, and no correlations between Mg and K were observed.
+A targeted search for [K/Fe] in RGB and main sequence turn-off stars in other clusters (NGC 6752, NGC 6121, NGC 1904, NGC 104, NGC 6397, NGC 7099, and $\omega$ Centauri) and field stars concluded that all K abundance ratios fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}, and no correlations between Mg and K were observed.
 Recent work by \cite{cerniauskas201747tuc} searched for unusual abundance patterns in Mg and K in NGC 104 through deriving abundances using 2df/HERMES spectra, and a more comprehensive study involving over 400 stars in NGC 104, NGC 6752, and NGC 6809 by \cite{mucciarelli2017K} using FLAMES spectra \citep{cerniauskas201747tuc} both found no correlations between Mg and K, and no significant intrinsic spreads in either Mg or K.
@@
 \item We required any two of the three Mg triplet lines to satisfy $A > 0.05$ and at least one K line to have $A < -0.05$, and for those amplitudes to have $|A|/\sigma_{A} \geq 3$.
-\item We required any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost\ and a reported $\chi_{r}^2 < 3$ from \tc.
+\item We required any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost\ and a reported $\chi_{r}^2 < 3$ from \tc \citep{ho2017,ness2016}.
 \end{enumerate}
@@
 These filters identified 384 unique stars.
-We visually inspected every candidate (multiple times) and excluded stars that showed any evidence of being a false positive, including candidates that exhibited data reduction issues, apparent absorption that was narrower than the expected spectral resolution, as well as 75 stars that exhibited chromospheric emission at H$\alpha$, indicative of chromospheric activity which can cause deceptively strong spectral lines.
+We visually inspected every candidate (multiple times) and excluded stars that showed any evidence of being a false positive, including candidates that exhibited data reduction issues, apparent absorption that was narrower than the expected spectral resolution, as well as 75 stars that exhibited chromospheric emission at H$\alpha$, indicative of chromospheric activity consistent with being a young star that bas been misclassified as a giant.
 The distilled catalogue contains 112 candidate stars with spectra consistent with enhancements in K and depletions in Mg.
@@
 K lines were unaffected by telluric contamination in these candidates.
-The estimated abundances from Magellan/MIKE spectra are consistent (within the uncertainties) of our initial abundance determinations from \lamost\ (Figure \ref{KvsMg}).
+The estimated abundances from Magellan/MIKE spectra are consistent (within the uncertainties) of our initial abundance determinations from \lamost\ (Figure \ref{KvsMg}), and are presented in Table \ref{data:magellan}.
 
@@
 \centering
+
+\begin{subfigure}{1\textwidth}
+\centering
+\includegraphics[width=\textwidth=1]{similarstarsplot.png}
+\caption{Mg-depleted, K-enhanced candidate J034458.82+592955.1. $\teff$=4812, $\logg$=2.66, [Fe/H]=0.058}
+\end{subfigure}
+
 \begin{subfigure}{1\textwidth}
@@
 
+If we allow a brief venture into the realm of speculation, the trend of [K/Fe] with iron may also provide a clue to the question of [Mg/Fe] abundances.
+While K is quite difficult to form, Mg is far more common.
+If we imagine that a cloud of gas formed with NGC 2419-like abundances of [Mg/Fe], [K/Fe], and [Fe/H] then we might expect that over time [Mg/Fe] would quickly approach typical galactic levels, as Mg is produced in large quantities and the cloud is enriched.
+However, the anomalously high level of [K/Fe] would vary only with increasing metalicity and therefore remain detectable in stars that formed from the cloud for far longer
+
 \subsection{Impact on potential scenarios explaining the Mg--K anti-correlation}
@@
 
+\begin{table}[]
+\centering
+\caption{Tabulated data for the 3 stars observed using MAGELLAN/MIKE}
+\label{data:magellan}
+\begin{tabular}{lllllllllll}
+designation\_1      & ra\_1\_1 & dec\_1\_1 & cannon\_teff\_1 & cannon\_logg\_1 & cannon\_m\_h\_1 & cannon\_alpha\_m\_1 & {[}Mg/Fe{]} & {[}K/Fe{]} & K\_FE & K\_FE\_err \\
+J075043.12+204658.0 & 117.68   & 20.78     & 4795.00         & 2.53            & -0.47           & 0.06                & 0.15        & 0.80       & 1.11  & 0.05       \\
+J120032.60+024438.2 & 180.14   & 2.74      & 4633.00         & 2.33            & -0.93           & 0.26                & 0.22        & 0.80       & 1.13  & 0.02       \\
+J091825.49+172114.5 & 139.61   & 17.35     & 4899.00         & 2.71            & -1.19           & 0.29                & 0.36        & 1.54       & 1.30  & 0.12      
+\end{tabular}
+\end{table}
+
 %Certainly the idea that both groups of anomalous stars arise from the same polluter source ought to be entertained.

### 2018-05-16 article/msculled.tex
changes

@@
 Here we present
-112 field stars, identified from \LamostGiants\ \lamost\ giant stars using a data-driven model (\tc), that show significantly enhanced [K/Fe] and likely depleted [Mg/Fe] abundance ratios.
+112 field stars, identified from \LamostGiants\ \lamost\ giant stars, that show significantly enhanced [K/Fe] and likely depleted [Mg/Fe] abundance ratios.
 Our sample spans a range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$) yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 
@@
 NGC 2419 is the Milky Way's third most massive globular cluster, and its chemical composition makes it perhaps the most unusual star cluster in the Galaxy.
-Recent spectroscopic studies of red giant branch (RGB) stars in NGC 2419 revealed a strong anti-correlation between Mg and K abundances in nearly half of the studied stars, and weaker abundance relations in Si, Sc, Ca, Ti and V with Mg \citep{mucciarelli2012,cohenkirby2012}.
+Recent spectroscopic studies of red giant branch (RGB) stars in NGC 2419 revealed a strong anti-correlation between Mg and K abundances in nearly half of the studied stars, and weaker abundance relations in Si, Sc, Ca, Ti, and V with Mg \citep{mucciarelli2012,cohenkirby2012}.
 
-A targeted search for [K/Fe] in RGB and main sequence turn-off stars in other clusters (NGC 6752, NGC 6121, NGC 1904, NGC 104, NGC 6397, NGC 7099, and $\omega$ Centauri) and field stars concluded that all K abundance ratios fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}, and no correlations between Mg and K were observed.
-Recent work by \cite{cerniauskas201747tuc} searched for unusual abundance patterns in Mg and K in NGC 104 through deriving abundances using 2df/HERMES spectra, and a more comprehensive study involving over 400 stars in NGC 104, NGC 6752, and NGC 6809 by \cite{mucciarelli2017K} using FLAMES spectra \citep{cerniauskas201747tuc} both found no correlations between Mg and K, and no significant intrinsic spreads in either Mg or K.
+%A targeted search for [K/Fe] in RGB and main sequence turn-off stars in other clusters 
+A targeted search for [K/Fe] in other globular clusters (NGC 6752, NGC 6121, NGC 1904, NGC 104, NGC 6397, NGC 7099, and $\omega$ Centauri) and field stars concluded that all K abundance ratios fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}, and no correlations between Mg and K were observed.
+Recent work by \cite{cerniauskas201747tuc} searched for unusual abundance patterns in Mg and K in NGC 104 by deriving abundances using 2dF/HERMES spectra, and a more comprehensive study involving over 400 stars in NGC 104, NGC 6752, and NGC 6809 by \cite{mucciarelli2017K} using FLAMES spectra \citep{cerniauskas201747tuc} both found no correlations between Mg and K, and no significant intrinsic spreads in either Mg or K.
 
@@
 
-Beyond the intrinsic scientific value of identifying the mechanism responsible for the puzzling Mg--K anti-correlation, a satisfactory explanation for the Mg--K signature may also offer insight into the underestimation of K abundances in the Milky Way predicted by Galactic chemical evolution models \citep{kobayashi2011} or more broadly help to understand globular cluster formation and evolution.
+Beyond the intrinsic scientific value of identifying the mechanism responsible for the puzzling Mg--K anti-correlation, a satisfactory explanation for the Mg--K signature may also offer insight into the underestimation of K abundances in the Milky Way predicted by Galactic chemical evolution models \citep{kobayashi2011}, or more broadly help to understand globular cluster formation and evolution.
 
-Here we use low resolution \lamost\ data to conduct the largest search to date for stars enhanced in potassium and depleted in magnesium.
-The discovery (or non-discovery) of such stars guides models that attempt to explain the Mg--K anti-correlation and related abundance phenomena.
+Here we use \lamost\ spectra to conduct the largest search to date for stars enhanced in potassium and depleted in magnesium.
+The discovery (or non-discovery) of such stars helps guide models that attempt to explain the Mg--K anti-correlation and related abundance phenomena.
 In particular, such a search provides strong evidence either for or against the uniqueness of the progenitor stars to globular clusters.
@@
 A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model).
-Figure \ref{posterchild} shows the \lamost\ spectrum and best-fitting model from \tc\ for candidate J034458.82+592955.1, as well as the spectra for J163532.2+234847.3, the star with closest stellar parameters to J034458.82+592955.1.
+Figure \ref{posterchild} shows the \lamost\ spectrum and best-fitting model from \tc\ for J034458.82+592955.1, a Mg--K candidate star we identified, as well as the observed spectra for J163532.2+234847.3, the star with closest stellar parameters to our Mg--K candidate star, J034458.82+592955.1.
 
 We fit a Gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167\,\AA, 5172\,\AA, 5184\,\AA) as well as the K doublet (7665\,\AA, 7699\,\AA) for all \LamostGiants\ giants.
-For each star we recorded the amplitudes, approximate widths and wavelength about which the Gaussian profiles were fit.
-The amplitude was used as the measure of the discrepancy from the model spectra, and is analogous to the depth of the absorption line.
-The relationship between equivalent width ($EW$), the amplitude ($A$) and the Gaussian width ($\sigma$) is given by $EW=\frac{2\pi A}{\sigma}$.
+For each star we recorded the amplitudes, widths (standard deviations) and wavelength (mean) about which the Gaussian profiles were fit.
+The amplitude was used as the measure of the discrepancy from the model spectra, and is analogous to the depth of the absorption line, and linearly dependent on the equivalent width.
+%The relationship between equivalent width ($EW$), the amplitude ($A$) and the Gaussian width ($\sigma$) is given by $EW=\frac{2\pi A}{\sigma}$.
 
@@
 \item We required any two of the three Mg triplet lines to satisfy $A > 0.05$ and at least one K line to have $A < -0.05$, and for those amplitudes to have $|A|/\sigma_{A} \geq 3$.
-\item We required any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost\ and a reported $\chi_{r}^2 < 3$ from \tc \citep{ho2017,ness2016}.
+\item We required any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost\ and a reported $\chi_{r}^2 < 3$ from \tc\ \citep{ness2016,ho2017}.
 \end{enumerate}
@@
 We note that although telluric absorption would usually swamp the K doublet lines, the contributions of telluric features have been removed from \lamost\ spectra as part of the data reduction process conducted by \lamost\ \citep{luo2016vizier}.
-Subsequent examination of the radial velocities for the (manually vetted) sample showed no behaviour indicating that the [K/Fe] over-abundances identified were due telluric absorption.
+Subsequent examination of the radial velocities for the (manually vetted) sample showed no behaviour indicating that the over-absorption at potassium wavelengths were due to telluric contamination.
 
-We estimated [K/Fe] abundance ratios for all candidates by synthesising spectra to account for the flux residuals \citep{marcs,sme,vald,ispec}.
-We assume that absorption due to metals is accounted for by \tc, and deviations in flux around the potassium doublet are due to an increased [K/Fe] with respect to the model.
+We estimated [K/Fe] abundance ratios for all candidates by synthesising spectra to account for the flux residuals.
+We adopted the data-driven stellar parameters ($T_{\rm eff}$, $\log{g}$, [Fe/H]) and estimated microturbulent velocities $v_t$ as per Eq.
+7 of \citet{kirby2008}.
+We used plane-parallel stellar photosphere models from \citet{marcs}, and compiled a list of atomic and molecular transitions from VALD \citep{vald}.
+We used Spectroscopy Made Easy \citep{sme} within the \texttt{iSpec} wrapper \citep{ispec} to calculate synthetic spectra.
+
+There are subtleties to this analysis which likely have no significant bias in our inferred abundances, but we include here for completeness.
+Specifically, we assume that some stellar absorption is already accounted for by our data-driven model.
+In a sense, the data-driven model predicts a `typical' spectrum for a star with the given stellar parameters.
+This `typical` spectrum will include some contribution from all abundances (e.g., Mg, K, Al, Na), which is encapsulated by the overall metallicity [Fe/H].
+That is to say that for a star of [Fe/H]$ = 0$, our data-driven model is predicting the spectrum of a \emph{typical} star at $[{\rm Fe/H}] = 0$, and that typical star would have $[{\rm K/Fe}] \sim 0$.
+We synthesise spectra to account for the flux residuals \emph{away} from the data-driven model.
+
+% vt = 2.700 ? 0.509 log g km/s. (7
+
+We assume that deviations in flux around the potassium doublet are due to an increased [K/Fe] with respect to the model.
 We include a conservative 0.2\,dex systematic error floor applied in quadrature with the fitting errors to account for some component of the flux differences not being from the abundance of K, but instead due to noise in the \lamost\ spectra.
@@
 We note that while enhancements in [K/Fe] or [Na/Fe] can be estimated by synthesising the flux residuals, we cannot easily estimate [Mg/Fe] depletions in the same manner because it is difficult to separate the flux contribution of [Mg/Fe] from [$\alpha$/Fe] in the data-driven model.
-For this reason, we will adopt [$\alpha$/Fe] as a conservative upper limit for [Mg/Fe].
+For this reason, we will adopt [$\alpha$/Fe] as a conservative upper limit for [Mg/Fe] such that $[{\rm Mg}/{\rm Fe}] \leq [\alpha/{\rm Fe}]$.\footnote{In some sense this is by construction because we required a flux depletion around the Mg lines to identify candidates, and our data-driven model includes the effects of [$\alpha$/Fe].}
 
@@
 \subsection{Follow-up observations with Magellan/MIKE}
-High resolution spectra of three of the candidate stars selected based on observability (J075043.12+204658.0, J120032.60+024438.2 and J091825.49+172114.5) were obtained using Magellan/MIKE (Magellan Inamori Kyocera Echelle) \citep{shectman2003magellan,bernstein2003mike}.
-Exposure times were calculated to achieve S/N per pixel of 30 per pixel at 450\,nm, sufficient to verify the K-enriched and Mg-poor nature of these stars.
+We acquired high-resolution spectra of three of our candidates as ancillary targets to an existing observing campaign.
+The three targets (J075043.12+204658.0, J120032.60+024438.2 and J091825.49+172114.5) were selected based on their observability from Las Campanas Observatory, and we used the Magellan Inamori Kyocera Echelle (MIKE) spectrograph on the Magellan Clay telescope \citep{shectman2003magellan,bernstein2003mike}.
+Exposure times were calculated to achieve a S/N of 30 per pixel at 450\,nm, sufficient to verify the K-enriched and Mg-poor nature of these stars.
 We reduced the data using the \texttt{CarPy} package \citep{kelson2003}.
-Spline functions were used to continuum-normalize individual echelle orders, before combining them to produce a continuum-normalized spectrum that is contiguous from 350\,nm to 950\,nm.
-With the stellar parameters from \lamost, we calculated [K/Fe] and [Mg/Fe] abundances from individual atomic lines by measuring Gaussian profiles \citep{castelli2004,sneden,casey2014}.
-K lines were unaffected by telluric contamination in these candidates.
+We used smoothing spline functions to continuum-normalize individual echelle orders, before combining them to produce a continuum-normalized spectrum that is contiguous from 350\,nm to 950\,nm.
+With the stellar parameters from \lamost, we calculated [K/Fe] and [Mg/Fe] abundances from individual atomic lines by measuring equivalent widths with Gaussian absorption profiles \citep{castelli2004,sneden,casey2014}.
+From the Magellan/MIKE spectra we confirmed that the K lines in these candidates were unaffected by telluric contamination.
 The estimated abundances from Magellan/MIKE spectra are consistent (within the uncertainties) of our initial abundance determinations from \lamost\ (Figure \ref{KvsMg}), and are presented in Table \ref{data:magellan}.
@@
 
-Figure \ref{loggTeffFeh} shows that the candidate stars are distributed across the entire giant branch, implying that the abundance signature is not associated with any single stage in evolution or any NLTE effects.
-One benefit of the data-driven approach is that NLTE effects need not be explicitly corrected for, as in a physically driven model.
-\tc\ predicts the flux of each star based its $\teff$, $\logg$, metalicity, and [$\alpha$/Fe] and then anomalously abundant stars are identified as those with flux significantly different from this prediction.
-Thus although it is possible the numeric value of the [K/Fe] abundances may be overpredicted due to NLTE effects, NLTE effects will not produce false positives.
-The independence of the calculated [K/Fe] abundances from these effects is demonstrated in Figures \ref{Kvslogg} and \ref{KvsTeff}, which show that no relationship exists between [K/Fe] for the identified candidate stars and $\logg$ or $\teff$.
+Figure \ref{loggTeffFeh} shows that the identified candidates are distributed across the entire red giant branch, implying that the abundance signature is not associated with any single stage in evolution or any NLTE effects.
+One benefit of the data-driven approach is that NLTE effects need not be explicitly accounted for, as in a physically driven model.
+\tc\ predicts the flux of each star based its $\teff$, $\logg$, metallicity, and [$\alpha$/Fe] and then anomalously abundant stars are identified as those with flux significantly different from this prediction.
+Thus although it is likely the numeric value of the [K/Fe] abundances may be over-predicted due to NLTE effects, NLTE effects will not identify false positive candidates.
+This is consistent with what we observe: we find no relationship between the inferred [K/Fe] abundance and the stellar parameters $\teff$ or $\logg$ from \lamost\ (Figures \ref{KvsTeff} and \ref{Kvslogg}).
+
+%The independence of the calculated [K/Fe] abundances from these effects is demonstrated in Figures \ref{Kvslogg} and \ref{KvsTeff}, which show that no relationship exists between [K/Fe] for the identified candidate stars and $\logg$ or $\teff$.
 %@ANDY is this a comment we want to make?
@@
 \label{sec:globclustasoc}
-We cross-matched our candidates with the positions of all known globular clusters \citep{harris1996}.
-The spread in metallicity (Figure \ref{mhist}) is consistent with all candidates being field stars.
-The distribution reflects the original \LamostGiants\ sample of giants from which the candidates were selected.
+We cross-matched our candidates with the positions of all known globular clusters \citep{harris1996} and found no obvious (or plausible) associations.
+The metallicity distribution function of our candidates (Figure \ref{mhist}) is consistent with the field, and the distribution reflects the original \LamostGiants\ sample of giants from which the candidates were selected.
 No candidates have [Fe/H] $\approx -2$, the approximate metallicity of NGC 2419, nor are there many stars with [Fe/H] $\approx -1$, the metallicity of NGC 2808.
@@
 \end{figure}
-Upon examining [Na/Fe] as estimated from the \lamost\ spectra, using the doublet around 5850 \AA, two distinct populations were observed: one population making up approximately 30 percent of the sample with [Na/Fe] > 0.5, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second with [Na/Fe] consistent with typical Galactic abundances.
-The two groups can be clearly distinguished in Figure \ref{NavsFeh}, which also shows abundances of [Na/Fe] versus [Fe/H] from the APOGEE survey for comparison.
+The modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment, while observational data for NGC 2808 implies a positive correlation between Na and K.
+Upon examining the [Na/Fe] abundance ratios we estimated from \lamost\ spectra of our candidates, based on the doublet around 5850 \AA, we observed two distinct populations: one population making up approximately 30 percent of the sample with [Na/Fe] $> 0.5$, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second population with [Na/Fe] abundance ratios consistent with typical Galactic levels.
+The two groups can be clearly distinguished in Figure \ref{NavsFeh}, where for comparison we also show the abundances of [Na/Fe] versus [Fe/H] from the \apogee\ survey.
 
-The high [Na/Fe] abundance ratios we observe are possibly due to the effect of interstellar dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption.
+However, we concluded that the high [Na/Fe] abundance ratios we derive are likely due to interstellar dust contributing.
+Nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, and all but four stars with high [Na/Fe] are found in the disk of our Galaxy, at low absolute galactic latitudes (Figures \ref{Navsb} and \ref{Navsradvel}).
+Thus, we find no evidence for genuine  enhancement of [Na/Fe] among our Mg--K candidates.
+%suggesting that the stellar absorption lines are blended with interstellar dust absorption.
 This is supported by Figures \ref{Navsb} and \ref{Navsradvel}, which show the [Na/Fe] distribution with respect to galactic latitude and the radial velocity.
-It is apparent that almost all of the stars in the anomalous group lie close to the disk of the galaxy, with radial velocities at least somewhat close to zero.
-However, further investigation revealed no evidence of a diffuse interstellar band (DIB) impacting LAMOST spectra around the Na doublet (nor around the Mg or K lines).
-It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment, while observational data for NGC 2808 implies a positive correlation between Na and K.
+%It is apparent that almost all of the stars in the anomalous group lie close to the disk of the galaxy, with radial velocities at least somewhat close to zero.
+%However, further investigation revealed no evidence of a diffuse interstellar band (DIB) impacting LAMOST spectra around the Na doublet (nor around the Mg or K lines).
 
@@
 However, the \lamost\ spectral flux residuals with \tc\ model are consistent with an under-abundance of Mg.
-The small sample of stars for which we have high resolution spectra, coupled with the conflict with the \lamost\ spectra, means we are unable to confidently make a statement regarding the level of [Mg/Fe] in our sample.
+The small sample of stars for which we have high resolution spectra, coupled with the conflict with the \lamost\ spectra, means we are unable to confidently make a statement regarding the level of [Mg/Fe] in our entire sample of 112 stars.
 
-Given that the sample is almost certainly comprised of disk stars, it is relevant to also compare with typical Galactic abundances for [K/Fe], taken from the APOGEE survey \citep{alam2015} and shown in Figures \ref{KvsMg} and \ref{KvsFe}.
+Given that the sample is almost certainly comprised of disk stars, it is relevant to also compare with typical Galactic abundances for [K/Fe].
+In Figure \ref{KvsMg} and \ref{KvsFe} we make these comparisons with data from the \apogee\ survey \citep{alam2015}.
 The sample's [K/Fe] appears definitively anomalous, with Galactic [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] of 0.8 to 1.3.
@@
 It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation.
-However we caution that this may be an artefact of our analysis.
-Further high resolution observations are needed to verify this trend.
+However, we recommend additional high-resolution observations are needed to verify this trend.
+
+%However we caution that this may be an artefact of our analysis. Further high resolution observations are needed to verify this trend.
 
@@
 
+\subsection{Impact on potential scenarios explaining the Mg--K anti-correlation}
+
 The implications of the abundance ratios we find are intriguing.
-The fact that in such a large sample of field stars, none were found that replicated (or exceeded) the extreme abundance pattern of NGC 2419 reinforces for the cluster's uniqueness.
+The fact that in such a large sample of \LamostGiants\ field stars, none were found that replicated (or exceeded) the extreme abundance pattern of NGC 2419.
+This highlights the uniqueness of NGC 2419.
+% for the cluster's uniqueness.
 %regarding the extreme bi-modal nature of its abundance pattern. 
@@
 If we imagine that a cloud of gas formed with NGC 2419-like abundances of [Mg/Fe], [K/Fe], and [Fe/H] then we might expect that over time [Mg/Fe] would quickly approach typical galactic levels, as Mg is produced in large quantities and the cloud is enriched.
-However, the anomalously high level of [K/Fe] would vary only with increasing metalicity and therefore remain detectable in stars that formed from the cloud for far longer
-
-\subsection{Impact on potential scenarios explaining the Mg--K anti-correlation}
+However, the anomalously high level of [K/Fe] would vary only with increasing metallicity and therefore remain detectable in stars that formed from the cloud for far longer.
 
@@
 
-A recent attempt to replicate the Mg--K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}.
+A recent attempt to replicate the Mg--K abundance signature in NGC 2419 by \cite{iliadis2016} also examined abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}.
 The study aimed to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.
-Unless extremely high densities were invoked ($>10^8\,{\rm g\,cm}^{-3}$), it was found that temperatures between 100 and 200\,MK were necessary depending on the density.
+Unless extremely high densities were invoked (i.e., $>\,10^8\,{\rm g\,cm}^{-3}$), it was found that temperatures between 100 and 200\,MK were necessary \todo{to produce K in net quantities?}, depending on the density.
 This constraint rules out many pollution sites, including core and shell burning of low-mass stars, high-mass and super-massive stars, and normal AGB stars.
-However, SAGB stars were considered as potential candidates, with only a relatively small (roughly 10 to 20 MK) increase in temperature at the bottom of the envelope required to fall in the acceptable band of parameter space identified, implying that it is possible that the conditions for K production through the Ar-K reaction pathway could be met in some SAGB stars.
+However, super-AGB (SAGB) stars were considered as potential candidates, with only a relatively small (roughly 10 to 20 MK) increase in temperature at the bottom of the envelope required to fall in the acceptable band of parameter space identified, implying that it is possible that the conditions for K production through the Ar-K reaction pathway could be met in some SAGB stars.
 The other potential candidates identified were novae, although the lack of detailed models of white dwarf accretion of metal-poor material adds considerable uncertainty.
-However, based on current nova frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1 percent of the total required mass to pollute 30 percent of NGC 2419.
+Based on current nova frequency in globular clusters determined by \cite{kato2013novae}, \cite{iliadis2016} conclude that the amount of material that would be produced by novae is at most 1 percent of the total required mass to pollute 30 percent of NGC 2419.
 
@@
 The main argument for this idea is that the extreme rarity of these events, coupled with the huge masses of processed material released, could allow for the abundance signature in NGC 2419 to be the result of a single event, which would explain why a similar abundance trend is not seen in any other globular clusters.
-However, the signature odd-even proton number abundance pattern associated with PISNs, where odd Z elements are enhanced and even Z elements are depleted, is absent from NGC 2419 \citep{carretta2013, cohenkirby2012}.
+However, the signature odd-even proton number abundance pattern associated with PISNs, where odd Z elements are enhanced and even Z elements are depleted, appears absent from NGC 2419 \citep{carretta2013, cohenkirby2012}.
 
-Our study presents a collection of stars in the disk of the Galaxy over a range of metallicities showing anomalously high levels of [K/Fe].
+Our study presents a collection of stars in the disk of the Galaxy over a range of metallicities that show anomalously high levels of [K/Fe].
 The spread in metallicities among our candidates is important.
@@
 These stars with enhanced potassium apparently tend to form at all ages, across all metallicities, so it is probable that the polluting source is also independent of metallicity.
-If we assume that the polluter star forms at a range of metallicities, then we can attempt to constrain scenarios that may be responsible for the Mg--K anti-correlation by disregarding polluters that are reliant on specific metallicity environments to form.
+If we assume that the polluter star forms at a range of metallicities, then we can attempt to constrain scenarios that may be responsible for the Mg--K anti-correlation by disregarding polluters that are reliant on specific environments to form (e.g., low metallicity environments).
 
@@
 Reducing Mg is possible by converting \ce{^{24}Mg} to \ce{^{27}Al} through Mg--Al chains at temperatures around $75\,$MK, which is attainable in hot-bottom burning (HBB) environments in AGB stars.
-However, temperatures upwards of 150 MK are required to produce K, and these temperatures can only potentially be reached at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
-This implies that the Mg depletion and K enrichment likely occur at separate sites, assuming a relatively simple hydrogen burning system.
+However, temperatures upwards of 150\,MK are required to produce K, and these temperatures might only be reached at the bottom of the convective envelope in SAGB stars \citep{iliadis2016}.
+This implies that the Mg depletion and K enrichment likely occurs at separate sites, assuming a relatively simple hydrogen burning system.
 
-We hypothesise that the SAGB-binary may produce a [K/Fe] over-abundance in some stars within the Milky Way as follows.
+We hypothesise that a SAGB-binary system may produce a [K/Fe] over-abundance in some stars within the Milky Way as follows.
 The SAGB star produces K \citep[destroying Na in the process;][]{prantzos2017}, that is then mixed throughout the star's envelope.
@@
 In this scenario, it is the lower-mass binary companion stars that make up our sample of 112 giants.
-A direct test would be to determine whether the candidates are binaries with O-Ne white dwarf remnants, which would indicate that they formed from SAGB stars.
-\newpage
-\begin{table*}
-\centering
-\caption{Tabulated data for 10 of the 112 candidate stars. Data for the full sample is available online.}
-\label{data}
-\begin{tabular}{cccccccccccccc}
-\hline
-\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{V$_\textrm{r}$} & \textbf{T$_\textrm{eff}$} & $\boldsymbol \log{ \, \textbf{g}}$ & \textbf{{[}Fe/H{]}} & \textbf{{[}$\alpha$/Fe{]}} & \textbf{$\boldsymbol \chi_r ^\textbf{2}$} & \textbf{{[}K/Fe{]}} & \textbf{Error} & \textbf{{[}Na/Fe{]}} & \textbf{Error} \\
-- & {[}deg{]} & {[}deg{]} & [pixel$^{-1}]$ & {[${\rm km\,s}^{-1}$]} & {[}K{]} & $[{\rm cm\,s}^{-2}]$ & {[}dex{]} & {[}dex{]} & - & {[}dex{]} & {[}dex{]} & {[}dex{]} & {[}dex{]} \\ \hline
-J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.26 & 0.86 & 0.23 \\
-J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.22 & 0.39 & 0.22 \\
-J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.21 & -0.20 & 0.20 \\
-J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 & 0.96 & 0.33 & -0.16 & 0.20 \\
-J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.1 & 0.44 & 0.76 & 0.23 & -0.02 & 0.20 \\
-J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.1 & 0.05 & 1.17 & 0.95 & 0.21 & -0.07 & 0.20 \\
-J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.20 & -0.04 & 0.20 \\
-J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.21 & 0.46 & 0.21 \\
-J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1 & 8.70 & -0.02 & 0.20 \\
-J032423.46+425429.6 & 51.1 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.22 & 0.80 & 0.20 \\ \hline
-\end{tabular}
-\end{table*}
-
-\begin{table}[]
-\centering
-\caption{Tabulated data for the 3 stars observed using MAGELLAN/MIKE}
-\label{data:magellan}
-\begin{tabular}{lllllllllll}
-designation\_1      & ra\_1\_1 & dec\_1\_1 & cannon\_teff\_1 & cannon\_logg\_1 & cannon\_m\_h\_1 & cannon\_alpha\_m\_1 & {[}Mg/Fe{]} & {[}K/Fe{]} & K\_FE & K\_FE\_err \\
-J075043.12+204658.0 & 117.68   & 20.78     & 4795.00         & 2.53            & -0.47           & 0.06                & 0.15        & 0.80       & 1.11  & 0.05       \\
-J120032.60+024438.2 & 180.14   & 2.74      & 4633.00         & 2.33            & -0.93           & 0.26                & 0.22        & 0.80       & 1.13  & 0.02       \\
-J091825.49+172114.5 & 139.61   & 17.35     & 4899.00         & 2.71            & -1.19           & 0.29                & 0.36        & 1.54       & 1.30  & 0.12      
-\end{tabular}
-\end{table}
+A direct test would be to determine whether the candidates are binaries with O-Ne white dwarf remnant companions, which would indicate that they formed from SAGB stars.
 
@@
 
+\begin{table*}
+\centering
+\caption{Tabulated data for 10 of the 112 candidate stars. Data for the full sample is available online.}
+\label{data}
+\begin{tabular}{cccccccccccccc}
+\hline
+\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{V$_\textrm{r}$} & \textbf{T$_\textrm{eff}$} & $\boldsymbol \log{ \, \textbf{g}}$ & \textbf{{[}Fe/H{]}} & \textbf{{[}$\alpha$/Fe{]}} & \textbf{$\boldsymbol \chi_r ^\textbf{2}$} & \textbf{{[}K/Fe{]}} & \textbf{Error} & \textbf{{[}Na/Fe{]}} & \textbf{Error} \\
+- & {[}deg{]} & {[}deg{]} & [pixel$^{-1}]$ & {[${\rm km\,s}^{-1}$]} & {[}K{]} & $[{\rm cm\,s}^{-2}]$ & {[}dex{]} & {[}dex{]} & - & {[}dex{]} & {[}dex{]} & {[}dex{]} & {[}dex{]} \\ \hline
+J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.26 & 0.86 & 0.23 \\
+J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.22 & 0.39 & 0.22 \\
+J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.21 & -0.20 & 0.20 \\
+J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 & 0.96 & 0.33 & -0.16 & 0.20 \\
+J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.1 & 0.44 & 0.76 & 0.23 & -0.02 & 0.20 \\
+J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.1 & 0.05 & 1.17 & 0.95 & 0.21 & -0.07 & 0.20 \\
+J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.20 & -0.04 & 0.20 \\
+J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.21 & 0.46 & 0.21 \\
+J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1 & 8.70 & -0.02 & 0.20 \\
+J032423.46+425429.6 & 51.1 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.22 & 0.80 & 0.20 \\ \hline
+\end{tabular}
+\end{table*}
+
+\begin{table}[]
+\centering
+\caption{Tabulated data for the 3 stars observed using MAGELLAN/MIKE}
+\label{data:magellan}
+\begin{tabular}{lllllllllll}
+designation\_1      & ra\_1\_1 & dec\_1\_1 & cannon\_teff\_1 & cannon\_logg\_1 & cannon\_m\_h\_1 & cannon\_alpha\_m\_1 & {[}Mg/Fe{]} & {[}K/Fe{]} & K\_FE & K\_FE\_err \\
+J075043.12+204658.0 & 117.68   & 20.78     & 4795.00         & 2.53            & -0.47           & 0.06                & 0.15        & 0.80       & 1.11  & 0.05       \\
+J120032.60+024438.2 & 180.14   & 2.74      & 4633.00         & 2.33            & -0.93           & 0.26                & 0.22        & 0.80       & 1.13  & 0.02       \\
+J091825.49+172114.5 & 139.61   & 17.35     & 4899.00         & 2.71            & -1.19           & 0.29                & 0.36        & 1.54       & 1.30  & 0.12      
+\end{tabular}
+\end{table}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-05-20 article/msculled.tex
fixed captions, collected figures, minor text improvements, minor figure bug fixes

@@
 A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model).
-Figure \ref{posterchild} shows the \lamost\ spectrum and best-fitting model from \tc\ for J034458.82+592955.1, a Mg--K candidate star we identified, as well as the observed spectra for J163532.2+234847.3, the star with closest stellar parameters to our Mg--K candidate star, J034458.82+592955.1.
+Figure \ref{posterchild} shows the \lamost\ spectrum and best-fitting model from \tc\ for J075043.1+204658, a Mg--K candidate star we identified, as well as the observed spectra for J055435.4+152946, the star with closest stellar parameters to our Mg--K candidate star, J075043.1+204658.
 
@@
 \includegraphics[width=\textwidth=1]{similarstarsplot.png}
-\caption{Mg-depleted, K-enhanced candidate J034458.82+592955.1. $\teff$=4812, $\logg$=2.66, [Fe/H]=0.058}
+\caption{Mg-depleted, K-enhanced candidate J075043.1+204658. $\teff$=4812, $\logg$=2.66, [Fe/H]=0.058}
 \end{subfigure}
@@
 \includegraphics[width=\textwidth=1]{posterchild.png}
-\caption{Mg-depleted, K-enhanced candidate J034458.82+592955.1. $\teff$=4812, $\logg$=2.66, [Fe/H]=0.058}
+\caption{Mg-depleted, K-enhanced candidate J075043.1+204658. $\teff$=4812, $\logg$=2.66, [Fe/H]=0.058}
 \end{subfigure}
@@
 \includegraphics[width=\textwidth=1]{postermimic.png}
-\caption{Mg-normal, K-normal star J163532.2+234847.3. $\teff$=4809, $\logg$=2.66, [Fe/H]=0.062}
+\caption{Mg-normal, K-normal star J055435.4+152946. $\teff$=4809, $\logg$=2.66, [Fe/H]=0.062}
 \end{subfigure}
 
-\caption{Normalised \lamost\ spectrum for the Mg-depleted and K-enhanced candidate J034458.82+592955.1 and for the comparable star J163532.2+234847.35.
-J163532.2+234847.35 was selected by minimising the similarity norm defined as $n=(\frac{\Delta \text{T}_{\text{eff}}}{1000})^2 +\Delta \text{logg} ^2 + \Delta \text{[Fe/H]}^2$.
+\caption{Normalised \lamost\ spectrum for the Mg-depleted and K-enhanced candidate J075043.1+204658 and for the comparable star J055435.4+152946.
+J055435.4+152946 was selected by minimising the similarity norm defined as $n=(\frac{\Delta \text{T}_{\text{eff}}}{1000})^2 +\Delta \text{logg} ^2 + \Delta \text{[Fe/H]}^2$.
 The data are shown in black and the best-fitting data-driven model from \tc\ is in red.
 We zoom in around the magnesium triplet and potassium doublet, which we used to identify Mg--K candidates.
-Note that $[\alpha/{\rm Fe}]$ is a label in \tc\ model used and J034458.82+592955.1 shows Mg depletions relative to the estimated [$\alpha$/Fe] value.}
+Note that $[\alpha/{\rm Fe}]$ is a label in \tc\ model used and J075043.1+204658 shows Mg depletions relative to the estimated [$\alpha$/Fe] value.}
 \label{posterchild}
@@
 	\includegraphics[width=\columnwidth]{mhist.png}
-    \caption{Metallicity distribution for all 112 candidate stars identified with K-enhancement and Mg-depletion.}
+    \caption{Metallicity distribution for all 112 candidate stars identified with K-enhancement and Mg-depletion. The stars apparently exist in significant numbers across a wide spread of metalicity.}
     \label{mhist}
@@
 %The independence of the calculated [K/Fe] abundances from these effects is demonstrated in Figures \ref{Kvslogg} and \ref{KvsTeff}, which show that no relationship exists between [K/Fe] for the identified candidate stars and $\logg$ or $\teff$.
-%@ANDY is this a comment we want to make?
-If we make no assumptions about LTE...
-then I feel like we shouldn't be saying this last part, as it reads like: We made an assumption, and hey look its not violated.
 
@@
 	\includegraphics[width=\columnwidth]{loggTeffFeH.png}
-    \caption{Effective temperature, surface gravity and [Fe/H] as per label transfer by the \tc for LAMOST, overlaid with the 112 candidates.}
+    \caption{Effective temperature, surface gravity and [Fe/H] as per label transfer by the \tc\ for LAMOST, overlaid with the 112 candidates.
+The sample stars can clearly be seen to be spread out all along the giant branch.}
     \label{loggTeffFeh}
@@
 \begin{figure}
+
+\begin{subfigure}{0.5\textwidth}
+\includegraphics[width=\columnwidth]{KvsTeff.png}
+\caption{[K/Fe] versus $\teff$}
+\label{KvsTeff}
+\end{subfigure}
+
+\begin{subfigure}{0.5\textwidth}
 \includegraphics[width=\columnwidth]{Kvslogg.png}
@@
 \label{Kvslogg}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[width=\columnwidth]{KvsTeff.png}
-    \caption{[K/Fe] versus $\teff$} 
-    \label{KvsTeff}
+\end{subfigure}
+\caption{No relationship is evident between [K/Fe] and either $\logg$ or $\teff$, as expected due to the use of the data-driven model.}
 \end{figure}
@@
 
-\begin{figure}
+\begin{figure*}
+\begin{subfigure}{0.5\textwidth}
 	\includegraphics[width=\columnwidth]{NavsFeh.png}
@@
     \label{NavsFeh}
-\end{figure}
+\end{subfigure}
 
-\begin{figure}
+\begin{subfigure}{0.5\textwidth}
 	\includegraphics[width=\columnwidth]{Navsb.png}
@@
     \label{Navsb}
-\end{figure}
-
-\begin{figure}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
 	\includegraphics[width=\columnwidth]{Navsradvel.png}
@@
     \label{Navsradvel}
-\end{figure}
+\end{subfigure}
+%\end{figure*}
+%\begin{figure*}
+%\ContinuedFloat
+
+\caption{A strong bimodality in [Na/Fe] abundances of the candidate stars is observed, with a significant population displaying anomolously high abundances.
+Due to the apparent near-exclusivity of this population within the disk of the galaxy, and their notably higher E(B-V) values \citep{schlafly2011}, this phenomena is almost certainly due to interstellar dust.}
+\end{figure*}
+
 The modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment, while observational data for NGC 2808 implies a positive correlation between Na and K.
@@
 However, we concluded that the high [Na/Fe] abundance ratios we derive are likely due to interstellar dust contributing.
-Nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, and all but four stars with high [Na/Fe] are found in the disk of our Galaxy, at low absolute galactic latitudes (Figures \ref{Navsb} and \ref{Navsradvel}).
+Nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, and all but four stars with high [Na/Fe] are found in the disk of our Galaxy, at low absolute galactic latitudes and velocities (Figures \ref{Navsb} and \ref{Navsradvel}).
 Thus, we find no evidence for genuine  enhancement of [Na/Fe] among our Mg--K candidates.
@@
     \caption{[K/Fe] vs [$\alpha$/Fe] for the candidate stars, overlaid with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
-See Section \ref{sec:method} for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].}
+Note that in principle, [$\alpha/Fe$] acts only as an upper limit for [Mg/Fe], and is used as such for our sample in this figure due to difficulties in calculating reliable [Mg/Fe] from \lamost data.}
     \label{KvsMg}
 \end{figure}
-
+ %See Section \ref{sec:method} for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].} 
 \begin{figure}
 	\includegraphics[width=\columnwidth]{KvsFe.png}
-    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
-Metalicities for NGC 2808 are taken as the average metalicity for the cluster from \citet{harris1996}, as individual metallicities for these stars were not available.}
+    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.}
     \label{KvsFe}
@@
 The study aimed to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters.
-Unless extremely high densities were invoked (i.e., $>\,10^8\,{\rm g\,cm}^{-3}$), it was found that temperatures between 100 and 200\,MK were necessary \todo{to produce K in net quantities?}, depending on the density.
+Unless extremely high densities were invoked (i.e., $>\,10^8\,{\rm g\,cm}^{-3}$), it was found that temperatures between 100 and 200\,MK (depending on the density) were necessary to produce sufficient K to match the abundances observed.
 This constraint rules out many pollution sites, including core and shell burning of low-mass stars, high-mass and super-massive stars, and normal AGB stars.

### 2018-05-21 article/msculled.tex
Further figure refinements, altered mimic, altered captions

@@
 A positive residual implies a higher observed normalised flux than expected by the model (less stellar absorption than predicted by the model), while a negative residual implies a lower observed normalised flux than expected (more stellar absorption than predicted by the model).
-Figure \ref{posterchild} shows the \lamost\ spectrum and best-fitting model from \tc\ for J075043.1+204658, a Mg--K candidate star we identified, as well as the observed spectra for J055435.4+152946, the star with closest stellar parameters to our Mg--K candidate star, J075043.1+204658.
+Figure \ref{posterchild} shows the \lamost\ spectrum and best-fitting model from \tc\ for J075043.1+204658, a Mg--K candidate star we identified, as well as the observed spectra for J053622.4+223600, the star with closest stellar parameters to our Mg--K candidate star, J075043.1+204658.
 
@@
 \includegraphics[width=\textwidth=1]{similarstarsplot.png}
-\caption{Mg-depleted, K-enhanced candidate J075043.1+204658. $\teff$=4812, $\logg$=2.66, [Fe/H]=0.058}
+\caption{Overlaid \lamost\ spectra for candidate J075043.1+204658 and J053622.4+223600, a star with similar stellar parameters}
 \end{subfigure}
@@
 \includegraphics[width=\textwidth=1]{posterchild.png}
-\caption{Mg-depleted, K-enhanced candidate J075043.1+204658. $\teff$=4812, $\logg$=2.66, [Fe/H]=0.058}
+\caption{Mg-depleted, K-enhanced candidate J075043.1+204658. $\teff$=4795, $\logg$=2.53, [Fe/H]=-0.47}
 \end{subfigure}
@@
 \includegraphics[width=\textwidth=1]{postermimic.png}
-\caption{Mg-normal, K-normal star J055435.4+152946. $\teff$=4809, $\logg$=2.66, [Fe/H]=0.062}
+\caption{Mg-normal, K-normal star J053622.4+223600. $\teff$=4804 K, $\logg$=2.53, [Fe/H]=0.062}
 \end{subfigure}
 
-\caption{Normalised \lamost\ spectrum for the Mg-depleted and K-enhanced candidate J075043.1+204658 and for the comparable star J055435.4+152946.
-J055435.4+152946 was selected by minimising the similarity norm defined as $n=(\frac{\Delta \text{T}_{\text{eff}}}{1000})^2 +\Delta \text{logg} ^2 + \Delta \text{[Fe/H]}^2$.
+\caption{Normalised \lamost\ spectrum for the Mg-depleted and K-enhanced candidate J075043.1+204658 and for the comparable star J053622.4+223600.
+J053622.4+223600 was selected by minimising the similarity norm defined as $n=(\frac{\Delta \text{T}_{\text{eff}}}{1000})^2 +\Delta \text{logg} ^2 + \Delta \text{[Fe/H]}^2$.
 The data are shown in black and the best-fitting data-driven model from \tc\ is in red.
@@
     \caption{[K/Fe] vs [$\alpha$/Fe] for the candidate stars, overlaid with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
-Note that in principle, [$\alpha/Fe$] acts only as an upper limit for [Mg/Fe], and is used as such for our sample in this figure due to difficulties in calculating reliable [Mg/Fe] from \lamost data.}
+Note that in principle, [$\alpha$/Fe] acts only as an upper limit for [Mg/Fe], and is used as such for our sample in this figure due to difficulties in calculating reliable [Mg/Fe] from \lamost data.}
     \label{KvsMg}

### 2018-05-24 article/msculled.tex
add tables
tables
moved some tables, changed some text, fixed some figures

@@
 The estimated abundances from Magellan/MIKE spectra are consistent (within the uncertainties) of our initial abundance determinations from \lamost\ (Figure \ref{KvsMg}), and are presented in Table \ref{data:magellan}.
+Additional atomic line abundances are included in Table \ref{data:atomiclines} in the Appendix.
+\begin{table}[H]
+\centering
+\caption{Summary of line abundances measured from Magellan/MIKE follow-up spectra.}
+\label{data:magellan}
+\begin{tabular}{lcccc}
+\multicolumn{5}{c}{J075043.12+204658.0} \\
+\hline
+Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
+\hline
+\ion{Mg}{I} & 5 & 7.45 & $+$0.32 & 0.10 \\
+\ion{K}{I}  & 2 & 5.33 & $+$0.77 & 0.07 \\
+\hline
+\\
+\multicolumn{5}{c}{J091825.48+172114.5} \\
+\hline
+Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
+\hline
+\ion{Mg}{I} & 5 & 6.34 & $+$0.29 & 0.08 \\
+\ion{K}{I}  & 2 & 6.28 & $+$0.85 & 0.11 \\
+\hline
+\\
+\multicolumn{5}{c}{J120032.60+024438.2} \\
+\hline
+Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
+\hline
+\ion{Mg}{I} & 6 & 6.96 & $-$0.03 & 0.10 \\
+\ion{K}{I}  & 2 & 4.96 & $+$1.22 & 0.31 \\
+\hline
+\end{tabular}
+\end{table}
 
@@
 \subsection{Detailed chemical abundances}
+In this section, we describe the abundance trends evident from the \lamost\ and Magellan/MIKE spectra and compare with stars identified as anomalous regarding their [Mg/Fe] and [K/Fe] abundances in other studies.
+Abundances as well as several physical and observational parameters are available for all candidate stars online, with a sample shown in Table \ref{data:lamost}
+
 \label{sec:abundances}
@@
 
-\begin{figure*}
-\begin{subfigure}{0.5\textwidth}
+\begin{figure}
+\centering
+\begin{subfigure}{0.35\textwidth}
+\centering
 	\includegraphics[width=\columnwidth]{NavsFeh.png}
@@
 
-\begin{subfigure}{0.5\textwidth}
+\begin{subfigure}{0.35\textwidth}
+\centering
 	\includegraphics[width=\columnwidth]{Navsb.png}
@@
     \label{Navsb}
-\end{subfigure}%
-\begin{subfigure}{0.5\textwidth}
+\end{subfigure}
+
+\begin{subfigure}{0.35\textwidth}
+\centering
 	\includegraphics[width=\columnwidth]{Navsradvel.png}
@@
 Due to the apparent near-exclusivity of this population within the disk of the galaxy, and their notably higher E(B-V) values \citep{schlafly2011}, this phenomena is almost certainly due to interstellar dust.}
-\end{figure*}
+\end{figure}
 
@@
 It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation.
-However, we recommend additional high-resolution observations are needed to verify this trend.
+For completeness, we caution that this trend may be an artefact of our analysis.
+[K/Fe] is calculated from the flux residuals ( $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$), and the data-driven model may already account for some level of [K/Fe] in the star due to the model representing the typical star at a given $\teff$, $\logg$, metalicity and [$\alpha$/Fe].
+This has potential to cause spurious effects; however, it should also be emphasized that these effects would be within the uncertainties associated with estimating abundances from \lamost\ spectra.
+We recommend additional high-resolution observations to verify this trend.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
+
+\appendix
+
+\section{Additional atomic line abundances from Magellan/MIKE}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{table*}
+\centering
+\caption{Atomic line abundances measured from Magellan/MIKE follow-up spectra of three Mg/K candidates.}
+\label{data:atomiclines}
+\begin{tabular}{crrrcccccc}
+\hline
+& & & & \multicolumn{2}{c}{J075043.12+204658.0} & \multicolumn{2}{c}{J091825.48+172114.5} & \multicolumn{2}{c}{J120032.60+024438.2} \\
+
+Species & $\lambda$ & $\chi$ & $\log{gf}$ & E.W. & $\log_\epsilon(\textrm{X})$ & E.W. & $\log_\epsilon(\textrm{X})$ & E.W. & $\log_\epsilon(\textrm{X})$ \\
+& $({\textrm \AA})$ & $(\textrm{eV})$ & & $(\textrm{m\AA})$ & & $(\textrm{m\AA})$ & & $(\textrm{m\AA})$ \\
+\hline
+\ion{Mg}{I} & 4057.51 & 4.346 & $-$0.890 & 208.5 & 7.71 & 154.4 & 6.66 & 167.6 & 6.95 \\
+\ion{Mg}{I} & 4167.27 & 4.346 & $-$0.710 & 231.1 & 7.11 & 123.9 & 6.27 & 192.9 & 6.69 \\
+\ion{Mg}{I} & 4571.10 &   0.0 & $-$5.623 & 208.4 & 7.71 & 154.4 & 6.66 & 167.6 & 6.95 \\
+\ion{Mg}{I} & 4571.10 &   0.0 & $-$5.688 & 129.7 & 7.39 & 142.1 & 7.03 &  76.4 & 7.18 \\
+\ion{Mg}{I} & 4702.99 & 4.330 & $-$0.380 & 231.1 & 7.11 & 123.9 & 6.27 & 192.9 & 6.69 \\
+\ion{Mg}{I} & 4730.04 & 4.340 & $-$2.389 & 129.7 & 7.39 & 142.1 & 7.03 &  76.4 & 7.18 \\
+\ion{Mg}{I} & 5528.41 & 4.340 & $-$0.498 &  80.0 & 7.68 & 175.9 & 6.65 & 115.0 & 7.09 \\
+\ion{Mg}{I} & 5711.09 & 4.345 & $-$1.729 & 129.7 & 7.39 & 142.1 & 7.03 &  76.4 & 7.18 \\
+\ion{Mg}{I} & 5711.09 & 4.340 & $-$1.724 & 129.3 & 7.38 & 165.1 &  6.4 & 204.5 & 6.91 \\
+\ion{Mg}{I} & 6318.72 & 5.108 & $-$1.945 &  80.0 & 7.68 & 175.9 & 6.65 & 115.0 & 7.09 \\
+\ion{K}{I}  & 7664.90 &   0.0 & $+$0.135 & 257.8 & 5.41 &  85.6 & 6.79 & 200.7 & 4.80 \\
+\ion{K}{I}  & 7698.96 &   0.0 & $-$0.168 & 202.6 & 5.25 & 379.8 & 5.76 & 201.7 & 5.11 \\
+\hline
+\end{tabular}
+\end{table*}
+
 \begin{table*}
@@
 \caption{Tabulated data for 10 of the 112 candidate stars. Data for the full sample is available online.}
-\label{data}
+\label{data:lamost}
 \begin{tabular}{cccccccccccccc}
@@
 \end{table*}
-
-\begin{table}[]
-\centering
-\caption{Tabulated data for the 3 stars observed using MAGELLAN/MIKE}
-\label{data:magellan}
-\begin{tabular}{lllllllllll}
-designation\_1      & ra\_1\_1 & dec\_1\_1 & cannon\_teff\_1 & cannon\_logg\_1 & cannon\_m\_h\_1 & cannon\_alpha\_m\_1 & {[}Mg/Fe{]} & {[}K/Fe{]} & K\_FE & K\_FE\_err \\
-J075043.12+204658.0 & 117.68   & 20.78     & 4795.00         & 2.53            & -0.47           & 0.06                & 0.15        & 0.80       & 1.11  & 0.05       \\
-J120032.60+024438.2 & 180.14   & 2.74      & 4633.00         & 2.33            & -0.93           & 0.26                & 0.22        & 0.80       & 1.13  & 0.02       \\
-J091825.49+172114.5 & 139.61   & 17.35     & 4899.00         & 2.71            & -1.19           & 0.29                & 0.36        & 1.54       & 1.30  & 0.12      
-\end{tabular}
-\end{table}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-05-24 article/msculled.tex
updated affiliations

@@
 $^{5}$Institute of Astronomy, Madingley Road, Cambridge, CB3 0HA, United Kingdom\\
-$^{6}$Columbia University\\
-$^{7}$Carnegie Observatories
+$^{6}$Department of Astronomy, Columbia University, 550 West 120th Street New York, New York 10027\\
+$^{7}$The Observatories of the Carnegie Institution of Washington, 813 Santa Barbara St., Pasadena, CA 91101, USA
 }

### 2018-05-31 article/msculled.tex
Large alterations to referee response, minor changes to paper.

@@
 The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters.
-Here we present
-112 field stars, identified from \LamostGiants\ \lamost\ giant stars, that show significantly enhanced [K/Fe] and likely depleted [Mg/Fe] abundance ratios.
-Our sample spans a range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$) yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 
-We conclude that the nucleosynthetic process producing the anomalous abundances in [K/Fe] and [Mg/Fe] probably occurs at a wide range of metallicities.
+Here we present 112 field stars, identified from \LamostGiants\ \lamost\ giants, that show significantly enhanced [K/Fe] and possibly depleted [Mg/Fe] abundance ratios.
+Our sample spans a wide range of metallicities ($-1.5 < [{\rm Fe}/{\rm H}] < 0.3$), yet none show abundance ratios of [K/Fe] or [Mg/Fe] that are as extreme as those observed in NGC~2419. 
+If confirmed, the identified sample of stars represents evidence that the nucleosynthetic process producing the anomalous abundances ratios of [K/Fe] and [Mg/Fe] probably occurs at a wide range of metallicities.
 This would suggest that pollution scenarios that are limited to early epochs (such as Population III supernovae) are an unlikely explanation, although they cannot be ruled out entirely.
@@
 
-%Recently \cite{youngwooklee} used a Ca filter to identify two population in NGC 2419 corresponding to two generations of stars: G1, first generation metal poor stars, and G2, second generation stars displaying enhanced Ca and significantly increased He abundance ($\Delta Y = 0.19$).
-The Mg-depleted population identified previously was found to be contained with the G2 population.
-
-%It has been suggested that NGC 2419's position and size, being both very massive and very distant from the Milky Way compared to many other globular clusters, aids it in retaining enriched material from explosive events \citep{mucciarelli2012}.
-It is also perhaps noteworthy that NGC 2808 is also one of the more massive globular clusters of the Milky Way, although it is far closer to the Galactic Centre.
-But if this unknown pollution event is common among globular clusters and the cause of its apparent exclusivity to NGC 2808 and NGC 2419 is enhanced ejecta retention due to high mass, then other massive clusters such as $\omega$ Centauri would also be expected contain the signature, which to date has not been observed.
-
-%While it is plausible that the increased mass and greater distance from the gaseous disk of the Milky Way would cause a clusters first generation polluter stars to have an increased effect on the second generation of stars, this effect would apply to all ejecta (assuming comparable energies).
-So while it might be expected that second generation stars in clusters similar to NGC 2419 made up of more material processed by the first generation than other lighter globular clusters, it doesn't explain why the ejecta from the first generation was apparently dominated by this as yet unknown polluter object resulting in the Mg--K anti-correlation.
-In the opinion of the author, it is the identity and physical characterisation of this unknown polluter that is of the greatest scientific interest, with such a result also hopefully answering the question of the signatures uniqueness.
-
 Beyond the intrinsic scientific value of identifying the mechanism responsible for the puzzling Mg--K anti-correlation, a satisfactory explanation for the Mg--K signature may also offer insight into the underestimation of K abundances in the Milky Way predicted by Galactic chemical evolution models \citep{kobayashi2011}, or more broadly help to understand globular cluster formation and evolution.
@@
 In Section \ref{sec:discussion} we discuss our results and their implications for possible pollution mechanisms.
-
-%This study, which queries \LamostGiants\ \lamost\ giants for depleted Mg and enhanced K, seeks to provide additional information which can be used to guide and test models attempting to explain the Mg--K anti-correlation and related phenomena.
-The large sample size provides greater insight into the supposed exclusivity of the signature, and the stars identified present an important opportunity for follow up observations.
 
@@
 For each star we recorded the amplitudes, widths (standard deviations) and wavelength (mean) about which the Gaussian profiles were fit.
-The amplitude was used as the measure of the discrepancy from the model spectra, and is analogous to the depth of the absorption line, and linearly dependent on the equivalent width.
+The amplitude was used as the measure of the discrepancy from the model spectra, and is analogous to the depth of the absorption line, and in principle linearly dependent on the equivalent width.
+This measure was favoured as more reliable than attempting to quantify line widths from the low resolution \lamost\ spectra.
 %The relationship between equivalent width ($EW$), the amplitude ($A$) and the Gaussian width ($\sigma$) is given by $EW=\frac{2\pi A}{\sigma}$.
@@
 We synthesise spectra to account for the flux residuals \emph{away} from the data-driven model.
-
+%@andy
 % vt = 2.700 ? 0.509 log g km/s. (7
@@
 We applied the same method (and error floor) to estimate [Na/Fe] from \lamost\ spectra.
-We note that while enhancements in [K/Fe] or [Na/Fe] can be estimated by synthesising the flux residuals, we cannot easily estimate [Mg/Fe] depletions in the same manner because it is difficult to separate the flux contribution of [Mg/Fe] from [$\alpha$/Fe] in the data-driven model.
+We note that while enhancements in [K/Fe] or [Na/Fe] can be estimated by synthesising the flux residuals, we cannot estimate [Mg/Fe] depletions in the same manner because it is difficult to separate the flux contribution of [Mg/Fe] from [$\alpha$/Fe] in the data-driven model.
 For this reason, we will adopt [$\alpha$/Fe] as a conservative upper limit for [Mg/Fe] such that $[{\rm Mg}/{\rm Fe}] \leq [\alpha/{\rm Fe}]$.\footnote{In some sense this is by construction because we required a flux depletion around the Mg lines to identify candidates, and our data-driven model includes the effects of [$\alpha$/Fe].}
@@
 We acquired high-resolution spectra of three of our candidates as ancillary targets to an existing observing campaign.
-The three targets (J075043.12+204658.0, J120032.60+024438.2 and J091825.49+172114.5) were selected based on their observability from Las Campanas Observatory, and we used the Magellan Inamori Kyocera Echelle (MIKE) spectrograph on the Magellan Clay telescope \citep{shectman2003magellan,bernstein2003mike}.
+The three targets (J075043.12+204658.0, J091825.49+172114.5, and J120032.60+024438.2) were selected based on their observability from Las Campanas Observatory, and we used the Magellan Inamori Kyocera Echelle (MIKE) spectrograph on the Magellan Clay telescope \citep{shectman2003magellan,bernstein2003mike}.
 Exposure times were calculated to achieve a S/N of 30 per pixel at 450\,nm, sufficient to verify the K-enriched and Mg-poor nature of these stars.
@@
 Our sample of \lamost\ giants carries with it certain selection effects from both the \apogee\ DR12 and \lamost\ samples.
+The scope of this the data-driven model is necesarily confined to the training sample, which is in turn confined in this case to stars common between \lamost\ and \apogee\.
 For example, metal-poor stars with [Fe/H] $\lesssim-2$ are mostly absent from our sample because they were too dissimilar from the training stars for label transfer from \apogee.
 Similarly, the target selection process for \lamost\ is not easily invertible so we do not consider selection effects present in \lamost\ beyond comparing the candidate stars' metallicity distribution with that of \cite{ho2017}.
-We find that the frequency of Mg--K stars is consistent (within the errors) of being flat with metallicity.
+We find that the frequency of Mg--K candidate stars is consistent (within the errors) of being flat with metallicity.
 
@@
 \tc\ predicts the flux of each star based its $\teff$, $\logg$, metallicity, and [$\alpha$/Fe] and then anomalously abundant stars are identified as those with flux significantly different from this prediction.
-Thus although it is likely the numeric value of the [K/Fe] abundances may be over-predicted due to NLTE effects, NLTE effects will not identify false positive candidates.
+Thus although it is possible the numeric value of the [K/Fe] abundances may be over-predicted due to NLTE effects, NLTE effects will not result in the identification of false positive candidates.
 This is consistent with what we observe: we find no relationship between the inferred [K/Fe] abundance and the stellar parameters $\teff$ or $\logg$ from \lamost\ (Figures \ref{KvsTeff} and \ref{Kvslogg}).
-
-%The independence of the calculated [K/Fe] abundances from these effects is demonstrated in Figures \ref{Kvslogg} and \ref{KvsTeff}, which show that no relationship exists between [K/Fe] for the identified candidate stars and $\logg$ or $\teff$.
 
@@
 \label{sec:globclustasoc}
-We cross-matched our candidates with the positions of all known globular clusters \citep{harris1996} and found no obvious (or plausible) associations.
+We cross-matched our candidates with the positions of known globular clusters \citep{harris1996} and found no obvious (or plausible) associations.
 The metallicity distribution function of our candidates (Figure \ref{mhist}) is consistent with the field, and the distribution reflects the original \LamostGiants\ sample of giants from which the candidates were selected.
@@
 In this section, we describe the abundance trends evident from the \lamost\ and Magellan/MIKE spectra and compare with stars identified as anomalous regarding their [Mg/Fe] and [K/Fe] abundances in other studies.
-Abundances as well as several physical and observational parameters are available for all candidate stars online, with a sample shown in Table \ref{data:lamost}
+Abundances as well as several physical and observational parameters are available for all candidate stars online, with a 10-star sample shown in Table \ref{data:lamost}
 
@@
 Figure \ref{KvsMg} shows [K/Fe]  for the 112 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
-As described in Section \ref{sec:method}, we adopt [$\alpha$/Fe] as an upper limit for [Mg/Fe].
+As described in Section \ref{sec:method}, we are forced to adopt [$\alpha$/Fe] as an upper limit for [Mg/Fe] for our sample stars as we are unable to estimate [Mg/Fe] from the LAMOST spectra.
 [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE and for over 60000 stars from APOGEE \citep{alam2015} is also shown.
-%The use of $[\alpha$/Fe] to position the sample in \ref{KvsMg} is supported by the [Mg/Fe] measurements from the high-resolution spectra, which vary less than 0.1\,dex from the level of $[\alpha$/Fe] for each of the relevant stars in the \lamost\ data.
-However, for the bulk of the sample decoupling [Mg/Fe] from $[\alpha$/Fe] is impossible, and so in general  we are unable to draw firm conclusions as to whether the sample exhibits anomalously low [Mg/Fe].
 We note that [K/Fe] for the candidate stars is generally lower than that of the Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population.
-The [K/Fe] level for the candidates estimated by \lamost\ is significantly higher than the [K/Fe] abundance in NGC 2808.
+The [K/Fe] level for the candidates estimated by \lamost\ is significantly higher than the [K/Fe] abundances in NGC 2808.
 
@@
 The [Mg/Fe] abundances derived from Magellan/MIKE's high resolution spectra are consistent with the Mg-normal population in NGC 2419.
-However, the \lamost\ spectral flux residuals with \tc\ model are consistent with an under-abundance of Mg.
+However, the \lamost\ spectral flux residuals with \tc\ model indicate an under-abundance of Mg relative to a 'typical' star in our sample of \lamost\ giants.
 The small sample of stars for which we have high resolution spectra, coupled with the conflict with the \lamost\ spectra, means we are unable to confidently make a statement regarding the level of [Mg/Fe] in our entire sample of 112 stars.
@@
 In Figure \ref{KvsMg} and \ref{KvsFe} we make these comparisons with data from the \apogee\ survey \citep{alam2015}.
-The sample's [K/Fe] appears definitively anomalous, with Galactic [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] of 0.8 to 1.3.
-Note that the Magellan/MIKE abundance for candidate star J091825.49+172114.5 has [K/Fe] $=1.54$, confirming that at least some of the sample stars have extremely high levels of [K/Fe], approaching the extreme levels observed in NGC 2419.
+The sample's [K/Fe] appears definitively anomalous, with Galactic [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8 to 1.3 dex.
 
-The [K/Fe] abundance ratios in our sample also show an anti-correlation with total metallicity, illustrated in Figure \ref{KvsFe}, which is not present in the bulk of Milky Way stars.
+The [K/Fe] abundance ratios in our sample also show an anti-correlation with total metallicity, illustrated in Figure \ref{KvsFe}, which is not present when examining the bulk of Milky Way stars.
 It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation.
+
 For completeness, we caution that this trend may be an artefact of our analysis.
-[K/Fe] is calculated from the flux residuals ( $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$), and the data-driven model may already account for some level of [K/Fe] in the star due to the model representing the typical star at a given $\teff$, $\logg$, metalicity and [$\alpha$/Fe].
-This has potential to cause spurious effects; however, it should also be emphasized that these effects would be within the uncertainties associated with estimating abundances from \lamost\ spectra.
+[K/Fe] is calculated from the flux residuals ($f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$), and the data-driven model may already account for some level of [K/Fe] in the star due to the model representing the typical star at a given $\teff$, $\logg$, metalicity and [$\alpha$/Fe].
+In principle, this has potential to cause spurious effects; however, it should also be emphasized that these effects would be within the uncertainties associated with estimating abundances from \lamost\ spectra.
 We recommend additional high-resolution observations to verify this trend.
-
-%However we caution that this may be an artefact of our analysis. Further high resolution observations are needed to verify this trend.
-
-% due to the data-driven nature of our model, it is possible that this relation is an artefact of the process for calculating [K/Fe];
-
-%However, for reasons related to the use of both a data-driven model and a physical model for calculating abundances \todo{@andy add any elaboration on what the problem was, if necessary}, it is possible that this effect is an artefact of abundance processing rather than a physical relation.
-Without further observations of the sample stars, we are unable to say with certainty whether this phenomena is real or not.
-
-%In contrast with the marked departure from Galactic values for [K/Fe], [$\alpha$/Fe] varies from around 0-0.3\,dex in the \lamost \ sample, similar to Galactic levels of [Mg/Fe], which vary with metallicity from approximately 0.4$\pm$0.2 for [Fe/H] $\sim$ -1.5 to 0.1 $\pm$0.2 for [Fe/H] $\sim$ -0.3 \citep{kobayashi2011}.
-No variation with metallicity is observed within the \lamost sample's [$\alpha$/Fe].
 
@@
 This highlights the uniqueness of NGC 2419.
-% for the cluster's uniqueness.
-%regarding the extreme bi-modal nature of its abundance pattern. 
+
 However, we repeat that our sample of \lamost\ giants searched had already been filtered of most of the stars that would have matched NGC 2419's metallicity.

### 2018-06-04 article/msculled.tex
foo
m,ef'
ascii, very minor punctuation corrections.

@@
 Additional atomic line abundances are included in Table \ref{data:atomiclines} in the Appendix.
-\begin{table}[H]
+\begin{table}
 \centering
@@
 \hline
-\ion{Mg}{I} & 5 & 7.45 & $+$0.32 & 0.10 \\
-\ion{K}{I}  & 2 & 5.33 & $+$0.77 & 0.07 \\
+\ion{Mg}{I} & 3 & 7.39 & $+$0.34 & 0.13 \\
+\ion{K}{I}  & 2 & 5.33 & $+$0.85 & 0.07 \\
 \hline
@@
 \hline
-\ion{Mg}{I} & 5 & 6.34 & $+$0.29 & 0.08 \\
-\ion{K}{I}  & 2 & 6.28 & $+$0.85 & 0.11 \\
+\ion{Mg}{I} & 5 & 6.56 & $-$0.05 & 0.08 \\
+\ion{K}{I}  & 2 & 5.32 & $+$1.28 & 0.31 \\
 \hline
@@
 \hline
-\ion{Mg}{I} & 6 & 6.96 & $-$0.03 & 0.10 \\
-\ion{K}{I}  & 2 & 4.96 & $+$1.22 & 0.31 \\
+\ion{Mg}{I} & 4 & 6.96 & $+$0.30 & 0.09 \\
+\ion{K}{I}  & 2 & 4.96 & $+$0.86 & 0.11 \\
 \hline
@@
 In this section, we describe the abundance trends evident from the \lamost\ and Magellan/MIKE spectra and compare with stars identified as anomalous regarding their [Mg/Fe] and [K/Fe] abundances in other studies.
-Abundances as well as several physical and observational parameters are available for all candidate stars online, with a 10-star sample shown in Table \ref{data:lamost}
+Abundances as well as several physical and observational parameters are available for all candidate stars online, with a 10-star sample shown in Table \ref{data:lamost}.
 
@@
 \hline
-\ion{Mg}{I} & 4057.51 & 4.346 & $-$0.890 & 208.5 & 7.71 & 154.4 & 6.66 & 167.6 & 6.95 \\
-\ion{Mg}{I} & 4167.27 & 4.346 & $-$0.710 & 231.1 & 7.11 & 123.9 & 6.27 & 192.9 & 6.69 \\
-\ion{Mg}{I} & 4571.10 &   0.0 & $-$5.623 & 208.4 & 7.71 & 154.4 & 6.66 & 167.6 & 6.95 \\
-\ion{Mg}{I} & 4571.10 &   0.0 & $-$5.688 & 129.7 & 7.39 & 142.1 & 7.03 &  76.4 & 7.18 \\
-\ion{Mg}{I} & 4702.99 & 4.330 & $-$0.380 & 231.1 & 7.11 & 123.9 & 6.27 & 192.9 & 6.69 \\
-\ion{Mg}{I} & 4730.04 & 4.340 & $-$2.389 & 129.7 & 7.39 & 142.1 & 7.03 &  76.4 & 7.18 \\
-\ion{Mg}{I} & 5528.41 & 4.340 & $-$0.498 &  80.0 & 7.68 & 175.9 & 6.65 & 115.0 & 7.09 \\
-\ion{Mg}{I} & 5711.09 & 4.345 & $-$1.729 & 129.7 & 7.39 & 142.1 & 7.03 &  76.4 & 7.18 \\
-\ion{Mg}{I} & 5711.09 & 4.340 & $-$1.724 & 129.3 & 7.38 & 165.1 &  6.4 & 204.5 & 6.91 \\
-\ion{Mg}{I} & 6318.72 & 5.108 & $-$1.945 &  80.0 & 7.68 & 175.9 & 6.65 & 115.0 & 7.09 \\
-\ion{K}{I}  & 7664.90 &   0.0 & $+$0.135 & 257.8 & 5.41 &  85.6 & 6.79 & 200.7 & 4.80 \\
-\ion{K}{I}  & 7698.96 &   0.0 & $-$0.168 & 202.6 & 5.25 & 379.8 & 5.76 & 201.7 & 5.11 \\
+\ion{Mg}{1} & 4057.51 & 4.35 & $-$0.890 &        &       & 154.39 & 6.66 &        &      \\
+\ion{Mg}{1} & 4167.27 & 4.35 & $-$0.710 &        &       & 123.88 & 6.27 &        &      \\
+\ion{Mg}{1} & 4702.99 & 4.33 & $-$0.380 & 231.15 &  7.11 & 165.09 & 6.41 & 192.99 & 6.69 \\
+\ion{Mg}{1} & 4730.04 & 4.34 & $-$2.389 &        &       &        &      &  76.41 & 7.18 \\
+\ion{Mg}{1} & 5528.41 & 4.34 & $-$0.498 &        &       & 175.99 & 6.65 & 204.58 & 6.91 \\
+\ion{Mg}{1} & 5711.09 & 4.34 & $-$1.724 & 129.32 &  7.38 &  85.64 & 6.80 & 115.01 & 7.09 \\
+\ion{Mg}{1} & 6318.72 & 5.11 & $-$1.945 &  80.02 &  7.68 &        &      &        &      \\
+\ion{K}{1}  & 7664.90 &  0.0 & $+$0.135 & 257.85 &  5.41 & 379.79 & 5.76 & 200.77 & 4.80 \\
+\ion{K}{1}  & 7698.96 &  0.0 & $-$0.168 & 202.69 &  5.25 & 155.23 & 4.88 & 201.79 & 5.11 \\
 \hline

### 2018-06-07 article/Referee Response .txt
john changes. alteration to title

Comments to the Author

The manuscript describes the analysis of a sample of field stars 
with K and Mg abundances that seem to resemble those observed 
in some extreme globular clusters (like NGC2419 and NGC2808). 
Even if the topic is extremely interesting and an explanation of 
these peculiar stars is still lacking, several points, discussed below, 
should be clarified and better discussed before to consider the paper 
for the publication. I find the description of the analysis 
quite qualitative and not fully convincing. Additional details 
should be provided in order to demonstrate the reliability of the 
results. In particular, I'm not fully convinced that K abundances 
are totally free from bias or systematics.
I suggest to move the paper to the main journal in order to
provide all the needed information about the analysis.

The paper has been lengthened for submission to the main journal to accommodate a more thorough description of the analysis. Additional analysis has been included relating to the treatment of possible systematic effects, and relevant technical details have been added.

- The abundances from the resonance K lines at 7665 and 7699 A are 
highly sensitive to the adopted microturbulent velocities.
Also, they can be affected by significant NLTE corrections. 
These two effects are not discussed throughout the paper and they 
could be relevant (in particular to understand whether these 
stars are really K-enriched). 
Which value of microturbulent velocities has been adopted? 
I assume that, considering the low spectral resolution of LAMOST, 
microturbulent velocities have been assumed or derived from 
some parametrization (and not measured from the spectra).
Are the K abundances corrected for NLTE?
In principle, the NLTE corrections for K abundances 
are negative (depending on the metallicity and atmospheric parameters), 
pointing out that LTE K abundances are over-estimated.

We thank the referee for raising this point. Micro-turbulent velocities were adopted from a parameterization for giant stars, which we have now explicitly included in the updated manuscript. The quoted K abundances assume LTE in order to make comparisons with other literature sources that only quote LTE abundances. We have updated the manuscript to discuss the level of non-LTE corrections, and included figures of [K/Fe] against stellar parameters to demonstrate that there is no strong systematic trend.

We note that our data-driven model encapsulates the typical flux for a star with a given effective temperature, surface gravity, metallicity, et cetera, and we are identifying K-enhanced candidates as stars with significant enhancements away from this model. That is to say that when we identify a star as being enhanced in potassium, we are stating that it is showing flux enhancements at the potassium line that are larger than what we would expect for a star of that effective temperature, surface gravity, and metallicity. So while non-LTE effects may over-estimate the abundances we derive, non-LTE effects would not result in false positive detections of K-enhanced candidates.

- I think that the definition of K-enriched, Mg-depleted stars for 
the discussed targets is not totally correct. 
The K abundances are clearly higher than those observed in other stars 
of similar metallicities, but the [Mg/Fe] abundances are compatible with 
those stars. Also, the comparison between these stars 
and the APOGEE sample (Fig.3) suggests that the targets have 
the same Mg level of the APOGEE stars with similar [Fe/H]. 
In other words, they are normal stars in terms of Mg but not in terms of K.
In principle, I don't see any reason to consider 
these stars depleted in Mg. The Mg-poor stars observed in 
NGC2419 and NGC2808 show a depletion in Mg with respect to 
the Mg abundance observed in most of the cluster stars. 
The LAMOST targets can be consider as Mg-poor stars if they show 
abundances significantly lower than those of the majority of the stars 
with similar metallicity.

The authors acknowledge that further analysis is required to definitively label the candidate stars as Mg-depleted and K-enhanced.

In principle we required stars to show at least some depletion in [Mg/Fe] by the criteria we employed to select candidates. But the *enhancement* of [K/Fe] is much higher than the depletion of [Mg/Fe]. We have softened this definition throughout the manuscript and focused on [K/Fe] enhancement.

It is perhaps worth noting that even without a depletion in [Mg/Fe] relative to stars of similar metallicity, these candidate stars could still represent a population polluted by an event similar to NGC 2419, provided their level of [K/Fe] is confirmed as high. Although entirely speculative, it is possible that whatever mechanism produced the signature in NGC 2419 is then mixed with Mg-rich supernovae ejecta to make more metal-rich stars with more typical [Mg/Fe], but still displaying enhanced [K/Fe]. Thus, the absence of meaningful [Mg/Fe] abundances for the sample of stars presented in this study is perhaps not as significant as it might appear. However, we avoided making these speculative claims in the paper until detailed chemical abundances can be measured.

- The abundances of Fe, K and Mg of the entire sample should be 
shown and not only those of the stars selected as K-rich, Mg-poor. 
It is crucial to show also the other "normal" stars. 
If your analysis procedure is not affected by any bias, most of the stars 
should match with the APOGEE stars in terms of Mg and K.
The definition of "K-rich stars" should be done with respect to a sample 
of stars analyzed in the same way.

We agree. However, performing meaningful spectral synthesis for the entire 450000-star sample is not computationally feasible. Instead, we rely on flux residuals to identify the candidates. Deriving detailed chemical abundances for these candidates will be the subject of future work, which will also be critical in understanding the origin of this Mg/K abundance signature.

- Please show the comparison between two LAMOST spectra with similar 
parameters and metallicities but different K abundances, in order to 
demonstrate a clear difference in the strength of the K lines.

We have added a figure showing two LAMOST spectra with similar stellar parameters and different Mg/K abundances.

- The authors should show the behavior of [Mg/Fe] as a function of [Fe/H] 
(similar to Fig, 4 for K)

Regrettably, as we are unable to obtain [Mg/Fe] abundances for any stars other than those for which we have abundances from Magellan/MIKE, this figure is unable to be included. In light of this, we have avoided or softened claims pertaining to the [Mg/Fe] abundances of the candidate stars.

- The authors should show the behavior of [K/Fe] as a function 
of Teff and logg, in order to demonstrate that there are no spurious 
effects due to the analysis (uncertain parameters, NLTE effects...).

We have added this information to the paper (Figures 4a and 4b.).

- It is not totally clear what the authors mean with "amplitude A". 
Is it like an equivalent width? Which are the units of these amplitudes?

We failed to adequately explain this point. The amplitude is the strength of the Gaussian profile used to fit the flux residuals. It is analogous to the depth of the absorption line, and is related to the equivalent width by EW = 2\pi{}A\sigma, where \sigma is the width of the profile. We have updated the manuscript to more clearly explain the profile amplitude.

- The abundances of Fe, Mg and K for the three MIKE targets should 
be explicitly provided.

We have included a table of chemical abundances measured from the Magellan/MIKE spectra.

- A table with the main information about the K-rich stars (coordinates, magnitudes, 
atmospheric parameters) should be provided.

We have added a table of properties of the candidates, which includes coordinates, magnitudes, stellar parameters, and other ancillary information.

- The oscillator strengths for the used K lines should be quoted, 
in order to highlight possible systematics with other works.

Thank you for pointing this out, these should definitely have been included. We have now included these in the updated manuscript.

- The authors suggest that the mechanism responsible of the K-enhancement 
in these stars should be the same responsible of the K-rich, Mg-poor stars 
in some extreme globulars. However, the K enhancement in NGC2419 and NGC2808 
is explained in the framework of the self-enrichment process occurring 
in the early stage of life of the globulars and related to their high 
stellar density. How is possible that the same mechanism occurs in 
field stars?

We do not claim to have an answer to the Mg-K anti-correlation puzzle, but rather seek to provide information that might guide attempts to explain the phenomena. For example, this work is the first that shows that K-rich (and possibly somewhat Mg-poor) stars exist at metallicities other than [Fe/H] ~ -2. If these stars (or, more realistically, some subset of these stars) are related to the mechanism responsible in NGC 2419, then detailed abundances for our sample of stars will help guide efforts to explain the puzzle.

We discuss possible mechanisms only in the context of existing literature. This has been limited to globular clusters because the abundance signature has never been identified elsewhere. The origin of the abundance signature remains unknown. While it may be that self-enrichment is why there are so many peculiar stars in NGC 2419, it does not necessarily follow that the progenitor star could not form elsewhere and pollute other stars outside a globular cluster environment. It would seem unlikely that this extremely rare signature would have two unrelated origins that depend on whether it is found in a cluster environment or a galactic environment. All of this is speculation, which we have tried to avoid in this paper, but we aimed to discuss our results within the context of the existing literature.

- In Section 3.3 the authors claimed that the behaviour of [K/Fe] with 
the metallicity could be due to some artifacts of the analysis.
Which artifacts? This sentence seems to suggest possible systematics 
in the analysis that should be better investigated.

We have expanded the discussion on this point. In short, it is because we measure [K/Fe] from the flux residuals (observed flux - data driven model), but some [K/Fe] contribution may already be accounted for in the data-driven model, because the data-driven model just encapsulates ‘the typical flux for a star of the given temperature, surface gravity, metallicity, etc’. This potential bias is probably small (far smaller than the uncertainties from measuring abundances from LAMOST data!), but we comment on it in the paper for completeness.

- Concerning the check about [Na/Fe], the authors could investigate 
possible trend of [Na/Fe] with the radial velocity. I expect that 
the stars with Na lines contaminated by the interstellar features 
will be those with radial velocities close to 0 km/s.

This figure is now included, as well as some additional figures showing the behavior of [Na/Fe].

- In the Introduction, where the authors discuss about K abundance 
in other clusters, please quote also the works by Mucciarelli et al. 2017 
and Cerniauskas et al. 2017 that present abundances of K in samples 
larger than those discussed by Carretta et al. 2013.

These works are now referenced in the introduction. Thank you for raising this.

- Caption of Figure 4. The authors claim that the individual metallicities 
of the stars in NGC2808 are not available. The metallicities used by 
Mucciarelli et al. 2015 are those of the same stars analysed by 
Carretta et al. 2009.

These metallicities are now included in the relevant figure. Thank you for raising this.

The authors wish to thank the referee for their time, and the valuable and constructive feedback they have provided. The scientific value and robustness of the paper has been significantly increased as a result. We regret that we were unable to fully address some of the more fundamental concerns that were raised, specifically the absence of [Mg/Fe] and [K/Fe] abundance ratios for the full sample of LAMOST giants. However, we remain convinced that this sample of stars - even unconfirmed - is worthy of bringing to the attention of the relevant scientific community.

### 2018-06-09 article/msculled_initial_submission.tex
difflatex files from revised_1 and initial submission

--- 2018-02-23 article/ms.tex
@@
 Anna Y.~Q. Ho,$^{4}$\newauthor
-Christopher A. Tout$^{1,5}$
-%Melissa K. Ness,$^{6}$
-%David W. Hogg,$^{7}$
+Christopher A. Tout,$^{1,5}$
+Melissa Ness,$^{6}$
+Alexander P. Ji$^{7}$
 \\
@@
 $^{5}$Institute of Astronomy, Madingley Road, Cambridge, CB3 0HA, United Kingdom\\
-%$^{6}$ Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
-%$^{7}$ Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA\\
+$^{6}$Columbia University\\
+$^{7}$Carnegie Observatories
 }
@@
 
-One  mechanism for [Mg/Fe] depletion is the introduction of $\alpha$-poor and Fe-rich material released by Type Ia supernovae \citep{tsujimoto2012first} which locally pollutes the normal [Mg/Fe] ratios that arise from Type II supernovae.
-However, the two populations in NGC 2419 are indistinguishable in their [Fe/H] abundance \citep{cohenkirby2012}.
-Furthermore, Type Ia supernova enrichment cannot account for the enhanced K abundance observed in NGC 2419.
-In fact it is hard to make K in sufficient quantities anywhere without invoking unrealistic temperature conditions or increasing some reaction rates above those measured by several orders of magnitude \citep{ventura2012,iliadis2016}.
-Recent work by \cite{ritter2017} on K production in O-C shell mergers in very low-metallicity stars shows promise as an alternative source of K but this work not sufficiently quantitative yet.
-Another mechanism for reducing [Mg/Fe] is through the Mg--Al nucleosynthetic chain in high-temperature hydrogen burning.
-However, no correlation between Mg and Al is observed in NGC 2419 \citep{cohenkirby2012,mucciarelli2012}.
-
 Beyond the intrinsic scientific value of identifying the mechanism responsible for the puzzling Mg--K anti-correlation, a satisfactory explanation for the Mg--K signature may also offer insight into the underestimation of K abundances in the Milky Way predicted by Galactic chemical evolution models \citep{kobayashi2011} or more broadly help to understand globular cluster formation and evolution.
@@
 We cross-matched our candidates with the positions of all known globular clusters \citep{harris1996}.
-No candidates can be associated with NGC~2419 or NGC~2808.
-The closest candidate to any star cluster is J074807.22+261514.2, which lies 2.54\degree\ from Ko~2 \citep{koposov2007}.
-This separation implies a minimum 1.77\, kpc distance from Ko 2, while Ko 2 has an estimated size of around 3\, pc \citep{koposov2007}.
-
 The spread in metallicity (Figure \ref{mhist}) is consistent with all candidates being field stars.
@@
 
-Upon examining [Na/Fe] as estimated from the \lamost\ spectra, two distinct populations were observed: one population making up approximately 30 percent of the sample with [Na/Fe] > 0.5, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second with [Na/Fe] consistent with typical Galactic abundances.
-However, the high [Na/Fe] abundance ratios we observe are very likely due to the effect of interstellar dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption.
+Upon examining [Na/Fe] as estimated from the \lamost\ spectra, using the doublet around 5850 \AA, two distinct populations were observed: one population making up approximately 30 percent of the sample with [Na/Fe] > 0.5, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second with [Na/Fe] consistent with typical Galactic abundances.
+However, the high [Na/Fe] abundance ratios we observe are possibly due to the effect of interstellar
+dust contributing, as nearly every star with apparently enriched [Na/Fe] showed notably higher E(B-V) \citep{schlafly2011}, suggesting that the stellar absorption lines are blended with interstellar dust absorption.
+However, further investigation revealed no evidence of a diffuse interstellar band (DIB) impacting spectra around the Na doublet, nor Mg or K.
 It is worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment, while observational data for NGC 2808 implies a positive correlation between Na and K.
-No relation between Na and K abundances is observed.
 
@@
 \section*{Acknowledgements}
-We thank Alex P. Ji (Carnegie Observatories), Melissa Ness (Columbia), David W. Hogg (NYU), and Hans-Walter Rix (MPIA).
+We thank David W. Hogg (NYU), and Hans-Walter Rix (MPIA).
 %- Magellan/MIKE and Australian government

### 2018-06-09 article/msculled_revised_1.tex
difflatex files from revised_1 and initial submission

--- 2018-06-04 article/msculled.tex
@@
 % Keep the title short and informative.
-\title[Mg--K stars in LAMOST]{On the discovery of K-enhanced and Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}}
+\title[Mg--K stars in LAMOST]{On the discovery of K-enhanced and possibly Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}}
 
@@
 This would suggest that pollution scenarios that are limited to early epochs (such as Population III supernovae) are an unlikely explanation, although they cannot be ruled out entirely.
-This sample is expected to help guide modelling attempts to explain the origin of the Mg--K abundance signature, which we now show exists throughout the Milky Way.
+This sample is expected to help guide modelling attempts to explain the origin of the Mg--K abundance signature.
 \end{abstract}
@@
 \tc\ \citep{ness2016,ho2017} was used to estimate effective temperature $\teff$, surface gravity $\logg$, metallicity [Fe/H], and mean $\alpha$-element abundance relative to iron [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the \apogee\ \citep{alam2015} survey.
+This process is referred to as 'label transfer'.
 Unless otherwise stated, these transferred labels are those referred to throughout this study.
@@
 
-We fit a Gaussian profile to the flux residuals for all three absorption lines in the Mg triplet (5167\,\AA, 5172\,\AA, 5184\,\AA) as well as the K doublet (7665\,\AA, 7699\,\AA) for all \LamostGiants\ giants.
+We fit a Gaussian profile of amplitude $A$ to the flux residuals for all three absorption lines in the Mg triplet (5167\,\AA, 5172\,\AA, 5184\,\AA) as well as the K doublet (7665\,\AA, 7699\,\AA) for all \LamostGiants\ giants.
 For each star we recorded the amplitudes, widths (standard deviations) and wavelength (mean) about which the Gaussian profiles were fit.
@@
 \item We required any two of the three Mg triplet lines to satisfy $A > 0.05$ and at least one K line to have $A < -0.05$, and for those amplitudes to have $|A|/\sigma_{A} \geq 3$.
-\item We required any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost\ and a reported $\chi_{r}^2 < 3$ from \tc\ \citep{ness2016,ho2017}.
+\item We required the amplitude of any two of the three Mg triplet lines to have $A > 0$ and both K lines to have $A < 0$, and for the spectra to have a signal-to-noise ($S/N$) ratio of $S/N > 30$ in \lamost\ and a reported $\chi_{r}^2 < 3$ from \tc\ \citep{ness2016,ho2017}.
 \end{enumerate}
@@
 
-There are subtleties to this analysis which likely have no significant bias in our inferred abundances, but we include here for completeness.
-Specifically, we assume that some stellar absorption is already accounted for by our data-driven model.
+It can be assumed that some stellar absorption is already accounted for by our data-driven model.
 In a sense, the data-driven model predicts a `typical' spectrum for a star with the given stellar parameters.
@@
 Our sample of \lamost\ giants carries with it certain selection effects from both the \apogee\ DR12 and \lamost\ samples.
-The scope of this the data-driven model is necesarily confined to the training sample, which is in turn confined in this case to stars common between \lamost\ and \apogee\.
-For example, metal-poor stars with [Fe/H] $\lesssim-2$ are mostly absent from our sample because they were too dissimilar from the training stars for label transfer from \apogee.
+The scope of this the data-driven model is necesarily confined to the training sample, which is in turn confined in this case to stars common between \lamost\ and \apogee.\ For example, metal-poor stars with [Fe/H] $\lesssim-2$ are mostly absent from our sample because they were too dissimilar from the training stars for label transfer from \apogee.
 Similarly, the target selection process for \lamost\ is not easily invertible so we do not consider selection effects present in \lamost\ beyond comparing the candidate stars' metallicity distribution with that of \cite{ho2017}.
@@
 
-The modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180\,MK hydrogen burning environment, while observational data for NGC 2808 implies a positive correlation between Na and K.
+The modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K which could result from a 180\,MK hydrogen burning environment, while observational data for NGC 2808 implies a positive correlation between Na and K.
 Upon examining the [Na/Fe] abundance ratios we estimated from \lamost\ spectra of our candidates, based on the doublet around 5850 \AA, we observed two distinct populations: one population making up approximately 30 percent of the sample with [Na/Fe] $> 0.5$, significantly higher than typical Galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}, and a second population with [Na/Fe] abundance ratios consistent with typical Galactic levels.
@@
 In Figure \ref{KvsMg} and \ref{KvsFe} we make these comparisons with data from the \apogee\ survey \citep{alam2015}.
-The sample's [K/Fe] appears definitively anomalous, with Galactic [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8 to 1.3 dex.
+Our sample's [K/Fe] appears definitively anomalous, with Galactic [K/Fe] around $0.3 \pm 0.2$\,dex, while the identified candidate stars have a spread in [K/Fe] from around 0.8 to 1.3 dex.
 
@@
 The implications of the abundance ratios we find are intriguing.
-The fact that in such a large sample of \LamostGiants\ field stars, none were found that replicated (or exceeded) the extreme abundance pattern of NGC 2419.
-This highlights the uniqueness of NGC 2419.
+It is an astonishing fact that in such a large sample of \LamostGiants\ field stars, none were found that replicated (or exceeded) the extreme abundance pattern of NGC 2419 highlights the uniqueness of NGC 2419.
 
-However, we repeat that our sample of \lamost\ giants searched had already been filtered of most of the stars that would have matched NGC 2419's metallicity.
+However, we repeat that the sample of \lamost\ giants  we searched had already been filtered of most of the stars that would have matched NGC 2419's metallicity.
 The 112 star candidate pool identified of K enhanced stars represents a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical Galactic levels at a range of metallicities.
@@
 
-Our study presents a collection of stars in the disk of the Galaxy over a range of metallicities that show anomalously high levels of [K/Fe].
+Our study presents a collection of stars in the disk of the Galaxy with a range of metallicities that show anomalously high levels of [K/Fe].
 The spread in metallicities among our candidates is important.
 It implies that the process responsible for the Mg--K abundance signature may not be tied to a certain epoch in the Milky Way's evolution.
-These stars with enhanced potassium apparently tend to form at all ages, across all metallicities, so it is probable that the polluting source is also independent of metallicity.
+These stars with enhanced potassium apparently tend to form at all ages, across all metallicities, so it is probable that the polluting source is extant at all metallicities.
 If we assume that the polluter star forms at a range of metallicities, then we can attempt to constrain scenarios that may be responsible for the Mg--K anti-correlation by disregarding polluters that are reliant on specific environments to form (e.g., low metallicity environments).
@@
 One class of candidates that can be immediately eliminated under such an assumption are Population III stars.
-A hyper-massive Population III star may be been a plausible explanation for NGC~2419 \citep{carretta2013} exclusively, particularly given its isolation from the Milky Way ($d_{\rm GC} \approx 90\,{\rm kpc}$) and low metallicity.
+A hyper-massive Population III star may be been a plausible explanation for NGC~2419 \citep{carretta2013} exclusively, particularly given its isolation from the Milky Way at a distance of $\approx 90\,{\rm kpc}$ and low metallicity.
 However, being unable to form throughout the life of the Galaxy makes it unlikely for Population III stars to be the polluters responsible for the stars we identify.

### 2018-07-03 article/msculled_revised_2.tex
points 2 and 3 adressed. relevent text henceforth: msculled_revised_2.tex]

--- 2018-06-09 article/msculled_revised_1.tex
@@
 	\includegraphics[width=\columnwidth]{KvsMg.png}
-    \caption{[K/Fe] vs [$\alpha$/Fe] for the candidate stars, overlaid with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
-Note that in principle, [$\alpha$/Fe] acts only as an upper limit for [Mg/Fe], and is used as such for our sample in this figure due to difficulties in calculating reliable [Mg/Fe] from \lamost data.}
+    \caption{[K/Fe] vs [$\alpha$/Fe] for the candidate stars, overlaid with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015} as well as the three candidates observed using Magellan/MIKE (red diamonds).
+These three stars' abundances as per the \lamost\ spectra are indicated in the figure (red circles).
+Note that in principle, [$\alpha$/Fe] acts only as an upper limit for [Mg/Fe], and is used as such for our sample in this figure due to difficulties in calculating reliable [Mg/Fe] from \lamost\ data.}
     \label{KvsMg}
@@
 [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE and for over 60000 stars from APOGEE \citep{alam2015} is also shown.
+The \lamost\ abundances for the three stars observed by Magellan are also shown (red circles).
 We note that [K/Fe] for the candidate stars is generally lower than that of the Mg-depleted population in NGC 2419, but higher than that of the Mg-normal population.
@@
 - & {[}deg{]} & {[}deg{]} & [pixel$^{-1}]$ & {[${\rm km\,s}^{-1}$]} & {[}K{]} & $[{\rm cm\,s}^{-2}]$ & {[}dex{]} & {[}dex{]} & - & {[}dex{]} & {[}dex{]} & {[}dex{]} & {[}dex{]} \\ \hline
-J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.26 & 0.86 & 0.23 \\
-J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.22 & 0.39 & 0.22 \\
-J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.21 & -0.20 & 0.20 \\
-J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 & 0.96 & 0.33 & -0.16 & 0.20 \\
-J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.1 & 0.44 & 0.76 & 0.23 & -0.02 & 0.20 \\
-J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.1 & 0.05 & 1.17 & 0.95 & 0.21 & -0.07 & 0.20 \\
-J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.20 & -0.04 & 0.20 \\
-J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.21 & 0.46 & 0.21 \\
-J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1 & 8.70 & -0.02 & 0.20 \\
-J032423.46+425429.6 & 51.1 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.22 & 0.80 & 0.20 \\ \hline
+J000908.89+124821.9 & 2.2871 & 12.8061 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.26 & 0.86 & 0.23 \\
+J002619.36+565612.1 & 6.5807 & 56.9367 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.22 & 0.39 & 0.22 \\
+J002907.61+354701.0 & 7.2817 & 35.7836 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.21 & -0.20 & 0.20 \\
+J003451.10+424543.0 & 8.7130 & 42.7620 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 & 0.96 & 0.33 & -0.16 & 0.20 \\
+J005649.98+391722.9 & 14.2083 & 39.2897 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.1 & 0.44 & 0.76 & 0.23 & -0.02 & 0.20 \\
+J010305.95+043445.9 & 15.7748 & 4.5794 & 90 & 20.69 & 4646 & 2.72 & 0.1 & 0.05 & 1.17 & 0.95 & 0.21 & -0.07 & 0.20 \\
+J011949.36+063411.4 & 19.9557 & 6.5699 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.20 & -0.04 & 0.20 \\
+J013039.08+404843.8 & 22.6628 & 40.8122 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.21 & 0.46 & 0.21 \\
+J030101.42+560042.3 & 45.2560 & 56.0118 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1 & 8.70 & -0.02 & 0.20 \\
+J032423.46+425429.6 & 51.0978 & 42.9082 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.22 & 0.80 & 0.20 \\ \hline
 \end{tabular}

### 2018-07-09 article/msculled_revised_2.tex
add fe
a

@@
 	\includegraphics[width=\columnwidth]{KvsFe.png}
-    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.}
+    \caption{[K/Fe] vs [Fe/H] for the candidate stars, overlaid with [K/Fe] vs [Fe/H] for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}.
+The linear regression formula is \textrm{[K/Fe]$=-0.21 \times$[Fe/H]$+0.97$, with r$^2$=0.37}.}
     \label{KvsFe}

### 2018-07-09 article/Referee responses 2.txt
Point 4 adressed, draft of referee responses 2 included

Referee responses 2

Comments to the Author
I thank the authors to improve the manuscript that now it is 
ready to be recommended for the publication. 
I repeat my previous comment, the lack of a (small) sample of stars 
observed with LAMOST and with normal [K/Fe] weakens the result, 
because the suspect of possible systematics remains and the 
comparison with APOGEE data is not homogeneous. 
My suggestion would be to include a sample of about 50/100 LAMOST targets 
with metallicity similar to that of the K-rich stars but 
with not enhanced K abundances, in order to quantitatively estimate 
the amount of K enrichment of these stars. 
This is my own opinion to enforce the result but I understand that this 
task is an additional and probably time-consuming effort.
The authors are free to follow or not this suggestion.

- Regrettably, undertaking the abundance estimation for even a small sample of LAMOST targets is a non-trivial endeavor,
- and while taking a smaller sample makes the problem more tractable, the reduced sample size also diminishes the
- significance of the result. For this reason, we have opted not to include the additional sample of LAMOST stars.

Additionally, I have some minor comments/suggestions.

1) Please add explicitly [Fe/H] in Table 1.

- This information is now included in Table 1, along with [K/H] and [Mg/H].

2) The link between red circles and red hexagons is not easy 
to understand at a first glance. Please better explain it 
in the caption and in Section 2.2.

- The relationship between the red circles and diamonds is now explicitly dealt with in the caption,
- as well as in the figure explanation in Section 2.2.

3) Please provide the coordinates of the targets in Table A2 
with a more significant number of digits.

- Table A2 Right Ascension and Declination coordinates are now provided to 4 decimal points (units: degrees) in Table A2.

4) Please provide the statistical significance of the 
[K/Fe]-[Fe/H] anticorrelation.

- The linear regression using the LAMOST abundances is now included in Figure 7,
- and the equation and its statistical significance quantified by r^2 is given in the caption.
- The statistical significance is fairly low, though given the large uncertainties in the abundace estimations, this is not unexpected.
- The equation and r^2 value is: [K/Fe]= −0.21×[Fe/H]+0.97, with r^2 =0.37.

### 2018-07-09 article/msculled_revised_2.tex
Point 4 adressed, draft of referee responses 2 included

@@
 \label{data:magellan}
-\begin{tabular}{lcccc}
-\multicolumn{5}{c}{J075043.12+204658.0} \\
+\begin{tabular}{lccccc}
+\multicolumn{6}{c}{J075043.12+204658.0} \\
 \hline
-Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
+Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/H] & [X/Fe] & $\sigma/\sqrt{N}$ \\
 \hline
-\ion{Mg}{I} & 3 & 7.39 & $+$0.34 & 0.13 \\
-\ion{K}{I}  & 2 & 5.33 & $+$0.85 & 0.07 \\
+\ion{Fe}{I} & 82 & 6.95 & $-$0.55 &    0.00 & 0.02 \\
+\ion{Mg}{I} & 3  & 7.39 & $-$0.21 & $+$0.34 & 0.13 \\
+\ion{K}{I}  & 2  & 5.33 & $+$0.30 & $+$0.85 & 0.07 \\
 \hline
 \\
-\multicolumn{5}{c}{J091825.48+172114.5} \\
+\multicolumn{6}{c}{J091825.48+172114.5} \\
 \hline
-Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
+Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/H] & [X/Fe] & $\sigma/\sqrt{N}$ \\
 \hline
-\ion{Mg}{I} & 5 & 6.56 & $-$0.05 & 0.08 \\
-\ion{K}{I}  & 2 & 5.32 & $+$1.28 & 0.31 \\
+\ion{Fe}{I} & 43 & 6.51 & $-$0.99 &    0.00 & 0.03 \\
+\ion{Mg}{I} & 5  & 6.56 & $-$1.04 & $-$0.05 & 0.08 \\
+\ion{K}{I}  & 2  & 5.32 & $+$0.29 & $+$1.28 & 0.31 \\
 \hline
 \\
-\multicolumn{5}{c}{J120032.60+024438.2} \\
+\multicolumn{6}{c}{J120032.60+024438.2} \\
 \hline
-Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
+Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/H] & [X/Fe] & $\sigma/\sqrt{N}$ \\
 \hline
-\ion{Mg}{I} & 4 & 6.96 & $+$0.30 & 0.09 \\
-\ion{K}{I}  & 2 & 4.96 & $+$0.86 & 0.11 \\
+\ion{Fe}{I} & 77 & 6.56 & $-$0.14 & 0.00 & 0.03 \\
+\ion{Mg}{I} & 4  & 6.96 & $+$0.16 & $+$0.30 & 0.09 \\
+\ion{K}{I}  & 2  & 4.96 & $+$0.72 & $+$0.86 & 0.11 \\
 \hline
@@
 These three stars' abundances as per the \lamost\ spectra are indicated in the figure (red circles).
-Note that in principle, [$\alpha$/Fe] acts only as an upper limit for [Mg/Fe], and is used as such for our sample in this figure due to difficulties in calculating reliable [Mg/Fe] from \lamost\ data.}
+Note that in principle, [$\alpha$/Fe] acts only as an upper limit for [Mg/Fe] and is used as such for our sample in this figure due to difficulties in calculating reliable [Mg/Fe] from \lamost\ data.}
     \label{KvsMg}

### 2018-07-09 article/Referee responses 2.txt
minor

@@
 
-- Regrettably, undertaking the abundance estimation for even a small sample of LAMOST targets is a non-trivial endeavor,
-- and while taking a smaller sample makes the problem more tractable, the reduced sample size also diminishes the
-- significance of the result. For this reason, we have opted not to include the additional sample of LAMOST stars.
+- Regrettably, undertaking the abundance estimation for LAMOST targets
+- is a non-trivial endeavour, and while taking a smaller sample makes
+- the problem more tractable, the reduced sample size diminishes the
+- significance of the result. For this reason, we have opted to not
+- include an additional sample of LAMOST stars, and have instead started
+- a high-resolution spectroscopic campaign to measure detailed chemical
+- abundances for a large number of normal and Mg-K stars. The detailed
+- chemical abundances to be measured in that program will undoubtedly
+- shed light on the origin of the Mg-K anomaly.
 
@@
 - and the equation and its statistical significance quantified by r^2 is given in the caption.
-- The statistical significance is fairly low, though given the large uncertainties in the abundace estimations, this is not unexpected.
+- The statistical significance is fairly low, though given the large uncertainties in the abundance estimations, this is not surprising.
 - The equation and r^2 value is: [K/Fe]= −0.21×[Fe/H]+0.97, with r^2 =0.37.

### 2018-07-16 article/arxiv:mnras copy/arxivmnras.tex
arxiv/mnras subfolder+zip

--- 2018-07-09 article/msculled_revised_2.tex
@@
-% mnras_template.tex
-%
-% LaTeX template for creating an MNRAS paper
-%
-% v3.0 released 14 May 2015
-% (version numbers match those of mnras.cls)
-%
-% Copyright (C) Royal Astronomical Society 2015
-% Authors:
-% Keith T. Smith (Royal Astronomical Society)
-
-% Change log
-%
-% v3.0 May 2015
-%    Renamed to match the new package name
-%    Version number matches mnras.cls
-%    A few minor tweaks to wording
-% v1.0 September 2013
-%    Beta testing only - never publicly released
-%    First version: a simple (ish) template for creating an MNRAS paper
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Basic setup. Most papers should leave these options alone.
 \documentclass[a4paper,fleqn,usenatbib]{mnras}
 
-% MNRAS is set in Times font. If you don't have this installed (most LaTeX
-% installations will be fine) or prefer the old Computer Modern fonts, comment
-% out the following line
 \usepackage{newtxtext,newtxmath}
-% Depending on your LaTeX fonts installation, you might get better results with one of these:
-%\usepackage{mathptmx}
-%\usepackage{txfonts}
 
-% Use vector fonts, so it zooms properly in on-screen viewing software
-% Don't change these lines unless you know what you are doing
 \usepackage[T1]{fontenc}
@@
 \renewcommand{\maketitle}{\begingroup\let\footnote=\thanks \ACMmaketitle\endgroup}
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
 
-% Title of the paper, and the short title which is used in the headers.
-% Keep the title short and informative.
 \title[Mg--K stars in LAMOST]{On the discovery of K-enhanced and possibly Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}}
 
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
 \author[Kemp et al.]{Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
@@
 \\
-% List of institutions
 $^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
@@
 }
-% These dates will be filled out by the publisher
+
 \date{Accepted 2018 XX XX. Received 2018 YY YY; in original form 2018 ZZ ZZ}
 
-% Enter the current year, for the copyright statements etc.
 \pubyear{2018}
@@
 \maketitle
-
-% Abstract of the paper
-%The detailed chemical composition of a star acts as a fossil record of the conditions when it formed.
 
@@
 
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
 \begin{keywords}
@@
 
-%A targeted search for [K/Fe] in RGB and main sequence turn-off stars in other clusters 
 A targeted search for [K/Fe] in other globular clusters (NGC 6752, NGC 6121, NGC 1904, NGC 104, NGC 6397, NGC 7099, and $\omega$ Centauri) and field stars concluded that all K abundance ratios fell within the bounds of the Mg-normal population in NGC 2419 \citep{carretta2013}, and no correlations between Mg and K were observed.
@@
 This measure was favoured as more reliable than attempting to quantify line widths from the low resolution \lamost\ spectra.
-%The relationship between equivalent width ($EW$), the amplitude ($A$) and the Gaussian width ($\sigma$) is given by $EW=\frac{2\pi A}{\sigma}$.
 
@@
 We synthesise spectra to account for the flux residuals \emph{away} from the data-driven model.
-%@andy
-% vt = 2.700 ? 0.509 log g km/s. (7
 
@@
 For this reason, we will adopt [$\alpha$/Fe] as a conservative upper limit for [Mg/Fe] such that $[{\rm Mg}/{\rm Fe}] \leq [\alpha/{\rm Fe}]$.\footnote{In some sense this is by construction because we required a flux depletion around the Mg lines to identify candidates, and our data-driven model includes the effects of [$\alpha$/Fe].}
-
-%\todo{The presence of Na enhancements were visually estimated from the sample of 112 candidate stars' flux spectra.
-Flux-based estimates placed at most 40 of the 112 stars (35\%) as being likely Na enhanced targets.} Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with [Na/Fe] above 0.5\,dex.
-\todo{@andy add anything specific to Na abundance methods from LAMOST}.
 
@@
 \end{subfigure}
-%\end{figure*}
-%\begin{figure*}
-%\ContinuedFloat
 
@@
 Thus, we find no evidence for genuine  enhancement of [Na/Fe] among our Mg--K candidates.
-%suggesting that the stellar absorption lines are blended with interstellar dust absorption.
-This is supported by Figures \ref{Navsb} and \ref{Navsradvel}, which show the [Na/Fe] distribution with respect to galactic latitude and the radial velocity.
-%It is apparent that almost all of the stars in the anomalous group lie close to the disk of the galaxy, with radial velocities at least somewhat close to zero.
-%However, further investigation revealed no evidence of a diffuse interstellar band (DIB) impacting LAMOST spectra around the Na doublet (nor around the Mg or K lines).
 
@@
 \end{figure}
- %See Section \ref{sec:method} for discussion on the use of [$\alpha$/Fe] as a proxy for [Mg/Fe].} 
+
 \begin{figure}
@@
 
-%Significantly enhanced [K/Fe] is rare; significantly enhanced [K/Fe] without an accompanying depletion of [Mg/Fe] is unknown. The candidate stars are also spread across a wide range of metallicities.
-
 A recent attempt to replicate the Mg--K abundance signature in NGC 2419 by \cite{iliadis2016} also examined abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}.
@@
 
-%Certainly the idea that both groups of anomalous stars arise from the same polluter source ought to be entertained.
-
-%\todo{However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg-depleted, K enriched material in the first place must be emphasized.
-Indeed, if we assume the primordial abundances (pre-mystery event) are similar to those of NGC 2419's Mg-normal population, then it is impossible.
-If the primordial cloud already has [Mg/Fe]$\approx 0.5$, to reduce this necessitates the addition of large amounts of iron rich material that is also very depleted in [Mg/Fe].
-But as soon significant amounts of iron are added, [Fe/H] for the subsequent Mg-depleted population should increase, while no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}.
-This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS)}
-
-%\todo{One major issue facing this explanation is that it requires a single gas cloud to form many generations of stars almost continuously in order to be consistent with Figure \ref{KvsFe}.
-This is only known to occur in inside true galaxies, which are massive enough to form multiple star forming regions.
-Allowing the candidate stars to have originated in a dwarf Galaxy which later merged with the Milky Way introduces many issues.
-The required mass to be polluted by the mystery object increases drastically, implying multiple pollution events.
-But invoking multiple pollution events means that the rarity of the signal is harder to explain: if it happened multiple times within a single dwarf Galaxy, why not in other places?
-Further, a merger should result in stars with highly elliptical orbits, while the candidates identified appear to be disk stars.}
-
-%\todo{More generally, the [K/Fe]-[Fe/H] relation we observed is supportive of the origin of the Mg--K anti-correlation being temporally confined to an early epoch in the evolution of galaxies and globular clusters.
-However, this is not necessarily the only interpretation.
-For example, it could be that the K forming process is happening throughout the life of the Galaxy, but the amount of K produced decreases with the metallicity of the polluter star, though there is no obvious reason why this would be the case.}
-
-%An intriguing anti-correlation between [K/Fe] and [Fe/H] is observed, although whether or not this relation is physical remains uncertain without further higher resolution observations of the candidates.
-Further high resolution observations will also allow Mg and other elemental abundances to be determined.
-
-%Upon conducting an abundance analysis, anomalously high levels of K were found in the sample, with levels of [K/Fe] as high as 1.5 confirmed through high resolution spectroscopy using Magellan/MIKE.
-The [K/Fe] abundances were not consistent with the extreme populations previsously identified in either NGC 2419 or NGC 2808.
-No conclusion can be reached regarding the presence of [Mg/Fe] depletions in the sample as [Mg/Fe] abundances were unable to be determined from the \lamost\ spectra.
-
 \section*{Acknowledgements}
 We thank David W. Hogg (NYU), and Hans-Walter Rix (MPIA).
-%- Magellan/MIKE and Australian government
 ARC is supported through an Australian Research Council Discovery Project under grant DP160100637.
@@
 LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-% The best way to enter references is to use BibTeX:
 
 \bibliographystyle{mnras}
-\bibliography{mgkbib} % if your bibtex file is called example.bib
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
+\bibliography{mgkbib}
 
@@
 \section{Additional atomic line abundances from Magellan/MIKE}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{table*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% Don't change these lines
-\bsp	% typesetting comment
+\bsp	
 \label{lastpage}
 \end{document}
-
-% End of mnras_template.tex
